---
title: "Windowed article salience results"
subtitle: "Cumulative and trailing 3-, 6-, and 12-month LexisNexis article-count salience measures for intensive- and extensive-margin public-attention specifications"
author: "Jacopo Olivieri"
date: 2026-08-21
format:
  html:
    toc: true
    toc-depth: 2
    embed-resources: true
    theme: cosmo
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
library(knitr)
library(readr)
library(stringr)

tables_dir <- here::here("output", "tables")
source(here::here(
  "scripts", "R", "09_analysis", "05_news",
  "windowed_article_analysis_config.R"
))

measures <- names(windowed_article_salience_cols)
measure_slugs <- windowed_article_measure_slugs
intensive_radii <- windowed_article_intensive_radii
intensive_tables <- lapply(intensive_radii, function(radius) {
  setNames(
    paste0(
      "did_articles_windowed_prior_", radius, "m_", measure_slugs, ".tex"
    ),
    measures
  )
})
intensive_effect_size_paths <- setNames(
  paste0(
    "did_articles_windowed_prior_", intensive_radii, "m_effect_sizes.csv"
  ),
  names(intensive_radii)
)

extensive_specs <- windowed_article_extensive_comparisons
extensive_tables <- lapply(extensive_specs, function(specification) {
  setNames(
    paste0(
      "did_articles_windowed_prior_extensive_",
      specification$comparison_id, "_", measure_slugs, ".tex"
    ),
    measures
  )
})
extensive_effect_size_paths <- vapply(
  extensive_specs,
  function(specification) paste0(
    "did_articles_windowed_prior_extensive_",
    specification$comparison_id,
    "_effect_sizes.csv"
  ),
  character(1)
)

stat_labels <- c(
  "Property controls", "Location FE", "Time FE", "MSOA FE", "LSOA FE",
  "Observations", "Adj. R-squared"
)

html_escape <- function(value) {
  value |>
    str_replace_all("&", "&amp;") |>
    str_replace_all("<", "&lt;") |>
    str_replace_all(">", "&gt;") |>
    str_replace_all('"', "&quot;")
}

strip_outer_braces <- function(value) {
  value <- str_trim(value)
  if (str_starts(value, fixed("{")) && str_ends(value, fixed("}"))) {
    str_sub(value, 2, -2)
  } else {
    value
  }
}

replace_grouped_integers <- function(value) {
  str_replace_all(
    value,
    "(?<![\\w.,])\\d{4,}(?![\\w.,])",
    function(number) format(as.numeric(number), big.mark = ",", scientific = FALSE)
  )
}

clean_cell <- function(raw) {
  value <- str_trim(raw)
  if (identical(value, "")) return("")

  value <- strip_outer_braces(value)
  value <- str_replace_all(value, "\\\\textbf\\{([^}]*)\\}", "@@B_OPEN@@\\1@@B_CLOSE@@")
  value <- str_replace_all(value, "\\\\quad\\s*", "@@INDENT@@")
  value <- str_replace_all(value, fixed("\\\\"), "@@BREAK@@")
  value <- str_replace_all(value, "\\\\num\\{([^}]*)\\}", "\\1")
  value <- str_replace_all(value, "\\\\text\\{([^}]*)\\}", "\\1")
  value <- str_replace_all(value, "\\\\mathrm\\{([^}]*)\\}", "\\1")
  value <- str_replace_all(value, fixed("\\times"), "×")
  value <- str_replace_all(value, fixed("\\log"), "log")
  value <- str_replace_all(value, fixed("\\geq"), "≥")
  value <- str_replace_all(value, fixed("\\leq"), "≤")
  value <- str_replace_all(value, fixed("\\%"), "%")
  value <- str_replace_all(value, fixed("\\&"), "&")
  value <- str_replace_all(value, fixed("\\,"), " ")
  value <- str_replace_all(value, fixed("\\;"), " ")
  value <- str_replace_all(value, fixed("~"), " ")
  value <- str_replace_all(value, fixed("$"), "")
  value <- str_squish(value)
  value <- replace_grouped_integers(value)
  value <- str_replace_all(value, "(?<!\\w)-(?=\\d)", "−")
  value <- html_escape(value)
  value <- str_replace(value, "(\\*{1,3})$", '<sup class="stars">\\1</sup>')
  value |>
    str_replace_all(fixed("@@BREAK@@"), "<br>") |>
    str_replace_all(fixed("@@B_OPEN@@"), "<strong>") |>
    str_replace_all(fixed("@@B_CLOSE@@"), "</strong>") |>
    str_replace_all(fixed("@@INDENT@@"), "&nbsp;&nbsp;") |>
    str_replace_all("Articles_\\{(3m|6m|12m)\\}", "Articles<sub>\\1</sub>")
}

clean_note <- function(raw) {
  value <- str_trim(raw)
  value <- str_replace(value, "^\\\\footnotesize\\s*\\{(.*)\\}\\s*$", "\\1")
  value <- str_replace_all(value, "\\\\textbf\\{([^}]*)\\}", "@@B_OPEN@@\\1@@B_CLOSE@@")
  value <- str_replace_all(value, fixed("\\\\"), " ")
  value <- str_replace_all(value, "\\\\num\\{([^}]*)\\}", "\\1")
  value <- str_replace_all(value, "\\\\text\\{([^}]*)\\}", "\\1")
  value <- str_replace_all(value, "\\\\mathrm\\{([^}]*)\\}", "\\1")
  value <- str_replace_all(value, fixed("\\times"), "×")
  value <- str_replace_all(value, fixed("\\log"), "log")
  value <- str_replace_all(value, fixed("\\%"), "%")
  value <- str_replace_all(value, fixed("$"), "")
  value <- str_replace_all(value, fixed("--"), "–")
  value <- str_squish(value)
  value <- html_escape(value)
  value |>
    str_replace_all(fixed("@@B_OPEN@@"), "<strong>") |>
    str_replace_all(fixed("@@B_CLOSE@@"), "</strong>")
}

extract_balanced_value <- function(text, marker) {
  marker_start <- str_locate(text, fixed(marker))[1, "start"]
  if (is.na(marker_start)) return("")

  start <- marker_start + str_length(marker)
  characters <- str_split(text, "", simplify = TRUE)
  depth <- 1L
  for (index in seq.int(start, length(characters))) {
    if (characters[index] == "{") depth <- depth + 1L
    if (characters[index] == "}") depth <- depth - 1L
    if (depth == 0L) return(str_sub(text, start, index - 1L))
  }
  stop("Unbalanced braces after marker: ", marker, call. = FALSE)
}

expand_indices <- function(specification) {
  parts <- str_split(specification, fixed(","))[[1]] |> str_trim()
  unlist(lapply(parts, function(part) {
    if (str_detect(part, fixed("-"))) {
      limits <- str_split(part, fixed("-"))[[1]] |> as.integer()
      seq.int(limits[1], limits[2])
    } else {
      as.integer(part)
    }
  }))
}

parse_spans <- function(text) {
  directives <- str_extract_all(
    text,
    "cell\\{[^}]+\\}\\{[^}]+\\}=\\{[^}]*c=\\d+[^}]*\\}"
  )[[1]]
  spans <- integer()
  for (directive in directives) {
    match <- str_match(
      directive,
      "cell\\{([^}]+)\\}\\{([^}]+)\\}=\\{[^}]*c=(\\d+)"
    )
    for (row in expand_indices(match[2])) {
      for (column in expand_indices(match[3])) {
        spans[paste(row, column, sep = ",")] <- as.integer(match[4])
      }
    }
  }
  spans
}

parse_table <- function(filename) {
  path <- file.path(tables_dir, filename)
  if (!file.exists(path)) stop("Missing table: ", path, call. = FALSE)

  lines <- readLines(path, warn = FALSE)
  text <- paste(lines, collapse = "\n")
  caption <- str_match(text, regex("caption=\\{(.*?)\\},", dotall = TRUE))[, 2]
  label <- str_match(text, "label=\\{(.*?)\\}")[, 2]
  note <- extract_balanced_value(text, "note{}={")

  body_lines <- lines[str_detect(lines, "\\\\\\\\\\s*$")]
  body_lines <- str_remove(body_lines, "\\s*\\\\\\\\\\s*$")
  body <- lapply(body_lines, function(line) {
    str_split(line, "(?<!\\\\)&")[[1]]
  })

  list(
    filename = filename,
    caption = clean_note(caption),
    label = label,
    note = clean_note(note),
    body = body,
    ncols = max(lengths(body)),
    spans = parse_spans(text)
  )
}

span_at <- function(parsed, row, column) {
  key <- paste(row, column, sep = ",")
  value <- unname(parsed$spans[key])
  if (!length(value) || is.na(value)) 1L else value
}

render_table <- function(parsed, measure) {
  rows <- character()
  previous_kind <- "header"

  for (row_index in seq_along(parsed$body)) {
    cells <- parsed$body[[row_index]]
    is_header <- row_index <= 2L
    label <- if (length(cells)) clean_cell(cells[1]) else ""
    is_panel <- !is_header && span_at(parsed, row_index, 1L) >= 2L
    is_stat <- !is_header && !is_panel && label %in% stat_labels

    if (is_panel) {
      rows <- c(rows, sprintf(
        '<tr class="panel-row"><th class="panel-head" colspan="%s">%s</th></tr>',
        parsed$ncols, label
      ))
      previous_kind <- "panel"
      next
    }

    rendered <- character()
    column <- 1L
    while (column <= parsed$ncols) {
      span <- span_at(parsed, row_index, column)
      raw <- if (column <= length(cells)) cells[column] else ""
      value <- clean_cell(raw)
      colspan <- if (span > 1L) sprintf(' colspan="%s"', span) else ""

      if (is_header) {
        class <- if (span > 1L) ' class="spanner"' else ""
        rendered <- c(rendered, sprintf(
          '<th scope="col"%s%s>%s</th>', class, colspan, value
        ))
      } else if (column == 1L) {
        rendered <- c(rendered, sprintf(
          '<th scope="row" class="rowlab">%s</th>', value
        ))
      } else {
        rendered <- c(rendered, sprintf("<td%s>%s</td>", colspan, value))
      }
      column <- column + span
    }

    classes <- character()
    if (is_header) {
      kind <- "header"
    } else if (is_stat) {
      classes <- "statrow"
      if (!previous_kind %in% c("stat", "panel", "header")) {
        classes <- c(classes, "block-top")
      }
      kind <- "stat"
    } else {
      kind <- "coef"
    }
    class_attribute <- if (length(classes)) {
      sprintf(' class="%s"', paste(classes, collapse = " "))
    } else {
      ""
    }
    rows <- c(rows, sprintf(
      "<tr%s>%s</tr>", class_attribute, paste(rendered, collapse = "")
    ))
    previous_kind <- kind
  }

  caption <- sprintf("%s — %s", measure, parsed$caption)
  anchor <- str_replace_all(parsed$label, ":", "-")
  paste0(
    '<figure class="regression-table" id="', anchor, '">',
    "<figcaption>", caption, "</figcaption>",
    '<div class="table-wrap"><table><thead>',
    paste(rows[1:2], collapse = "\n"),
    "</thead><tbody>", paste(rows[-c(1:2)], collapse = "\n"),
    "</tbody></table></div>",
    '<p class="table-note">', parsed$note, "</p></figure>"
  )
}

find_interaction_rows <- function(parsed, fragment) {
  labels <- vapply(parsed$body, function(row) row[1], character(1))
  index <- which(str_detect(labels, fixed("\\times")) & str_detect(labels, fixed(fragment)))[1]
  if (is.na(index) || index == length(parsed$body)) {
    stop("Could not find interaction row containing: ", fragment, call. = FALSE)
  }
  list(coefficient = parsed$body[[index]], standard_error = parsed$body[[index + 1L]])
}

summary_coefficient_cells <- function(files, fragment, fixed_effects) {
  columns <- switch(
    fixed_effects,
    msoa = c(sales = 5L, rentals = 11L),
    lsoa = c(sales = 7L, rentals = 13L)
  )
  parsed <- unname(parsed_tables[unname(files)])
  rows <- lapply(parsed, find_interaction_rows, fragment = fragment)

  coefficients <- unlist(lapply(names(columns), function(market) {
    vapply(rows, function(item) clean_cell(item$coefficient[columns[[market]]]), character(1))
  }))
  standard_errors <- unlist(lapply(names(columns), function(market) {
    vapply(rows, function(item) clean_cell(item$standard_error[columns[[market]]]), character(1))
  }))
  list(coefficients = coefficients, standard_errors = standard_errors)
}

format_effect <- function(value) {
  output <- sprintf("%.2f", round(value, 2))
  if (identical(output, "-0.00")) output <- "0.00"
  str_replace(output, fixed("-"), "−")
}

stars_from_p_value <- function(p_value) {
  stars <- ifelse(
    p_value < 0.01, "***",
    ifelse(p_value < 0.05, "**", ifelse(p_value < 0.1, "*", ""))
  )
  ifelse(stars == "", "", paste0('<sup class="stars">', stars, "</sup>"))
}

effect_cells <- function(effect_sizes, fixed_effects, estimate, standard_error) {
  ordered <- do.call(rbind, lapply(c("sales", "rentals"), function(market) {
    do.call(rbind, lapply(measures, function(measure) {
      row <- effect_sizes[
        effect_sizes$fixed_effects == fixed_effects &
          effect_sizes$market == market &
          effect_sizes$measure == measure,
      ]
      if (nrow(row) != 1L) {
        stop(
          "Expected one effect-size row for ", fixed_effects, ", ", market,
          ", ", measure, call. = FALSE
        )
      }
      row
    }))
  }))
  list(
    estimates = paste0(
      vapply(ordered[[estimate]], format_effect, character(1)),
      stars_from_p_value(ordered$p_value)
    ),
    standard_errors = paste0(
      "(", vapply(ordered[[standard_error]], format_effect, character(1)), ")"
    )
  )
}

cells_html <- function(values) paste0("<td>", values, "</td>", collapse = "")

render_summary_table <- function(kind, files, effect_sizes) {
  intensive <- identical(kind, "intensive")
  fragment <- if (intensive) "Spills per week (avg.)" else "Near bin"
  coefficient_label <- if (intensive) {
    "Weekly spill count<br>× log (Articles measure)"
  } else {
    "Near bin<br>× log (Articles measure)"
  }
  caption <- if (intensive) {
    "Intensive margin: weekly spill count × article salience"
  } else {
    "Extensive margin: near bin × article salience"
  }
  effect_specs <- if (intensive) {
    list(
      c("effect_iqr_pct", "effect_iqr_se_pct", "IQR salience<br>× 1 SD spills (%)"),
      c("effect_sd_pct", "effect_sd_se_pct", "1 SD salience<br>× 1 SD spills (%)")
    )
  } else {
    list(
      c("effect_iqr_pct", "effect_iqr_se_pct", "IQR salience (%)"),
      c("effect_sd_pct", "effect_sd_se_pct", "1 SD salience (%)")
    )
  }

  rows <- character()
  for (fixed_effects in c("msoa", "lsoa")) {
    fixed_effects_label <- if (fixed_effects == "msoa") {
      "Property controls + MSOA FE"
    } else {
      "Property controls + LSOA FE"
    }
    coefficients <- summary_coefficient_cells(files, fragment, fixed_effects)
    rows <- c(
      rows,
      sprintf(
        '<tr class="panel-row"><th class="panel-head" colspan="9">%s</th></tr>',
        fixed_effects_label
      ),
      paste0(
        '<tr><th scope="row" class="rowlab">', coefficient_label, "</th>",
        cells_html(coefficients$coefficients), "</tr>"
      ),
      paste0(
        '<tr class="standard-error"><th scope="row" class="rowlab"></th>',
        cells_html(coefficients$standard_errors), "</tr>"
      )
    )
    for (specification in effect_specs) {
      effects <- effect_cells(
        effect_sizes, fixed_effects, specification[1], specification[2]
      )
      rows <- c(
        rows,
        paste0(
          '<tr class="effect-row"><th scope="row" class="rowlab">',
          specification[3], "</th>", cells_html(effects$estimates), "</tr>"
        ),
        paste0(
          '<tr class="effect-standard-error"><th scope="row" class="rowlab"></th>',
          cells_html(effects$standard_errors), "</tr>"
        )
      )
    }
  }

  note <- if (intensive) {
    paste(
      "The coefficient row reports the coefficient of interest from the stated",
      "fixed-effect specification; LSOA-clustered standard errors are in parentheses.",
      "Effect rows transform the same coefficient into approximate percent changes",
      "using transaction-sample contrasts: the IQR salience row uses the interquartile",
      "range of the article measure, and the 1 SD salience row uses its standard",
      "deviation; both intensive-margin rows also scale by one standard deviation of",
      "weekly spill exposure. Scaled standard errors are in parentheses under each",
      "effect row, and significance stars inherit the underlying interaction p-value.",
      "Raw coefficients are not directly comparable across salience windows because",
      "the article measures differ in empirical support. *** p&lt;0.01, ** p&lt;0.05,",
      "* p&lt;0.1."
    )
  } else {
    paste(
      "The coefficient row reports the coefficient of interest from the stated",
      "fixed-effect specification; LSOA-clustered standard errors are in parentheses.",
      "Effect rows transform the same coefficient into approximate percent changes in",
      "the near–far price or rent gap using transaction-sample contrasts: the IQR",
      "salience row uses the interquartile range of the article measure, and the 1 SD",
      "salience row uses its standard deviation. Scaled standard errors are in",
      "parentheses under each effect row, and significance stars inherit the underlying",
      "interaction p-value. Raw coefficients are not directly comparable across salience",
      "windows because the article measures differ in empirical support. *** p&lt;0.01,",
      "** p&lt;0.05, * p&lt;0.1."
    )
  }

  measure_headers <- paste0("<th>", measures, "</th>", collapse = "")
  paste0(
    '<figure class="regression-table summary-table"><figcaption>', caption, "</figcaption>",
    '<div class="table-wrap"><table><thead>',
    '<tr><th></th><th class="spanner" colspan="4">House Sales</th>',
    '<th class="spanner" colspan="4">House Rentals</th></tr>',
    "<tr><th></th>", measure_headers, measure_headers, "</tr>",
    "</thead><tbody>", paste(rows, collapse = "\n"), "</tbody></table></div>",
    '<p class="table-note"><strong>Notes:</strong> ', note, "</p></figure>"
  )
}

render_table_family <- function(files) {
  html <- Map(function(measure, filename) {
    render_table(parsed_tables[[filename]], measure)
  }, names(files), unname(files))
  paste(unlist(html), collapse = "\n")
}

validate_artifacts <- function() {
  table_files <- c(unlist(intensive_tables), unlist(extensive_tables))
  effect_files <- c(intensive_effect_size_paths, extensive_effect_size_paths)
  expected_paths <- file.path(tables_dir, c(table_files, effect_files))
  missing_paths <- expected_paths[!file.exists(expected_paths)]
  if (length(missing_paths) > 0L) {
    stop(
      "The report is missing generated analysis artifacts:\n- ",
      paste(missing_paths, collapse = "\n- "),
      "\nRun both windowed article analysis scripts before rendering.",
      call. = FALSE
    )
  }
  if (anyDuplicated(table_files)) {
    stop("The report configuration maps multiple panels to the same table.", call. = FALSE)
  }
}

validate_effect_sizes <- function(data, margin, metadata) {
  required_keys <- expand.grid(
    fixed_effects = c("msoa", "lsoa"),
    market = c("sales", "rentals"),
    measure = measures,
    stringsAsFactors = FALSE
  )
  observed_keys <- data[c("fixed_effects", "market", "measure")]
  if (nrow(data) != 16L || anyDuplicated(observed_keys) ||
      !setequal(do.call(paste, required_keys), do.call(paste, observed_keys))) {
    stop("Effect-size summary is incomplete or duplicated for ", margin, call. = FALSE)
  }
  if (!all(data$margin == margin)) {
    stop("Effect-size summary has the wrong margin label: ", margin, call. = FALSE)
  }
  expected_salience_cols <- unname(windowed_article_salience_cols[data$measure])
  if (!all(data$salience_col == expected_salience_cols)) {
    stop("Effect-size summary has a measure/salience-column mismatch for ", margin,
         call. = FALSE)
  }
  for (field in names(metadata)) {
    if (!field %in% names(data) || !all(data[[field]] == metadata[[field]])) {
      stop("Effect-size metadata mismatch for `", field, "`.", call. = FALSE)
    }
  }
  data
}

validate_artifacts()

table_files <- unique(c(unlist(intensive_tables), unlist(extensive_tables)))
parsed_tables <- setNames(lapply(table_files, parse_table), table_files)

intensive_label_manifest <- do.call(c, unname(Map(function(radius, files) {
  setNames(
    paste0(
      "tbl:did-articles-windowed-prior-", radius, "m-", measure_slugs
    ),
    unname(files)
  )
}, intensive_radii, intensive_tables)))
extensive_label_manifest <- do.call(c, unname(Map(function(specification, files) {
  setNames(
    paste0(
      "tbl:did-articles-windowed-prior-extensive-",
      specification$comparison_id, "-", measure_slugs
    ),
    unname(files)
  )
}, extensive_specs, extensive_tables)))
table_label_manifest <- c(intensive_label_manifest, extensive_label_manifest)

observed_table_labels <- vapply(
  parsed_tables[names(table_label_manifest)], `[[`, character(1), "label"
)
label_mismatches <- names(table_label_manifest)[
  observed_table_labels != unname(table_label_manifest)
]
if (length(label_mismatches) > 0L) {
  stop(
    "Generated tables do not match their expected specification/measure labels:\n- ",
    paste(label_mismatches, collapse = "\n- "),
    "\nRerun both windowed article analysis scripts before rendering.",
    call. = FALSE
  )
}

intensive_effect_sizes <- Map(function(path, radius) {
  read_csv(file.path(tables_dir, path), show_col_types = FALSE) |>
    validate_effect_sizes("intensive", list(radius = radius))
}, intensive_effect_size_paths, intensive_radii)

extensive_effect_sizes <- Map(function(path, specification) {
  read_csv(file.path(tables_dir, path), show_col_types = FALSE) |>
    validate_effect_sizes("extensive", specification)
}, extensive_effect_size_paths, extensive_specs)

render_panel_tabset <- function(tabs, group) {
  asis_output(paste0(
    '::: {.panel-tabset group="', group, '"}\n\n',
    paste(unlist(tabs), collapse = "\n\n"),
    "\n\n:::"
  ))
}

render_summary_tabset <- function(kind, tables, effect_sizes, group) {
  Map(function(label, files, effects) {
    paste0(
      "### ", label, "\n\n",
      render_summary_table(kind, files, effects)
    )
  }, names(tables), tables, effect_sizes) |>
    render_panel_tabset(group)
}

render_detail_tabset <- function(tables, group) {
  Map(function(label, files) {
    paste0("## ", label, "\n\n", render_table_family(files))
  }, names(tables), tables) |>
    render_panel_tabset(group)
}
```

<style>
.quarto-title-banner { background: linear-gradient(180deg, #fff 0%, #f2f8f6 100%); }
#quarto-content { max-width: 1180px; }
h2 { border-top: 2px solid #d9ded5; padding-top: 1.4rem; margin-top: 2.7rem; }
h3 { color: #245f73; }
.equation-note { color: #5b675f; font-size: 0.86rem; }
.regression-table { margin: 1.2rem 0 1.8rem; }
.regression-table figcaption { font-weight: 650; margin-bottom: 0.55rem; }
.table-wrap { overflow-x: auto; border: 1px solid #d9ded5; border-radius: 6px; }
.regression-table table { border-collapse: collapse; width: 100%; margin: 0; font-size: 0.78rem; font-variant-numeric: tabular-nums; }
.regression-table thead th { background: #f1f5f2; font-weight: 650; padding: 0.38rem 0.5rem; text-align: center; white-space: nowrap; }
.regression-table thead th.spanner { border-bottom: 1px solid #c4ccc2; font-weight: 700; }
.regression-table tbody th.rowlab { text-align: left; font-weight: 500; padding: 0.32rem 0.65rem; white-space: nowrap; }
.regression-table tbody td { text-align: center; padding: 0.32rem 0.5rem; white-space: nowrap; }
.regression-table tbody tr:nth-child(even) { background: #fafbf9; }
.regression-table tbody tr.statrow th,
.regression-table tbody tr.statrow td,
.summary-table .standard-error th,
.summary-table .standard-error td,
.summary-table .effect-standard-error th,
.summary-table .effect-standard-error td { color: #5b675f; background: #f4f7f7; }
.regression-table tbody tr.block-top th,
.regression-table tbody tr.block-top td { border-top: 1px solid #d9ded5; }
.regression-table tbody tr.panel-row th.panel-head { text-align: left; background: #e2f0f3; color: #143b48; font-weight: 700; padding: 0.4rem 0.7rem; }
.summary-table .effect-row th,
.summary-table .effect-row td { color: #5b675f; background: #fbfcfc; font-size: 0.74rem; }
.summary-table .effect-row th.rowlab { padding-left: 1.15rem; }
.table-note { color: #5b675f; font-size: 0.74rem; line-height: 1.5; margin: 0.6rem 0.1rem 0; }
sup.stars { font-size: 0.72em; }
details.table-family { border-top: 1px dashed #d9ded5; margin-top: 1.1rem; }
details.table-family summary { cursor: pointer; padding: 0.8rem 0.1rem 0.45rem; font-weight: 680; }
.report-meta { display: grid; grid-template-columns: repeat(2, minmax(0, 1fr)); gap: 0.65rem; margin: 1rem 0 1.5rem; }
.report-meta > div { border: 1px solid #d9ded5; border-radius: 6px; padding: 0.65rem 0.8rem; background: #fbfcfa; }
.report-meta strong { display: block; color: #5b675f; font-size: 0.7rem; text-transform: uppercase; letter-spacing: 0.05em; }
@media (max-width: 760px) { .report-meta { grid-template-columns: 1fr; } }
</style>

<div class="report-meta">
  <div><strong>Sample</strong>England, sales 2021–2024 / rentals 2021–2023</div>
  <div><strong>Source tables</strong>28 regression tables and 7 effect-size summaries</div>
</div>

# Summary

This section reports the coefficient of interest from each public-attention specification and comparable effect-size transformations. Full regression tables appear below; the model specifications are repeated here so the summary coefficients can be read directly.

The scaled effect rows place the cumulative, three-month, six-month, and twelve-month salience measures on a common empirical scale:

1. **Intensive margin:** the implied percentage change associated with an interquartile-range or one-standard-deviation increase in article salience, evaluated at a one-standard-deviation increase in weekly spill exposure.
2. **Extensive margin:** the implied percentage change in the near–far price or rent gap associated with an interquartile-range or one-standard-deviation increase in article salience.

## Intensive margin

$$
\log p_{it}=\alpha+\beta\,\overline{S}^{B}_{it}
+\kappa\left(\overline{S}^{B}_{it}\times A_t^a\right)
+\mathbf{X}_{i}'\gamma+\delta_{\ell(i)}+\lambda_{m(t)}+\varepsilon_{it}.
$$

::: {.equation-note}
Here, $p_{it}$ is the sale price or weekly asking rent; $\overline{S}^{B}_{it}$ is average weekly spill events across overflows within radius $B\in\{250,500,1000\}$ m from January 2021 to the transaction date; $\kappa$ is the coefficient of interest; and $\mathbf{X}_{i}$, $\delta_{\ell(i)}$, and $\lambda_{m(t)}$ denote property controls, location fixed effects, and transaction-month fixed effects. The salience main effect is included in no-FE columns and absorbed by transaction-month fixed effects.
:::

```{r summary-intensive, results="asis"}
render_summary_tabset(
  "intensive", intensive_tables, intensive_effect_sizes, "intensive-radius"
)
```

## Extensive margin

$$
\log p_{it}=\alpha+\phi\,\mathrm{Near}_{i}
+\kappa\left(\mathrm{Near}_{i}\times A_t^a\right)
+\mathbf{X}_{i}'\gamma+\delta_{\ell(i)}+\lambda_{m(t)}+\varepsilon_{it}.
$$

::: {.equation-note}
Here, $p_{it}$ is the sale price or weekly asking rent; $\mathrm{Near}_{i}$ equals one for properties in the near band named by the active tab and zero for properties in that tab's far band; $\kappa$ is the coefficient of interest; and the remaining controls and fixed effects are as above. The salience main effect is included in no-FE columns and absorbed by transaction-month fixed effects.
:::

```{r summary-extensive, results="asis"}
render_summary_tabset(
  "extensive", extensive_tables, extensive_effect_sizes, "extensive-comparison"
)
```

# Article salience measures

The comparison uses the cumulative LexisNexis article-count measure from the main public-attention specification and trailing 3-, 6-, and 12-month measures inclusive of the transaction month:

$$
\begin{aligned}
A_t^{\mathrm{cum}} &= \log\left(\sum_{\tau=t_0}^{t}N_\tau\right), &
A_t^{(w)} &= \log\left(\sum_{\tau=t-w+1}^{t}N_\tau\right),
\quad w\in\{3,6,12\},\\
A_t^a &\in \left\{A_t^{\mathrm{cum}},A_t^{(3)},A_t^{(6)},A_t^{(12)}\right\}.
\end{aligned}
$$

::: {.equation-note}
$N_\tau$ is the LexisNexis sewage-spill article count in month $\tau$. The cumulative measure starts in January 2021; each windowed measure covers months $t-w+1$ through $t$.
:::

# Intensive margin

The intensive-margin models estimate how transaction prices vary with nearby spill intensity, allowing the spill-price gradient to shift with article salience.

```{r intensive-tables, results="asis"}
render_detail_tabset(intensive_tables, "intensive-radius")
```

# Extensive margin

The extensive-margin models compare four near-versus-far definitions based on distance to the nearest mapped overflow, allowing each tab's near–far gap to shift with article salience.

```{r extensive-tables, results="asis"}
render_detail_tabset(extensive_tables, "extensive-comparison")
```

---

This report is generated from `output/tables/*.tex` and `output/tables/*effect_sizes.csv` by this Quarto document. Re-run the windowed article analysis scripts and then render this document to refresh the report after the source tables are regenerated.
