---
title: "Sample impact of the harmonized missing-evidence rule"
subtitle: "Stage-2 dry run of the exposure-builder refactor: what changes, by how much, and what it does to the preferred hedonic"
date: 2026-08-19
format:
  html:
    toc: true
    embed-resources: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
# Arrow's ALTREP vectors are lazily materialized and are not safe under
# data.table's multi-threaded operations: joins and sorts on them return
# nondeterministic results. Materialize eagerly for the whole document.
options(arrow.use_altrep = FALSE)

suppressMessages({
  library(arrow)
  library(data.table)
  library(fixest)
  library(knitr)
})

repo_root <- here::here()
# Post-promotion defaults: the canonical tree holds the Stage-2 generations,
# and the Stage-1 generations survive in the ticket-01 baseline snapshot
# (proved bit-identical to the accepted Stage-1 outputs by the ticket-06
# reconciliation). During the pre-promotion dry run this memo was rendered
# with the same env vars pointing at canonical (then Stage 1) and the staging
# root instead.
stage1_root <- Sys.getenv(
  "STAGE2_MEMO_STAGE1_ROOT",
  file.path(
    repo_root, ".scratch", "exposure-builder-refactor", "baseline-snapshot"
  )
)
stage2_root <- Sys.getenv(
  "STAGE2_MEMO_STAGE2_ROOT",
  file.path(repo_root, "data", "processed", "cross_section")
)
if (identical(normalizePath(stage1_root, mustWork = FALSE),
              normalizePath(stage2_root, mustWork = FALSE))) {
  stop(
    "The two roots resolve to the same directory; the comparison would be ",
    "vacuous. Set STAGE2_MEMO_STAGE1_ROOT and STAGE2_MEMO_STAGE2_ROOT to ",
    "distinct generations.",
    call. = FALSE
  )
}
changing <- list(
  list(dir = "sales/prior_to_sale", id = "house_id",
       label = "Prior exposure, sales (radius grain)"),
  list(dir = "rentals/prior_to_rental", id = "rental_id",
       label = "Prior exposure, rentals (radius grain)"),
  list(dir = "sales/study_period", id = "house_id",
       label = "Study period, sales (events)"),
  list(dir = "rentals/study_period", id = "rental_id",
       label = "Study period, rentals (events)")
)
required <- c(
  file.path(stage1_root, vapply(changing, `[[`, "", "dir")),
  file.path(stage2_root, vapply(changing, `[[`, "", "dir"))
)
if (!all(dir.exists(required))) {
  stop(
    "Both dataset generations must be readable before rendering. Missing: ",
    paste(required[!dir.exists(required)], collapse = ", "),
    call. = FALSE
  )
}

read_stage <- function(root, dir, id) {
  cols <- c(id, "radius", "spill_count",
            "spill_count_weekly_avg", "spill_hrs_weekly_avg")
  dt <- arrow::open_dataset(file.path(root, dir)) |>
    dplyr::select(dplyr::all_of(cols)) |>
    dplyr::collect() |>
    data.table::as.data.table()
  data.table::setnames(dt, id, "transaction_id")
  data.table::setkey(dt, transaction_id, radius)
  dt
}

impact <- lapply(changing, function(spec) {
  before <- read_stage(stage1_root, spec$dir, spec$id)
  after <- read_stage(stage2_root, spec$dir, spec$id)
  stopifnot(
    nrow(before) == nrow(after),
    identical(before$transaction_id, after$transaction_id),
    identical(before$radius, after$radius)
  )
  newly_na <- !is.na(before$spill_count) & is.na(after$spill_count)
  unmasked <- is.na(before$spill_count) & !is.na(after$spill_count)
  stopifnot(sum(unmasked) == 0L)
  counts <- data.table::data.table(
    radius = sort(unique(before$radius))
  )
  counts <- counts[, {
    rows <- before$radius == radius
    list(
      n_rows = sum(rows),
      known_before = sum(rows & !is.na(before$spill_count)),
      known_after = sum(rows & !is.na(after$spill_count)),
      newly_na = sum(rows & newly_na)
    )
  }, by = radius]
  dist <- data.table::rbindlist(lapply(
    c("spill_count_weekly_avg", "spill_hrs_weekly_avg"),
    function(measure) {
      data.table::rbindlist(lapply(sort(unique(before$radius)), function(r) {
        removed <- before[[measure]][before$radius == r & newly_na]
        retained <- before[[measure]][
          before$radius == r & !newly_na & !is.na(before$spill_count)
        ]
        summarise_group <- function(values, group) {
          if (length(values) == 0L) {
            return(data.table::data.table(
              measure = measure, radius = r, group = group, n = 0L,
              share_zero = NA_real_, mean = NA_real_, p25 = NA_real_,
              median = NA_real_, p75 = NA_real_, max = NA_real_
            ))
          }
          data.table::data.table(
            measure = measure, radius = r, group = group,
            n = length(values),
            share_zero = base::mean(values == 0),
            mean = base::mean(values),
            p25 = stats::quantile(values, 0.25, names = FALSE),
            median = stats::median(values),
            p75 = stats::quantile(values, 0.75, names = FALSE),
            max = base::max(values)
          )
        }
        rbind(
          summarise_group(removed, "removed"),
          summarise_group(retained, "retained")
        )
      }))
    }
  ))
  list(label = spec$label, dir = spec$dir, counts = counts, dist = dist)
})
```

## What this memo is

Stage 2 of the exposure-builder refactor applies one harmonized
missing-evidence rule to every event-based exposure dataset: a Site Group's
evidence over a window is unknown when any window year carries a missing
Annual Return (`annual_returns_na`), a Site Group absent from the register
(`annual_returns_absent`), or a reported-positive year with zero matched EDM
events (`reported_positive_without_matched_events`). The four prior-exposure
datasets previously masked on the register-absence flag alone at the radius
grain, and the two study-period event datasets masked on the two
Annual-Returns flags without the unverifiable-positive flag. The site-grain
prior datasets already carried the full three-flag rule, and the
Annual-Returns study-period variant keeps its two-flag rule by design, so
neither changes.

This memo quantifies what the harmonized rule does to the estimation samples.
It is the acceptance document for the Stage-2 dry run: the rebuilt datasets
are staged outside the canonical tree, every difference from the accepted
Stage-1 outputs has been attributed row by row to the added flags in the
Stage-2 reconciliation, and **nothing is promoted to canonical until this memo
is signed off**. Every number here is computed inside this document from the
two dataset generations; no analysis script is modified or re-run.

All changes are NA flips: a row whose exposure was known under Stage 1
becomes unknown under the harmonized rule. No row changes value, no row is
added or removed, and no unknown row becomes known. "Rows with known
exposure" below therefore counts rows whose exposure measures are non-missing;
total row counts are identical before and after by construction.

## Sample impact by dataset and radius

```{r impact-table, results="asis"}
for (item in impact) {
  tab <- data.table::copy(item$counts)
  tab[, `:=`(
    share_known_before = known_before / n_rows,
    share_known_after = known_after / n_rows,
    newly_na_share_of_known = newly_na / known_before
  )]
  out <- data.table::data.table(
    `Radius (m)` = tab$radius,
    `Rows` = format(tab$n_rows, big.mark = ","),
    `Known before` = format(tab$known_before, big.mark = ","),
    `Known after` = format(tab$known_after, big.mark = ","),
    `Newly NA` = format(tab$newly_na, big.mark = ","),
    `Known share before` = sprintf("%.1f%%", 100 * tab$share_known_before),
    `Known share after` = sprintf("%.1f%%", 100 * tab$share_known_after),
    `Removed share of known` = sprintf(
      "%.2f%%", 100 * tab$newly_na_share_of_known
    )
  )
  print(knitr::kable(out, caption = paste0(
    item$label, " (`", item$dir, "`)."
  )))
  cat("\n")
}
```

The two site-grain prior datasets (`sales/prior_to_sale_house_site`,
`rentals/prior_to_rental_rental_site`) and the two Annual-Returns study-period
datasets (`sales/study_period_ea`, `rentals/study_period_ea`) are unchanged:
the Stage-2 reconciliation compared every row of each against its accepted
Stage-1 generation and found zero differences, as the harmonized rule
predicts. They are omitted from the table above because every count is
identical.

## Exposure distribution of the removed rows

The removed rows are those flipping from known to unknown exposure. Their
Stage-1 exposure values, alongside the retained rows' for reference:

```{r dist-table, results="asis"}
measure_labels <- c(
  spill_count_weekly_avg = "Weekly spill count (avg.)",
  spill_hrs_weekly_avg = "Weekly spill hours (avg.)"
)
for (item in impact) {
  tab <- data.table::copy(item$dist)
  out <- data.table::data.table(
    Measure = measure_labels[tab$measure],
    `Radius (m)` = tab$radius,
    Group = tab$group,
    N = format(tab$n, big.mark = ","),
    `Share zero` = sprintf("%.1f%%", 100 * tab$share_zero),
    Mean = sprintf("%.4f", tab$mean),
    P25 = sprintf("%.4f", tab$p25),
    Median = sprintf("%.4f", tab$median),
    P75 = sprintf("%.4f", tab$p75),
    Max = sprintf("%.2f", tab$max)
  )
  print(knitr::kable(out, caption = paste0(
    item$label, " (`", item$dir,
    "`): Stage-1 exposure of removed versus retained rows."
  )))
  cat("\n")
}
```

## The preferred 250-metre continuous hedonic, before and after

The preferred cross-sectional specification regresses the log price on the
average weekly spill count within 250 metres prior to the transaction, with
property controls and MSOA or LSOA fixed effects and heteroskedasticity-robust
standard errors, on properties with at least one spill site within the radius
(`scripts/R/09_analysis/02_hedonic/hedonic_continuous_prior.R`). The same
sample construction and estimation are replicated here, inside this document,
on three samples per market:

1. **Stage 1** — the accepted Stage-1 dataset under the current sample rule
   (no manual exclusion).
2. **Stage 1 + manual exclusion** — the same dataset with the removed
   `annual_returns_na_then_absent` exclusion reapplied: the branch's previous
   preferred estimate, shown because that exclusion removed 1.66 percent of
   the 250-metre sales sample and moved the sales estimate from insignificant
   to significant at 5 percent.
3. **Stage 2 (harmonized)** — the dry-run dataset, where the harmonized rule
   masks every row the exclusion targeted and more.

```{r hedonic}
preferred_radius_m <- 250L

sales_meta <- arrow::read_parquet(
  file.path(repo_root, "data", "processed", "house_price.parquet"),
  col_select = c("house_id", "price", "lsoa", "msoa",
                 "property_type", "old_new", "duration")
) |>
  data.table::as.data.table()
rentals_meta <- arrow::read_parquet(
  file.path(repo_root, "data", "processed", "zoopla", "zoopla_rentals.parquet"),
  col_select = c("rental_id", "listing_price", "lsoa", "msoa",
                 "property_type", "bedrooms", "bathrooms")
) |>
  data.table::as.data.table()

load_hedonic_sample <- function(root, market, manual_exclusion = FALSE) {
  dir <- if (market == "sales") "sales/prior_to_sale" else "rentals/prior_to_rental"
  id <- if (market == "sales") "house_id" else "rental_id"
  dat <- arrow::open_dataset(file.path(root, dir)) |>
    dplyr::filter(radius == preferred_radius_m, n_spill_sites > 0) |>
    dplyr::select(dplyr::all_of(c(
      id, "spill_count_weekly_avg", "spill_hrs_weekly_avg",
      "annual_returns_na_then_absent"
    ))) |>
    dplyr::collect() |>
    data.table::as.data.table()
  if (manual_exclusion) {
    # The removed analysis-script filter dropped flagged rows; a missing flag
    # would silently widen that into dropping NA rows too, so assert first.
    stopifnot(!anyNA(dat$annual_returns_na_then_absent))
    dat <- dat[annual_returns_na_then_absent == FALSE]
  }
  if (market == "sales") {
    dat <- data.table::as.data.table(
      dplyr::inner_join(dat, sales_meta, by = id)
    )
    dat <- dat[
      !is.na(spill_count_weekly_avg) & !is.na(spill_hrs_weekly_avg) &
        !is.na(lsoa) & !is.na(property_type) & !is.na(old_new) & !is.na(duration)
    ]
    dat[, log_price := log(price)]
  } else {
    dat <- data.table::as.data.table(
      dplyr::inner_join(dat, rentals_meta, by = id)
    )
    dat <- dat[
      !is.na(spill_count_weekly_avg) & !is.na(spill_hrs_weekly_avg) &
        !is.na(lsoa) & !is.na(property_type) & !is.na(bedrooms) & !is.na(bathrooms)
    ]
    dat[, log_price := log(listing_price)]
  }
  dat[, `:=`(
    lsoa = factor(lsoa), msoa = factor(msoa),
    property_type = factor(property_type)
  )]
  dat
}

fit_preferred <- function(dat, market, fe) {
  controls <- if (market == "sales") {
    "property_type + old_new + duration"
  } else {
    "property_type + bedrooms + bathrooms"
  }
  fml <- stats::as.formula(paste0(
    "log_price ~ spill_count_weekly_avg + ", controls, " | ", fe
  ))
  fixest::feols(fml, data = dat, vcov = "hetero")
}

variants <- list(
  list(name = "Stage 1", root = stage1_root, exclusion = FALSE),
  list(name = "Stage 1 + manual exclusion", root = stage1_root, exclusion = TRUE),
  list(name = "Stage 2 (harmonized)", root = stage2_root, exclusion = FALSE)
)

hedonic_rows <- data.table::rbindlist(lapply(
  c("sales", "rentals"),
  function(market) {
    data.table::rbindlist(lapply(variants, function(v) {
      dat <- load_hedonic_sample(v$root, market, v$exclusion)
      data.table::rbindlist(lapply(c("msoa", "lsoa"), function(fe) {
        model <- fit_preferred(dat, market, fe)
        ct <- fixest::coeftable(model)["spill_count_weekly_avg", ]
        data.table::data.table(
          market = market, variant = v$name, fe = toupper(fe),
          estimate = ct[["Estimate"]], se = ct[["Std. Error"]],
          p = ct[["Pr(>|t|)"]], n = stats::nobs(model)
        )
      }))
    }))
  }
))
```

```{r hedonic-table, results="asis"}
stars <- function(p) {
  ifelse(p < 0.01, "***", ifelse(p < 0.05, "**", ifelse(p < 0.1, "*", "")))
}
for (mkt in c("sales", "rentals")) {
  tab <- hedonic_rows[market == mkt]
  out <- data.table::data.table(
    Sample = tab$variant,
    `Fixed effects` = tab$fe,
    Estimate = sprintf("%.5f%s", tab$estimate, stars(tab$p)),
    `Std. error` = sprintf("(%.5f)", tab$se),
    `p-value` = sprintf("%.4f", tab$p),
    N = format(tab$n, big.mark = ",")
  )
  print(knitr::kable(out, caption = paste0(
    "Preferred 250 m continuous hedonic, ",
    ifelse(mkt == "sales", "house sales (log transaction price)",
           "house rentals (log weekly asking rent)"),
    ". Coefficient on the average weekly spill count; property controls",
    " included; heteroskedasticity-robust standard errors;",
    " *** p<0.01, ** p<0.05, * p<0.1."
  )))
  cat("\n")
}
```

The three samples per market differ only through the rows each rule removes:
the manual exclusion dropped rows flagged `annual_returns_na_then_absent`,
while the harmonized rule masks every row whose within-radius evidence
includes a missing Annual Return or an unverifiable reported positive —
a strict superset of the exclusion's target, applied as missingness in the
dataset rather than as a filter in the analysis script.

## Provenance and reproducibility

The Stage-1 generation read by this memo is the accepted Stage-1 output: at
sign-off time the canonical tree itself, and after promotion the ticket-01
baseline snapshot, which the ticket-06 reconciliation proved bit-identical to
it (the defaults above reflect the post-promotion layout; the displaced
Stage-1 directories are also parked beside their canonical paths as
`<name>.stage1-parked-20260819`). The Stage-2 generation is the ticket-09 dry
run, built by the unmodified builder entry scripts with their published
output redirected to a staging root and promoted to canonical on sign-off.
Set `STAGE2_MEMO_STAGE1_ROOT` and `STAGE2_MEMO_STAGE2_ROOT` to render against
relocated generations. The row-by-row attribution backing this memo — every
difference is an NA flip, and the newly-NA row sets equal the flag-predicted
sets exactly — is recorded in the ticket-09 reconciliation log.

## Sign-off

Per the locked plan (R26), this memo is the gate between "rebuilt" and
"canonical": the Stage-2 generations are promoted only once Jacopo has read
this memo and recorded sign-off in the ticket-09 file, with its date.
