---
title: "Lagged public attention and house sales"
subtitle: "Extensive-margin core and intensive-margin extension"
date: 2026-08-06
format:
  html:
    toc: true
    embed-resources: true
execute:
  echo: false
  warning: false
  message: false
---

```{r}
repo_root <- here::here()
results_path <- Sys.getenv(
  "LAGGED_ATTENTION_RESULTS_PATH",
  file.path(repo_root, "output", "tables", "did_news_lagged_sales_effect_sizes.csv")
)
figure_path <- Sys.getenv(
  "LAGGED_ATTENTION_FIGURE_PATH",
  file.path(repo_root, "output", "figures", "did_news_lagged_sales_coefficient_paths.png")
)
if (!file.exists(results_path) || !file.exists(figure_path)) {
  stop(
    "Run summarise_lagged_attention_sales.R before rendering this report.",
    call. = FALSE
  )
}
results <- utils::read.csv(results_path, stringsAsFactors = FALSE)

path_sample <- function(measure) if (measure == "post") "full" else "common"

pattern_assessment <- function(measure) {
  sample_name <- path_sample(measure)
  core <- results[
    results$margin == "extensive" & results$market == "sales" &
      results$measure == measure & results$sample == sample_name,
  ]
  rental <- results[
    results$margin == "extensive" & results$market == "rentals" &
      results$measure == measure & results$sample == sample_name,
  ]
  core <- core[order(core$lag), ]
  rental <- rental[order(rental$lag), ]
  sales_zero <- core$estimate[core$lag == 0L]
  rental_zero <- rental$estimate[rental$lag == 0L]
  lagged <- core[core$lag > 0L, ]
  same_sign <- sign(lagged$estimate) == sign(rental_zero)
  closer <- abs(lagged$estimate - rental_zero) <
    abs(sales_zero - rental_zero)
  relevant <- if (abs(rental_zero) < .Machine$double.eps) {
    rep(FALSE, nrow(lagged))
  } else {
    abs(lagged$estimate) >= 0.5 * abs(rental_zero)
  }
  qualifies <- same_sign & closer & relevant
  rental_zero_abs <- abs(rental_zero)
  rental_lag_strength <- if (rental_zero_abs < .Machine$double.eps) {
    NA_real_
  } else {
    stats::median(abs(rental$estimate[rental$lag > 0L])) / rental_zero_abs
  }
  data.frame(
    measure = measure,
    qualifying_lags = paste(lagged$lag[qualifies], collapse = ", "),
    n_qualifying = sum(qualifies),
    supports = sum(qualifies) >= 2L,
    rental_lag_strength = rental_lag_strength,
    stringsAsFactors = FALSE
  )
}

assessment <- do.call(rbind, lapply(c("post", "articles"), pattern_assessment))
n_support <- sum(assessment$supports)
verdict <- if (n_support == 2L) {
  "The lag paths support mistimed attention as a plausible explanation across both measures."
} else if (n_support == 1L) {
  "The evidence is mixed: only one attention measure satisfies the pattern criterion, so mistiming does not provide a general explanation for the sales null."
} else {
  "The lag paths do not support mistimed attention as an explanation for the sales null."
}

fmt <- function(x) formatC(x, digits = 4L, format = "f")
display_results <- results
display_results$estimate_ci <- paste0(
  fmt(display_results$estimate), " [", fmt(display_results$conf_low), ", ",
  fmt(display_results$conf_high), "]"
)

margin_sign_agreement <- function(measure) {
  sample_name <- path_sample(measure)
  extensive_lagged <- results[
    results$margin == "extensive" & results$market == "sales" &
      results$measure == measure & results$sample == sample_name &
      results$lag > 0L,
  ]
  intensive_lagged <- results[
    results$margin == "intensive" & results$market == "sales" &
      results$measure == measure & results$sample == sample_name &
      results$lag > 0L,
  ]
  extensive_sign <- sign(stats::median(extensive_lagged$estimate))
  radius_signs <- tapply(
    intensive_lagged$estimate, intensive_lagged$radius,
    function(x) sign(stats::median(x))
  )
  sum(radius_signs == extensive_sign)
}
sign_agreement <- vapply(
  c("post", "articles"), margin_sign_agreement, integer(1)
)
```

## Conclusion

`r verdict`

This judgement implements the pre-specified pattern rule rather than selecting a
single p-value. For each measure, a lag qualifies only when the sales estimate
(i) has the contemporaneous rental sign, (ii) is closer to the comparable rental
lag-0 estimate than the sales lag-0 estimate is, and (iii) reaches at least half
the rental estimate's absolute magnitude. A measure supports the timing account
only when at least two of lags 3, 6, and 12 qualify. The criterion is satisfied
for `r n_support` of the two attention measures; qualifying lags are
`r paste(paste0(assessment$measure, ": ", ifelse(assessment$n_qualifying == 0L, "none", assessment$qualifying_lags)), collapse = "; ")`.

The lag-12 post estimate deserves less weight than the other points: shifting the
August 2022 threshold forward by 12 months leaves only five post-threshold months
(August--December 2023), even though the full 36-month estimation sample remains.
All intervals shown here are ordinary pointwise 95% confidence intervals; no
simultaneous-band or multiple-testing adjustment is applied.

## Coefficient paths

```{r}
#| fig-cap: "Lagged-attention coefficient paths. The extensive sales panels are the issue-closing core; rentals are a secondary placebo; radius paths are an intensive-margin extension."
#| out-width: "100%"
knitr::include_graphics(figure_path)
```

## Extensive-margin core and rental placebo

```{r}
extensive <- display_results[display_results$margin == "extensive", ]
extensive$role <- ifelse(
  extensive$market == "sales", "Sales core", "Rental placebo"
)
extensive <- extensive[order(
  match(extensive$measure, c("post", "articles")),
  match(extensive$role, c("Sales core", "Rental placebo")),
  match(extensive$sample, c("full", "common", "full_reference")),
  extensive$lag
), ]
knitr::kable(
  extensive[c("role", "measure", "sample", "lag", "estimate_ci", "n")],
  col.names = c("Role", "Measure", "Sample", "Lag", "Estimate [95% CI]", "N"),
  caption = "Extensive-margin estimates and contemporaneous references."
)
```

The rental placebo is informative about temporal specificity. Relative to each
measure's contemporaneous rental estimate, the median absolute lagged rental
coefficient is `r ifelse(is.na(assessment$rental_lag_strength[assessment$measure == "post"]), "undefined", sprintf("%.2f", assessment$rental_lag_strength[assessment$measure == "post"]))`
times as large for the post measure and
`r ifelse(is.na(assessment$rental_lag_strength[assessment$measure == "articles"]), "undefined", sprintf("%.2f", assessment$rental_lag_strength[assessment$measure == "articles"]))`
times as large for articles. Ratios near or above one weaken a sharp mistiming
story because the rental relationship remains at least as strong when attention
is deliberately backdated; materially smaller ratios support temporal
specificity. This placebo evidence is interpreted jointly with the sales paths,
not as a separate significance test.

## Intensive-margin extension

```{r}
intensive <- display_results[display_results$margin == "intensive", ]
intensive <- intensive[order(
  match(intensive$measure, c("post", "articles")),
  match(intensive$market, c("sales", "rentals")),
  intensive$radius,
  match(intensive$sample, c("full", "common", "full_reference")),
  intensive$lag
), ]
knitr::kable(
  intensive[c(
    "market", "measure", "radius", "sample", "lag", "estimate_ci", "n"
  )],
  col.names = c(
    "Market", "Measure", "Radius (m)", "Sample", "Lag",
    "Estimate [95% CI]", "N"
  ),
  caption = "Intensive-margin extension and contemporaneous rental benchmarks."
)
```

The intensive estimates are an extension, not the issue-closing test. Radius
comparisons should be read within radius because the 250m, 500m, and 1000m
specifications select different property samples. Post models use January
2021--December 2023 at every lag. Article paths use the common January
2022--December 2023 sample, while `full_reference` rows preserve the
contemporaneous January 2021--December 2023 benchmark.

As a descriptive cross-margin check, the median lagged intensive sales estimate
has the same sign as the median lagged extensive sales estimate at
`r sign_agreement[["post"]]` of three radii for the post measure and
`r sign_agreement[["articles"]]` of three radii for articles. Agreement across
all radii reinforces the extensive pattern; partial or zero agreement records
divergence. This comparison does not override the extensive-margin verdict
because the intensive radius samples and coefficient scales differ.
