---
author: "Jacopo Olivieri"
date: 2024-10-15
editor: source
format: html
number-sections: true
number-depth: 4
execute: 
  echo: false
  warning: false
  message: false
  freeze: auto
  fig-width: 9
  fig-asp: 0.618 
  fig-align: center
---

# Cross-Sectional Binned Regressions

```{r setup}
# Initialize packages with version control
if (!requireNamespace("renv", quietly = TRUE)) {
  install.packages("renv")
}

# Run manual renv commands if needed
# renv::activate() # Activate the project library
# renv::restore()  # Restore the environment if running for first time
# renv::snapshot()  # After adding/updating packages, snapshot the state

# Load required packages
required_packages <- c(
  "arrow",
  "rmarkdown",
  "rio",
  "tidyverse",
  "purrr",
  "here",
  "janitor",
  "sf",
  "sp",
  "rnaturalearth",
  "rnaturalearthdata",
  "rnrfa",
  "DescTools",
  "gridExtra",
  "modelsummary",
  "tmap",
  "leaflet",
  "htmltools",
  "servr",
  "viridis",
  "readxl",
  "reactable",
  "plotly",
  "ggExtra",
  "sandwich",
  "fixest",
  "gt",
  "flextable"
)

install_if_missing <- function(packages) {
  new_packages <- packages[!sapply(packages, requireNamespace, quietly = TRUE)]
  if (length(new_packages) > 0) {
    install.packages(new_packages)
  }
  invisible(sapply(required_packages, library, character.only = TRUE))
}
install_if_missing(required_packages)
```

## Sewage Spills

For each year, we classify sewage spill sites into states based on their spill metrics: "0" for no spills, and quartiles Q1-Q4 for sites with positive spills. We then calculate the probability of transitions between these states from one year to the next.

```{r}
# Sewage Spills
path_spill_yr <- here::here(
  "data",
  "processed",
  "agg_spill_stats",
  "agg_spill_yr.parquet"
)

## Load sewage spills
spills <- import(path_spill_yr, trust = TRUE)
```

```{r prepare-transition-data}
# Function to bin spill metrics by year (0 or quartiles for positive values)
bin_spills_by_year <- function(data, metric_col) {
  data %>%
    group_by(year) %>%
    mutate(
      metric_value = .data[[metric_col]],
      # For non-zero values, compute quartiles within each year
      metric_for_quartile = if_else(metric_value == 0, NA_real_, metric_value),
      quartile = ntile(metric_for_quartile, 4),
      state = case_when(
        is.na(metric_value) ~ NA_character_,
        metric_value == 0 ~ "0",
        TRUE ~ paste0("Q", quartile)
      )
    ) %>%
    ungroup() %>%
    select(site_id, year, state)
}

# Prepare transition data for spill count
spill_count_states <- bin_spills_by_year(spills, "spill_count_yr") %>%
  rename(state_count = state)

# Prepare transition data for spill hours
spill_hrs_states <- bin_spills_by_year(spills, "spill_hrs_yr") %>%
  rename(state_hrs = state)

# Create year-to-year transitions (t -> t+1)
# Only keep sites that have data in both consecutive years
create_transitions <- function(state_data, state_col) {
  state_data %>%
    arrange(site_id, year) %>%
    group_by(site_id) %>%
    mutate(
      state_next = lead(.data[[state_col]]),
      year_next = lead(year)
    ) %>%
    ungroup() %>%
    filter(
      !is.na(.data[[state_col]]),
      !is.na(state_next),
      year_next == year + 1 # Ensure consecutive years
    ) %>%
    rename(
      state_current = !!state_col,
      transition_year = year
    ) %>%
    select(site_id, transition_year, state_current, state_next)
}

transitions_count <- create_transitions(spill_count_states, "state_count")
transitions_hrs <- create_transitions(spill_hrs_states, "state_hrs")
```

```{r calculate-transition-probabilities}
# Function to calculate transition probability matrix
calc_transition_matrix <- function(transitions_data) {
  # Count transitions
  transition_counts <- transitions_data %>%
    count(state_current, state_next, name = "n_transitions")

  # Calculate totals for each starting state
  state_totals <- transition_counts %>%
    group_by(state_current) %>%
    summarise(total = sum(n_transitions), .groups = "drop")

  # Calculate probabilities
  transition_probs <- transition_counts %>%
    left_join(state_totals, by = "state_current") %>%
    mutate(
      probability = n_transitions / total,
      pct_label = sprintf("%.1f%%", probability * 100)
    ) %>%
    select(state_current, state_next, probability, pct_label)

  return(transition_probs)
}

# Calculate transition matrices for both metrics
trans_prob_count <- calc_transition_matrix(transitions_count)
trans_prob_hrs <- calc_transition_matrix(transitions_hrs)
```

```{r plot-phase-diagrams, fig.width=12, fig.asp=0.5}
# Function to create phase diagram heatmap
plot_phase_diagram <- function(trans_prob_data, title) {
  # Define state order
  state_levels <- c("0", "Q1", "Q2", "Q3", "Q4")

  # Ensure all state combinations exist (fill missing with 0)
  complete_grid <- expand.grid(
    state_current = state_levels,
    state_next = state_levels,
    stringsAsFactors = FALSE
  )

  plot_data <- complete_grid %>%
    left_join(trans_prob_data, by = c("state_current", "state_next")) %>%
    mutate(
      probability = replace_na(probability, 0),
      pct_label = if_else(
        probability == 0,
        "",
        sprintf("%.1f%%", probability * 100)
      ),
      state_current = factor(state_current, levels = state_levels),
      state_next = factor(state_next, levels = rev(state_levels))
    )

  ggplot(
    plot_data,
    aes(x = state_current, y = state_next, fill = probability)
  ) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(
      aes(label = pct_label),
      color = "white",
      size = 3.5,
      fontface = "bold"
    ) +
    scale_fill_viridis_c(
      option = "mako",
      direction = -1,
      limits = c(0, 1),
      begin = 0.15,
      end = 1,
      labels = scales::percent_format(accuracy = 1),
      name = "Transition\nProbability"
    ) +
    labs(
      title = title,
      x = "State in Year t",
      y = "State in Year t+1"
    ) +
    theme_minimal(base_size = 12) +
    theme(
      plot.title = element_text(hjust = 0.5, face = "bold"),
      panel.grid = element_blank(),
      axis.text = element_text(face = "bold")
    ) +
    coord_fixed()
}

# Create plots
p_count <- plot_phase_diagram(
  trans_prob_count,
  "Spill Count Quartile (2021-2023 Pooled)"
)
ggsave(
  filename = here::here("output", "figures", "spill_count_persistence.pdf"),
  plot = p_count,
  width = 1.618 * 8,
  height = 8,
  dpi = 300,
  unit = "in"
)

p_hrs <- plot_phase_diagram(
  trans_prob_hrs,
  "Spill Hours Quartile (2021-2023 Pooled)"
)
ggsave(
  filename = here::here("output", "figures", "spill_hours_persistence.pdf"),
  plot = p_hrs,
  width = 8,
  height = 1.618 * 8,
  dpi = 300,
  unit = "in"
)
```

### Spill Count

```{r}
p_count
```

### Spill Hours

```{r}
p_hrs
```



## Sales

We collapse the data to the household level. For each household, we compute the sum of spills from spill sites within a 250m radius over the entire period (2021-2023), and we record the quartile bin for that total so that later regressions compare properties across spill-intensity quartiles.

```{r load-data-sales}
# House Prices
path_sales <- here::here("data", "processed", "house_price.parquet")

# Panel Data

## General
path_general_panel_sales <- here::here(
  "data",
  "processed",
  "general_panel",
  "sales"
)

rad <- 250L
base_year <- 2021
gen_panel_sales <- arrow::open_dataset(path_general_panel_sales) |>
  filter(radius == rad) |>
  collect() |>
  mutate(
    year = (qtr_id - 1) %/% 4 + base_year,
    year_transfer = qtr_id_transfer %/% 4 + base_year
  ) |>
  distinct(house_id, site_id, year, year_transfer, distance_m, within_radius)

sales <- import(path_sales, trust = TRUE) |>
  mutate(year = (qtr_id - 1) %/% 4 + 1) |>
  select(
    -transaction_id,
    -date_of_transfer,
    -quality,
    -paon,
    -saon,
    -street,
    -locality,
    -town_city,
    -district,
    -county,
    -ppd_category,
    -record_status
  ) |>
  mutate(
    property_type = forcats::as_factor(property_type),
    old_new = forcats::as_factor(old_new),
    duration = forcats::as_factor(duration)
  )

## Assemble sales data
dat_sales <- gen_panel_sales |>
  left_join(sales, by = join_by(house_id, year)) |>
  left_join(spills, by = join_by(site_id, year))
```

```{r prep-data-sales}
spill_sales_collapsed <- gen_panel_sales |>
  filter(!is.na(site_id)) |>
  left_join(spills, by = join_by(site_id, year)) |>
  # filter(is.na(distance_m) | distance_m <= 125) |>
  group_by(house_id) |>
  summarise(
    spill_count = sum(spill_count_yr, na.rm = TRUE),
    spill_hrs = sum(spill_hrs_yr, na.rm = TRUE),
  )

# Helper to bucket spill metrics into "0 spills" plus four quartiles
bin_spill_measure <- function(x) {
  x_for_ntile <- dplyr::if_else(x == 0, NA_real_, x, missing = NA_real_)
  quartile <- dplyr::ntile(x_for_ntile, 4)
  bins <- dplyr::case_when(
    is.na(x) ~ NA_character_,
    x == 0 ~ "0 spills",
    TRUE ~ paste0("Q", quartile)
  )
  factor(bins, levels = c("0 spills", paste0("Q", 1:4)))
}

dat <- sales |>
  left_join(spill_sales_collapsed, by = join_by(house_id)) |>
  mutate(
    spill_count_bin = bin_spill_measure(spill_count),
    spill_hrs_bin = bin_spill_measure(spill_hrs),
    log_price = log(price)
  )
```

```{r}
#| tbl-pos: H
#| layout-ncol: 1

dat_no_na <- dat |>
  filter(
    !is.na(spill_count),
    !is.na(spill_hrs),
    !is.na(lsoa)
  ) |>
  mutate(
    spill_count_bin = forcats::fct_relevel(spill_count_bin, "0 spills"),
    spill_count_bin = forcats::fct_drop(spill_count_bin),
    spill_hrs_bin = forcats::fct_relevel(spill_hrs_bin, "0 spills"),
    spill_hrs_bin = forcats::fct_drop(spill_hrs_bin),
    lsoa = forcats::fct_drop(forcats::as_factor(lsoa)),
    property_type = forcats::fct_drop(property_type),
    old_new = forcats::fct_drop(old_new),
    duration = forcats::fct_drop(duration)
  )

model_spill_count <- fixest::feols(
  log_price ~ spill_count_bin,
  data = dat_no_na,
  vcov = "hetero"
)

model_spill_count_lsoa <- fixest::feols(
  log_price ~ spill_count_bin | lsoa,
  data = dat_no_na,
  vcov = "hetero"
)

model_spill_hrs <- fixest::feols(
  log_price ~ spill_hrs_bin,
  data = dat_no_na,
  vcov = "hetero"
)

model_spill_hrs_lsoa <- fixest::feols(
  log_price ~ spill_hrs_bin | lsoa,
  data = dat_no_na,
  vcov = "hetero"
)

model_spill_count_lsoa_controls <- fixest::feols(
  log_price ~ spill_count_bin + property_type + old_new + duration | lsoa,
  data = dat_no_na,
  vcov = "hetero"
)

model_spill_hrs_lsoa_controls <- fixest::feols(
  log_price ~ spill_hrs_bin + property_type + old_new + duration | lsoa,
  data = dat_no_na,
  vcov = "hetero"
)

coef_labels <- c(
  "(Intercept)" = "Constant (zero spills)",
  "spill_count_binQ1" = "Spill count Q1",
  "spill_count_binQ2" = "Spill count Q2",
  "spill_count_binQ3" = "Spill count Q3",
  "spill_count_binQ4" = "Spill count Q4",
  "spill_hrs_binQ1" = "Spill duration Q1",
  "spill_hrs_binQ2" = "Spill duration Q2",
  "spill_hrs_binQ3" = "Spill duration Q3",
  "spill_hrs_binQ4" = "Spill duration Q4"
)

gof_map <- tibble::tribble(
  ~raw        , ~clean         , ~fmt ,
  "nobs"      , "Observations" ,    0 ,
  "r.squared" , "R-squared"    ,    3
)

table_notes <- c(
  "Heteroskedasticity-robust standard errors in parentheses.",
  "Significance levels: * p < 0.10, ** p < 0.05, *** p < 0.01.",
  "Reference category: properties with zero sewage spills within 250m.",
  "Controls in the table include property type (detached, semi-detached, terraced, flats/maisonettes, other), old/new (binary variable indicating whether the property was a newly built property that had not been previously sold), and duration (freehold vs leasehold)."
)

create_regression_table <- function(
  models,
  add_rows,
  title,
  column_labels,
  spanner_map,
  source_note = NULL
) {
  base_table <- modelsummary::modelsummary(
    models,
    output = "gt",
    estimate = "{estimate}{stars}",
    statistic = "({std.error})",
    stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
    fmt = 3,
    coef_map = coef_labels,
    gof_map = gof_map,
    add_rows = add_rows,
    notes = table_notes
  )

  enhanced_table <- base_table |>
    gt::tab_header(title = gt::md(paste0("**", title, "**"))) |>
    gt::cols_label(.list = column_labels) |>
    gt::cols_align(
      align = "center",
      columns = dplyr::all_of(names(column_labels))
    ) |>
    gt::tab_options(
      table.width = gt::px(640),
      data_row.padding = gt::px(2),
      heading.title.font.size = 14,
      column_labels.font.weight = "bold",
      column_labels.font.size = 12,
      table.font.size = 11
    )

  if (!is.null(source_note)) {
    enhanced_table <- gt::tab_source_note(
      enhanced_table,
      source_note = source_note
    )
  }

  purrr::reduce(
    names(spanner_map),
    .init = enhanced_table,
    .f = function(tbl, spanner) {
      gt::tab_spanner(
        tbl,
        label = spanner,
        columns = dplyr::all_of(spanner_map[[spanner]])
      )
    }
  )
}

export_regression_docx <- function(models, add_rows, path) {
  dir_path <- dirname(path)
  if (!dir.exists(dir_path)) {
    dir.create(dir_path, recursive = TRUE, showWarnings = FALSE)
  }

  modelsummary::modelsummary(
    models,
    output = path,
    estimate = "{estimate}{stars}",
    statistic = "({std.error})",
    stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
    fmt = 3,
    coef_map = coef_labels,
    gof_map = gof_map,
    add_rows = add_rows,
    notes = table_notes
  )
}

sales_models <- list(
  "Model 1" = model_spill_count,
  "Model 2" = model_spill_count_lsoa,
  "Model 3" = model_spill_count_lsoa_controls,
  "Model 4" = model_spill_hrs,
  "Model 5" = model_spill_hrs_lsoa,
  "Model 6" = model_spill_hrs_lsoa_controls
)

sales_column_labels <- c(
  "Model 1" = "OLS",
  "Model 2" = "FE",
  "Model 3" = "FE + Controls",
  "Model 4" = "OLS",
  "Model 5" = "FE",
  "Model 6" = "FE + Controls"
)

sales_spanner_map <- list(
  "Spill count bins" = names(sales_column_labels)[1:3],
  "Spill duration bins" = names(sales_column_labels)[4:6]
)

sales_add_rows <- tibble::tribble(
  ~term               , ~`Model 1` , ~`Model 2` , ~`Model 3` , ~`Model 4` , ~`Model 5` , ~`Model 6` ,
  "LSOA FE"           , "No"       , "Yes"      , "Yes"      , "No"       , "Yes"      , "Yes"      ,
  # "Quarter FE", "No", "Yes", "Yes", "No", "Yes", "Yes",
  "Property controls" , "No"       , "No"       , "Yes"      , "No"       , "No"       , "Yes"
)

sales_table <- create_regression_table(
  models = sales_models,
  add_rows = sales_add_rows,
  title = "Effect of Sewage Spills on Log House Prices",
  column_labels = sales_column_labels,
  spanner_map = sales_spanner_map,
  source_note = "Dependent variable: log(price)"
)

sales_table
```


Only spill count
```{r}
# Only spill count
#| tbl-pos: H
#| layout-ncol: 1

dat_no_na <- dat |>
  filter(
    !is.na(spill_count),
    !is.na(spill_hrs),
    !is.na(lsoa)
  ) |>
  mutate(
    spill_count_bin = forcats::fct_relevel(spill_count_bin, "0 spills"),
    spill_count_bin = forcats::fct_drop(spill_count_bin),
    spill_hrs_bin = forcats::fct_relevel(spill_hrs_bin, "0 spills"),
    spill_hrs_bin = forcats::fct_drop(spill_hrs_bin),
    lsoa = forcats::fct_drop(forcats::as_factor(lsoa)),
    property_type = forcats::fct_drop(property_type),
    old_new = forcats::fct_drop(old_new),
    duration = forcats::fct_drop(duration)
  )

model_spill_count <- fixest::feols(
  log_price ~ spill_count_bin,
  data = dat_no_na,
  vcov = "hetero"
)

model_spill_count_lsoa <- fixest::feols(
  log_price ~ spill_count_bin | lsoa,
  data = dat_no_na,
  vcov = "hetero"
)

model_spill_hrs <- fixest::feols(
  log_price ~ spill_hrs_bin,
  data = dat_no_na,
  vcov = "hetero"
)

model_spill_hrs_lsoa <- fixest::feols(
  log_price ~ spill_hrs_bin | lsoa,
  data = dat_no_na,
  vcov = "hetero"
)

model_spill_count_lsoa_controls <- fixest::feols(
  log_price ~ spill_count_bin + property_type + old_new + duration | lsoa,
  data = dat_no_na,
  vcov = "hetero"
)

model_spill_hrs_lsoa_controls <- fixest::feols(
  log_price ~ spill_hrs_bin + property_type + old_new + duration | lsoa,
  data = dat_no_na,
  vcov = "hetero"
)

coef_labels <- c(
  "(Intercept)" = "Constant (zero spills)",
  "spill_count_binQ1" = "Spill count Q1",
  "spill_count_binQ2" = "Spill count Q2",
  "spill_count_binQ3" = "Spill count Q3",
  "spill_count_binQ4" = "Spill count Q4",
  "spill_hrs_binQ1" = "Spill duration Q1",
  "spill_hrs_binQ2" = "Spill duration Q2",
  "spill_hrs_binQ3" = "Spill duration Q3",
  "spill_hrs_binQ4" = "Spill duration Q4"
)

gof_map <- tibble::tribble(
  ~raw        , ~clean         , ~fmt ,
  "nobs"      , "Observations" ,    0 ,
  "r.squared" , "R-squared"    ,    3
)

table_notes <- c(
  "Heteroskedasticity-robust standard errors in parentheses.",
  "Significance levels: * p < 0.10, ** p < 0.05, *** p < 0.01.",
  "Reference category: properties with zero sewage spills within 250m.",
  "Controls in the table include property type (detached, semi-detached, terraced, flats/maisonettes, other), old/new (binary variable indicating whether the property was a newly built property that had not been previously sold), and duration (freehold vs leasehold)."
)

export_regression_latex <- function(models, add_rows, path, title = NULL) {
  dir_path <- dirname(path)
  if (!dir.exists(dir_path)) {
    dir.create(dir_path, recursive = TRUE, showWarnings = FALSE)
  }

  modelsummary::modelsummary(
    models,
    output = path,
    estimate = "{estimate}{stars}",
    statistic = "({std.error})",
    stars = c("*" = 0.1, "**" = 0.05, "***" = 0.01),
    fmt = 3,
    coef_map = coef_labels,
    gof_map = gof_map,
    add_rows = add_rows,
    notes = table_notes,
    title = title
  )
}

sales_models <- list(
  "OLS" = model_spill_count,
  "FE" = model_spill_count_lsoa,
  "FE + Controls" = model_spill_count_lsoa_controls
)

sales_add_rows <- tibble::tribble(
  ~term               , ~OLS , ~FE   , ~`FE + Controls` ,
  "LSOA FE"           , "No" , "Yes" , "Yes"            ,
  "Property controls" , "No" , "No"  , "Yes"
)

# Export to LaTeX
export_regression_latex(
  models = sales_models,
  add_rows = sales_add_rows,
  path = "tables/sales_table.tex",
  title = "Effect of Sewage Spills on Log House Prices"
)
```



## Rent

We collapse the data to the rental property level. For each rental property, we compute the sum of spills from spill sites within a 250m radius over the entire period (2021-2023), and we record the quartile bin for that total so that later regressions compare properties across spill-intensity quartiles.

```{r load-data-rent}
# Rental Prices
path_rent <- here::here("data", "processed", "zoopla", "zoopla_rentals.parquet")

# Panel Data

## General
path_general_panel_rental <- here::here(
  "data",
  "processed",
  "general_panel",
  "rentals"
)

rad <- 250L
base_year <- 2021
gen_panel_rental <- arrow::open_dataset(path_general_panel_rental) |>
  filter(radius == rad) |>
  collect() |>
  mutate(
    year = (qtr_id - 1) %/% 4 + base_year,
    year_transfer = qtr_id_transfer %/% 4 + base_year
  ) |>
  distinct(rental_id, site_id, year, year_transfer, distance_m, within_radius)

rentals <- import(path_rent, trust = TRUE) |>
  mutate(year = (qtr_id - 1) %/% 4 + 2021) |>
  select(
    -postcode,
    -listing_created,
    -latest_to_rent,
    -rented,
    -rented_est,
    -address_line_01,
    -address_line_02,
    -address_line_03
  ) |>
  mutate(
    property_type = forcats::as_factor(property_type)
  )

## Load sewage spills (reuse from sales section)
# spills <- import(path_spill_yr, trust = TRUE)

## Assemble rental data
dat_rental <- gen_panel_rental |>
  left_join(rentals, by = join_by(rental_id, year)) |>
  left_join(spills, by = join_by(site_id, year))
```

```{r prep-data-rent}
spill_rental_collapsed <- gen_panel_rental |>
  filter(!is.na(site_id)) |>
  left_join(spills, by = join_by(site_id, year)) |>
  group_by(rental_id) |>
  summarise(
    spill_count = sum(spill_count_yr, na.rm = TRUE),
    spill_hrs = sum(spill_hrs_yr, na.rm = TRUE),
  )

# Trim outliers at 2.5 and 97.5 percentiles
price_quantiles <- quantile(
  rentals$listing_price,
  c(0.025, 0.975),
  na.rm = TRUE
)

dat_rent <- rentals |>
  filter(
    listing_price >= price_quantiles[1],
    listing_price <= price_quantiles[2]
  ) |>
  left_join(spill_rental_collapsed, by = join_by(rental_id)) |>
  mutate(
    spill_count_bin = bin_spill_measure(spill_count),
    spill_hrs_bin = bin_spill_measure(spill_hrs),
    log_price = log(listing_price)
  )
```

```{r}
#| tbl-pos: H
#| layout-ncol: 1

dat_rent_no_na <- dat_rent |>
  filter(
    !is.na(spill_count),
    !is.na(spill_hrs),
    !is.na(lsoa)
  ) |>
  mutate(
    spill_count_bin = forcats::fct_relevel(spill_count_bin, "0 spills"),
    spill_count_bin = forcats::fct_drop(spill_count_bin),
    spill_hrs_bin = forcats::fct_relevel(spill_hrs_bin, "0 spills"),
    spill_hrs_bin = forcats::fct_drop(spill_hrs_bin),
    lsoa = forcats::fct_drop(forcats::as_factor(lsoa)),
    property_type = forcats::fct_drop(property_type)
  )


model_spill_count_rent <- fixest::feols(
  log_price ~ spill_count_bin,
  data = dat_rent_no_na,
  vcov = "hetero"
)

model_spill_count_lsoa_rent <- fixest::feols(
  log_price ~ spill_count_bin | lsoa,
  data = dat_rent_no_na,
  vcov = "hetero"
)

model_spill_hrs_rent <- fixest::feols(
  log_price ~ spill_hrs_bin,
  data = dat_rent_no_na,
  vcov = "hetero"
)

model_spill_hrs_lsoa_rent <- fixest::feols(
  log_price ~ spill_hrs_bin | lsoa,
  data = dat_rent_no_na,
  vcov = "hetero"
)

model_spill_count_lsoa_controls_rent <- fixest::feols(
  log_price ~ spill_count_bin + property_type + bedrooms + bathrooms | lsoa,
  data = dat_rent_no_na,
  vcov = "hetero"
)

model_spill_hrs_lsoa_controls_rent <- fixest::feols(
  log_price ~ spill_hrs_bin + property_type + bedrooms + bathrooms | lsoa,
  data = dat_rent_no_na,
  vcov = "hetero"
)

rent_models <- list(
  "Model 1" = model_spill_count_rent,
  "Model 2" = model_spill_count_lsoa_rent,
  "Model 3" = model_spill_count_lsoa_controls_rent,
  "Model 4" = model_spill_hrs_rent,
  "Model 5" = model_spill_hrs_lsoa_rent,
  "Model 6" = model_spill_hrs_lsoa_controls_rent
)

rent_column_labels <- c(
  "Model 1" = "OLS",
  "Model 2" = "FE",
  "Model 3" = "FE + Controls",
  "Model 4" = "OLS",
  "Model 5" = "FE",
  "Model 6" = "FE + Controls"
)

rent_spanner_map <- list(
  "Spill count bins" = names(rent_column_labels)[1:3],
  "Spill duration bins" = names(rent_column_labels)[4:6]
)

rent_add_rows <- tibble::tribble(
  ~term               , ~`Model 1` , ~`Model 2` , ~`Model 3` , ~`Model 4` , ~`Model 5` , ~`Model 6` ,
  "LSOA FE"           , "No"       , "Yes"      , "Yes"      , "No"       , "Yes"      , "Yes"      ,
  # "Quarter FE", "No", "Yes", "Yes", "No", "Yes", "Yes",
  "Dwelling controls" , "No"       , "No"       , "Yes"      , "No"       , "No"       , "Yes"
)

table_notes <- c(
  "Heteroskedasticity-robust standard errors in parentheses.",
  "Significance levels: * p < 0.10, ** p < 0.05, *** p < 0.01.",
  "Reference category: properties with zero sewage spills within 250m.",
  "Controls in the table include property type (detached, semi-detached, terraced, flats/maisonettes, other), number of bedrooms, and number of bathrooms."
)

rent_table <- create_regression_table(
  models = rent_models,
  add_rows = rent_add_rows,
  title = "Effect of Sewage Spills on Log Rental Prices",
  column_labels = rent_column_labels,
  spanner_map = rent_spanner_map,
  source_note = "Dependent variable: log(listing_price)"
)

rent_table
```
