---
author: "Jacopo Olivieri"
date: 2024-04-01
editor: source
format: html
number-sections: true
number-depth: 4
execute: 
  echo: false
  warning: false
  message: false
  freeze: auto
  fig-width: 9
  fig-asp: 0.618 
  fig-align: center
---

# Rental Event Study {#sec-06-event-study}

```{r setup, include=FALSE}
# Initialize packages with version control
if (!requireNamespace("renv", quietly = TRUE)) {
  install.packages("renv")
}

# Run manual renv commands if needed
# renv::activate() # Activate the project library
# renv::restore()  # Restore the environment if running for first time
# renv::snapshot()  # After adding/updating packages, snapshot the state

# Load required packages
required_packages <- c(
  "rmarkdown",
  "rio",
  "tidyverse",
  "purrr",
  "here",
  "janitor",
  "viridis",
  "data.table",
  "DIDmultiplegtDYN",
  "arrow",
  "furrr",
  "glue"
)
install_if_missing <- function(packages) {
  new_packages <- packages[!sapply(packages, requireNamespace, quietly = TRUE)]
  if (length(new_packages) > 0) {
    install.packages(new_packages)
  }
  invisible(sapply(packages, library, character.only = TRUE))
}
install_if_missing(required_packages)


# Initialize logging
log_path <- here::here("output", "log", "rental_event_study")
if (!dir.exists(dirname(log_path))) {
  dir.create(dirname(log_path), recursive = TRUE)
}
logger::log_appender(logger::appender_file(log_path))
logger::log_layout(logger::layout_glue_colors)

# Ggplot theme
theme_pref <- theme_minimal() +
  theme(
    text = element_text(size = 12),
    plot.title = element_text(
      face = "bold",
      size = 12,
      margin = ggplot2::margin(b = 10, unit = "pt")
    ),
    axis.title = element_text(face = "bold", size = 10),
    axis.text = element_text(angle = 45, hjust = 1, vjust = 1, size = 8),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_line(color = "gray95"),
    panel.grid.major.y = element_line(color = "gray95"),
    legend.position = "bottom",
    legend.title = element_text(face = "bold", size = 10),
    legend.text = element_text(size = 8),
    plot.margin = ggplot2::margin(t = 10, r = 10, b = 10, l = 10, unit = "pt")
  )
```


## Setting {#sec-06-01-setting}

## Site-Level Event Study Regressions Within Spill Buffers {#sec-06-02-basic-event-study-regressions}

```{r}
#| eval: false
#| include: false

# ---------- Function to run event study ----------

# Build model name (helper function)
build_model_name <- function(
  outcome,
  treatment_threshold,
  time_agg,
  normalized,
  same_switchers,
  treatment_type,
  controls = NULL
) {
  # Set binary (bin) or continuous
  base <- "model_"
  base <- ifelse(
    treatment_threshold == "cont",
    paste0(base, "cont"),
    paste0(base, "bin")
  )

  # Set spill statistic
  base <- ifelse(grepl("log_", outcome), paste0(base, "_logp"), base)
  base <- ifelse(grepl("_w$", outcome), paste0(base, "_w"), base)
  tt <- ifelse(grepl("spill_count", treatment_type), "sc", "sh")

  # Set model name
  base <- paste(base, tt, treatment_threshold, time_agg, sep = "_")

  # Set model parameters
  if (same_switchers) {
    base <- paste0(base, "_sw")
  }
  if (normalized) {
    base <- paste0(base, "_norm")
  }

  # Set controls
  if (!is.null(controls) && length(controls)) {
    ctrl_suffix <- paste(controls, collapse = "_")
    base <- paste(base, ctrl_suffix, sep = "_")
  }

  return(base)
}

# Build model description (helper function)
build_description <- function(
  outcome,
  treatment_threshold,
  time_agg,
  treatment_type,
  normalized,
  same_switchers,
  controls = NULL
) {
  # Labels
  outcome_lbl <- dplyr::case_when(
    outcome == "rent_median_w" ~ "Weighted Rent Median",
    outcome == "log_rent_median_w" ~ "Weighted Log Rent Median",
    outcome == "rent_median" ~ "Rent Median",
    outcome == "log_rent_median" ~ "Log Rent Median",
    outcome == "price_listing" ~ "Listing Price",
    outcome == "log_price_listing" ~ "Log Listing Price",
    TRUE ~ outcome
  )

  threshold_lbl <- dplyr::case_when(
    treatment_threshold == "mean" ~ "Mean",
    treatment_threshold == "p50" ~ "P50",
    treatment_threshold == "p75" ~ "P75",
    treatment_threshold == "p90" ~ "P90",
    treatment_threshold == "max" ~ "Max",
    treatment_threshold == "cont" ~ "Continuous",
    TRUE ~ stringr::str_to_title(treatment_threshold)
  )

  time_lbl <- dplyr::case_when(
    time_agg == "mo" ~ "Monthly",
    time_agg == "qtr" ~ "Quarterly",
    time_agg == "yr" ~ "Yearly",
    TRUE ~ time_agg
  )
  time_lbl <- ifelse(threshold_lbl == "Continuous", "", time_lbl)

  treat_lbl <- dplyr::case_when(
    grepl("spill_count", treatment_type) & treatment_threshold != "cont" ~
      "Spill Count",
    grepl("spill_hrs", treatment_type) & treatment_threshold != "cont" ~
      "Spill Hours",
    grepl("spill_count", treatment_type) & treatment_threshold == "cont" ~
      "Log Spill Count",
    grepl("spill_hrs", treatment_type) & treatment_threshold == "cont" ~
      "Log Spill Hours",
    TRUE ~ NA_character_
  )

  norm_lbl <- ifelse(normalized, "Norm", "No Norm")
  sw_lbl <- ifelse(same_switchers, "Same Switchers", "All Switchers")

  ctrl_lbl <- if (is.null(controls) || length(controls) == 0) {
    ""
  } else {
    paste0("; Controls: ", paste(controls, collapse = ", "))
  }

  # Compose
  glue::glue(
    "{outcome_lbl} ~ {time_lbl} {threshold_lbl} {treat_lbl} ",
    "({norm_lbl}, {sw_lbl}{ctrl_lbl})"
  ) %>%
    as.character()
}

# ---- main function --------------------------------------------------------- #

run_event_study <- function(
  param_grid,
  data,
  rad,
  time_var = c("month_id", "qtr_id"),
  group_var = "site_id",
  cluster_var = "site_id",
  overwrite = FALSE,
  file_name = "rentals_did_results_site_qtr_{rad}.rds"
) {
  stopifnot(
    is.data.frame(param_grid),
    is.data.frame(data),
    is.logical(overwrite),
    length(rad) == 1
  )

  # ---- 0. results file ----------------------------------------------------- #
  res_path <- here::here(
    "book",
    "book_regs",
    glue::glue(file_name)
  )
  fs::dir_create(fs::path_dir(res_path))

  existing <- if (!overwrite && fs::file_exists(res_path)) {
    readRDS(res_path)
  } else {
    list()
  }

  # ---- 1. decide what we still need to run --------------------------------- #
  param_grid <- tibble::as_tibble(param_grid) %>%
    dplyr::mutate(
      model_name = purrr::pmap_chr(
        list(
          outcome,
          treatment_threshold,
          time_agg,
          normalized,
          same_switchers,
          treatment_type,
          controls
        ),
        build_model_name
      )
    )

  existing_names <- if (length(existing)) names(existing) else character(0)

  todo <- dplyr::anti_join(
    param_grid,
    tibble::tibble(model_name = existing_names),
    by = "model_name"
  )

  if (nrow(todo) == 0) {
    message("No new models to run for radius ", rad, ".")
    return(invisible(existing))
  }
  message("Estimating ", nrow(todo), " models for radius ", rad, "...")

  # ---- 2. run the models (parallel) --------------------------------------- #
  furrr::future_map(
    todo$model_name,
    function(mn) {
      # Get model iteration
      p <- dplyr::filter(todo, model_name == mn) %>%
        dplyr::slice(1)

      # Define treatment variable
      treatment_var <- paste0(
        "d_",
        p$treatment_threshold,
        "_",
        p$treatment_type,
        "_",
        p$time_agg
      )
      treatment_var <- ifelse(
        p$treatment_threshold == "cont",
        p$treatment_type,
        gsub("log_spill", "spill", treatment_var)
      )

      desc <- build_description(
        p$outcome,
        p$treatment_threshold,
        p$time_agg,
        p$treatment_type,
        p$normalized,
        p$same_switchers,
        unlist(p$controls)
      )

      message(" • ", mn, " …")

      res <- DIDmultiplegtDYN::did_multiplegt_dyn(
        df = data,
        outcome = p$outcome,
        group = group_var,
        time = time_var,
        treatment = treatment_var,
        effects = 6,
        placebo = 2,
        cluster = cluster_var,
        normalized = p$normalized,
        same_switchers = p$same_switchers,
        controls = unlist(p$controls),
        graph_off = TRUE
      )

      attr(res, "description") <- desc
      # return a named list so purrr::flatten will keep names
      rlist <- list(res)
      names(rlist) <- mn
      rlist
    },
    .options = furrr::furrr_options(seed = TRUE),
    .progress = TRUE
  ) %>%
    purrr::flatten() -> new_results

  # ---- 3. merge + save ----------------------------------------------------- #
  final <- c(existing, new_results)
  saveRDS(final, res_path)
  message("Results saved → ", res_path)

  invisible(final)
}
```


```{r}
#| eval: false
#| include: false

param_grid_bin <- expand.grid(
  outcome = c("log_rent_median", "log_rent_median_w"),
  treatment_threshold = c("mean", "p50", "p75", "p90"),
  time_agg = c("qtr", "yr"),
  treatment_type = c("spill_count", "spill_hrs"),
  normalized = c(TRUE),
  same_switchers = c(TRUE),
  stringsAsFactors = FALSE,
  controls = list(NULL)
)
param_grid_cont <- expand.grid(
  outcome = c("log_rent_median", "log_rent_median_w"),
  treatment_threshold = c("cont"),
  time_agg = c("qtr"),
  treatment_type = c("log_spill_count", "log_spill_hrs"),
  normalized = c(TRUE),
  same_switchers = c(TRUE),
  stringsAsFactors = FALSE,
  controls = list(NULL)
)
param_grid <- bind_rows(param_grid_bin, param_grid_cont)

# Radii to loop over
radii <- c(250, 500, 1000)

# Parallel processing
plan(multisession, workers = 3)

# Load data
## Data paths
path_rental <- here::here("data", "processed", "within_radius_panel", "rentals")
path_site <- here::here("data", "processed", "dat_panel_site", "rentals")
path_spill <- here::here("data", "processed", "agg_spill_stats")
path_rental_controls <- here::here(
  "data",
  "processed",
  "zoopla",
  "zoopla_rentals.parquet"
)

# Rental panel data
rental_qtr <- open_dataset(path_rental) %>%
  filter(period_type == "quarterly") %>%
  select(-contains("month"))
# Aggregate site level panel data
site_qtr <- open_dataset(path_site) %>%
  filter(period_type == "quarterly") %>%
  select(-contains("month"))
# Spill statistics
spill_qtr <- open_dataset(path_spill) %>%
  filter(period_type == "quarterly") %>%
  collect() %>%
  select(-contains("month"), -contains("_mo"))
# Rental controls snapshot (not used directly here)
rental_controls <- open_dataset(path_rental_controls) %>%
  collect() %>%
  select(
    rental_id,
    listing_price,
    property_type,
    quality,
    country,
    nhs_ha,
    region,
    lsoa,
    msoa,
    admin_county,
    admin_ward
  )

for (r in radii) {
  message("Loading and preparing data for radius: ", r)

  # Site level panel data
  site_dat <- site_qtr %>%
    filter(radius == r) %>%
    collect()

  # Form panel data
  panel_site <- left_join(
    site_dat,
    spill_qtr,
    by = join_by(site_id, qtr_id, quarter, year, period_type)
  )

  message("Starting regressions for radius: ", r)
  run_event_study(
    param_grid = param_grid,
    data = panel_site,
    rad = r,
    time_var = "qtr_id",
    group_var = "site_id",
    cluster_var = "site_id",
    overwrite = TRUE,
    file_name = "rentals_did_results_site_qtr_{rad}.rds"
  )
}
```


```{r}
#| eval: false
#| include: false

# Create parameter grid
param_grid_bin <- expand.grid(
  outcome = c("log_price_listing"),
  treatment_threshold = c("mean", "p50", "p75", "p90"),
  time_agg = c("qtr", "yr"),
  treatment_type = c("spill_count", "spill_hrs"),
  normalized = c(TRUE),
  same_switchers = c(TRUE),
  stringsAsFactors = FALSE,
  controls = list(NULL, c("property_type"))
)
param_grid_cont <- expand.grid(
  outcome = c("log_price_listing"),
  treatment_threshold = c("cont"),
  time_agg = c("qtr"),
  treatment_type = c("log_spill_count", "log_spill_hrs"),
  normalized = c(TRUE),
  same_switchers = c(TRUE),
  stringsAsFactors = FALSE,
  controls = list(NULL, c("property_type"))
)
param_grid <- bind_rows(param_grid_bin, param_grid_cont)

# Radii to loop over
radii <- c(250, 500, 1000)

# Parallel processing
plan(multisession, workers = 3)

for (r in radii) {
  message("Loading and preparing data for radius: ", r)

  # Site level panel data
  rental_dat <- rental_qtr %>%
    filter(radius == r) %>%
    collect() %>%
    rename(
      price_listing = price,
      log_price_listing = log_price
    )

  # Form panel data
  panel_rental <- left_join(
    rental_dat,
    spill_qtr,
    by = join_by(site_id, qtr_id, quarter, year, period_type)
  ) %>%
    left_join(rental_controls, by = join_by(rental_id)) %>%
    mutate(
      property_type = factor(property_type)
    )

  message("Starting regressions for radius: ", r)
  run_event_study(
    param_grid = param_grid,
    data = panel_rental,
    rad = r,
    time_var = "qtr_id",
    group_var = "site_id",
    cluster_var = "site_id",
    overwrite = TRUE,
    file_name = "rentals_did_results_house_qtr_{rad}.rds"
  )
}
```

```{r}
# Load results
load_results <- function(
  radii = c(250, 500, 1000),
  freqs = c("qtr", "mo"),
  dir_path = here("output", "regs"),
  quiet = FALSE,
  pattern = "rentals_did_results_site_{f}_{r}.rds"
) {
  safe_rds <- purrr::possibly(readRDS, otherwise = NULL)
  results <- list() # <- final nested list to be returned

  for (r in radii) {
    r_chr <- as.character(r)

    for (f in freqs) {
      pattern_eval <- glue::glue(pattern, .envir = rlang::env(f = f, r = r))
      file <- Sys.glob(file.path(dir_path, pattern_eval))[1]

      # no file found → skip
      if (is.na(file) || is.null(file) || file == "") {
        next
      }

      obj <- safe_rds(file)
      if (is.null(obj)) {
        next
      } # corrupted file → skip

      # initialise slots if necessary
      if (is.null(results[[r_chr]])) {
        results[[r_chr]] <- list()
      }

      results[[r_chr]][[f]] <- obj # store
      if (!quiet) message("✓ loaded ", f, " ", r, ": ", basename(file))
    }
  }

  return(results)
}


# Make regression plot
plot_reg_chaisemartin <- function(
  data,
  radius,
  model,
  freq = c("qtr", "mo"),
  use_desc = TRUE
) {
  freq <- match.arg(freq)
  r <- as.character(radius)

  stopifnot(r %in% names(data))
  stopifnot(freq %in% names(data[[r]]))

  mod <- data[[r]][[freq]][[model]]
  if (is.null(mod)) {
    stop(
      "Model '",
      model,
      "' not found for radius ",
      r,
      " and freq '",
      freq,
      "'."
    )
  }

  if (is.null(mod$plot)) {
    stop("Model '", model, "' has no plot element.")
  }

  # ------------------------------------------------------------------------
  # Data wrangling
  df <- mod$plot$data %>%
    mutate(
      group = factor(
        ifelse(Time <= 0, "Pre", "Post"),
        levels = c("Pre", "Post")
      )
    )

  subtitle <- if (use_desc && !is.null(attr(mod, "description"))) {
    attr(mod, "description")
  } else {
    model
  }
  formula_caption <- paste0(
    "Regression specification: ",
    mod$args$outcome,
    " ~ ",
    mod$args$group,
    " + ",
    mod$args$time,
    " + ",
    mod$args$treatment
  )

  ggplot(df, aes(x = Time, y = Estimate, colour = group)) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
    geom_errorbar(aes(ymin = LB.CI, ymax = UB.CI), width = 0.2) +
    geom_point(aes(color = group), size = 1.2) +
    scale_color_manual(
      values = c(
        "Pre" = viridis(1, option = "magma"),
        "Post" = viridis(3, option = "magma")[2]
      ),
      breaks = c("Pre", "Post")
    ) +
    theme_minimal() +
    labs(
      x = "Time",
      y = "Estimate",
      subtitle = subtitle,
      caption = formula_caption
    ) +
    theme_pref +
    theme(plot.caption = element_text(hjust = 0))
}

results_qtr <- load_results(
  radii = c(250, 500, 1000),
  freqs = c("qtr", "mo"),
  dir_path = here("output", "regs"),
  quiet = TRUE,
  pattern = "rentals_did_results_site_{f}_{r}.rds"
)

results_rental_qtr <- load_results(
  radii = c(250, 500, 1000),
  freqs = c("qtr"),
  dir_path = here("output", "regs"),
  quiet = TRUE,
  pattern = "rentals_did_results_house_{f}_{r}.rds"
)
```

### Binary Treatment - Average Spill Count {#sec-06-02-01-binary-average}

::: {.panel-tabset group="threshold-site"}

#### 250m

::: {.panel-tabset group="radius-site-250m"}

##### Count Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_yr_sw_norm"
)
```

##### Duration Qt
```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-site-500m"}

##### Count Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-site-1000m"}  

##### Count Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_yr_sw_norm"
)
```

:::

:::

### Binary Treatment - Median Spill Count {#sec-06-02-02-binary-median}

::: {.panel-tabset group="threshold-site"}

#### 250m

::: {.panel-tabset group="radius-site-250m"}

##### Count Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-site-500m"}

##### Count Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_yr_sw_norm"
)
```

##### Duration Qt

```{r}  
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-site-1000m"}

##### Count Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_yr_sw_norm"
)
```

:::

:::

### Binary Treatment - 75th Percentile Spill Count {#sec-06-02-03-binary-p75}

::: {.panel-tabset group="threshold-site"}  

#### 250m

::: {.panel-tabset group="radius-site-250m"}

##### Count Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_qtr_sw_norm"
)
```

##### Count Yr

```{r}  
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_yr_sw_norm"
)
```

##### Duration Qt

```{r}  
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_qtr_sw_norm"
)
```

##### Duration Yr

```{r}  
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-site-500m"}

##### Count Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-site-1000m"}

##### Count Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_yr_sw_norm"
)
```

:::

:::

### Binary Treatment - 90th Percentile Spill Count {#sec-06-02-04-binary-p90}

::: {.panel-tabset group="threshold-site"}    

#### 250m

::: {.panel-tabset group="radius-site-250m"}

##### Count Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-site-500m"}

##### Count Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-site-1000m"}

##### Count Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_yr_sw_norm"
)
```

:::

:::

### Continuous Treatment - Average Spill Count {#sec-06-02-04-continuous-treatment}

::: {.panel-tabset group="continuous-site"}

#### 250m

::: {.panel-tabset group="radius-site-250m-cont"}

##### Count

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_cont_logp_sc_cont_qtr_sw_norm"
)
```

##### Duration

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_cont_logp_sh_cont_qtr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-site-500m-cont"}

##### Count

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_cont_logp_sc_cont_qtr_sw_norm"
)
```

##### Duration

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_cont_logp_sh_cont_qtr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-site-1000m-cont"}

##### Count

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_cont_logp_sc_cont_qtr_sw_norm"
)
```

##### Duration

```{r}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_cont_logp_sh_cont_qtr_sw_norm"
)
```

:::

:::

## Rental-Level Event Study Regressions Within Admin Boundaries {#sec-06-03-rental-event-study}

```{r}
#| eval: false
# Load Data

# Define file paths
path_rental_panel <- here::here("data", "processed", "general_panel", "rentals")
path_spill <- here::here("data", "processed", "agg_spill_stats")
path_rental_controls <- here::here(
  "data",
  "processed",
  "zoopla",
  "zoopla_rentals.parquet"
)

# Load rental panel data
rental_panel <- arrow::open_dataset(path_rental_panel)

# Load quarterly spill stats, filter to quarterly data
spill_qtr <- open_dataset(path_spill) %>%
  filter(period_type == "quarterly") %>%
  collect() %>%
  select(-contains("month"), -contains("_mo")) %>%
  as.data.table()

# Load rental controls, removing redundant columns
rental_controls <- open_dataset(path_rental_controls) %>%
  collect() %>%
  transmute(
    rental_id,
    price_listing = listing_price,
    log_price_listing = log(listing_price),
    property_type,
    bedrooms,
    bathrooms,
    receptions,
    quality,
    country,
    nhs_ha,
    region,
    lsoa,
    msoa,
    admin_county,
    admin_ward
  ) %>%
  as.data.table()
```


```{r}
#| eval: false
# Create Event Data

# Create event data for each radius
radii <- c(1000L)
event_data_list <- purrr::map(
  radii,
  function(rad) {
    # 1. Load data for radius and add spill statistics
    panel_dt_ext <- rental_panel %>%
      filter(radius == rad) %>%
      collect() %>%
      as.data.table()

    # 2. Calculate spill summaries
    # For rentals within radius, merge with spill data
    rental_qtr_in_sum <- merge(
      panel_dt_ext[within_radius == TRUE],
      spill_qtr[, .(site_id, qtr_id, spill_count, spill_hrs)],
      by = c("site_id", "qtr_id")
    )[,
      .(
        qtr_id_transfer = first(qtr_id_transfer),
        spill_count = sum(spill_count, na.rm = TRUE),
        spill_hrs = sum(spill_hrs, na.rm = TRUE),
        min_dist_m = min(distance_m, na.rm = TRUE),
        avg_dist_m = mean(distance_m, na.rm = TRUE),
        n_spill_sites = uniqueN(site_id),
        within_radius = TRUE,
        radius = rad
      ),
      by = .(rental_id, qtr_id)
    ]

    # For rentals outside radius, create zero-spill records
    rental_qtr_out_sum <- panel_dt_ext[
      within_radius == FALSE,
      .(
        qtr_id_transfer = first(qtr_id_transfer),
        spill_count = 0,
        spill_hrs = 0,
        min_dist_m = NA,
        avg_dist_m = NA,
        n_spill_sites = 0,
        within_radius = FALSE,
        radius = rad
      ),
      by = .(rental_id, qtr_id)
    ]

    # Combine and sort data
    rental_qtr_sum <- rbind(rental_qtr_in_sum, rental_qtr_out_sum)
    setorder(rental_qtr_sum, rental_id, qtr_id)

    ## 3. Create treatment indicators

    # Extract threshold column names
    thr_col_names <- grep("^thr_.*_all$", names(spill_qtr), value = TRUE)
    # Create threshold lookup
    thr <- unique(spill_qtr[, c("qtr_id", thr_col_names), with = FALSE])
    setorder(thr, qtr_id)

    # Join rentals with thresholds
    treat_cand <- merge(
      rental_qtr_in_sum,
      thr,
      by = "qtr_id",
      all.x = TRUE
    )

    # Separate threshold columns by type
    count_thr <- grep("_spill_count_", thr_col_names, value = TRUE)
    hrs_thr <- grep("_spill_hrs_", thr_col_names, value = TRUE)

    # Create count threshold indicators
    treat_cand[,
      paste0("d_", count_thr) := lapply(.SD, \(x) as.integer(spill_count > x)),
      .SDcols = count_thr
    ]

    # Create hours threshold indicators
    treat_cand[,
      paste0("d_", hrs_thr) := lapply(.SD, \(x) as.integer(spill_hrs > x)),
      .SDcols = hrs_thr
    ]

    # 4. First-treated indicators

    # Get all treatment columns
    treat_cols <- grep("^d_", names(treat_cand), value = TRUE)

    # Find first treatment quarter for each rental-threshold combination
    treat_long <- melt(
      treat_cand,
      id.vars = c("rental_id", "qtr_id"),
      measure.vars = treat_cols,
      variable.name = "threshold",
      value.name = "treated",
      variable.factor = FALSE
    )[
      treated == 1L, # Keep only treated observations
      .(first_qtr = min(qtr_id)), # Find earliest treatment quarter
      by = .(rental_id, threshold)
    ]

    # Convert to wide format
    treat_wide <- dcast(
      treat_long,
      rental_id ~ threshold,
      value.var = "first_qtr",
      fill = NA_integer_ # NA for never treated rentals
    )

    # Rename threshold columns
    setnames(
      treat_wide,
      old = grep("^d_thr_", names(treat_wide), value = TRUE),
      new = sub(
        "^d_thr_",
        "first_t_",
        grep("^d_thr_", names(treat_wide), value = TRUE)
      )
    )

    # 5. Finalise data

    # Join treatment data with rental data
    event_data <- treat_wide[
      rental_qtr_sum[qtr_id_transfer == qtr_id],
      on = "rental_id",
      nomatch = NA
    ][
      # Join with rental controls
      rental_controls,
      on = "rental_id",
      nomatch = NA
    ][,
      .(
        # IDs, time, and price
        rental_id,
        qtr_id,
        qtr_id_transfer,
        price_listing,
        log_price_listing,
        # Spill data
        spill_count,
        spill_hrs,
        # Treatment quarters
        first_t_mean_spill_count_all,
        first_t_mean_spill_hrs_all,
        first_t_p50_spill_count_all,
        first_t_p50_spill_hrs_all,
        first_t_p75_spill_count_all,
        first_t_p75_spill_hrs_all,
        first_t_p90_spill_count_all,
        first_t_p90_spill_hrs_all,
        first_t_max_spill_count_all,
        first_t_max_spill_hrs_all,
        # Spatial data
        min_dist_m,
        avg_dist_m,
        n_spill_sites,
        within_radius,
        radius,
        # Property characteristics
        property_type,
        bedrooms,
        bathrooms,
        receptions,
        quality,
        country,
        nhs_ha,
        region,
        lsoa,
        msoa,
        admin_county,
        admin_ward
      )
    ]

    # Convert categorical columns to factors using purrr::map
    categorical_cols <- c(
      "property_type",
      "quality",
      "country",
      "nhs_ha",
      "region",
      "lsoa",
      "msoa",
      "admin_county",
      "admin_ward"
    )

    event_data[,
      (categorical_cols) := purrr::map(.SD, as.factor),
      .SDcols = categorical_cols
    ]

    # Set quarter treated to above max quarter for never treated rentals
    event_data[,
      names(.SD) := purrr::map(.SD, ~ ifelse(is.na(.), 999999L, .)),
      .SDcols = patterns("^first_t_")
    ]

    # Clean up local variables
    rm(
      rental_qtr_in_sum,
      rental_qtr_out_sum,
      treat_cand,
      treat_long,
      treat_wide,
      rental_qtr_sum,
      panel_dt_ext
    )
    gc()

    return(event_data)
  }
) %>%
  purrr::set_names(paste0("rad_", radii))
```


```{r}
#| eval: false
# Define Functions to Run Event Study Regressions

# Helper: build model name
build_model_name <- function(
  outcome,
  treatment_threshold,
  treatment_type,
  thr_time_agg,
  time_agg,
  time_fe,
  space_fe,
  cluster_var,
  controls = NULL
) {
  # Set binary (bin) or continuous
  base <- ifelse(
    treatment_threshold == "cont",
    "cont",
    "bin"
  )

  # Set outcome
  base <- ifelse(grepl("log_price", outcome), paste0(base, "_logp"), base)
  base <- ifelse(
    outcome %in% c("price", "price_listing"),
    paste0(base, "_p"),
    base
  )

  # Set treatment
  tt <- ifelse(treatment_type == "spill_count", "sc", "sh")
  base <- paste(base, tt, treatment_threshold, sep = "_")

  # Set time aggregation
  base <- paste0(base, "_", thr_time_agg)

  # Set FE unit
  base <- paste0(base, "_fe_", time_fe, "-", space_fe)

  # Set controls
  if (!is.null(controls) && length(controls)) {
    ctrl_suffix <- paste(controls, collapse = "_")
    base <- paste(base, ctrl_suffix, sep = "_")
  }

  # Clean up
  janitor::make_clean_names(base)
}

# Helper: Build Model Description
build_description <- function(
  outcome,
  treatment_threshold,
  treatment_type,
  time_agg,
  thr_time_agg,
  time_fe,
  space_fe,
  cluster_var,
  controls = NULL
) {
  # Outcome
  outcome_lbl <- dplyr::case_when(
    grepl("log_price_listing", outcome) ~ "Log Listing Price",
    grepl("price_listing", outcome) ~ "Listing Price",
    grepl("log_price", outcome) ~ "Log Price",
    grepl("price", outcome) ~ "Price",
    TRUE ~ outcome
  )

  # Threshold
  threshold_lbl <- dplyr::case_when(
    treatment_threshold == "mean" ~ "Mean",
    treatment_threshold == "p50" ~ "P50",
    treatment_threshold == "p75" ~ "P75",
    treatment_threshold == "p90" ~ "P90",
    treatment_threshold == "max" ~ "Max",
    treatment_threshold == "cont" ~ "Continuous",
    TRUE ~ stringr::str_to_title(treatment_threshold)
  )

  # Time aggregation
  time_lbl <- dplyr::case_when(
    grepl("mo", time_agg) ~ "Monthly",
    grepl("qtr", time_agg) ~ "Quarterly",
    grepl("yr", time_agg) ~ "Yearly",
    TRUE ~ time_agg
  )
  time_lbl <- ifelse(threshold_lbl == "Continuous", "", time_lbl)

  # Treatment
  treat_lbl <- dplyr::case_when(
    grepl("spill_count", treatment_type) & treatment_threshold != "cont" ~
      "Spill Count",
    grepl("spill_hrs", treatment_type) & treatment_threshold != "cont" ~
      "Spill Hours",
    grepl("spill_count", treatment_type) & treatment_threshold == "cont" ~
      "Log Spill Count",
    grepl("spill_hrs", treatment_type) & treatment_threshold == "cont" ~
      "Log Spill Hours",
    TRUE ~ NA_character_
  )

  # Fixed effects
  time_fe_lbl <- dplyr::case_when(
    time_fe == "mo" ~ "Monthly FE",
    time_fe == "qtr" ~ "Quarterly FE",
    time_fe == "yr" ~ "Yearly FE",
    TRUE ~ "No time FE"
  )
  space_fe_lbl <- dplyr::case_when(
    space_fe == "lsoa" ~ "LSOA FE",
    space_fe == "msoa" ~ "MSOA FE",
    space_fe == "admin_ward" ~ "Admin Ward FE",
    space_fe == "admin_county" ~ "Admin County FE",
    space_fe == "county" ~ "County FE",
    space_fe == "region" ~ "Region FE",
    space_fe == "country" ~ "Country FE",
    space_fe == "nhs_ha" ~ "NHS HA FE",
    TRUE ~ "No location FE"
  )

  # Controls
  ctrl_lbl <- if (is.null(controls) || length(controls) == 0) {
    "No controls"
  } else {
    paste(controls, collapse = ", ")
  }

  # Compose
  glue::glue(
    "Outcome: {outcome_lbl}; Treatment: {treat_lbl}; Aggregation: {time_lbl};
    FE: {time_fe_lbl} + {space_fe_lbl}; Controls: {ctrl_lbl}"
  ) %>%
    as.character()
}

# Main function ------------------------------------------------------
run_event_study_sunab <- function(
  param_grid,
  data,
  rad,
  overwrite = FALSE,
  file_name = "rentals_sunab_results_{rad}.rds"
) {
  # Data validation
  stopifnot(
    is.data.frame(param_grid),
    is.data.frame(data),
    length(rad) == 1
  )

  # ---- 0. results directory/file setup ----------------------------------- #
  # Create directory for individual model files
  res_dir <- here::here(
    "book",
    "book_regs",
    glue::glue("rentals_sunab_models_rad_{rad}")
  )
  fs::dir_create(res_dir)

  # Create/read index file to track which models are complete
  index_path <- file.path(res_dir, "model_index.rds")
  if (!overwrite && fs::file_exists(index_path)) {
    model_index <- readRDS(index_path)
  } else {
    model_index <- tibble::tibble(
      model_name = character(),
      completed = logical(),
      file_path = character()
    )
  }
  existing_names <- model_index$model_name

  # ---- 1. identify the models still to run ------------------------------- #
  param_grid <- tibble::as_tibble(param_grid) %>%
    dplyr::mutate(
      model_name = purrr::pmap_chr(
        list(
          outcome,
          treatment_threshold,
          treatment_type,
          thr_time_agg,
          time_agg,
          time_fe,
          space_fe,
          cluster_var,
          controls
        ),
        build_model_name
      )
    )

  todo <- dplyr::anti_join(
    param_grid,
    tibble::tibble(model_name = existing_names),
    by = "model_name"
  )

  if (nrow(todo) == 0) {
    cli::cli_alert_info("No new models to run for radius {rad}.")
    return(invisible(model_index))
  }
  cli::cli_alert_info("Estimating {nrow(todo)} models for radius {rad} …")

  # ---- 2. run the models one by one, saving each individually ------------- #
  for (i in 1:nrow(todo)) {
    mn <- todo$model_name[i]
    cli::cli_alert(" • {i}/{nrow(todo)}: {mn}")

    # Get model iteration
    p <- todo[i, ]

    # Define treatment variable
    treatment_var <- paste0(
      "first_t_",
      p$treatment_threshold,
      "_",
      p$treatment_type,
      "_",
      p$thr_time_agg
    )

    # Build formula -------------------------------------------------
    rhs_terms <- c(
      paste0("sunab(", treatment_var, ", ", p$time_agg, ")"),
      unlist(p$controls)
    ) %>%
      purrr::compact()

    fml <- as.formula(
      paste0(
        p$outcome,
        " ~ ",
        paste(rhs_terms, collapse = " + "),
        " | ",
        p$space_fe,
        " + ",
        p$time_fe
      )
    )
    cl_fml <- as.formula(paste0(" ~ ", p$cluster_var, " + ", p$time_fe))

    # Build description
    desc <- build_description(
      p$outcome,
      p$treatment_threshold,
      p$treatment_type,
      p$time_agg,
      p$thr_time_agg,
      p$time_fe,
      p$space_fe,
      p$cluster_var,
      unlist(p$controls)
    )

    # Run the model
    res <- tryCatch(
      {
        fixest::feols(
          fml = fml,
          data = data,
          vcov = cl_fml
        )
      },
      error = function(e) {
        cli::cli_alert_danger("Error fitting model {mn}: {e$message}")
        return(NULL)
      }
    )

    # Skip if model failed
    if (is.null(res)) {
      next
    }

    # Only save the plotting data
    res <- ggfixest::iplot_data(
      res,
      .ci_level = 0.95
    )

    # Build specification for ggplot
    controls <- if (is.null(p$controls) || length(p$controls) == 0) {
      ""
    } else {
      paste0(
        "+ ",
        paste(unlist(p$controls), collapse = " + ")
      )
    }

    spec <- glue::glue(
      "{p$outcome} ~ {p$time_fe} + {p$space_fe} + {treatment_var} {controls}"
    )

    attr(res, "description") <- desc
    attr(res, "spec") <- spec

    # Save to individual file
    model_file <- file.path(res_dir, paste0(mn, ".rds"))
    saveRDS(res, model_file)

    # Update index
    model_index <- model_index %>%
      dplyr::add_row(
        model_name = mn,
        completed = TRUE,
        file_path = model_file
      )
    saveRDS(model_index, index_path)

    # Clean up memory
    rm(res, fml, cl_fml, desc, spec, treatment_var, rhs_terms, controls)
    gc(verbose = FALSE)
  }

  cli::cli_alert_success("All models saved in → {res_dir}")
  invisible(model_index)
}
```


```{r}
#| eval: false
# Run Event Study Regressions

param_grid <- expand.grid(
  outcome = c("log_price_listing"),
  treatment_threshold = c("mean", "p50", "p75", "p90"),
  treatment_type = c("spill_count", "spill_hrs"),
  thr_time_agg = "all",
  time_agg = "qtr_id",
  time_fe = "qtr_id",
  space_fe = "lsoa",
  cluster_var = "lsoa",
  controls = I(list(
    NULL,
    c("property_type")
  ))
)

event_data_list_sample <- purrr::map(1:length(event_data_list), function(i) {
  event_data_list[[i]] %>%
    slice_sample(prop = 0.10)
}) %>%
  purrr::set_names(paste0("rad_", radii))

purrr::imap(
  event_data_list,
  ~ {
    rad_value <- as.numeric(gsub("rad_", "", .y))
    run_event_study_sunab(
      param_grid = param_grid,
      data = .x,
      rad = rad_value,
      overwrite = TRUE,
      file_name = glue::glue("rentals_sunab_results_{rad_value}.rds")
    )
  }
)
```


```{r}
# Define Function to Load Results
load_results_sunab <- function(
  radii = c(250, 500, 1000),
  freqs = c("qtr", "mo"),
  dir_path = here::here("output", "regs"),
  quiet = FALSE,
  pattern = "rentals_sunab_models_rad_{r}"
) {
  results <- list()

  for (r in radii) {
    r_chr <- as.character(r)

    # Initialize radius slot if needed
    if (is.null(results[[r_chr]])) {
      results[[r_chr]] <- list()
    }

    for (f in freqs) {
      # Create path to model index file
      model_dir_pattern <- glue::glue(
        pattern,
        .envir = rlang::env(r = r, f = f)
      )
      model_dir <- file.path(dir_path, model_dir_pattern)
      index_path <- file.path(model_dir, "model_index.rds")

      # Skip if no index file exists
      if (!file.exists(index_path)) {
        if (!quiet) {
          cli::cli_alert_warning(
            "No model index found for radius {r}, freq {f}"
          )
        }
        next
      }

      # Read model index
      model_index <- readRDS(index_path)

      # Initialize frequency slot
      results[[r_chr]][[f]] <- list()

      # Load each model into the structure
      model_count <- 0
      for (mn in model_index$model_name) {
        model_path <- file.path(model_dir, paste0(mn, ".rds"))
        if (file.exists(model_path)) {
          results[[r_chr]][[f]][[mn]] <- readRDS(model_path)
          model_count <- model_count + 1
        }
      }

      if (!quiet) {
        cli::cli_alert_success(
          "Loaded {model_count} models for radius {r}, freq {f}"
        )
      }
    }
  }

  return(results)
}
```


```{r}
# Define Function to Plot Sunab Regressions
plot_reg_sunab <- function(
  data,
  radius,
  model,
  freq = c("qtr", "mo"),
  use_desc = TRUE
) {
  freq <- match.arg(freq)
  r <- as.character(radius)

  stopifnot(r %in% names(data))
  stopifnot(freq %in% names(data[[r]]))

  mod <- data[[r]][[freq]][[model]]
  if (is.null(mod)) {
    stop(
      "Model '",
      model,
      "' not found for radius ",
      r,
      " and freq '",
      freq,
      "'."
    )
  }

  # ------------------------------------------------------------------------
  # Data Wrangling
  subtitle <- if (use_desc && !is.null(attr(mod, "description"))) {
    attr(mod, "description")
  } else {
    model
  }
  spec <- if (use_desc && !is.null(attr(mod, "spec"))) {
    attr(mod, "spec")
  } else {
    ""
  }

  # Plot
  mod %>%
    mutate(
      estimate_names = estimate_names + 1,
      group = factor(
        ifelse(estimate_names <= 0, "Pre", "Post"),
        levels = c("Pre", "Post")
      )
    ) %>%
    filter(
      estimate_names <= 8,
      estimate_names >= -4,
      ci_level == .95
    ) %>%
    ggplot(aes(x = estimate_names, y = estimate, color = group)) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    geom_errorbar(aes(ymin = ci_low, ymax = ci_high), width = 0.2) +
    geom_point(size = 1.2) +
    # geom_line(aes(group = 1), linewidth = 0.25) +
    scale_color_manual(
      values = c(
        "Pre" = viridis(1, option = "magma"),
        "Post" = viridis(3, option = "magma")[2]
      ),
      breaks = c("Pre", "Post")
    ) +
    theme_minimal() +
    labs(
      x = "Time",
      y = "Estimate",
      title = "",
      subtitle = subtitle,
      caption = spec
    ) +
    theme_pref +
    theme(plot.caption = element_text(hjust = 0))
}
```

```{r}
results_sunab <- load_results_sunab(
  radii = c(250, 500, 1000),
  freqs = c("qtr"),
  quiet = FALSE,
  pattern = "rentals_sunab_models_rad_{r}"
)
```

### Binary Treatment - Average Spill Count {#sec-06-03-01-binary-average}

::: {.panel-tabset group="threshold-rental"}

#### 250m

::: {.panel-tabset group="radius-rental-250m"}

##### Count (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_mean_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_mean_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_mean_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_mean_all_fe_qtr_id_lsoa_property_type"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-rental-500m"}

##### Count (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_mean_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_mean_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_mean_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_mean_all_fe_qtr_id_lsoa_property_type"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-rental-1000m"}

##### Count (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_mean_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_mean_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_mean_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_mean_all_fe_qtr_id_lsoa_property_type"
)
```

:::

:::

### Binary Treatment - Median Spill Count {#sec-06-03-02-binary-median}

::: {.panel-tabset group="threshold-rental"}

#### 250m

::: {.panel-tabset group="radius-rental-250m"}

##### Count (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_p50_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_p50_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_p50_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_p50_all_fe_qtr_id_lsoa_property_type"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-rental-500m"}

##### Count (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_p50_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_p50_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_p50_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_p50_all_fe_qtr_id_lsoa_property_type"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-rental-1000m"}

##### Count (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_p50_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_p50_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_p50_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_p50_all_fe_qtr_id_lsoa_property_type"
)
```

:::

:::

### Binary Treatment - 75th Percentile Spill Count {#sec-06-03-03-binary-p75}

::: {.panel-tabset group="threshold-rental"}

#### 250m

::: {.panel-tabset group="radius-rental-250m"}

##### Count (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_p75_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_p75_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_p75_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_p75_all_fe_qtr_id_lsoa_property_type"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-rental-500m"}

##### Count (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_p75_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_p75_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_p75_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_p75_all_fe_qtr_id_lsoa_property_type"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-rental-1000m"}

##### Count (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_p75_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_p75_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_p75_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_p75_all_fe_qtr_id_lsoa_property_type"
)
```

:::

:::

### Binary Treatment - 90th Percentile Spill Count {#sec-06-03-04-binary-p90}

::: {.panel-tabset group="threshold-rental"}

#### 250m

::: {.panel-tabset group="radius-rental-250m"}

##### Count (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_p90_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_p90_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_p90_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_p90_all_fe_qtr_id_lsoa_property_type"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-rental-500m"}

##### Count (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_p90_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_p90_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_p90_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_p90_all_fe_qtr_id_lsoa_property_type"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-rental-1000m"}

##### Count (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_p90_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_p90_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_p90_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_p90_all_fe_qtr_id_lsoa_property_type"
)
```

:::

:::
