---
title: "Direction-Aware Extensive-Margin News Analysis"
format:
  html:
    toc: true
    toc-depth: 3
    code-fold: true
execute:
  echo: false
  warning: false
  message: false
---

## What This Notebook Shows

This notebook combines the extensive-margin publicity design with the upstream/downstream nearest-site classification. It asks whether public attention changes the near-far price gap differently when the nearest signed overflow is upstream rather than downstream of the property.

The estimating equation is:

`log_price ~ near_bin * upstream * attention + controls | location FE + month FE`

The headline object is the triple interaction, `near_bin:upstream:attention`. The tables below report it as an interpretable contrast: the upstream-minus-downstream difference in the publicity-driven near-far gap.

This is not the same sample as the broader extensive-margin notebook. Here, every property must have a nearest overflow that can be classified on the river network. Because the signed-pair files currently cover properties within 1km of an overflow, the analysis uses comparisons inside that support only.

```{r}
#| label: setup

install_if_missing <- function(packages) {
  missing_packages <- packages[!vapply(packages, requireNamespace, logical(1), quietly = TRUE)]
  if (length(missing_packages) > 0) {
    install.packages(missing_packages)
  }
  invisible(lapply(packages, library, character.only = TRUE))
}

required_packages <- c(
  "arrow",
  "dplyr",
  "fixest",
  "forcats",
  "ggplot2",
  "glue",
  "here",
  "knitr",
  "lubridate",
  "purrr",
  "readr",
  "readxl",
  "rio",
  "scales",
  "stringr",
  "tibble",
  "tidyr"
)

install_if_missing(required_packages)

START_DATE <- as.Date("2021-01-01")
END_DATE <- as.Date("2023-12-31")
LOOKUP_MAX_DISTANCE <- 1000
RIVER_DIST_CAP <- 1000
LATERAL_CAP <- 250
VCOV_MODE <- "hetero"

MARKET_COLOURS <- c(Sales = "#1F78B4", Rentals = "#D95F02")
EFFECT_COLOURS <- c(
  "Downstream" = "#1F78B4",
  "Upstream" = "#D95F02",
  "Upstream - downstream" = "#4D4D4D"
)

comparison_specs <- tibble::tribble(
  ~comparison_id,      ~comparison_label,       ~near_min, ~near_max, ~far_min, ~far_max,
  "250_vs_250_500",    "0-250m vs 250-500m",     0, 250, 250, 500,
  "250_vs_250_1000",   "0-250m vs 250-1000m",    0, 250, 250, 1000,
  "250_vs_500_1000",   "0-250m vs 500-1000m",    0, 250, 500, 1000,
  "500_vs_500_1000",   "0-500m vs 500-1000m",    0, 500, 500, 1000
)

spec_grid <- tibble::tribble(
  ~spec_id,              ~spec_label,                  ~controls, ~fe_unit,
  "ols",                 "OLS",                         FALSE,     "none",
  "ols_controls",        "OLS + controls",              TRUE,      "none",
  "msoa_month_controls", "MSOA + month FE + controls",  TRUE,      "msoa",
  "lsoa_month_controls", "LSOA + month FE + controls",  TRUE,      "lsoa"
)

FAMILIES <- c("post", "articles")
EFFECT_LEVELS <- c("Downstream", "Upstream", "Upstream - downstream")

`%||%` <- function(x, y) if (is.null(x) || length(x) == 0 || is.na(x)) y else x

month_id_from_date <- function(x) {
  x_date <- as.Date(x)
  (lubridate::year(x_date) - 2021L) * 12L + lubridate::month(x_date)
}

pretty_market <- function(market) {
  dplyr::case_when(
    market == "sales" ~ "Sales",
    market == "rentals" ~ "Rentals",
    TRUE ~ as.character(market)
  )
}

pretty_family <- function(family) {
  dplyr::case_when(
    family == "post" ~ "Near x Post",
    family == "articles" ~ "Near x log(Articles)",
    TRUE ~ as.character(family)
  )
}

controls_for_market <- function(market) {
  switch(
    tolower(as.character(market)),
    sales = c("property_type", "old_new", "duration"),
    rentals = c("property_type", "bedrooms", "bathrooms"),
    character()
  )
}

attention_var_for_family <- function(family) {
  switch(
    family,
    post = "post",
    articles = "log_cumulative_articles",
    stop("Unknown family: ", family)
  )
}

fmt_num <- function(x, digits = 3) {
  if (length(x) == 0 || is.null(x) || is.na(x)) {
    return("n/a")
  }
  formatC(as.numeric(x), format = "f", digits = digits)
}

fmt_big_n <- function(x) {
  if (length(x) == 0 || is.null(x) || is.na(x)) {
    return("n/a")
  }
  scales::comma(round(as.numeric(x)))
}

fmt_est_se <- function(estimate, std_error, status) {
  if (!identical(status, "ok") || is.na(estimate) || is.na(std_error)) {
    return(status)
  }
  paste0(fmt_num(estimate, 4), " (", fmt_num(std_error, 4), ")")
}

row_value <- function(data, column, default = NA) {
  if (nrow(data) == 0 || !column %in% names(data)) {
    return(default)
  }
  data[[column]][[1]] %||% default
}

load_peak_month_id <- function() {
  google_trends <- readxl::read_excel(
    here::here("data", "raw", "google_trends", "google_trends_uk.xlsx"),
    sheet = "united_kingdom"
  ) |>
    dplyr::filter(.data$Year >= 2021, .data$Year <= 2023)

  peak_row <- google_trends |>
    dplyr::slice_max(`'Sewage Spill' Google Searches`, n = 1, with_ties = FALSE)

  peak_year <- peak_row$Year[[1]]
  peak_month <- as.integer(substr(as.character(peak_row$Date[[1]]), 6, 7))

  (peak_year - 2021L) * 12L + peak_month
}

load_articles <- function() {
  arrow::read_parquet(
    here::here("data", "processed", "lexis_nexis", "search1_monthly.parquet")
  ) |>
    dplyr::filter(.data$month_id >= 1L, .data$month_id <= 36L) |>
    dplyr::arrange(.data$month_id) |>
    dplyr::mutate(
      cumulative_articles = cumsum(.data$article_count),
      log_cumulative_articles = log(.data$cumulative_articles)
    )
}

load_signed_nearest_lookup <- function(market) {
  if (market == "sales") {
    path <- here::here(
      "upstream_downstream", "output", "18-03", "river_filter",
      "spill_house_signed.csv"
    )
    id_col <- "house_id"
    property_lateral_col <- "house_lateral_m"
    distance_col <- "spill_house_euclid_m"
  } else {
    path <- here::here(
      "upstream_downstream", "output", "18-03", "river_filter",
      "spill_rental_signed.csv"
    )
    id_col <- "rental_id"
    property_lateral_col <- "rental_lateral_m"
    distance_col <- "spill_rental_euclid_m"
  }

  readr::read_csv(path, show_col_types = FALSE, progress = FALSE) |>
    dplyr::select(dplyr::all_of(c(
      id_col, "site_id", "signed_dist_m", "direction", "spill_lateral_m",
      property_lateral_col, distance_col
    ))) |>
    dplyr::rename(
      property_lateral_m = dplyr::all_of(property_lateral_col),
      distance_m = dplyr::all_of(distance_col)
    ) |>
    dplyr::mutate(
      dist_river_m = abs(.data$signed_dist_m),
      upstream = as.integer(.data$direction == -1),
      direction_label = dplyr::if_else(.data$upstream == 1L, "Upstream", "Downstream")
    ) |>
    dplyr::filter(
      !is.na(.data$site_id),
      !is.na(.data$direction),
      !is.na(.data$distance_m),
      !is.na(.data$dist_river_m),
      .data$distance_m <= LOOKUP_MAX_DISTANCE,
      .data$dist_river_m <= RIVER_DIST_CAP,
      .data$spill_lateral_m <= LATERAL_CAP,
      .data$property_lateral_m <= LATERAL_CAP
    ) |>
    dplyr::arrange(.data[[id_col]], .data$distance_m, .data$dist_river_m, .data$site_id) |>
    dplyr::group_by(.data[[id_col]]) |>
    dplyr::slice_head(n = 1) |>
    dplyr::ungroup() |>
    dplyr::rename(nearest_site_id = .data$site_id)
}

load_sales_transactions <- function() {
  rio::import(
    here::here("data", "processed", "house_price.parquet"),
    trust = TRUE
  ) |>
    tibble::as_tibble() |>
    dplyr::select(dplyr::any_of(c(
      "house_id", "price", "date_of_transfer", "property_type",
      "old_new", "duration", "lsoa", "msoa", "latitude", "longitude"
    ))) |>
    dplyr::mutate(
      date_of_transfer = as.Date(.data$date_of_transfer),
      month_id = month_id_from_date(.data$date_of_transfer),
      log_price = log(.data$price),
      property_type = forcats::fct_drop(forcats::as_factor(.data$property_type)),
      old_new = forcats::fct_drop(forcats::as_factor(.data$old_new)),
      duration = forcats::fct_drop(forcats::as_factor(.data$duration))
    ) |>
    dplyr::filter(
      .data$date_of_transfer >= START_DATE,
      .data$date_of_transfer <= END_DATE,
      .data$month_id >= 1L,
      .data$month_id <= 36L,
      is.finite(.data$log_price)
    )
}

load_rental_transactions <- function() {
  rio::import(
    here::here("data", "processed", "zoopla", "zoopla_rentals.parquet"),
    trust = TRUE
  ) |>
    tibble::as_tibble() |>
    dplyr::select(dplyr::any_of(c(
      "rental_id", "listing_price", "rented_est", "property_type",
      "bedrooms", "bathrooms", "lsoa", "msoa", "latitude", "longitude"
    ))) |>
    dplyr::mutate(
      rented_est = as.Date(.data$rented_est),
      month_id = month_id_from_date(.data$rented_est),
      log_price = log(.data$listing_price),
      property_type = forcats::fct_drop(forcats::as_factor(.data$property_type))
    ) |>
    dplyr::filter(
      .data$rented_est >= START_DATE,
      .data$rented_est <= END_DATE,
      .data$month_id >= 1L,
      .data$month_id <= 36L,
      is.finite(.data$log_price)
    )
}

prepare_market_data <- function(market, peak_month_id, articles) {
  if (market == "sales") {
    transactions <- load_sales_transactions()
    id_col <- "house_id"
  } else {
    transactions <- load_rental_transactions()
    id_col <- "rental_id"
  }

  transactions |>
    dplyr::inner_join(load_signed_nearest_lookup(market), by = id_col) |>
    dplyr::left_join(
      articles |>
        dplyr::select(
          .data$month_id, .data$cumulative_articles, .data$log_cumulative_articles
        ),
      by = "month_id"
    ) |>
    dplyr::mutate(
      post = as.integer(.data$month_id >= peak_month_id),
      market = market
    )
}

build_comparison_sample <- function(data, comparison_row) {
  data |>
    dplyr::filter(
      (.data$distance_m >= comparison_row$near_min &
         .data$distance_m <= comparison_row$near_max) |
        (.data$distance_m > comparison_row$far_min &
           .data$distance_m <= comparison_row$far_max)
    ) |>
    dplyr::mutate(
      near_bin = as.integer(.data$distance_m <= comparison_row$near_max),
      near_group = dplyr::if_else(.data$near_bin == 1L, "Near", "Far"),
      comparison_id = comparison_row$comparison_id,
      comparison_label = comparison_row$comparison_label
    )
}

sample_cell_summary <- function(sample, market, comparison_row) {
  sample |>
    dplyr::count(.data$near_group, .data$direction_label, name = "observations") |>
    tidyr::complete(
      near_group = c("Near", "Far"),
      direction_label = c("Downstream", "Upstream"),
      fill = list(observations = 0L)
    ) |>
    dplyr::left_join(
      sample |>
        dplyr::group_by(.data$near_group, .data$direction_label) |>
        dplyr::summarise(
          mean_distance_m = mean(.data$distance_m, na.rm = TRUE),
          mean_log_price = mean(.data$log_price, na.rm = TRUE),
          post_share = mean(.data$post, na.rm = TRUE),
          mean_articles = mean(.data$cumulative_articles, na.rm = TRUE),
          .groups = "drop"
        ),
      by = c("near_group", "direction_label")
    ) |>
    dplyr::mutate(
      market = market,
      comparison_id = comparison_row$comparison_id,
      comparison_label = comparison_row$comparison_label,
      .before = 1
    )
}

support_summary <- function(sample, market, comparison_row) {
  cell_counts <- sample |>
    dplyr::count(.data$near_bin, .data$upstream, name = "observations")

  tibble::tibble(
    market = market,
    comparison_id = comparison_row$comparison_id,
    comparison_label = comparison_row$comparison_label,
    observations = nrow(sample),
    near_values = dplyr::n_distinct(sample$near_bin),
    upstream_values = dplyr::n_distinct(sample$upstream),
    near_upstream_cells = nrow(cell_counts),
    min_cell_n = min(cell_counts$observations),
    month_values = dplyr::n_distinct(sample$month_id),
    post_values = dplyr::n_distinct(sample$post),
    ok_for_triple = near_values == 2L &&
      upstream_values == 2L &&
      near_upstream_cells == 4L &&
      month_values > 1L &&
      post_values == 2L
  )
}

build_formula <- function(family, spec_row, market) {
  attention_var <- attention_var_for_family(family)
  controls <- if (isTRUE(spec_row$controls)) controls_for_market(market) else character()
  rhs <- c(glue::glue("near_bin * upstream * {attention_var}"), controls)
  rhs_text <- paste(rhs, collapse = " + ")

  if (spec_row$fe_unit == "none") {
    stats::as.formula(glue::glue("log_price ~ {rhs_text}"))
  } else {
    stats::as.formula(glue::glue("log_price ~ {rhs_text} | {spec_row$fe_unit} + month_id"))
  }
}

required_vars_for_model <- function(family, spec_row, market) {
  vars <- c("log_price", "near_bin", "upstream", attention_var_for_family(family))
  if (isTRUE(spec_row$controls)) {
    vars <- c(vars, controls_for_market(market))
  }
  if (spec_row$fe_unit != "none") {
    vars <- c(vars, spec_row$fe_unit, "month_id")
  }
  unique(vars)
}

term_matches_parts <- function(term, parts) {
  term_parts <- strsplit(term, ":", fixed = TRUE)[[1]]
  setequal(term_parts, parts)
}

find_term_by_parts <- function(coef_names, parts) {
  hits <- coef_names[vapply(
    coef_names,
    term_matches_parts,
    logical(1),
    parts = parts
  )]
  hits[[1]] %||% NA_character_
}

empty_effect_rows <- function(metadata, status, nobs = NA_integer_, note = NA_character_) {
  tibble::as_tibble(metadata) |>
    tidyr::crossing(
      effect = factor(EFFECT_LEVELS, levels = EFFECT_LEVELS)
    ) |>
    dplyr::mutate(
      term = NA_character_,
      estimate = NA_real_,
      std_error = NA_real_,
      statistic = NA_real_,
      p_value = NA_real_,
      nobs = nobs,
      adj_r2 = NA_real_,
      status = status,
      note = note
    )
}

linear_combo <- function(model, terms, weights, effect, metadata) {
  if (any(is.na(terms))) {
    return(
      tibble::as_tibble(metadata) |>
        dplyr::mutate(
          effect = factor(effect, levels = EFFECT_LEVELS),
          term = paste(terms, collapse = " + "),
          estimate = NA_real_,
          std_error = NA_real_,
          statistic = NA_real_,
          p_value = NA_real_,
          nobs = stats::nobs(model),
          adj_r2 = suppressWarnings(tryCatch(
            as.numeric(fixest::fitstat(model, "ar2"))[[1]],
            error = function(e) NA_real_
          )),
          status = "effect_terms_missing",
          note = paste("Missing term for", effect)
        )
    )
  }

  coefs <- stats::coef(model)
  vc <- stats::vcov(model)
  missing_terms <- terms[!terms %in% names(coefs)]

  if (length(missing_terms) > 0) {
    return(
      tibble::as_tibble(metadata) |>
        dplyr::mutate(
          effect = factor(effect, levels = EFFECT_LEVELS),
          term = paste(terms, collapse = " + "),
          estimate = NA_real_,
          std_error = NA_real_,
          statistic = NA_real_,
          p_value = NA_real_,
          nobs = stats::nobs(model),
          adj_r2 = suppressWarnings(tryCatch(
            as.numeric(fixest::fitstat(model, "ar2"))[[1]],
            error = function(e) NA_real_
          )),
          status = "effect_terms_missing",
          note = paste(missing_terms, collapse = "; ")
        )
    )
  }

  names(weights) <- terms
  vc_sub <- vc[terms, terms, drop = FALSE]
  estimate <- sum(weights * coefs[terms])
  variance <- as.numeric(t(weights) %*% vc_sub %*% weights)
  std_error <- sqrt(max(variance, 0))
  statistic <- estimate / std_error
  df <- stats::df.residual(model)
  p_value <- if (is.finite(df) && df > 0) {
    2 * stats::pt(abs(statistic), df = df, lower.tail = FALSE)
  } else {
    2 * stats::pnorm(abs(statistic), lower.tail = FALSE)
  }

  tibble::as_tibble(metadata) |>
    dplyr::mutate(
      effect = factor(effect, levels = EFFECT_LEVELS),
      term = paste(terms, collapse = " + "),
      estimate = estimate,
      std_error = std_error,
      statistic = statistic,
      p_value = p_value,
      nobs = stats::nobs(model),
      adj_r2 = suppressWarnings(tryCatch(
        as.numeric(fixest::fitstat(model, "ar2"))[[1]],
        error = function(e) NA_real_
      )),
      status = "ok",
      note = NA_character_
    )
}

extract_effects <- function(model, family, metadata) {
  attention_var <- attention_var_for_family(family)
  coef_names <- names(stats::coef(model))
  downstream_term <- find_term_by_parts(coef_names, c("near_bin", attention_var))
  triple_term <- find_term_by_parts(coef_names, c("near_bin", "upstream", attention_var))

  dplyr::bind_rows(
    linear_combo(
      model = model,
      terms = downstream_term,
      weights = 1,
      effect = "Downstream",
      metadata = metadata
    ),
    linear_combo(
      model = model,
      terms = c(downstream_term, triple_term),
      weights = c(1, 1),
      effect = "Upstream",
      metadata = metadata
    ),
    linear_combo(
      model = model,
      terms = triple_term,
      weights = 1,
      effect = "Upstream - downstream",
      metadata = metadata
    )
  )
}

estimate_one_model <- function(sample, market, comparison_row, family, spec_row) {
  metadata <- list(
    market = market,
    comparison_id = comparison_row$comparison_id,
    comparison_label = comparison_row$comparison_label,
    family = family,
    spec_id = spec_row$spec_id,
    spec_label = spec_row$spec_label
  )

  needed <- required_vars_for_model(family, spec_row, market)
  data_est <- sample |>
    dplyr::filter(stats::complete.cases(dplyr::pick(dplyr::all_of(needed))))

  cell_count <- data_est |>
    dplyr::distinct(.data$near_bin, .data$upstream) |>
    nrow()

  if (
    nrow(data_est) == 0 ||
      dplyr::n_distinct(data_est$near_bin) < 2 ||
      dplyr::n_distinct(data_est$upstream) < 2 ||
      dplyr::n_distinct(data_est[[attention_var_for_family(family)]]) < 2 ||
      cell_count < 4
  ) {
    return(empty_effect_rows(metadata, "insufficient_variation", nrow(data_est)))
  }

  model <- tryCatch(
    fixest::feols(
      fml = build_formula(family, spec_row, market),
      data = data_est,
      vcov = VCOV_MODE
    ),
    error = function(e) e
  )

  if (inherits(model, "error")) {
    return(empty_effect_rows(metadata, "model_error", nrow(data_est), model$message))
  }

  extract_effects(model, family, metadata)
}

estimate_comparison <- function(sample, market, comparison_row) {
  rows <- list()
  idx <- 1L

  for (family in FAMILIES) {
    for (j in seq_len(nrow(spec_grid))) {
      rows[[idx]] <- estimate_one_model(
        sample = sample,
        market = market,
        comparison_row = comparison_row,
        family = family,
        spec_row = spec_grid[j, ]
      )
      idx <- idx + 1L
    }
  }

  dplyr::bind_rows(rows)
}

make_effect_plot <- function(data, title, subtitle) {
  dodge <- ggplot2::position_dodge(width = 0.65)

  ggplot2::ggplot(
    data,
    ggplot2::aes(
      x = .data$estimate,
      y = .data$comparison_label,
      xmin = .data$estimate - 1.96 * .data$std_error,
      xmax = .data$estimate + 1.96 * .data$std_error,
      colour = .data$effect,
      group = .data$effect
    )
  ) +
    ggplot2::geom_vline(xintercept = 0, linetype = 2, colour = "grey60") +
    ggplot2::geom_errorbarh(height = 0.16, alpha = 0.8, position = dodge) +
    ggplot2::geom_point(size = 2.1, position = dodge) +
    ggplot2::facet_grid(.data$market ~ .data$family, scales = "free_x") +
    ggplot2::scale_colour_manual(values = EFFECT_COLOURS, drop = FALSE) +
    ggplot2::labs(
      title = title,
      subtitle = subtitle,
      x = "Attention effect on the near-far log-price gap",
      y = NULL,
      colour = NULL
    ) +
    ggplot2::theme_minimal(base_size = 11) +
    ggplot2::theme(
      legend.position = "bottom",
      panel.grid.minor = ggplot2::element_blank(),
      panel.grid.major.y = ggplot2::element_line(colour = "grey92"),
      strip.text = ggplot2::element_text(face = "bold"),
      plot.title = ggplot2::element_text(face = "bold")
    )
}
```

```{r}
#| label: data-prep

peak_month_id <- load_peak_month_id()
articles <- load_articles()

market_data <- list(
  sales = prepare_market_data("sales", peak_month_id, articles),
  rentals = prepare_market_data("rentals", peak_month_id, articles)
)

market_overview <- purrr::imap_dfr(market_data, function(data, market) {
  tibble::tibble(
    market = pretty_market(market),
    observations = nrow(data),
    mean_distance_m = mean(data$distance_m, na.rm = TRUE),
    median_distance_m = stats::median(data$distance_m, na.rm = TRUE),
    upstream_share = mean(data$upstream, na.rm = TRUE),
    post_share = mean(data$post, na.rm = TRUE),
    min_month_id = min(data$month_id, na.rm = TRUE),
    max_month_id = max(data$month_id, na.rm = TRUE)
  )
})

sample_rows <- list()
support_rows <- list()
result_rows <- list()
idx <- 1L

for (market in names(market_data)) {
  data_market <- market_data[[market]]

  for (i in seq_len(nrow(comparison_specs))) {
    comp <- comparison_specs[i, ]
    sample <- build_comparison_sample(data_market, comp)

    sample_rows[[idx]] <- sample_cell_summary(sample, market, comp)
    support_rows[[idx]] <- support_summary(sample, market, comp)
    result_rows[[idx]] <- estimate_comparison(sample, market, comp)
    idx <- idx + 1L
  }
}

sample_summaries <- dplyr::bind_rows(sample_rows) |>
  dplyr::mutate(market = pretty_market(.data$market))

support_checks <- dplyr::bind_rows(support_rows) |>
  dplyr::mutate(market = pretty_market(.data$market))

main_results <- dplyr::bind_rows(result_rows) |>
  dplyr::mutate(
    market = pretty_market(.data$market),
    family = factor(.data$family, levels = FAMILIES, labels = pretty_family(FAMILIES)),
    effect = factor(.data$effect, levels = EFFECT_LEVELS)
  )

main_results_display <- main_results |>
  dplyr::mutate(
    cell = purrr::pmap_chr(
      list(.data$estimate, .data$std_error, .data$status),
      fmt_est_se
    )
  ) |>
  dplyr::select(
    .data$market, .data$comparison_label, .data$family, .data$effect,
    .data$spec_label, .data$cell
  ) |>
  tidyr::pivot_wider(names_from = .data$spec_label, values_from = .data$cell) |>
  dplyr::arrange(.data$market, .data$family, .data$comparison_label, .data$effect)

preferred_lsoa_plot_data <- main_results |>
  dplyr::filter(.data$spec_id == "lsoa_month_controls", .data$status == "ok") |>
  dplyr::mutate(
    comparison_label = factor(.data$comparison_label, levels = rev(comparison_specs$comparison_label)),
    market = factor(.data$market, levels = c("Sales", "Rentals"))
  )

preferred_msoa_plot_data <- main_results |>
  dplyr::filter(.data$spec_id == "msoa_month_controls", .data$status == "ok") |>
  dplyr::mutate(
    comparison_label = factor(.data$comparison_label, levels = rev(comparison_specs$comparison_label)),
    market = factor(.data$market, levels = c("Sales", "Rentals"))
  )

missing_effect_terms <- main_results |>
  dplyr::filter(.data$status != "ok") |>
  dplyr::count(
    .data$market, .data$comparison_label, .data$family,
    .data$spec_label, .data$status, .data$note,
    name = "effects"
  )

top_lsoa_difference <- main_results |>
  dplyr::filter(
    .data$spec_id == "lsoa_month_controls",
    .data$effect == "Upstream - downstream",
    .data$status == "ok"
  ) |>
  dplyr::mutate(abs_t = abs(.data$statistic)) |>
  dplyr::arrange(dplyr::desc(.data$abs_t)) |>
  dplyr::slice_head(n = 1)
```

::: {.callout-note appearance="simple"}
## Main Takeaway

The preferred LSOA specification's strongest upstream-minus-downstream contrast in this render is `r row_value(top_lsoa_difference, "market")`, `r row_value(top_lsoa_difference, "comparison_label")`, `r row_value(top_lsoa_difference, "family")`: estimate `r fmt_num(row_value(top_lsoa_difference, "estimate"), 4)` with standard error `r fmt_num(row_value(top_lsoa_difference, "std_error"), 4)`.

Read this as the difference between the upstream and downstream publicity effects on the near-far log-price gap. The downstream effect is the `near_bin x attention` coefficient; the upstream effect is that coefficient plus the triple interaction.
:::

## Matched Market Overview

These are the transaction samples after joining to the nearest signed overflow. The join requires a direction-classifiable river-network match, so the sample is narrower than the generic nearest-overflow extensive-margin sample.

```{r}
knitr::kable(
  market_overview |>
    dplyr::mutate(dplyr::across(dplyr::where(is.numeric), ~ round(.x, 3))),
  caption = "Transaction samples after joining to nearest signed overflows."
)
```

## Sample Counts

The table reports near/far cells separately for upstream and downstream nearest overflows. These are the cells that identify the triple interaction.

```{r}
knitr::kable(
  sample_summaries |>
    dplyr::mutate(
      mean_distance_m = round(.data$mean_distance_m, 1),
      mean_log_price = round(.data$mean_log_price, 3),
      post_share = round(.data$post_share, 3),
      mean_articles = round(.data$mean_articles, 1)
    ) |>
    dplyr::arrange(.data$market, .data$comparison_label, .data$near_group, .data$direction_label),
  caption = "Sample counts by market, comparison, near/far group, and direction."
)
```

## Support Checks

Each retained market-comparison cell should contain both near and far properties, both upstream and downstream nearest overflows, and all four near-by-direction cells.

```{r}
knitr::kable(
  support_checks,
  caption = "Variation checks for the triple-interaction design."
)
```

## Coefficient Plots

Each point is a linear combination from one triple-interaction regression. `Downstream` is the publicity effect on the near-far gap when the nearest signed overflow is downstream. `Upstream` adds the triple interaction. `Upstream - downstream` is the triple interaction itself.

```{r}
#| fig-width: 10
#| fig-height: 6
make_effect_plot(
  preferred_msoa_plot_data,
  title = "Direction-aware extensive-margin publicity effects",
  subtitle = "MSOA + month FE + controls"
)
```

```{r}
#| fig-width: 10
#| fig-height: 6
make_effect_plot(
  preferred_lsoa_plot_data,
  title = "Direction-aware extensive-margin publicity effects",
  subtitle = "LSOA + month FE + controls"
)
```

## Main Coefficient Tables

Cells report estimates with heteroskedasticity-robust standard errors in parentheses. The three effect rows are linear combinations from the same underlying regression.

```{r}
knitr::kable(
  main_results_display,
  caption = "Direction-aware near-far attention effects across specifications."
)
```

## Missing-Term Diagnostics

This diagnostic is intentionally explicit. If fixed effects absorb a requested term, or a comparison lacks enough variation, the relevant row appears here rather than causing the render to fail.

```{r}
if (nrow(missing_effect_terms) == 0) {
  cat("All requested effect terms were available in every retained model.")
} else {
  knitr::kable(
    missing_effect_terms,
    caption = "Models or effects that could not be estimated as requested."
  )
}
```

