---
title: "Investigating Partial Availability Missingness Patterns"
format:
  html:
    toc: true
    number-sections: true
    code-fold: true
execute:
  echo: true
  warning: false
  message: false
---

## Setup & Config

```{r}
required_packages <- c(
  "arrow",
  "dplyr",
  "tidyr",
  "forcats",
  "stringr",
  "ggplot2",
  "gt",
  "here",
  "scales"
)

install_if_missing <- function(packages) {
  new_packages <- packages[!sapply(packages, requireNamespace, quietly = TRUE)]
  if (length(new_packages) > 0) {
    install.packages(new_packages)
  }
  invisible(lapply(packages, library, character.only = TRUE))
}
install_if_missing(required_packages)

USE_SAMPLE <- FALSE
SAMPLE_N <- 500L
YEARS <- 2021:2023

path_unique_sites <- here::here("data", "processed", "unique_spill_sites.parquet")
path_annual_return <- here::here("data", "processed", "annual_return_edm.parquet")
path_lookup <- here::here("data", "processed", "annual_return_lookup.parquet")
```

## Load Data & Define Partial-Availability Population

```{r}
unique_sites <- arrow::read_parquet(path_unique_sites)
annual_return <- arrow::read_parquet(path_annual_return)
lookup <- arrow::read_parquet(path_lookup)

cat("Unique spill sites:", nrow(unique_sites), "\n")
cat("Annual return rows:", nrow(annual_return), "\n")
cat("Lookup rows:", nrow(lookup), "\n")
```

```{r}
avail_cols <- paste0("available_year_", YEARS)

unique_sites <- unique_sites |>
  dplyr::mutate(
    n_available = rowSums(dplyr::pick(dplyr::all_of(avail_cols)), na.rm = TRUE)
  )

cat("\nAvailability distribution:\n")
table(unique_sites$n_available) |> print()

partial_sites <- unique_sites |>
  dplyr::filter(n_available > 0, n_available < length(YEARS))

cat("\nPartial-availability sites:", nrow(partial_sites), "\n")
cat("Share of all sites:",
    scales::percent(nrow(partial_sites) / nrow(unique_sites), accuracy = 0.1), "\n")

if (USE_SAMPLE && nrow(partial_sites) > SAMPLE_N) {
  set.seed(42)
  partial_sites <- partial_sites |>
    dplyr::slice_sample(n = SAMPLE_N)
  cat("Sampled down to", nrow(partial_sites), "sites for development\n")
}
```

## Availability Pattern Summary

```{r}
partial_sites <- partial_sites |>
  dplyr::mutate(
    pattern = paste0(
      ifelse(available_year_2021, "T", "F"),
      ifelse(available_year_2022, "T", "F"),
      ifelse(available_year_2023, "T", "F")
    )
  )

pattern_counts <- partial_sites |>
  dplyr::count(pattern, name = "n_sites") |>
  dplyr::mutate(share = n_sites / sum(n_sites)) |>
  dplyr::arrange(dplyr::desc(n_sites))

pattern_counts |>
  gt::gt() |>
  gt::fmt_number(columns = n_sites, decimals = 0, sep_mark = ",") |>
  gt::fmt_percent(columns = share, decimals = 1) |>
  gt::cols_label(
    pattern = "Pattern (2021/2022/2023)",
    n_sites = "N Sites",
    share = "Share"
  ) |>
  gt::tab_header(
    title = "Availability Patterns Among Partial-Availability Sites",
    subtitle = "T = available, F = missing in matched events"
  )
```

```{r}
pattern_company <- partial_sites |>
  dplyr::count(water_company, pattern, name = "n") |>
  tidyr::pivot_wider(
    names_from = pattern,
    values_from = n,
    values_fill = 0
  )

pattern_company |>
  gt::gt() |>
  gt::fmt_number(columns = where(is.numeric), decimals = 0, sep_mark = ",") |>
  gt::tab_header(title = "Availability Pattern by Water Company")
```

## Join Annual Return Data via Lookup

Replicate the join logic from `create_unique_spill_sites.R:map_annual_to_canonical_sites`,
but also carry `spill_hrs_ea`, `spill_count_ea`, `asset_type`, and `edm_operation_action`.

```{r}
id_cols <- paste0("site_id_", YEARS)

# Pivot lookup from wide to long
lookup_long <- lookup |>
  dplyr::select(site_id, dplyr::any_of(id_cols)) |>
  tidyr::pivot_longer(
    cols = dplyr::any_of(id_cols),
    names_to = "id_year_col",
    values_to = "year_site_id"
  ) |>
  dplyr::mutate(year = as.integer(readr::parse_number(id_year_col))) |>
  dplyr::filter(year %in% YEARS, !is.na(year_site_id)) |>
  dplyr::group_by(year, year_site_id) |>
  dplyr::summarise(site_id = dplyr::first(site_id), .groups = "drop")

# Pivot annual return from wide to long, matching year to the correct site_id column
annual_long <- annual_return |>
  dplyr::filter(year %in% YEARS) |>
  dplyr::select(
    year, water_company, edm_commission_date,
    edm_operation_percent, edm_operation_reason, edm_operation_action,
    spill_hrs_ea, spill_count_ea, asset_type,
    dplyr::any_of(id_cols)
  ) |>
  tidyr::pivot_longer(
    cols = dplyr::any_of(id_cols),
    names_to = "id_year_col",
    values_to = "year_site_id"
  ) |>
  dplyr::mutate(id_year = as.integer(readr::parse_number(id_year_col))) |>
  dplyr::filter(year == id_year, !is.na(year_site_id)) |>
  dplyr::select(-id_year_col, -id_year)

# Join to get canonical site_id
annual_mapped <- annual_long |>
  dplyr::left_join(lookup_long, by = c("year", "year_site_id")) |>
  dplyr::mutate(
    site_id = dplyr::coalesce(as.integer(site_id), as.integer(year_site_id))
  ) |>
  dplyr::select(-year_site_id)

cat("Annual return rows mapped to canonical site_id:", nrow(annual_mapped), "\n")

# Filter to partial-availability sites
annual_partial <- annual_mapped |>
  dplyr::filter(site_id %in% partial_sites$site_id)

cat("Annual return rows for partial-availability sites:", nrow(annual_partial), "\n")
```

## Validate NA Spill Metrics Mechanism

The hypothesis: sites are marked unavailable because both `spill_hrs_ea` and `spill_count_ea`
are NA in the annual return. When both are NA, the row fails both the zero-spill filter
(`== 0`) and the non-zero filter (`!= 0`) in `merge_individ_annual_location.R:383-396`.

```{r}
# Build a site-year panel from partial sites
site_year_panel <- tidyr::expand_grid(
  site_id = partial_sites$site_id,
  year = YEARS
)

# Add availability flag from unique_sites
avail_long <- partial_sites |>
  dplyr::select(site_id, dplyr::all_of(avail_cols)) |>
  tidyr::pivot_longer(
    cols = dplyr::all_of(avail_cols),
    names_to = "avail_col",
    values_to = "available"
  ) |>
  dplyr::mutate(year = as.integer(stringr::str_extract(avail_col, "\\d{4}"))) |>
  dplyr::select(site_id, year, available)

site_year_panel <- site_year_panel |>
  dplyr::left_join(avail_long, by = c("site_id", "year"))

# Add spill metrics from annual return
site_year_panel <- site_year_panel |>
  dplyr::left_join(
    annual_partial |>
      dplyr::select(site_id, year, spill_hrs_ea, spill_count_ea) |>
      dplyr::distinct(site_id, year, .keep_all = TRUE),
    by = c("site_id", "year")
  ) |>
  dplyr::mutate(
    both_na = is.na(spill_hrs_ea) & is.na(spill_count_ea),
    in_annual_return = !is.na(spill_hrs_ea) | !is.na(spill_count_ea) |
      (site_id %in% annual_partial$site_id &
         paste(site_id, year) %in% paste(annual_partial$site_id, annual_partial$year))
  )

# Cross-tab: both_na vs available
validation_tab <- site_year_panel |>
  dplyr::count(available, both_na, name = "n") |>
  dplyr::arrange(available, both_na)

validation_tab |>
  gt::gt() |>
  gt::fmt_number(columns = n, decimals = 0, sep_mark = ",") |>
  gt::tab_header(
    title = "Validation: both_na (spill_hrs & spill_count) vs available_year",
    subtitle = "Expect: available=FALSE strongly associated with both_na=TRUE"
  )
```

```{r}
# Check for exceptions: available=TRUE but both_na=TRUE, or available=FALSE but both_na=FALSE
exceptions_avail_but_na <- site_year_panel |>
  dplyr::filter(available == TRUE, both_na == TRUE)

exceptions_missing_but_not_na <- site_year_panel |>
  dplyr::filter(available == FALSE, both_na == FALSE)

cat("Exceptions: available=TRUE but both spill metrics NA:",
    nrow(exceptions_avail_but_na), "\n")
cat("Exceptions: available=FALSE but spill metrics NOT both NA:",
    nrow(exceptions_missing_but_not_na), "\n")

# Sites not in annual return at all for a given year
not_in_ar <- site_year_panel |>
  dplyr::filter(
    available == FALSE,
    !paste(site_id, year) %in% paste(annual_partial$site_id, annual_partial$year)
  )
cat("Missing site-years with no annual return row at all:", nrow(not_in_ar), "\n")
```

## Reasons for Missing Years (Core Analysis)

For each missing site-year, gather the `edm_operation_reason` from four sources (coalesced):

1. Annual return for year Y directly
2. `unique_spill_sites` wide column for year Y
3. Annual return for year Y-1 (look-back)
4. `unique_spill_sites` wide column for year Y-1

```{r}
# Prepare reason from annual return (source 1 & 3)
ar_reasons <- annual_partial |>
  dplyr::select(site_id, year, edm_operation_reason, edm_operation_percent) |>
  dplyr::distinct(site_id, year, .keep_all = TRUE)

# Prepare reason from unique_sites wide columns (source 2 & 4)
reason_cols <- paste0("edm_operation_reason_", YEARS)
percent_cols <- paste0("edm_operation_percent_", YEARS)

us_reasons <- partial_sites |>
  dplyr::select(site_id, dplyr::all_of(reason_cols), dplyr::all_of(percent_cols)) |>
  tidyr::pivot_longer(
    cols = dplyr::all_of(reason_cols),
    names_to = "reason_col",
    values_to = "us_reason"
  ) |>
  dplyr::mutate(year = as.integer(stringr::str_extract(reason_col, "\\d{4}"))) |>
  dplyr::select(-reason_col) |>
  tidyr::pivot_longer(
    cols = dplyr::all_of(percent_cols),
    names_to = "pct_col",
    values_to = "us_percent"
  ) |>
  dplyr::mutate(pct_year = as.integer(stringr::str_extract(pct_col, "\\d{4}"))) |>
  dplyr::filter(year == pct_year) |>
  dplyr::select(site_id, year, us_reason, us_percent)

# Build missing site-years
missing_site_years <- site_year_panel |>
  dplyr::filter(available == FALSE) |>
  dplyr::select(site_id, year)

# Join all four reason sources
missing_reasons <- missing_site_years |>
  # Source 1: annual return for year Y
  dplyr::left_join(
    ar_reasons |> dplyr::rename(ar_reason_y = edm_operation_reason,
                                 ar_percent_y = edm_operation_percent),
    by = c("site_id", "year")
  ) |>
  # Source 2: unique_sites for year Y
  dplyr::left_join(
    us_reasons |> dplyr::rename(us_reason_y = us_reason, us_percent_y = us_percent),
    by = c("site_id", "year")
  ) |>
  # Source 3: annual return for year Y-1
  dplyr::left_join(
    ar_reasons |>
      dplyr::mutate(year = year + 1L) |>
      dplyr::rename(ar_reason_ym1 = edm_operation_reason,
                     ar_percent_ym1 = edm_operation_percent),
    by = c("site_id", "year")
  ) |>
  # Source 4: unique_sites for year Y-1
  dplyr::left_join(
    us_reasons |>
      dplyr::mutate(year = year + 1L) |>
      dplyr::rename(us_reason_ym1 = us_reason, us_percent_ym1 = us_percent),
    by = c("site_id", "year")
  )

# Coalesce: prefer Y direct, then Y unique_sites, then Y-1 direct, then Y-1 unique_sites
missing_reasons <- missing_reasons |>
  dplyr::mutate(
    best_reason = dplyr::coalesce(ar_reason_y, us_reason_y, ar_reason_ym1, us_reason_ym1),
    reason_source = dplyr::case_when(
      !is.na(ar_reason_y)   ~ "1_ar_year_y",
      !is.na(us_reason_y)   ~ "2_us_year_y",
      !is.na(ar_reason_ym1) ~ "3_ar_year_ym1",
      !is.na(us_reason_ym1) ~ "4_us_year_ym1",
      TRUE                  ~ "5_none_found"
    )
  )
```

### Reason Source Distribution

```{r}
source_dist <- missing_reasons |>
  dplyr::count(reason_source, name = "n") |>
  dplyr::mutate(share = n / sum(n)) |>
  dplyr::arrange(reason_source)

source_dist |>
  gt::gt() |>
  gt::fmt_number(columns = n, decimals = 0, sep_mark = ",") |>
  gt::fmt_percent(columns = share, decimals = 1) |>
  gt::cols_label(reason_source = "Reason Source", n = "N", share = "Share") |>
  gt::tab_header(
    title = "Where Did We Find the Reason?",
    subtitle = "Coalesced from 4 sources: AR year Y, US year Y, AR year Y-1, US year Y-1"
  )
```

### Best Reason Distribution

```{r}
# Clean and group reason labels
missing_reasons <- missing_reasons |>
  dplyr::mutate(
    reason_clean = best_reason |>
      stringr::str_to_lower() |>
      stringr::str_squish() |>
      stringr::str_replace_all("[^a-z0-9 /]", "") |>
      forcats::fct_lump_min(min = 3, other_level = "other/rare")
  )

reason_dist <- missing_reasons |>
  dplyr::count(reason_clean, name = "n") |>
  dplyr::mutate(share = n / sum(n)) |>
  dplyr::arrange(dplyr::desc(n))

reason_dist |>
  gt::gt() |>
  gt::fmt_number(columns = n, decimals = 0, sep_mark = ",") |>
  gt::fmt_percent(columns = share, decimals = 1) |>
  gt::cols_label(reason_clean = "Reason", n = "N", share = "Share") |>
  gt::tab_header(title = "Reason Distribution for Missing Site-Years")
```

### Reason by Year

```{r}
reason_year <- missing_reasons |>
  dplyr::count(year, reason_clean, name = "n") |>
  tidyr::pivot_wider(names_from = year, values_from = n, values_fill = 0)

reason_year |>
  gt::gt() |>
  gt::fmt_number(columns = where(is.numeric), decimals = 0, sep_mark = ",") |>
  gt::tab_header(title = "Reason by Missing Year")
```

## EDM Operation Percent for Missing Years

```{r}
# Get operation percent from annual return for missing site-years
missing_pct <- missing_reasons |>
  dplyr::mutate(
    best_percent = dplyr::coalesce(ar_percent_y, us_percent_y, ar_percent_ym1, us_percent_ym1)
  )

missing_pct_available <- missing_pct |>
  dplyr::filter(!is.na(best_percent))

cat("Missing site-years with operation percent data:",
    nrow(missing_pct_available), "/", nrow(missing_pct), "\n")

if (nrow(missing_pct_available) > 0) {
  ggplot2::ggplot(missing_pct_available, ggplot2::aes(x = best_percent)) +
    ggplot2::geom_histogram(binwidth = 5, fill = "steelblue", colour = "white") +
    ggplot2::geom_vline(xintercept = 90, linetype = "dashed", colour = "red", linewidth = 0.8) +
    ggplot2::annotate("text", x = 92, y = Inf, label = "90% threshold",
                      vjust = 2, hjust = 0, colour = "red", size = 3.5) +
    ggplot2::scale_x_continuous(breaks = seq(0, 100, 10)) +
    ggplot2::labs(
      title = "EDM Operation Percent for Missing Site-Years",
      subtitle = "Below 90% requires a reason; red line = 90% threshold",
      x = "EDM Operation Percent",
      y = "Count"
    ) +
    ggplot2::theme_minimal()
}
```

## Water Company Breakdown

```{r}
missing_with_company <- missing_reasons |>
  dplyr::left_join(
    partial_sites |> dplyr::select(site_id, water_company),
    by = "site_id"
  )

get_top_reason <- function(x) {
  x <- x[!is.na(x)]
  if (length(x) == 0) return(NA_character_)
  names(sort(table(x), decreasing = TRUE))[1]
}

company_summary <- missing_with_company |>
  dplyr::group_by(water_company) |>
  dplyr::summarise(
    n_missing_site_years = dplyr::n(),
    share_reason_found = mean(reason_source != "5_none_found"),
    top_reason = get_top_reason(best_reason),
    .groups = "drop"
  ) |>
  dplyr::arrange(dplyr::desc(n_missing_site_years))

company_summary |>
  gt::gt() |>
  gt::fmt_number(columns = n_missing_site_years, decimals = 0, sep_mark = ",") |>
  gt::fmt_percent(columns = share_reason_found, decimals = 1) |>
  gt::cols_label(
    water_company = "Water Company",
    n_missing_site_years = "Missing Site-Years",
    share_reason_found = "Share with Reason",
    top_reason = "Top Reason"
  ) |>
  gt::tab_header(title = "Missing Site-Years by Water Company")
```

## Commission Date Patterns

For "appearing late" patterns (FTT, FFT): check if `edm_commission_date` post-dates the
missing year.

```{r}
appearing_late <- partial_sites |>
  dplyr::filter(pattern %in% c("FTT", "FFT"))

cat("Appearing-late sites (FTT + FFT):", nrow(appearing_late), "\n")

if (nrow(appearing_late) > 0) {
  appearing_late_dates <- appearing_late |>
    dplyr::mutate(
      commission_date_parsed = suppressWarnings(as.Date(edm_commission_date)),
      first_missing_year = dplyr::case_when(
        pattern == "FTT" ~ 2021L,
        pattern == "FFT" ~ 2021L
      ),
      last_missing_year = dplyr::case_when(
        pattern == "FTT" ~ 2021L,
        pattern == "FFT" ~ 2022L
      ),
      commissioned_after_missing = dplyr::case_when(
        is.na(commission_date_parsed) ~ "Unknown (no date)",
        commission_date_parsed > as.Date(paste0(last_missing_year, "-12-31")) ~
          "Commissioned after missing period",
        commission_date_parsed > as.Date(paste0(first_missing_year, "-01-01")) ~
          "Commissioned during missing period",
        TRUE ~ "Commissioned before missing period"
      )
    )

  commission_tab <- appearing_late_dates |>
    dplyr::count(pattern, commissioned_after_missing, name = "n") |>
    tidyr::pivot_wider(names_from = pattern, values_from = n, values_fill = 0)

  commission_tab |>
    gt::gt() |>
    gt::fmt_number(columns = where(is.numeric), decimals = 0, sep_mark = ",") |>
    gt::tab_header(
      title = "Commission Timing for Appearing-Late Sites",
      subtitle = "Does commission date explain why early years are missing?"
    )
}
```

## Disappearing Sites

For "disappearing" patterns (TTF, TFF): examine the reason in the last available year and
first missing year.

```{r}
disappearing <- partial_sites |>
  dplyr::filter(pattern %in% c("TTF", "TFF"))

cat("Disappearing sites (TTF + TFF):", nrow(disappearing), "\n")

if (nrow(disappearing) > 0) {
  # Get the transition year (last available -> first missing)
  disappearing_transitions <- disappearing |>
    dplyr::mutate(
      last_avail_year = dplyr::case_when(
        pattern == "TTF" ~ 2022L,
        pattern == "TFF" ~ 2021L
      ),
      first_missing_year = dplyr::case_when(
        pattern == "TTF" ~ 2023L,
        pattern == "TFF" ~ 2022L
      )
    )

  # Get reasons for the transition year from annual return
  transition_reasons <- disappearing_transitions |>
    dplyr::select(site_id, pattern, first_missing_year) |>
    dplyr::left_join(
      ar_reasons |> dplyr::rename(transition_reason = edm_operation_reason),
      by = c("site_id", "first_missing_year" = "year")
    ) |>
    dplyr::mutate(
      transition_reason = tidyr::replace_na(transition_reason, "(no annual return row)")
    )

  transition_tab <- transition_reasons |>
    dplyr::count(pattern, transition_reason, name = "n") |>
    dplyr::arrange(pattern, dplyr::desc(n))

  transition_tab |>
    gt::gt() |>
    gt::fmt_number(columns = n, decimals = 0, sep_mark = ",") |>
    gt::tab_header(
      title = "Reason in First Missing Year for Disappearing Sites",
      subtitle = "What does the annual return say about why these sites vanished?"
    )
}
```

## Asset Type Comparison

```{r}
# Asset type for partial-availability sites
partial_asset <- annual_mapped |>
  dplyr::filter(site_id %in% partial_sites$site_id) |>
  dplyr::distinct(site_id, asset_type) |>
  dplyr::group_by(site_id) |>
  dplyr::summarise(asset_type = dplyr::first(asset_type), .groups = "drop")

# Asset type for all sites
all_asset <- annual_mapped |>
  dplyr::distinct(site_id, asset_type) |>
  dplyr::group_by(site_id) |>
  dplyr::summarise(asset_type = dplyr::first(asset_type), .groups = "drop")

asset_comparison <- dplyr::bind_rows(
  partial_asset |> dplyr::mutate(group = "Partial availability"),
  all_asset |> dplyr::mutate(group = "All sites")
) |>
  dplyr::count(group, asset_type, name = "n") |>
  dplyr::group_by(group) |>
  dplyr::mutate(share = n / sum(n)) |>
  dplyr::ungroup() |>
  dplyr::arrange(group, dplyr::desc(n))

asset_wide <- asset_comparison |>
  dplyr::select(asset_type, group, share) |>
  tidyr::pivot_wider(names_from = group, values_from = share, values_fill = 0)

asset_wide |>
  gt::gt() |>
  gt::fmt_percent(columns = where(is.numeric), decimals = 1) |>
  gt::cols_label(asset_type = "Asset Type") |>
  gt::tab_header(
    title = "Asset Type Distribution: Partial vs All Sites",
    subtitle = "Share of sites by asset type"
  )
```

## Summary of Findings

```{r}
n_total <- nrow(unique_sites)
n_partial <- nrow(unique_sites |> dplyr::filter(n_available > 0, n_available < length(YEARS)))
n_missing_sy <- nrow(missing_reasons)
n_reason_found <- sum(missing_reasons$reason_source != "5_none_found")
n_reason_from_ym1 <- sum(missing_reasons$reason_source %in% c("3_ar_year_ym1", "4_us_year_ym1"))

summary_metrics <- tibble::tibble(
  metric = c(
    "Total unique spill sites",
    "Partial-availability sites",
    "Share partial",
    "Missing site-years (partial population)",
    "Reason found (any source)",
    "Reason coverage",
    "Reason from Y-1 look-back only",
    "Y-1 look-back added coverage"
  ),
  value = c(
    scales::comma(n_total),
    scales::comma(n_partial),
    scales::percent(n_partial / n_total, accuracy = 0.1),
    scales::comma(n_missing_sy),
    scales::comma(n_reason_found),
    scales::percent(n_reason_found / n_missing_sy, accuracy = 0.1),
    scales::comma(n_reason_from_ym1),
    scales::percent(n_reason_from_ym1 / n_missing_sy, accuracy = 0.1)
  )
)

summary_metrics |>
  gt::gt() |>
  gt::cols_label(metric = "Metric", value = "Value") |>
  gt::tab_header(title = "Key Metrics Summary")
```

### Narrative

The partial-availability population consists of sites that appear in matched events for
some years (2021-2023) but not others. The primary mechanism driving missingness is that
both `spill_hrs_ea` and `spill_count_ea` are NA in the annual return for the missing year.
When both values are NA, the row fails both the zero-spill filter (`== 0`) and the non-zero
filter (`!= 0`) in `merge_individ_annual_location.R`, causing the site to drop out of
matched events entirely for that year.

The `edm_operation_reason` field -- sourced from the annual return or the unique spill sites
dataset, with a Y-1 look-back fallback -- provides insight into *why* these metrics are
missing. Common reasons include EDM not yet commissioned, equipment failure, or operation
below the 90% reporting threshold. The Y-1 look-back materially improves reason coverage
for sites that disappear, since the reason for decommissioning is typically recorded in
the last year the site was operational.

For sites that appear late (FTT, FFT patterns), commission dates frequently post-date the
missing years, confirming these are genuinely new installations. For disappearing sites
(TTF, TFF), the transition-year reasons point to decommissioning or operational changes.
