---
title: "Missing Annual Observation Patterns (2021-2023)"
format:
  html:
    toc: true
    number-sections: true
params:
  sample_mode: false
  sample_n_sites: 1500
  seed: 123
  output_dir: "output/tables/missing_data_patterns"
  figure_dir: "output/figures/missing_data_patterns"
execute:
  echo: true
  warning: false
  message: false
---

## Setup

```{r}
required_packages <- c(
  "arrow",
  "dplyr",
  "tidyr",
  "stringr",
  "ggplot2",
  "readr",
  "purrr",
  "here",
  "forcats",
  "scales"
)

invisible(lapply(required_packages, function(pkg) {
  if (!requireNamespace(pkg, quietly = TRUE)) {
    stop("Missing required package: ", pkg)
  }
  library(pkg, character.only = TRUE)
}))

set.seed(params$seed)

options(dplyr.summarise.inform = FALSE)

output_dir <- here::here(params$output_dir)
figure_dir <- here::here(params$figure_dir)

dir.create(output_dir, recursive = TRUE, showWarnings = FALSE)
dir.create(figure_dir, recursive = TRUE, showWarnings = FALSE)
```

```{r}
years <- 2021:2023

first_non_na <- function(x) {
  idx <- which(!is.na(x))
  if (length(idx) == 0) {
    return(x[NA_integer_][1])
  }
  x[idx[1]]
}

commission_bucket <- function(x) {
  y <- as.integer(format(as.Date(x), "%Y"))
  case_when(
    is.na(x) ~ "missing",
    !is.na(y) & y <= 2020 ~ "<=2020",
    !is.na(y) & y == 2021 ~ "2021",
    !is.na(y) & y == 2022 ~ "2022",
    !is.na(y) & y >= 2023 ~ "2023+",
    TRUE ~ "missing"
  )
}

stratified_sample_sites <- function(data, n_target, seed = 123) {
  stopifnot(all(c("site_id", "pattern", "water_company") %in% names(data)))
  data <- data %>% distinct(site_id, pattern, water_company)

  n_total <- nrow(data)
  if (n_total <= n_target) {
    return(data %>% mutate(sampled = TRUE))
  }

  strata <- data %>%
    count(pattern, water_company, name = "n_stratum") %>%
    arrange(desc(n_stratum), pattern, water_company)

  n_strata <- nrow(strata)
  strata <- strata %>% mutate(alloc = 0L)

  if (n_target >= n_strata) {
    base_alloc <- floor(n_target * strata$n_stratum / sum(strata$n_stratum))
    strata$alloc <- pmax(1L, as.integer(base_alloc))
  } else {
    strata$alloc[seq_len(n_target)] <- 1L
  }

  strata$alloc <- pmin(strata$alloc, strata$n_stratum)
  current <- sum(strata$alloc)

  if (current < n_target) {
    room <- strata$n_stratum - strata$alloc
    while (current < n_target && any(room > 0)) {
      idx <- which.max(room)
      strata$alloc[idx] <- strata$alloc[idx] + 1L
      room[idx] <- room[idx] - 1L
      current <- current + 1L
    }
  }

  if (current > n_target) {
    reducible <- which(strata$alloc > 1L)
    while (current > n_target && length(reducible) > 0) {
      idx <- reducible[1]
      strata$alloc[idx] <- strata$alloc[idx] - 1L
      current <- current - 1L
      reducible <- which(strata$alloc > 1L)
    }
  }

  stopifnot(sum(strata$alloc) == n_target)

  set.seed(seed)
  sampled <- strata %>%
    select(pattern, water_company, alloc) %>%
    left_join(data, by = c("pattern", "water_company")) %>%
    group_by(pattern, water_company, alloc) %>%
    mutate(rand = runif(n())) %>%
    arrange(rand, site_id, .by_group = TRUE) %>%
    mutate(rn = row_number()) %>%
    filter(rn <= alloc) %>%
    ungroup() %>%
    select(site_id, pattern, water_company) %>%
    mutate(sampled = TRUE)

  sampled
}

map_annual_to_canonical_sites <- function(annual_data, lookup_data, years = 2021:2023) {
  id_cols <- paste0("site_id_", years)

  lookup_long <- lookup_data %>%
    select(site_id, any_of(id_cols)) %>%
    pivot_longer(
      cols = any_of(id_cols),
      names_to = "id_year_col",
      values_to = "year_site_id"
    ) %>%
    mutate(year = as.integer(readr::parse_number(id_year_col))) %>%
    filter(year %in% years, !is.na(year_site_id)) %>%
    group_by(year, year_site_id) %>%
    summarise(site_id = first_non_na(site_id), .groups = "drop")

  annual_long <- annual_data %>%
    filter(year %in% years) %>%
    select(
      year,
      water_company,
      spill_hrs_ea,
      spill_count_ea,
      edm_operation_reason,
      edm_operation_percent,
      any_of(id_cols)
    ) %>%
    pivot_longer(
      cols = any_of(id_cols),
      names_to = "id_year_col",
      values_to = "year_site_id"
    ) %>%
    mutate(id_year = as.integer(readr::parse_number(id_year_col))) %>%
    filter(year == id_year, !is.na(year_site_id)) %>%
    select(-id_year_col, -id_year) %>%
    left_join(lookup_long, by = c("year", "year_site_id")) %>%
    mutate(site_id = coalesce(as.integer(site_id), as.integer(year_site_id)))

  annual_long %>%
    select(
      site_id,
      year,
      water_company,
      spill_hrs_ea,
      spill_count_ea,
      edm_operation_reason,
      edm_operation_percent
    ) %>%
    group_by(site_id, year) %>%
    summarise(
      water_company_annual = first_non_na(water_company),
      spill_hrs_ea = first_non_na(spill_hrs_ea),
      spill_count_ea = first_non_na(spill_count_ea),
      annual_reason = first_non_na(edm_operation_reason),
      annual_operation_percent = first_non_na(edm_operation_percent),
      annual_rows = n(),
      .groups = "drop"
    )
}
```

## Data Load

```{r}
unique_sites <- arrow::read_parquet(
  here::here("data", "processed", "unique_spill_sites.parquet")
)

annual_return <- arrow::read_parquet(
  here::here("data", "processed", "annual_return_edm.parquet")
)

annual_lookup <- arrow::read_parquet(
  here::here("data", "processed", "annual_return_lookup.parquet")
)

required_unique_cols <- c(
  "site_id",
  "water_company",
  "edm_commission_date",
  "available_year_2021",
  "available_year_2022",
  "available_year_2023",
  "edm_operation_percent_2021",
  "edm_operation_percent_2022",
  "edm_operation_percent_2023",
  "edm_operation_reason_2021",
  "edm_operation_reason_2022",
  "edm_operation_reason_2023"
)

missing_cols <- setdiff(required_unique_cols, names(unique_sites))
if (length(missing_cols) > 0) {
  stop("Missing columns in unique_spill_sites: ", paste(missing_cols, collapse = ", "))
}
```

## Cohort Definition

```{r}
site_status <- unique_sites %>%
  mutate(
    across(starts_with("available_year_"), ~ replace_na(as.logical(.x), FALSE)),
    n_obs = as.integer(available_year_2021) +
      as.integer(available_year_2022) +
      as.integer(available_year_2023),
    pattern = paste0(
      as.integer(available_year_2021),
      as.integer(available_year_2022),
      as.integer(available_year_2023)
    ),
    cohort = case_when(
      n_obs == 0 ~ "all_missing",
      n_obs == 3 ~ "all_observed",
      n_obs %in% c(1, 2) ~ "mixed",
      TRUE ~ "other"
    ),
    commission_bucket = commission_bucket(edm_commission_date)
  )

mixed_sites_all <- site_status %>% filter(cohort == "mixed")

if (params$sample_mode) {
  sampled_sites <- stratified_sample_sites(
    data = mixed_sites_all %>% select(site_id, pattern, water_company),
    n_target = params$sample_n_sites,
    seed = params$seed
  )

  mixed_sites <- mixed_sites_all %>%
    inner_join(sampled_sites %>% select(site_id), by = "site_id")
} else {
  mixed_sites <- mixed_sites_all
}

site_pattern_counts <- site_status %>%
  count(cohort, pattern, name = "n_sites") %>%
  arrange(cohort, desc(n_sites))

readr::write_csv(
  site_pattern_counts,
  file.path(output_dir, "site_pattern_counts.csv")
)
```

```{r}
# Integrity checks for cohort logic
stopifnot(
  nrow(site_status) ==
    sum(site_status$cohort == "mixed") +
    sum(site_status$cohort == "all_missing") +
    sum(site_status$cohort == "all_observed")
)

if (params$sample_mode) {
  stopifnot(nrow(mixed_sites) <= params$sample_n_sites)
  stopifnot(all(mixed_sites$site_id %in% mixed_sites_all$site_id))

  strata_all <- mixed_sites_all %>%
    count(pattern, water_company, name = "n_all")
  strata_sample <- mixed_sites %>%
    count(pattern, water_company, name = "n_sample")

  if (params$sample_n_sites >= nrow(strata_all)) {
    stopifnot(
      nrow(anti_join(strata_all, strata_sample, by = c("pattern", "water_company"))) == 0
    )
  }
}
```

In-scope sites:

```{r}
tibble(
  mode = ifelse(params$sample_mode, "sample", "full"),
  total_sites = nrow(site_status),
  mixed_sites_all = nrow(mixed_sites_all),
  mixed_sites_used = nrow(mixed_sites),
  all_missing_sites = sum(site_status$cohort == "all_missing"),
  all_observed_sites = sum(site_status$cohort == "all_observed")
)
```

## Missing Site-Year Panel

```{r}
missing_panel <- mixed_sites %>%
  select(
    site_id,
    water_company,
    commission_bucket,
    n_obs,
    pattern,
    starts_with("available_year_"),
    starts_with("edm_operation_reason_"),
    starts_with("edm_operation_percent_")
  ) %>%
  pivot_longer(
    cols = starts_with("available_year_"),
    names_to = "avail_col",
    values_to = "available"
  ) %>%
  mutate(
    year = as.integer(str_remove(avail_col, "available_year_")),
    reason_y = case_when(
      year == 2021 ~ edm_operation_reason_2021,
      year == 2022 ~ edm_operation_reason_2022,
      year == 2023 ~ edm_operation_reason_2023
    ),
    reason_y_minus1 = case_when(
      year == 2021 ~ NA_character_,
      year == 2022 ~ edm_operation_reason_2021,
      year == 2023 ~ edm_operation_reason_2022
    ),
    op_pct_y = case_when(
      year == 2021 ~ edm_operation_percent_2021,
      year == 2022 ~ edm_operation_percent_2022,
      year == 2023 ~ edm_operation_percent_2023
    ),
    op_pct_y_minus1 = case_when(
      year == 2021 ~ NA_real_,
      year == 2022 ~ edm_operation_percent_2021,
      year == 2023 ~ edm_operation_percent_2022
    )
  ) %>%
  filter(!available) %>%
  mutate(
    reason_y_present = !is.na(reason_y) & reason_y != "",
    reason_y_minus1_present = !is.na(reason_y_minus1) & reason_y_minus1 != "",
    op_pct_y_present = !is.na(op_pct_y),
    op_pct_y_minus1_present = !is.na(op_pct_y_minus1)
  ) %>%
  select(
    site_id,
    year,
    water_company,
    commission_bucket,
    n_obs,
    pattern,
    reason_y,
    reason_y_minus1,
    reason_y_present,
    reason_y_minus1_present,
    op_pct_y,
    op_pct_y_minus1,
    op_pct_y_present,
    op_pct_y_minus1_present
  )

annual_context <- map_annual_to_canonical_sites(
  annual_data = annual_return,
  lookup_data = annual_lookup,
  years = years
)

missing_panel <- missing_panel %>%
  left_join(
    annual_context,
    by = c("site_id", "year")
  ) %>%
  mutate(
    spill_hrs_ea_missing = is.na(spill_hrs_ea),
    spill_count_ea_missing = is.na(spill_count_ea),
    annual_reason_present = !is.na(annual_reason) & annual_reason != "",
    annual_operation_percent_present = !is.na(annual_operation_percent)
  )
```

```{r}
# Integrity checks for missing panel
expected_rows <- mixed_sites %>%
  summarise(n = sum(3L - n_obs)) %>%
  pull(n)

stopifnot(nrow(missing_panel) == expected_rows)
stopifnot(nrow(missing_panel) == nrow(distinct(missing_panel, site_id, year)))
stopifnot(all(is.na(missing_panel$reason_y_minus1[missing_panel$year == 2021])))
```

## Key Tables

```{r}
missing_year_reason_presence <- missing_panel %>%
  count(year, reason_y_present, reason_y_minus1_present, name = "n_missing_site_years") %>%
  group_by(year) %>%
  mutate(share = n_missing_site_years / sum(n_missing_site_years)) %>%
  ungroup() %>%
  arrange(year, desc(n_missing_site_years))

reason_prev_when_y_missing <- missing_panel %>%
  filter(!reason_y_present, reason_y_minus1_present) %>%
  count(year, reason_y_minus1, name = "n_missing_site_years") %>%
  group_by(year) %>%
  mutate(share = n_missing_site_years / sum(n_missing_site_years)) %>%
  ungroup() %>%
  arrange(year, desc(n_missing_site_years))

core_covariate_summary <- bind_rows(
  missing_panel %>%
    count(year, water_company, name = "n_missing_site_years") %>%
    group_by(year) %>%
    mutate(share = n_missing_site_years / sum(n_missing_site_years)) %>%
    ungroup() %>%
    transmute(year, variable = "water_company", level = water_company, n_missing_site_years, share),
  missing_panel %>%
    count(year, commission_bucket, name = "n_missing_site_years") %>%
    group_by(year) %>%
    mutate(share = n_missing_site_years / sum(n_missing_site_years)) %>%
    ungroup() %>%
    transmute(year, variable = "commission_bucket", level = commission_bucket, n_missing_site_years, share),
  missing_panel %>%
    mutate(level = if_else(op_pct_y_present, "present", "missing")) %>%
    count(year, level, name = "n_missing_site_years") %>%
    group_by(year) %>%
    mutate(share = n_missing_site_years / sum(n_missing_site_years)) %>%
    ungroup() %>%
    transmute(year, variable = "op_pct_y", level, n_missing_site_years, share),
  missing_panel %>%
    mutate(level = if_else(op_pct_y_minus1_present, "present", "missing")) %>%
    count(year, level, name = "n_missing_site_years") %>%
    group_by(year) %>%
    mutate(share = n_missing_site_years / sum(n_missing_site_years)) %>%
    ungroup() %>%
    transmute(year, variable = "op_pct_y_minus1", level, n_missing_site_years, share),
  missing_panel %>%
    mutate(level = if_else(spill_hrs_ea_missing, "missing", "present")) %>%
    count(year, level, name = "n_missing_site_years") %>%
    group_by(year) %>%
    mutate(share = n_missing_site_years / sum(n_missing_site_years)) %>%
    ungroup() %>%
    transmute(year, variable = "annual_spill_hrs_ea", level, n_missing_site_years, share),
  missing_panel %>%
    mutate(level = if_else(spill_count_ea_missing, "missing", "present")) %>%
    count(year, level, name = "n_missing_site_years") %>%
    group_by(year) %>%
    mutate(share = n_missing_site_years / sum(n_missing_site_years)) %>%
    ungroup() %>%
    transmute(year, variable = "annual_spill_count_ea", level, n_missing_site_years, share)
)

readr::write_csv(
  missing_year_reason_presence,
  file.path(output_dir, "missing_year_reason_presence.csv")
)
readr::write_csv(
  reason_prev_when_y_missing,
  file.path(output_dir, "reason_y_minus1_when_y_missing.csv")
)
readr::write_csv(
  core_covariate_summary,
  file.path(output_dir, "core_covariate_summary.csv")
)
```

### Site Pattern Counts

```{r}
site_pattern_counts %>%
  mutate(share = n_sites / sum(n_sites)) %>%
  arrange(desc(n_sites))
```

### Missing Year Reason Presence

```{r}
missing_year_reason_presence
```

### Top Previous-Year Reasons When Reason in Y Is Missing

```{r}
reason_prev_when_y_missing %>%
  group_by(year) %>%
  slice_head(n = 12) %>%
  ungroup()
```

### Core Covariate Summary

```{r}
core_covariate_summary
```

## Figures

```{r}
mixed_pattern_plot <- site_status %>%
  filter(cohort == "mixed") %>%
  count(pattern, name = "n_sites") %>%
  mutate(pattern = forcats::fct_reorder(pattern, n_sites, .desc = TRUE)) %>%
  ggplot(aes(x = pattern, y = n_sites)) +
  geom_col(fill = "#2C7FB8") +
  labs(
    x = "Availability pattern (2021-2023)",
    y = "Number of mixed sites",
    title = "Mixed-site availability patterns"
  ) +
  theme_minimal(base_size = 12)

ggsave(
  filename = file.path(figure_dir, "availability_pattern_bar.png"),
  plot = mixed_pattern_plot,
  width = 8,
  height = 4.5,
  dpi = 300
)

mixed_pattern_plot
```

```{r}
reason_presence_heatmap_data <- missing_year_reason_presence %>%
  mutate(
    state = paste0(
      "reason_Y=",
      if_else(reason_y_present, "present", "missing"),
      ", reason_Y-1=",
      if_else(reason_y_minus1_present, "present", "missing")
    )
  )

reason_presence_heatmap <- ggplot(
  reason_presence_heatmap_data,
  aes(x = factor(year), y = state, fill = share)
) +
  geom_tile(color = "white") +
  geom_text(aes(label = scales::percent(share, accuracy = 0.1)), size = 3.5) +
  scale_fill_gradient(low = "#F7FBFF", high = "#08519C", labels = scales::percent) +
  labs(
    x = "Year with missing observation",
    y = "Reason availability state",
    fill = "Share",
    title = "Reason completeness for missing site-years"
  ) +
  theme_minimal(base_size = 12)

ggsave(
  filename = file.path(figure_dir, "reason_presence_heatmap.png"),
  plot = reason_presence_heatmap,
  width = 9,
  height = 4.8,
  dpi = 300
)

reason_presence_heatmap
```

```{r}
top_reason_prev_plot_data <- reason_prev_when_y_missing %>%
  group_by(year) %>%
  slice_head(n = 8) %>%
  ungroup() %>%
  mutate(reason_y_minus1 = forcats::fct_reorder(reason_y_minus1, n_missing_site_years))

top_reason_prev_plot <- ggplot(
  top_reason_prev_plot_data,
  aes(x = reason_y_minus1, y = n_missing_site_years, fill = factor(year))
) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  facet_wrap(~ year, scales = "free_y") +
  labs(
    x = "Reason in Y-1",
    y = "Missing site-years in Y",
    title = "Top previous-year reasons when reason in Y is missing"
  ) +
  theme_minimal(base_size = 12)

ggsave(
  filename = file.path(figure_dir, "top_reason_prev_bar.png"),
  plot = top_reason_prev_plot,
  width = 10,
  height = 6,
  dpi = 300
)

top_reason_prev_plot
```

## Findings Summary

```{r}
n_total_sites <- nrow(site_status)
n_mixed_all <- nrow(mixed_sites_all)
n_mixed_used <- nrow(mixed_sites)
n_missing_rows <- nrow(missing_panel)

dominant_pattern <- site_status %>%
  filter(cohort == "mixed") %>%
  count(pattern, sort = TRUE) %>%
  slice_head(n = 1)

dominant_prev_reason <- reason_prev_when_y_missing %>%
  group_by(year) %>%
  slice_head(n = 1) %>%
  ungroup()

reason_absence_by_year <- missing_panel %>%
  group_by(year) %>%
  summarise(
    share_reason_y_missing = mean(!reason_y_present),
    share_reason_y_minus1_missing = mean(!reason_y_minus1_present),
    share_spill_hrs_missing = mean(spill_hrs_ea_missing),
    share_spill_count_missing = mean(spill_count_ea_missing)
  )
```

- Mode: `r ifelse(params$sample_mode, "sample", "full")`
- Sites in `unique_spill_sites`: `r scales::comma(n_total_sites)`
- Mixed sites (`n_obs` in {1,2}): `r scales::comma(n_mixed_all)`; used in this run: `r scales::comma(n_mixed_used)`
- Missing site-year rows analysed: `r scales::comma(n_missing_rows)`
- Most common mixed availability pattern: `r dominant_pattern$pattern` (`r scales::comma(dominant_pattern$n)` sites)

```{r}
reason_absence_by_year %>%
  mutate(
    across(starts_with("share_"), ~ scales::percent(.x, accuracy = 0.1))
  )
```

Top previous-year reason when the current-year reason is missing:

```{r}
dominant_prev_reason
```
