---
title: "Residual Spill-Count Variation Shares (Prior, Continuous)"
format:
  html:
    toc: true
    number-sections: true
    code-fold: true
execute:
  echo: true
  warning: false
  message: false
---

## Setup

```{r}
required_packages <- c(
  "arrow",
  "rio",
  "dplyr",
  "forcats",
  "fixest",
  "ggplot2",
  "gt",
  "here",
  "purrr",
  "scales",
  "sf",
  "tidyr",
  "tibble"
)

install_if_missing <- function(packages) {
  new_packages <- packages[!sapply(packages, requireNamespace, quietly = TRUE)]
  if (length(new_packages) > 0) {
    install.packages(new_packages)
  }
  invisible(lapply(packages, library, character.only = TRUE))
}
install_if_missing(required_packages)

RAD <- 250L

add_month_id <- function(df, date_col) {
  if ("month_id" %in% names(df)) {
    return(df)
  }

  if (!(date_col %in% names(df))) {
    stop("month_id not found and date column '", date_col, "' is unavailable.")
  }

  month_raw <- as.Date(df[[date_col]])
  if (all(is.na(month_raw))) {
    stop("Could not derive month_id from '", date_col, "'.")
  }

  df$month_id <- format(month_raw, "%Y-%m")
  df
}

build_lsoa_area_lookup <- function(shapefile_path, lsoa_values = NULL) {
  lsoa_sf <- sf::st_read(shapefile_path, quiet = TRUE)
  code_candidates <- c(
    "LSOA21CD",
    "LSOA21NM",
    "LSOA11CD",
    "LSOA11NM",
    "lsoa21cd",
    "lsoa21nm",
    "lsoa11cd",
    "lsoa11nm",
    "lsoa"
  )
  candidate_cols <- code_candidates[code_candidates %in% names(lsoa_sf)]

  if (length(candidate_cols) == 0) {
    stop(
      "Could not find a usable LSOA code/name column in shapefile. Expected one of: ",
      paste(code_candidates, collapse = ", "),
      "."
    )
  }

  overlap_n <- NA_integer_
  n_values <- NA_integer_

  if (is.null(lsoa_values)) {
    join_col <- candidate_cols[1]
  } else {
    clean_values <- unique(as.character(lsoa_values))
    clean_values <- clean_values[!is.na(clean_values)]
    n_values <- length(clean_values)

    overlap_by_col <- vapply(
      candidate_cols,
      function(col_nm) sum(clean_values %in% as.character(lsoa_sf[[col_nm]])),
      integer(1)
    )

    join_col <- candidate_cols[which.max(overlap_by_col)]
    overlap_n <- max(overlap_by_col)
  }

  tibble::tibble(
    lsoa = as.character(lsoa_sf[[join_col]]),
    lsoa_area_m2 = as.numeric(sf::st_area(lsoa_sf))
  ) |>
    dplyr::filter(!is.na(lsoa)) |>
    dplyr::distinct(lsoa, .keep_all = TRUE) |>
    (\(lookup_tbl) {
      list(
        lookup = lookup_tbl,
        join_col = join_col,
        overlap_n = overlap_n,
        n_values = n_values
      )
    })()
}

build_aux_formula_with_lhs <- function(
  lhs_var,
  controls_terms,
  use_controls,
  use_geo_fe,
  use_month_fe,
  fe_var
) {
  rhs <- if (isTRUE(use_controls)) controls_terms else "1"

  fe_terms <- c(
    if (isTRUE(use_geo_fe)) fe_var,
    if (isTRUE(use_month_fe)) "month_id"
  )

  if (length(fe_terms) == 0) {
    formula_text <- paste0(lhs_var, " ~ ", rhs)
  } else {
    formula_text <- paste0(
      lhs_var,
      " ~ ",
      rhs,
      " | ",
      paste(fe_terms, collapse = " + ")
    )
  }

  list(
    formula = stats::as.formula(formula_text),
    formula_text = formula_text
  )
}

build_aux_formula <- function(
  controls_terms,
  use_controls,
  use_geo_fe,
  use_month_fe,
  fe_var
) {
  build_aux_formula_with_lhs(
    lhs_var = "spill_count_daily_avg",
    controls_terms = controls_terms,
    use_controls = use_controls,
    use_geo_fe = use_geo_fe,
    use_month_fe = use_month_fe,
    fe_var = fe_var
  )
}

compute_residual_share <- function(formula_obj, data) {
  model <- fixest::feols(
    formula_obj,
    data = data,
    vcov = "hetero"
  )

  resid <- stats::residuals(model)
  spill <- stats::fitted(model) + resid

  var_raw <- stats::var(spill, na.rm = TRUE)
  var_resid <- stats::var(resid, na.rm = TRUE)

  residual_share <- if (is.na(var_raw) || var_raw <= 0) {
    NA_real_
  } else {
    var_resid / var_raw
  }

  r2 <- unname(as.numeric(fixest::fitstat(model, "r2")))
  one_minus_r2 <- 1 - r2

  tibble::tibble(
    n = stats::nobs(model),
    var_raw = var_raw,
    var_resid = var_resid,
    residual_share = residual_share,
    r2 = r2,
    one_minus_r2 = one_minus_r2,
    identity_gap = abs(residual_share - one_minus_r2)
  )
}

spec_grid <- tibble::tribble(
  ~spec_num , ~lsoa_fe , ~month_fe , ~property_controls ,
  1L        , FALSE    , FALSE     , FALSE              ,
  2L        , FALSE    , FALSE     , TRUE               ,
  3L        , TRUE     , FALSE     , FALSE              ,
  4L        , TRUE     , FALSE     , TRUE               ,
  5L        , FALSE    , TRUE      , FALSE              ,
  6L        , FALSE    , TRUE      , TRUE               ,
  7L        , TRUE     , TRUE      , FALSE              ,
  8L        , TRUE     , TRUE      , TRUE
)

run_panel <- function(
  data,
  panel_label,
  controls_terms,
  spec_prefix,
  fe_var
) {
  spec_grid |>
    mutate(
      panel = panel_label,
      spec_id = paste0(spec_prefix, spec_num),
      formula_info = purrr::pmap(
        list(property_controls, lsoa_fe, month_fe),
        \(use_controls, use_geo_fe, use_month_fe) {
          build_aux_formula(
            controls_terms = controls_terms,
            use_controls = use_controls,
            use_geo_fe = use_geo_fe,
            use_month_fe = use_month_fe,
            fe_var = fe_var
          )
        }
      ),
      formula = purrr::map(formula_info, "formula"),
      formula_text = purrr::map_chr(formula_info, "formula_text"),
      stats = purrr::map(formula, \(fml) compute_residual_share(fml, data))
    ) |>
    select(-formula_info, -formula) |>
    tidyr::unnest(cols = c(stats))
}

run_direction_panel <- function(
  data,
  panel_label,
  variant_label,
  controls_terms,
  spec_prefix,
  upstream_var,
  downstream_var,
  fe_var
) {
  variable_grid <- tibble::tribble(
    ~variable    , ~outcome_var   ,
    "Upstream"   , upstream_var   ,
    "Downstream" , downstream_var
  )

  tidyr::crossing(spec_grid, variable_grid) |>
    dplyr::mutate(
      panel = panel_label,
      variant = variant_label,
      spec_id = paste0(spec_prefix, spec_num),
      formula_info = purrr::pmap(
        list(outcome_var, property_controls, lsoa_fe, month_fe),
        \(outcome_var, use_controls, use_geo_fe, use_month_fe) {
          build_aux_formula_with_lhs(
            lhs_var = outcome_var,
            controls_terms = controls_terms,
            use_controls = use_controls,
            use_geo_fe = use_geo_fe,
            use_month_fe = use_month_fe,
            fe_var = fe_var
          )
        }
      ),
      formula = purrr::map(formula_info, "formula"),
      formula_text = purrr::map_chr(formula_info, "formula_text"),
      stats = purrr::map(formula, \(fml) compute_residual_share(fml, data))
    ) |>
    dplyr::select(-formula_info, -formula, -outcome_var) |>
    tidyr::unnest(cols = c(stats))
}
```

## Load and Prepare Data

```{r}
# Cross-section data with spill metrics
# Filter for properties with at least one spill site within radius.
dat_cs_sales_all <- arrow::open_dataset(
  here::here("data", "processed", "cross_section", "sales", "prior_to_sale")
) |>
  dplyr::filter(radius == RAD) |>
  dplyr::collect()

dat_cs_sales <- dat_cs_sales_all |>
  dplyr::filter(n_spill_sites > 0)

sales <- rio::import(
  here::here("data", "processed", "house_price.parquet"),
  trust = TRUE
) |>
  add_month_id("date_of_transfer") |>
  dplyr::select(
    -dplyr::any_of(c(
      "transaction_id",
      "date_of_transfer",
      "quality",
      "paon",
      "saon",
      "street",
      "locality",
      "town_city",
      "district",
      "county",
      "ppd_category",
      "record_status"
    ))
  ) |>
  dplyr::mutate(
    property_type = forcats::as_factor(property_type),
    old_new = forcats::as_factor(old_new),
    duration = forcats::as_factor(duration)
  )

dat_sales_clean <- dat_cs_sales |>
  dplyr::select(-dplyr::any_of("price")) |>
  dplyr::inner_join(sales, by = "house_id") |>
  dplyr::mutate(log_price = log(price)) |>
  dplyr::filter(
    !is.na(spill_count_daily_avg),
    !is.na(lsoa),
    !is.na(msoa),
    !is.na(property_type),
    !is.na(old_new),
    !is.na(duration),
    !is.na(month_id)
  ) |>
  dplyr::mutate(
    lsoa = forcats::fct_drop(forcats::as_factor(lsoa)),
    msoa = forcats::fct_drop(forcats::as_factor(msoa)),
    property_type = forcats::fct_drop(forcats::as_factor(property_type)),
    old_new = forcats::fct_drop(forcats::as_factor(old_new)),
    duration = forcats::fct_drop(forcats::as_factor(duration)),
    month_id = forcats::fct_drop(forcats::as_factor(month_id))
  )


dat_cs_rentals_all <- arrow::open_dataset(
  here::here("data", "processed", "cross_section", "rentals", "prior_to_rental")
) |>
  dplyr::filter(radius == RAD) |>
  dplyr::collect()

dat_cs_rentals <- dat_cs_rentals_all |>
  dplyr::filter(n_spill_sites > 0)

rentals <- rio::import(
  here::here("data", "processed", "zoopla", "zoopla_rentals.parquet"),
  trust = TRUE
) |>
  add_month_id("listing_created") |>
  dplyr::select(
    -dplyr::any_of(c(
      "postcode",
      "listing_created",
      "latest_to_rent",
      "rented",
      "rented_est",
      "address_line_01",
      "address_line_02",
      "address_line_03"
    ))
  ) |>
  dplyr::mutate(
    property_type = forcats::as_factor(property_type)
  )

dat_rental_clean <- dat_cs_rentals |>
  dplyr::select(-dplyr::any_of("listing_price")) |>
  dplyr::inner_join(rentals, by = "rental_id") |>
  dplyr::mutate(log_price = log(listing_price)) |>
  dplyr::filter(
    !is.na(spill_count_daily_avg),
    !is.na(lsoa),
    !is.na(msoa),
    !is.na(property_type),
    !is.na(bedrooms),
    !is.na(bathrooms),
    !is.na(month_id)
  ) |>
  dplyr::mutate(
    lsoa = forcats::fct_drop(forcats::as_factor(lsoa)),
    msoa = forcats::fct_drop(forcats::as_factor(msoa)),
    property_type = forcats::fct_drop(forcats::as_factor(property_type)),
    month_id = forcats::fct_drop(forcats::as_factor(month_id))
  )

cat("Sales observations:", nrow(dat_sales_clean), "\n")
cat("Rental observations:", nrow(dat_rental_clean), "\n")
```

## Build LSOA Diagnostics Data

```{r}
lsoa_obs_dist <- dplyr::bind_rows(
  dat_sales_clean |>
    dplyr::count(lsoa, name = "n_obs") |>
    dplyr::mutate(sample = "Sales"),
  dat_rental_clean |>
    dplyr::count(lsoa, name = "n_obs") |>
    dplyr::mutate(sample = "Rentals")
) |>
  dplyr::mutate(lsoa = as.character(lsoa))

lsoa_area_lookup_info <- build_lsoa_area_lookup(
  here::here(
    "data",
    "raw",
    "shapefiles",
    "lsoa_2011",
    "LSOA_2011_EW_BFC_V3.shp"
  ),
  lsoa_values = lsoa_obs_dist$lsoa
)

lsoa_area_lookup <- lsoa_area_lookup_info$lookup

lsoa_area_dist <- lsoa_obs_dist |>
  dplyr::distinct(sample, lsoa) |>
  dplyr::left_join(lsoa_area_lookup, by = "lsoa")

area_match_summary <- lsoa_area_dist |>
  dplyr::summarise(
    n_lsoa = dplyr::n(),
    n_with_area = sum(!is.na(lsoa_area_m2)),
    share_with_area = n_with_area / n_lsoa
  )

buffer_area_m2 <- pi * (RAD^2)
area_p95_m2 <- as.numeric(
  stats::quantile(lsoa_area_dist$lsoa_area_m2, probs = 0.95, na.rm = TRUE)
)
obs_p95_n <- as.numeric(
  stats::quantile(lsoa_obs_dist$n_obs, probs = 0.95, na.rm = TRUE)
)

if (!is.finite(area_p95_m2) || area_p95_m2 <= 0) {
  stop("Invalid pooled p95 for LSOA area; check area diagnostics input.")
}
if (!is.finite(obs_p95_n) || obs_p95_n <= 0) {
  stop("Invalid pooled p95 for observations-per-LSOA; check diagnostics input.")
}

cat("LSOA area-match diagnostics\n")
cat(" - Area lookup join column:", lsoa_area_lookup_info$join_col, "\n")
cat(
  " - Distinct sample LSOAs matched in lookup column:",
  lsoa_area_lookup_info$overlap_n,
  "/",
  lsoa_area_lookup_info$n_values,
  "\n"
)
cat(" - LSOAs in sample:", area_match_summary$n_lsoa, "\n")
cat(" - LSOAs matched to area:", area_match_summary$n_with_area, "\n")
cat(
  " - Match rate:",
  scales::percent(area_match_summary$share_with_area, accuracy = 0.1),
  "\n"
)
cat(
  " - 250m buffer area (m^2):",
  scales::comma(buffer_area_m2, accuracy = 1),
  "\n"
)
cat(
  " - Pooled p95 LSOA area (m^2):",
  scales::comma(area_p95_m2, accuracy = 1),
  "\n"
)
cat(
  " - Pooled p95 observations per LSOA:",
  scales::comma(obs_p95_n, accuracy = 1),
  "\n"
)

if (area_match_summary$n_with_area == 0) {
  stop(
    "No LSOAs matched area lookup. Check LSOA code column/vintage alignment."
  )
}

dat_sales_base <- dat_cs_sales_all |>
  dplyr::select(-dplyr::any_of("price")) |>
  dplyr::inner_join(sales, by = "house_id") |>
  dplyr::filter(!is.na(lsoa)) |>
  dplyr::mutate(lsoa = as.character(lsoa))

dat_rental_base <- dat_cs_rentals_all |>
  dplyr::select(-dplyr::any_of("listing_price")) |>
  dplyr::inner_join(rentals, by = "rental_id") |>
  dplyr::filter(!is.na(lsoa)) |>
  dplyr::mutate(lsoa = as.character(lsoa))

lsoa_retention_counts_dist <- dplyr::bind_rows(
  dat_sales_base |>
    dplyr::group_by(lsoa) |>
    dplyr::summarise(
      n_total = dplyr::n(),
      n_kept = sum(dplyr::coalesce(n_spill_sites, 0) > 0),
      n_dropped = n_total - n_kept,
      .groups = "drop"
    ) |>
    dplyr::mutate(sample = "Sales"),
  dat_rental_base |>
    dplyr::group_by(lsoa) |>
    dplyr::summarise(
      n_total = dplyr::n(),
      n_kept = sum(dplyr::coalesce(n_spill_sites, 0) > 0),
      n_dropped = n_total - n_kept,
      .groups = "drop"
    ) |>
    dplyr::mutate(sample = "Rentals")
)

retention_total_p99_n <- as.numeric(
  stats::quantile(
    lsoa_retention_counts_dist$n_total,
    probs = 0.99,
    na.rm = TRUE
  )
)

if (!is.finite(retention_total_p99_n) || retention_total_p99_n <= 0) {
  stop("Invalid pooled p99 for retention n_total; check diagnostics input.")
}

lsoa_area_dist_plot <- lsoa_area_dist |>
  dplyr::filter(!is.na(lsoa_area_m2), lsoa_area_m2 <= area_p95_m2) |>
  dplyr::mutate(lsoa_area_km2 = lsoa_area_m2 / 1e6)

lsoa_obs_dist_plot <- lsoa_obs_dist |>
  dplyr::filter(!is.na(n_obs), n_obs <= obs_p95_n)

lsoa_retention_counts_dist_plot <- lsoa_retention_counts_dist |>
  dplyr::filter(
    !is.na(n_total),
    n_total > 0,
    n_total <= retention_total_p99_n
  )

lsoa_retention_counts_long_plot <- lsoa_retention_counts_dist_plot |>
  dplyr::select(sample, lsoa, n_total, n_kept, n_dropped) |>
  tidyr::pivot_longer(
    cols = c(n_kept, n_dropped),
    names_to = "status",
    values_to = "n_component"
  ) |>
  dplyr::mutate(
    status = factor(
      status,
      levels = c("n_kept", "n_dropped"),
      labels = c(
        "Kept (>0 spill site)",
        "Dropped (0 spill sites)"
      )
    ),
    lsoa_weight_component = n_component / n_total
  )

buffer_area_km2 <- buffer_area_m2 / 1e6
area_p95_km2 <- area_p95_m2 / 1e6

area_bins <- 40L
obs_bins <- 40L
retention_bins <- 40L

cat(
  " - Pooled p99 n_total for retention plot:",
  scales::comma(retention_total_p99_n, accuracy = 1),
  "\n"
)
cat(
  " - Histogram bins (area / obs / retention):",
  area_bins,
  "/",
  obs_bins,
  "/",
  retention_bins,
  "\n"
)
```

## Compute Residual Variation Shares

```{r}
sales_results_lsoa <- run_panel(
  data = dat_sales_clean,
  panel_label = "Sales",
  controls_terms = "property_type + old_new + duration",
  spec_prefix = "S",
  fe_var = "lsoa"
)

rental_results_lsoa <- run_panel(
  data = dat_rental_clean,
  panel_label = "Rentals",
  controls_terms = "property_type + bedrooms + bathrooms",
  spec_prefix = "R",
  fe_var = "lsoa"
)

sales_results_msoa <- run_panel(
  data = dat_sales_clean,
  panel_label = "Sales",
  controls_terms = "property_type + old_new + duration",
  spec_prefix = "S",
  fe_var = "msoa"
)

rental_results_msoa <- run_panel(
  data = dat_rental_clean,
  panel_label = "Rentals",
  controls_terms = "property_type + bedrooms + bathrooms",
  spec_prefix = "R",
  fe_var = "msoa"
)

all_results <- dplyr::bind_rows(
  dplyr::mutate(sales_results_lsoa, geo_fe = "lsoa"),
  dplyr::mutate(rental_results_lsoa, geo_fe = "lsoa"),
  dplyr::mutate(sales_results_msoa, geo_fe = "msoa"),
  dplyr::mutate(rental_results_msoa, geo_fe = "msoa")
)
```

## Base Table Helpers

```{r}
format_results <- function(df, fe_label) {
  out <- df |>
    dplyr::arrange(spec_num) |>
    dplyr::transmute(
      Specification = spec_id,
      fe_status = dplyr::if_else(lsoa_fe, "Yes", "No"),
      `Month FE` = dplyr::if_else(month_fe, "Yes", "No"),
      `Property controls` = dplyr::if_else(property_controls, "Yes", "No"),
      Observations = n,
      `Var(spill count)` = var_raw,
      `Var(residual)` = var_resid,
      `Residual variation share` = residual_share
    )

  names(out)[names(out) == "fe_status"] <- fe_label
  out
}

make_styled_table <- function(df, title, fe_label) {
  gt::gt(df) |>
    gt::tab_header(title = gt::md(paste0("**", title, "**"))) |>
    gt::cols_align(
      align = "center",
      columns = tidyselect::all_of(c(fe_label, "Month FE", "Property controls"))
    ) |>
    gt::cols_align(
      align = "right",
      columns = c(
        Observations,
        `Var(spill count)`,
        `Var(residual)`,
        `Residual variation share`
      )
    ) |>
    gt::fmt_integer(columns = c(Observations), sep_mark = ",") |>
    gt::fmt_number(
      columns = c(`Var(spill count)`, `Var(residual)`),
      decimals = 4
    ) |>
    gt::fmt_number(columns = c(`Residual variation share`), decimals = 3) |>
    gt::opt_row_striping() |>
    gt::tab_options(
      table.width = gt::pct(100),
      data_row.padding = gt::px(5),
      column_labels.font.weight = "bold",
      column_labels.font.size = gt::px(12),
      table.font.size = gt::px(12)
    )
}
```

## LSOA Identification Diagnostics

```{r}
#| label: fig-lsoa-area-dist-sales
#| fig-cap: "Sales: Distribution of LSOA areas (km^2) for LSOAs with at least one house within 250 m of at least one spill site. X-axis is capped at pooled p95; dashed line marks the area of a 250m-radius circle."
#| fig-width: 8
#| fig-height: 4.8
lsoa_area_dist_plot |>
  dplyr::filter(sample == "Sales") |>
  ggplot2::ggplot(ggplot2::aes(x = lsoa_area_km2)) +
  ggplot2::geom_histogram(
    bins = area_bins,
    fill = "#2C7FB8",
    color = "white",
    alpha = 0.9
  ) +
  ggplot2::annotate(
    geom = "segment",
    x = buffer_area_km2,
    xend = buffer_area_km2,
    y = 0,
    yend = Inf,
    linetype = "dashed",
    linewidth = 0.7,
    color = "#D55E00"
  ) +
  ggplot2::annotate(
    geom = "text",
    x = buffer_area_km2,
    y = Inf,
    label = "250m radius buffer",
    angle = 0,
    vjust = 1,
    hjust = -0.1,
    size = 3,
    color = "#D55E00"
  ) +
  ggplot2::scale_x_continuous(labels = scales::label_number(accuracy = 0.01)) +
  ggplot2::coord_cartesian(xlim = c(0, area_p95_km2)) +
  ggplot2::labs(
    x = "LSOA area (km^2)",
    y = "Number of LSOAs"
  ) +
  ggplot2::theme_minimal(base_size = 12)
```

```{r}
#| label: fig-lsoa-area-dist-rentals
#| fig-cap: "Rentals: Distribution of LSOA areas (km^2) for LSOAs with at least one rental listing within 250 m of at least one spill site. X-axis is capped at pooled p95; dashed line marks the area of a 250m-radius circle."
#| fig-width: 8
#| fig-height: 4.8
lsoa_area_dist_plot |>
  dplyr::filter(sample == "Rentals") |>
  ggplot2::ggplot(ggplot2::aes(x = lsoa_area_km2)) +
  ggplot2::geom_histogram(
    bins = area_bins,
    fill = "#2C7FB8",
    color = "white",
    alpha = 0.9
  ) +
  ggplot2::annotate(
    geom = "segment",
    x = buffer_area_km2,
    xend = buffer_area_km2,
    y = 0,
    yend = Inf,
    linetype = "dashed",
    linewidth = 0.7,
    color = "#D55E00"
  ) +
  ggplot2::annotate(
    geom = "text",
    x = buffer_area_km2,
    y = Inf,
    label = "250m radius buffer",
    angle = 90,
    vjust = 1.4,
    hjust = -0.1,
    size = 3,
    color = "#D55E00"
  ) +
  ggplot2::scale_x_continuous(labels = scales::label_number(accuracy = 0.01)) +
  ggplot2::coord_cartesian(xlim = c(0, area_p95_km2)) +
  ggplot2::labs(
    x = "LSOA area (km^2)",
    y = "Number of LSOAs"
  ) +
  ggplot2::theme_minimal(base_size = 12)
```

```{r}
#| label: fig-lsoa-obs-dist-sales
#| fig-cap: "Sales: Distribution of observations per LSOA for LSOAs with at least one house within 250 m of at least one spill site. X-axis is capped at pooled p95."
#| fig-width: 8
#| fig-height: 4.8
lsoa_obs_dist_plot |>
  dplyr::filter(sample == "Sales") |>
  ggplot2::ggplot(ggplot2::aes(x = n_obs)) +
  ggplot2::geom_histogram(
    bins = 30,
    fill = "#2C7FB8",
    color = "white",
    alpha = 0.9
  ) +
  ggplot2::scale_x_continuous(labels = scales::label_number()) +
  ggplot2::coord_cartesian(xlim = c(0, obs_p95_n)) +
  ggplot2::labs(
    x = "Observations per LSOA",
    y = "Number of LSOAs"
  ) +
  ggplot2::theme_minimal(base_size = 12)
```

```{r}
#| label: fig-lsoa-obs-dist-rentals
#| fig-cap: "Rentals: Distribution of observations per LSOA in the cleaned 250m sample used for FE specifications. X-axis is capped at pooled p95."
#| fig-width: 8
#| fig-height: 4.8
lsoa_obs_dist_plot |>
  dplyr::filter(sample == "Rentals") |>
  ggplot2::ggplot(ggplot2::aes(x = n_obs)) +
  ggplot2::geom_histogram(
    bins = obs_bins,
    fill = "#2C7FB8",
    color = "white",
    alpha = 0.9
  ) +
  ggplot2::scale_x_continuous(labels = scales::label_number()) +
  ggplot2::coord_cartesian(xlim = c(0, obs_p95_n)) +
  ggplot2::labs(
    x = "Observations per LSOA",
    y = "Number of LSOAs"
  ) +
  ggplot2::theme_minimal(base_size = 12)
```

```{r}
#| label: fig-lsoa-retention-dist-sales
#| fig-cap: "Sales: Stacked distribution of LSOAs by pre-filter size (n_total) at 250m. Bar height is number of LSOAs in each n_total bin; colors split each LSOA into kept vs dropped shares."
#| fig-width: 8
#| fig-height: 4.8
lsoa_retention_counts_long_plot |>
  dplyr::filter(sample == "Sales") |>
  ggplot2::ggplot(
    ggplot2::aes(x = n_total, weight = lsoa_weight_component, fill = status)
  ) +
  ggplot2::geom_histogram(
    bins = retention_bins,
    color = "white",
    alpha = 0.9,
    boundary = 0,
    position = ggplot2::position_stack(reverse = TRUE)
  ) +
  ggplot2::scale_fill_manual(
    values = c(
      "Kept (>0 spill site)" = "#2A9D8F",
      "Dropped (0 spill sites)" = "#E76F51"
    ),
    breaks = c(
      "Kept (>0 spill site)",
      "Dropped (0 spill sites)"
    )
  ) +
  ggplot2::scale_x_continuous(
    limits = c(0, retention_total_p99_n),
    breaks = scales::breaks_pretty(n = 6),
    labels = scales::label_number()
  ) +
  ggplot2::labs(
    x = "Total observations per LSOA (Kept + Dropped)",
    y = "Number of LSOAs",
    fill = NULL
  ) +
  ggplot2::theme_minimal(base_size = 12)
```

```{r}
#| label: fig-lsoa-retention-dist-rentals
#| fig-cap: "Rentals: Stacked distribution of LSOAs by pre-filter size (n_total) at 250m. Bar height is number of LSOAs in each n_total bin; colors split each LSOA into kept vs dropped shares."
#| fig-width: 8
#| fig-height: 4.8
lsoa_retention_counts_long_plot |>
  dplyr::filter(sample == "Rentals") |>
  ggplot2::ggplot(
    ggplot2::aes(x = n_total, weight = lsoa_weight_component, fill = status)
  ) +
  ggplot2::geom_histogram(
    bins = retention_bins,
    color = "white",
    alpha = 0.9,
    boundary = 0,
    position = ggplot2::position_stack(reverse = TRUE)
  ) +
  ggplot2::scale_fill_manual(
    values = c(
      "Kept (>0 spill site)" = "#2A9D8F",
      "Dropped (0 spill sites)" = "#E76F51"
    ),
    breaks = c(
      "Kept (>0 spill site)",
      "Dropped (0 spill sites)"
    )
  ) +
  ggplot2::scale_x_continuous(
    limits = c(0, retention_total_p99_n),
    breaks = scales::breaks_pretty(n = 6),
    labels = scales::label_number()
  ) +
  ggplot2::labs(
    x = "Total observations per LSOA (Kept + Dropped)",
    y = "Number of LSOAs",
    fill = NULL
  ) +
  ggplot2::theme_minimal(base_size = 12)
```

## Sales Table (LSOA FE)

```{r}
sales_table_lsoa <- format_results(sales_results_lsoa, fe_label = "LSOA FE")
make_styled_table(
  sales_table_lsoa,
  "Sales: Residual Spill-Count Variation Share (LSOA FE)",
  fe_label = "LSOA FE"
)
```

## Rentals Table (LSOA FE)

```{r}
rental_table_lsoa <- format_results(rental_results_lsoa, fe_label = "LSOA FE")
make_styled_table(
  rental_table_lsoa,
  "Rentals: Residual Spill-Count Variation Share (LSOA FE)",
  fe_label = "LSOA FE"
)
```

## Sales Table (MSOA FE)

```{r}
sales_table_msoa <- format_results(sales_results_msoa, fe_label = "MSOA FE")
make_styled_table(
  sales_table_msoa,
  "Sales: Residual Spill-Count Variation Share (MSOA FE)",
  fe_label = "MSOA FE"
)
```

## Rentals Table (MSOA FE)

```{r}
rental_table_msoa <- format_results(rental_results_msoa, fe_label = "MSOA FE")
make_styled_table(
  rental_table_msoa,
  "Rentals: Residual Spill-Count Variation Share (MSOA FE)",
  fe_label = "MSOA FE"
)
```

## Load and Prepare Upstream/Downstream Data

```{r}
dat_cs_sales_site <- arrow::open_dataset(
  here::here(
    "data",
    "processed",
    "cross_section",
    "sales",
    "prior_to_sale",
    "house_site"
  )
) |>
  dplyr::filter(radius == RAD) |>
  dplyr::collect()

dat_cs_rentals_site <- arrow::open_dataset(
  here::here(
    "data",
    "processed",
    "cross_section",
    "rentals",
    "prior_to_rental",
    "rental_site"
  )
) |>
  dplyr::filter(radius == RAD) |>
  dplyr::collect()

upstream_downstream_sales <- rio::import(
  here::here(
    "upstream_downstream",
    "output",
    "03-02",
    "river_filter",
    "spill_house_signed_with_lateral.csv"
  )
) |>
  dplyr::mutate(
    direction = ifelse(direction == -1, 1, 0),
    direction = factor(
      direction,
      levels = c(1, 0),
      labels = c("Upstream", "Downstream")
    ),
    dist_river_m = abs(signed_dist_m)
  ) |>
  dplyr::filter(
    spill_lateral_m < RAD,
    house_lateral_m < RAD,
    dist_river_m < 1000
  )

upstream_downstream_rentals <- rio::import(
  here::here(
    "upstream_downstream",
    "output",
    "03-02",
    "river_filter",
    "spill_rental_signed_with_lateral.csv"
  )
) |>
  dplyr::mutate(
    direction = ifelse(direction == -1, 1, 0),
    direction = factor(
      direction,
      levels = c(1, 0),
      labels = c("Upstream", "Downstream")
    ),
    dist_river_m = abs(signed_dist_m)
  ) |>
  dplyr::filter(
    spill_lateral_m < RAD,
    rental_lateral_m < RAD,
    dist_river_m < 1000
  )

dat_sales_direction_clean <- dat_cs_sales_site |>
  dplyr::select(-dplyr::any_of("price")) |>
  dplyr::inner_join(sales, by = "house_id") |>
  dplyr::inner_join(upstream_downstream_sales, by = c("house_id", "site_id")) |>
  dplyr::filter(
    !is.na(spill_count_daily_avg),
    !is.na(lsoa),
    !is.na(msoa),
    !is.na(property_type),
    !is.na(old_new),
    !is.na(duration),
    !is.na(month_id),
    !is.na(direction)
  ) |>
  dplyr::mutate(
    lsoa = forcats::fct_drop(forcats::as_factor(lsoa)),
    msoa = forcats::fct_drop(forcats::as_factor(msoa)),
    property_type = forcats::fct_drop(forcats::as_factor(property_type)),
    old_new = forcats::fct_drop(forcats::as_factor(old_new)),
    duration = forcats::fct_drop(forcats::as_factor(duration)),
    month_id = forcats::fct_drop(forcats::as_factor(month_id))
  )

dat_rental_direction_clean <- dat_cs_rentals_site |>
  dplyr::select(-dplyr::any_of("listing_price")) |>
  dplyr::inner_join(rentals, by = "rental_id") |>
  dplyr::inner_join(
    upstream_downstream_rentals,
    by = c("rental_id", "site_id")
  ) |>
  dplyr::filter(
    !is.na(spill_count_daily_avg),
    !is.na(lsoa),
    !is.na(msoa),
    !is.na(property_type),
    !is.na(bedrooms),
    !is.na(bathrooms),
    !is.na(month_id),
    !is.na(direction)
  ) |>
  dplyr::mutate(
    lsoa = forcats::fct_drop(forcats::as_factor(lsoa)),
    msoa = forcats::fct_drop(forcats::as_factor(msoa)),
    property_type = forcats::fct_drop(forcats::as_factor(property_type)),
    month_id = forcats::fct_drop(forcats::as_factor(month_id))
  )

alpha <- 1

dat_exposure_sales <- dat_sales_direction_clean |>
  dplyr::group_by(house_id) |>
  dplyr::mutate(
    inv_dist_weight_raw = (dist_river_m + 0.01)^(-alpha)
  ) |>
  dplyr::summarise(
    upstream_count = sum(
      spill_count_daily_avg * (direction == "Upstream"),
      na.rm = TRUE
    ),
    downstream_count = sum(
      spill_count_daily_avg * (direction == "Downstream"),
      na.rm = TRUE
    ),
    upstream_count_exposure = sum(
      inv_dist_weight_raw * spill_count_daily_avg * (direction == "Upstream"),
      na.rm = TRUE
    ),
    downstream_count_exposure = sum(
      inv_dist_weight_raw * spill_count_daily_avg * (direction == "Downstream"),
      na.rm = TRUE
    ),
    .groups = "drop"
  ) |>
  dplyr::inner_join(
    sales |>
      dplyr::select(
        house_id,
        lsoa,
        msoa,
        month_id,
        property_type,
        old_new,
        duration
      ),
    by = "house_id"
  ) |>
  dplyr::filter(
    !is.na(lsoa),
    !is.na(msoa),
    !is.na(month_id),
    !is.na(property_type),
    !is.na(old_new),
    !is.na(duration)
  ) |>
  dplyr::mutate(
    lsoa = forcats::fct_drop(forcats::as_factor(lsoa)),
    msoa = forcats::fct_drop(forcats::as_factor(msoa)),
    property_type = forcats::fct_drop(forcats::as_factor(property_type)),
    old_new = forcats::fct_drop(forcats::as_factor(old_new)),
    duration = forcats::fct_drop(forcats::as_factor(duration)),
    month_id = forcats::fct_drop(forcats::as_factor(month_id))
  )

dat_exposure_rentals <- dat_rental_direction_clean |>
  dplyr::group_by(rental_id) |>
  dplyr::mutate(
    inv_dist_weight_raw = (dist_river_m + 0.01)^(-alpha)
  ) |>
  dplyr::summarise(
    upstream_count = sum(
      spill_count_daily_avg * (direction == "Upstream"),
      na.rm = TRUE
    ),
    downstream_count = sum(
      spill_count_daily_avg * (direction == "Downstream"),
      na.rm = TRUE
    ),
    upstream_count_exposure = sum(
      inv_dist_weight_raw * spill_count_daily_avg * (direction == "Upstream"),
      na.rm = TRUE
    ),
    downstream_count_exposure = sum(
      inv_dist_weight_raw * spill_count_daily_avg * (direction == "Downstream"),
      na.rm = TRUE
    ),
    .groups = "drop"
  ) |>
  dplyr::inner_join(
    rentals |>
      dplyr::select(
        rental_id,
        lsoa,
        msoa,
        month_id,
        property_type,
        bedrooms,
        bathrooms
      ),
    by = "rental_id"
  ) |>
  dplyr::filter(
    !is.na(lsoa),
    !is.na(msoa),
    !is.na(month_id),
    !is.na(property_type),
    !is.na(bedrooms),
    !is.na(bathrooms)
  ) |>
  dplyr::mutate(
    lsoa = forcats::fct_drop(forcats::as_factor(lsoa)),
    msoa = forcats::fct_drop(forcats::as_factor(msoa)),
    property_type = forcats::fct_drop(forcats::as_factor(property_type)),
    month_id = forcats::fct_drop(forcats::as_factor(month_id))
  )

cat(
  "Sales directional house-site pairs:",
  nrow(dat_sales_direction_clean),
  "\n"
)
cat(
  "Rental directional rental-site pairs:",
  nrow(dat_rental_direction_clean),
  "\n"
)
cat("Sales directional exposure observations:", nrow(dat_exposure_sales), "\n")
cat(
  "Rental directional exposure observations:",
  nrow(dat_exposure_rentals),
  "\n"
)
```

## Compute Upstream/Downstream Residual Variation Shares

```{r}
sales_direction_unweighted_lsoa <- run_direction_panel(
  data = dat_exposure_sales,
  panel_label = "Sales",
  variant_label = "Unweighted count",
  controls_terms = "property_type + old_new + duration",
  spec_prefix = "S",
  upstream_var = "upstream_count",
  downstream_var = "downstream_count",
  fe_var = "lsoa"
)

sales_direction_weighted_lsoa <- run_direction_panel(
  data = dat_exposure_sales,
  panel_label = "Sales",
  variant_label = "Distance-weighted count",
  controls_terms = "property_type + old_new + duration",
  spec_prefix = "S",
  upstream_var = "upstream_count_exposure",
  downstream_var = "downstream_count_exposure",
  fe_var = "lsoa"
)

rental_direction_unweighted_lsoa <- run_direction_panel(
  data = dat_exposure_rentals,
  panel_label = "Rentals",
  variant_label = "Unweighted count",
  controls_terms = "property_type + bedrooms + bathrooms",
  spec_prefix = "R",
  upstream_var = "upstream_count",
  downstream_var = "downstream_count",
  fe_var = "lsoa"
)

rental_direction_weighted_lsoa <- run_direction_panel(
  data = dat_exposure_rentals,
  panel_label = "Rentals",
  variant_label = "Distance-weighted count",
  controls_terms = "property_type + bedrooms + bathrooms",
  spec_prefix = "R",
  upstream_var = "upstream_count_exposure",
  downstream_var = "downstream_count_exposure",
  fe_var = "lsoa"
)

sales_direction_unweighted_msoa <- run_direction_panel(
  data = dat_exposure_sales,
  panel_label = "Sales",
  variant_label = "Unweighted count",
  controls_terms = "property_type + old_new + duration",
  spec_prefix = "S",
  upstream_var = "upstream_count",
  downstream_var = "downstream_count",
  fe_var = "msoa"
)

sales_direction_weighted_msoa <- run_direction_panel(
  data = dat_exposure_sales,
  panel_label = "Sales",
  variant_label = "Distance-weighted count",
  controls_terms = "property_type + old_new + duration",
  spec_prefix = "S",
  upstream_var = "upstream_count_exposure",
  downstream_var = "downstream_count_exposure",
  fe_var = "msoa"
)

rental_direction_unweighted_msoa <- run_direction_panel(
  data = dat_exposure_rentals,
  panel_label = "Rentals",
  variant_label = "Unweighted count",
  controls_terms = "property_type + bedrooms + bathrooms",
  spec_prefix = "R",
  upstream_var = "upstream_count",
  downstream_var = "downstream_count",
  fe_var = "msoa"
)

rental_direction_weighted_msoa <- run_direction_panel(
  data = dat_exposure_rentals,
  panel_label = "Rentals",
  variant_label = "Distance-weighted count",
  controls_terms = "property_type + bedrooms + bathrooms",
  spec_prefix = "R",
  upstream_var = "upstream_count_exposure",
  downstream_var = "downstream_count_exposure",
  fe_var = "msoa"
)

all_direction_results <- dplyr::bind_rows(
  dplyr::mutate(sales_direction_unweighted_lsoa, geo_fe = "lsoa"),
  dplyr::mutate(sales_direction_weighted_lsoa, geo_fe = "lsoa"),
  dplyr::mutate(rental_direction_unweighted_lsoa, geo_fe = "lsoa"),
  dplyr::mutate(rental_direction_weighted_lsoa, geo_fe = "lsoa"),
  dplyr::mutate(sales_direction_unweighted_msoa, geo_fe = "msoa"),
  dplyr::mutate(sales_direction_weighted_msoa, geo_fe = "msoa"),
  dplyr::mutate(rental_direction_unweighted_msoa, geo_fe = "msoa"),
  dplyr::mutate(rental_direction_weighted_msoa, geo_fe = "msoa")
)
```

## Directional Table Helpers

```{r}
format_direction_results <- function(df, fe_label) {
  obs_check <- df |>
    dplyr::group_by(spec_id) |>
    dplyr::summarise(obs_unique = dplyr::n_distinct(n), .groups = "drop")

  if (any(obs_check$obs_unique > 1L)) {
    warning(
      "Observation counts differ between upstream and downstream models for some specifications."
    )
  }

  spec_meta <- df |>
    dplyr::group_by(spec_id, spec_num, lsoa_fe, month_fe, property_controls) |>
    dplyr::summarise(Observations = dplyr::first(n), .groups = "drop")

  share_wide <- df |>
    dplyr::mutate(
      variable = paste0("Residual variation share (", variable, ")")
    ) |>
    dplyr::select(spec_id, variable, residual_share) |>
    tidyr::pivot_wider(names_from = variable, values_from = residual_share)

  out <- spec_meta |>
    dplyr::left_join(share_wide, by = "spec_id") |>
    dplyr::arrange(spec_num) |>
    dplyr::transmute(
      Specification = spec_id,
      fe_status = dplyr::if_else(lsoa_fe, "Yes", "No"),
      `Month FE` = dplyr::if_else(month_fe, "Yes", "No"),
      `Property controls` = dplyr::if_else(property_controls, "Yes", "No"),
      Observations = Observations,
      `Residual variation share (Upstream)` = `Residual variation share (Upstream)`,
      `Residual variation share (Downstream)` = `Residual variation share (Downstream)`
    )

  names(out)[names(out) == "fe_status"] <- fe_label
  out
}

make_direction_styled_table <- function(df, title, fe_label) {
  gt::gt(df) |>
    gt::tab_header(title = gt::md(paste0("**", title, "**"))) |>
    gt::cols_align(
      align = "center",
      columns = tidyselect::all_of(c(fe_label, "Month FE", "Property controls"))
    ) |>
    gt::cols_align(
      align = "right",
      columns = c(
        Observations,
        `Residual variation share (Upstream)`,
        `Residual variation share (Downstream)`
      )
    ) |>
    gt::fmt_integer(columns = c(Observations), sep_mark = ",") |>
    gt::fmt_number(
      columns = c(
        `Residual variation share (Upstream)`,
        `Residual variation share (Downstream)`
      ),
      decimals = 3
    ) |>
    gt::opt_row_striping() |>
    gt::tab_options(
      table.width = gt::pct(100),
      data_row.padding = gt::px(5),
      column_labels.font.weight = "bold",
      column_labels.font.size = gt::px(12),
      table.font.size = gt::px(12)
    )
}
```

## Upstream/Downstream Tables: Unweighted Count (LSOA FE)

### Sales Table

```{r}
sales_direction_unweighted_table_lsoa <- format_direction_results(
  sales_direction_unweighted_lsoa,
  fe_label = "LSOA FE"
)
make_direction_styled_table(
  sales_direction_unweighted_table_lsoa,
  "Sales: Upstream/Downstream Residual Spill-Count Variation Shares (Unweighted, LSOA FE)",
  fe_label = "LSOA FE"
)
```

### Rentals Table

```{r}
rental_direction_unweighted_table_lsoa <- format_direction_results(
  rental_direction_unweighted_lsoa,
  fe_label = "LSOA FE"
)
make_direction_styled_table(
  rental_direction_unweighted_table_lsoa,
  "Rentals: Upstream/Downstream Residual Spill-Count Variation Shares (Unweighted, LSOA FE)",
  fe_label = "LSOA FE"
)
```

## Upstream/Downstream Tables: Distance-Weighted Count (LSOA FE)

### Sales Table

```{r}
sales_direction_weighted_table_lsoa <- format_direction_results(
  sales_direction_weighted_lsoa,
  fe_label = "LSOA FE"
)
make_direction_styled_table(
  sales_direction_weighted_table_lsoa,
  "Sales: Upstream/Downstream Residual Spill-Count Variation Shares (Distance-Weighted, LSOA FE)",
  fe_label = "LSOA FE"
)
```

### Rentals Table

```{r}
rental_direction_weighted_table_lsoa <- format_direction_results(
  rental_direction_weighted_lsoa,
  fe_label = "LSOA FE"
)
make_direction_styled_table(
  rental_direction_weighted_table_lsoa,
  "Rentals: Upstream/Downstream Residual Spill-Count Variation Shares (Distance-Weighted, LSOA FE)",
  fe_label = "LSOA FE"
)
```

## Upstream/Downstream Tables: Unweighted Count (MSOA FE)

### Sales Table

```{r}
sales_direction_unweighted_table_msoa <- format_direction_results(
  sales_direction_unweighted_msoa,
  fe_label = "MSOA FE"
)
make_direction_styled_table(
  sales_direction_unweighted_table_msoa,
  "Sales: Upstream/Downstream Residual Spill-Count Variation Shares (Unweighted, MSOA FE)",
  fe_label = "MSOA FE"
)
```

### Rentals Table

```{r}
rental_direction_unweighted_table_msoa <- format_direction_results(
  rental_direction_unweighted_msoa,
  fe_label = "MSOA FE"
)
make_direction_styled_table(
  rental_direction_unweighted_table_msoa,
  "Rentals: Upstream/Downstream Residual Spill-Count Variation Shares (Unweighted, MSOA FE)",
  fe_label = "MSOA FE"
)
```

## Upstream/Downstream Tables: Distance-Weighted Count (MSOA FE)

### Sales Table

```{r}
sales_direction_weighted_table_msoa <- format_direction_results(
  sales_direction_weighted_msoa,
  fe_label = "MSOA FE"
)
make_direction_styled_table(
  sales_direction_weighted_table_msoa,
  "Sales: Upstream/Downstream Residual Spill-Count Variation Shares (Distance-Weighted, MSOA FE)",
  fe_label = "MSOA FE"
)
```

### Rentals Table

```{r}
rental_direction_weighted_table_msoa <- format_direction_results(
  rental_direction_weighted_msoa,
  fe_label = "MSOA FE"
)
make_direction_styled_table(
  rental_direction_weighted_table_msoa,
  "Rentals: Upstream/Downstream Residual Spill-Count Variation Shares (Distance-Weighted, MSOA FE)",
  fe_label = "MSOA FE"
)
```
