## Introduction

Matching unique spill sites across 2021-2024.
- 2024: `unique_id`
- 2023: `unique_id` (matches `unique_id_2023` in 2024 data for non-WW; NA for WW)
- 2021-2022: No reliable unique IDs; use composite keys.

**Goal:** Consolidated lookup table: `primary_id_2024`, `primary_id_2023`, `primary_id_2022` (composite), `primary_id_2021` (composite).

## Setup and Data Preparation

Load packages and configure environment.
```{r setup}
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  "tidyverse", "arrow", "stringr", "stringdist", "fastLink", "reclin2",
  "pbapply", "rnrfa", "sf", "here", "ranger", "speedglm", "conflicted",
  "igraph"
)

# Configuration
YEARS <- 2021:2024
DATA_PATH <- here("data", "processed", "annual_return_edm.parquet")
CORE_IDENTIFIER_COLS <- c(
  "year", "water_company",
  "site_name_ea", "site_name_wa_sc",
  "permit_reference_ea", "permit_reference_wa_sc",
  "activity_reference",
  "outlet_discharge_ngr"
)

conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("first", "dplyr")
```

Load and prepare data by year.
```{r load_data}
# Load and prepare data by year
full_data <- arrow::read_parquet(DATA_PATH)

data_list <- lapply(YEARS, function(yr) {
  df <- filter(full_data, year == yr)

  # Create primary_id for 2024
  if (yr == 2024 && "unique_id" %in% names(df)) {
    df <- df %>%
      mutate(primary_id = unique_id)
  }

  # Handle 2023 unique IDs
  if (yr == 2023 && "unique_id" %in% names(df)) {
    df <- df %>%
      mutate(unique_id_2023 = unique_id)
  }

  # Select base columns
  year_site_id <- paste0("site_id_", yr)
  df <- df %>%
    select(any_of(
      c(
        "primary_id", "unique_id", "unique_id_2023", CORE_IDENTIFIER_COLS,
        year_site_id
      )
    ))

  return(df)
})

names(data_list) <- paste0("df", YEARS)
data_list$df2021
```


## Windfall Matching

### Windfall Matching Functions

Define function to perform windfall matching. The function takes as input the left and right data frames, the join keys, and the suffixes for the left and right data frames. It returns a list of three data frames: the joined data frame, the left-only data frame, and the right-only data frame.

```{r matching_functions}
f_outer_join <- function(df_left, df_right, join_keys,
                         suffix_left = "_left", suffix_right = "_right") {
  df_left <- mutate(df_left, ..rowid_left = row_number())
  df_right <- mutate(df_right, ..rowid_right = row_number())

  joined_df <- full_join(df_left, df_right,
    by = join_keys, suffix = c(suffix_left, suffix_right),
    multiple = "all", na_matches = "never"
  ) %>% suppressWarnings()

  joined_df <- joined_df %>%
    mutate(join_origin = case_when(
      !is.na(..rowid_left) & is.na(..rowid_right) ~ "left_only",
      is.na(..rowid_left) & !is.na(..rowid_right) ~ "right_only",
      !is.na(..rowid_left) & !is.na(..rowid_right) ~ "matched",
      TRUE ~ NA_character_
    ))

  matched_rows <- filter(joined_df, join_origin == "matched")

  if (nrow(matched_rows) > 0) {
    match_results <- matched_rows %>%
      group_by(across(all_of(join_keys))) %>%
      summarise(
        n_left = n_distinct(..rowid_left),
        n_right = n_distinct(..rowid_right),
        .groups = "drop"
      ) %>%
      mutate(match_type = case_when(
        n_left == 1 & n_right == 1 ~ "1_to_1",
        n_left == 1 ~ "1_to_many",
        n_right == 1 ~ "many_to_1",
        TRUE ~ "many_to_many"
      ))

    joined_df <- left_join(joined_df,
      select(match_results, all_of(join_keys), match_type),
      by = join_keys, na_matches = "never"
    )

    problem_keys <- filter(match_results, match_type != "1_to_1") %>%
      select(all_of(join_keys))
  } else {
    joined_df <- mutate(joined_df, match_type = NA_character_)
    problem_keys <- data.frame()
  }

  get_problem_ids <- function(side) {
    unmatched_ids <- joined_df %>%
      filter(join_origin == paste0(side, "_only")) %>%
      pull(!!sym(paste0("..rowid_", side)))

    matched_problem_ids <- if (nrow(problem_keys) > 0) {
      matched_rows %>%
        semi_join(problem_keys, by = join_keys) %>%
        pull(!!sym(paste0("..rowid_", side))) %>%
        unique()
    } else {
      integer(0)
    }

    base::union(unmatched_ids, matched_problem_ids)
  }

  problem_left_ids <- get_problem_ids("left")
  problem_right_ids <- get_problem_ids("right")

  problem_left_df <- slice(df_left, sort(problem_left_ids)) %>%
    select(-any_of("..rowid_left"))
  problem_right_df <- slice(df_right, sort(problem_right_ids)) %>%
    select(-any_of("..rowid_right"))

  final_joined_df <- joined_df %>%
    mutate(
      join_keys = if_else(
        join_origin == "matched" &
          match_type %in% c("1_to_1", "1_to_many", "many_to_1"),
        paste0(join_keys, collapse = "|"),
        NA_character_
      )
    ) %>%
    select(-c(..rowid_left, ..rowid_right))

  return(list(
    joined_data = final_joined_df,
    non_1_to_1_matched_left = problem_left_df,
    non_1_to_1_matched_right = problem_right_df
  ))
}
```

Define function to perform windfall matching. The function takes as input the pair key, the matching levels, the data list, and a verbose flag. It returns a list of three data frames: the joined data frame, the left-only data frame, and the right-only data frame.

```{r}
# Windfall matching function - simplified to work directly with data_list
perform_windfall_matching <- function(
    pair_key, matching_levels, data_list, verbose = FALSE) {
  years <- as.numeric(unlist(strsplit(pair_key, "_")))
  left_year <- years[1]
  right_year <- years[2]

  # Use full years for variable names
  year_suffix <- paste0(left_year, "_", right_year)

  df_left <- data_list[[paste0("df", left_year)]]
  df_right <- data_list[[paste0("df", right_year)]]

  left_remaining <- df_left
  right_remaining <- df_right
  all_matches <- list()

  for (level in seq_along(matching_levels)) {
    join_keys <- c("water_company", matching_levels[[level]])

    match_res <- f_outer_join(
      df_left = left_remaining,
      df_right = right_remaining,
      join_keys = join_keys,
      suffix_left = paste0("_", left_year),
      suffix_right = paste0("_", right_year)
    )

    matches <- match_res$joined_data %>%
      filter(join_origin == "matched", match_type == "1_to_1") %>%
      mutate(!!paste0("match_level_", year_suffix) := level)

    all_matches[[level]] <- matches
    left_remaining <- match_res$non_1_to_1_matched_left
    right_remaining <- match_res$non_1_to_1_matched_right

    if (verbose) {
      cat(sprintf("%s Level %d: Matched %d rows\n", pair_key, level, nrow(matches)))
    }
  }

  combined_matches <- bind_rows(all_matches) %>%
    mutate(!!paste0("match_method_", year_suffix) := "windfall") %>%
    rename(
      !!paste0("match_type_", year_suffix) := match_type,
      !!paste0("join_keys_", year_suffix) := join_keys
    ) %>%
    select(
      !!sym(paste0("site_id_", right_year)),
      !!sym(paste0("site_id_", left_year)),
      starts_with(paste0("match_level_", year_suffix)),
      starts_with(paste0("match_method_", year_suffix)),
      starts_with(paste0("match_type_", year_suffix)),
      starts_with(paste0("join_keys_", year_suffix))
    )

  return(list(
    matches = combined_matches,
    unmatched_left_ids = pull(left_remaining, !!sym(paste0("site_id_", left_year))),
    unmatched_right_ids = pull(right_remaining, !!sym(paste0("site_id_", right_year)))
  ))
}
```

### Matching Configuration

Define matching configurations.

```{r matching_config}
# Generate all variable combinations for matching
vars <- c(
  "site_name_ea", "site_name_wa_sc",
  "permit_reference_ea", "permit_reference_wa_sc",
  "activity_reference", "outlet_discharge_ngr"
)

# Generate all variable combinations for windfall matching
var_list <- unlist(
  lapply(1:length(vars), function(i) combn(vars, i, simplify = FALSE)),
  recursive = FALSE
) %>%
  {
    \(x) x[order(sapply(x, length), decreasing = TRUE)]
  }()

# Matching configurations
config_general <- var_list
config_2023_2024 <- c(list(c("unique_id_2023")), config_general)

# Generate all year pairs to match
year_pairs <- expand.grid(
  left_year = YEARS,
  right_year = YEARS,
  stringsAsFactors = FALSE
) %>%
  filter(left_year < right_year) %>%
  arrange(desc(right_year), desc(left_year))
```

### Run Matching Process

Define function to run all matches. The function takes as input the year pairs, the data list, and a verbose flag. It returns a list of joined data frames.

```{r run_matching}
run_all_matches <- function(year_pairs, data_list, verbose = FALSE) {
  # Generate pair keys
  pair_keys <- apply(year_pairs, 1, function(x) paste(x[1], x[2], sep = "_"))

  # Get configs for all pairs
  configs <- lapply(seq_along(pair_keys), function(i) {
    left_year <- year_pairs$left_year[i]
    right_year <- year_pairs$right_year[i]

    if (left_year == 2023 && right_year == 2024) {
      return(config_2023_2024)
    } else {
      return(config_general)
    }
  })
  names(configs) <- pair_keys

  # Run matches in parallel over pair keys
  match_results <- lapply(pair_keys, function(pair_key) {
    perform_windfall_matching(
      pair_key = pair_key,
      matching_levels = configs[[pair_key]],
      data_list = data_list,
      verbose = verbose
    )
  })
  names(match_results) <- pair_keys

  match_dataframes <- lapply(match_results, function(x) x$matches)
  return(match_dataframes)
}

# Execute matching more concisely
match_dataframes <- run_all_matches(year_pairs, data_list, verbose = FALSE)
```

### Create Lookup Table

We use graph theory to create a consolidated lookup table. In particular, we use the minimum spanning tree (MST) to create a consolidated lookup table. The MST is a tree that connects all the nodes with the minimum possible total edge weight. In this case, the edge weight is the number of join keys (proxy for match quality).

```{r}
## --- Build a year‑aware edge list ---
edges_df <- lapply(match_dataframes, function(df) {
  site_cols <- grep("^site_id_", names(df), value = TRUE)
  match_method_col <- grep("^match_method_", names(df), value = TRUE)
  match_type_col <- grep("^match_type_", names(df), value = TRUE)
  level_col <- grep("^match_level_", names(df), value = TRUE)
  join_keys_col <- grep("^join_keys_", names(df), value = TRUE)

  yr_l <- str_extract(site_cols[1], "\\d{4}$")
  yr_r <- str_extract(site_cols[2], "\\d{4}$")

  df %>%
    filter(!is.na(.data[[join_keys_col]])) %>%
    transmute(
      from = paste0(yr_l, "_", .data[[site_cols[1]]]),
      to = paste0(yr_r, "_", .data[[site_cols[2]]]),
      match_method = .data[[match_method_col]],
      match_type = .data[[match_type_col]],
      match_level = as.integer(.data[[level_col]]),
      join_keys = .data[[join_keys_col]]
    ) %>%
    filter(from != "", to != "")
}) %>%
  bind_rows() %>%
  distinct()

### --- Compute weights ---

# Compute number of join keys (proxy for match quality)
edges_df <- edges_df %>%
  mutate(n_keys = str_count(join_keys, "\\|") + 1)
max_keys <- max(edges_df$n_keys, na.rm = TRUE)

# Build weighting measure
# unique_id edges get max weight, otherwise weight is number of join keys
# tiebreak on match_level (1 is best), so subtract it
edges_df <- edges_df %>%
  mutate(
    raw_score = if_else(
      str_detect(join_keys, "unique_id"),
      max_keys + 1,
      n_keys
    ),
    weight = raw_score * 100 - match_level
  )

## --- Create graph and components ---
g <- graph_from_data_frame(edges_df, directed = FALSE)
g_mst <- mst(g, weights = -E(g)$weight)
comps_mst <- components(g_mst)


## --- Recover raw site_id and year from vertex names ---
membership_mst <- tibble(
  vertex    = names(comps_mst$membership),
  component = comps_mst$membership
) %>%
  mutate(
    year    = str_extract(vertex, "^\\d{4}"),
    site_id = str_remove(vertex, "^\\d{4}_")
  )

## --- Assemble final cross‑year lookup table ---
lookup_table <- membership_mst %>%
  group_by(component, year) %>%
  summarise(site_id = first(site_id), .groups = "drop") %>%
  pivot_wider(
    names_from   = year,
    values_from  = site_id,
    names_prefix = "site_id_",
    values_fill  = NA_character_
  ) %>%
  select(site_id_2021, site_id_2022, site_id_2023, site_id_2024)

## --- Edge metadata from the minimum‑spanning tree --------------------------
edge_metadata <- igraph::as_data_frame(g_mst, what = "edges") %>%
  mutate(
    component     = comps_mst$membership[from],
    year_from     = str_extract(from, "^\\d{4}"),
    site_id_from  = str_remove(from, "^\\d{4}_"),
    year_to       = str_extract(to, "^\\d{4}"),
    site_id_to    = str_remove(to, "^\\d{4}_")
  ) %>%
  select(
    component,
    year_from, site_id_from,
    year_to, site_id_to,
    match_method, match_type, match_level, join_keys, weight
  ) %>%
  as_tibble()
```

We then use the lookup table to analyse coverage.

```{r analyze_results}
# Create clean year names for analysis
year_names <- gsub("df", "", names(total_records_by_year))

match_coverage <- data.frame(
  year = year_names,
  total_records = unname(total_records_by_year),
  matched_records = matched_records_by_year[year_names],
  stringsAsFactors = FALSE
) %>%
  mutate(coverage_pct = round(matched_records / total_records * 100, 1))

match_coverage
```


## Fuzzy Matching using Reclin2 and Random Forest

### Define Comparator Function

```{r}
# Helper function for Jaro-Winkler (JW) comparison with NA handling
# Returns -1 if both inputs NA, -2 if one input NA, otherwise JW score.
jaro_winkler_na <- function(threshold = 0.85, na_placeholder = "") {
  SCORE_BOTH_NA <- -1L
  SCORE_ONE_NA <- -2L
  base_comparator <- reclin2::cmp_jarowinkler(threshold = threshold)

  function(x, y) {
    is_na_x <- is.na(x) | x == na_placeholder
    is_na_y <- is.na(y) | y == na_placeholder

    scores <- ifelse(
      is_na_x & is_na_y, SCORE_BOTH_NA,
      ifelse(is_na_x | is_na_y, SCORE_ONE_NA, base_comparator(x, y))
    )
    return(scores)
  }
}
```

### Train Model on 2024-2023 using Windfall Matches

Train the Random Forest model using the windfall matches between 2023-2024 
datasets as training data. The model will be used to predict matches for 
unmatched records.

```{r, use-rf-train-function}
# Function to train a Random Forest model for record linkage using reclin2 framework.
train_rf_linkage_model <- function(
    df_left, df_right, # Dataframes to match (e.g., df2023, df2024)
    known_matches, # Dataframe with known matches
    match_vars = c( # Variables used for comparison vectors
      "site_name_ea", "site_name_wa_sc", "permit_reference_ea",
      "permit_reference_wa_sc", "activity_reference", "outlet_discharge_ngr"
    ),
    blocking_var = "water_company", # Variable for blocking pairs
    comparators_list = NULL, # Optional custom reclin2 comparators
    default_threshold = 0.85, # Default threshold for string comparisons if not specified
    model_file = NULL, # Optional file path to save model (.rds)
    num_trees = 500, # RF parameter
    max_depth = 8, # RF parameter
    importance = "impurity", # RF parameter
    num_threads = 4, # RF parameter
    probability = TRUE # RF parameter
    ) {
  # --- Input Validation and Setup ---
  # Validate and extract site_id column name and year for left dataframe
  site_id_cols_left <- names(df_left)[startsWith(names(df_left), "site_id_")]
  if (length(site_id_cols_left) != 1) {
    stop(
      "df_left must have exactly one column starting with 'site_id_'"
    )
  }
  site_id_left <- site_id_cols_left[1]
  left_year <- sub("^site_id_", "", site_id_left)

  # Validate and extract site_id column name and year for right dataframe
  site_id_cols_right <- names(df_right)[startsWith(names(df_right), "site_id_")]
  if (length(site_id_cols_right) != 1) {
    stop(
      "df_right must have exactly one column starting with 'site_id_'"
    )
  }
  site_id_right <- site_id_cols_right[1]
  right_year <- sub("^site_id_", "", site_id_right)

  year_suffix <- paste0(left_year, "_", right_year)

  # --- Data Preparation ---
  # Clean specific text values ("TBC") and convert to data.table
  df_left_clean <- df_left %>%
    mutate(across(
      all_of(match_vars),
      ~ if_else(toupper(.) %in% c("TBC", "N/A"), NA_character_, .)
    )) %>%
    as.data.table()

  df_right_clean <- df_right %>%
    mutate(across(
      all_of(match_vars),
      ~ if_else(toupper(.) %in% c("TBC", "N/A"), NA_character_, .)
    )) %>%
    as.data.table()

  # Assign a unique match_id to known matches and join to datasets
  known_matches <- as.data.table(known_matches)[, match_id := .I]
  df_left_clean[known_matches, on = site_id_left, match_id := i.match_id]
  df_right_clean[known_matches, on = site_id_right, match_id := i.match_id]

  # --- Pair Generation and Comparison ---
  # Create candidate pairs using blocking
  pairs <- pair_blocking(df_left_clean, df_right_clean, on = blocking_var, add_xy = TRUE)

  # Define default comparators using the NA-aware Jaro-Winkler function
  if (is.null(comparators_list)) {
    comparators_list <- list(
      site_name_ea = jaro_winkler_na(threshold = 0.89),
      site_name_wa_sc = jaro_winkler_na(threshold = 0.85),
      permit_reference_ea = jaro_winkler_na(threshold = 0.9),
      permit_reference_wa_sc = jaro_winkler_na(threshold = 0.9),
      activity_reference = jaro_winkler_na(threshold = 0.9),
      outlet_discharge_ngr = jaro_winkler_na(threshold = 0.97)
    )
  }
  # Ensure match_id comparator is always included for training label generation
  if (!("match_id" %in% names(comparators_list))) {
    comparators_list$match_id <- reclin2::cmp_identical()
  }

  # Compare candidate pairs based on specified variables
  compare_pairs(
    pairs,
    on = c(match_vars, "match_id"), # Include match_id for comparison result
    default_comparator = jaro_winkler_na(default_threshold),
    comparators = comparators_list,
    inplace = TRUE
  )

  # --- Model Training ---
  # Convert the match_id comparison result into a factor for classification
  pairs[, match_id := factor(
    ifelse(is.na(match_id), 0L, as.integer(match_id > 0)), # Handles pairs not in known_matches
    levels = c(0, 1), labels = c("non_match", "match")
  )]

  # Define formula for Random Forest
  formula_rf <- as.formula(paste("match_id ~", paste(match_vars, collapse = " + ")))

  cat("Training random forest model for", year_suffix, "...\n")
  gc(full = TRUE)
  m_rf <- ranger::ranger(
    formula = formula_rf, data = pairs,
    num.trees = num_trees, max.depth = max_depth,
    probability = probability, importance = importance,
    num.threads = num_threads
  )

  # --- Save and Return Results ---
  # Save model object and metadata if path provided
  if (!is.null(model_file)) {
    dir.create(dirname(model_file), showWarnings = FALSE, recursive = TRUE)
    results_to_save <- list(
      m_rf = m_rf,
      training_info = list(
        left_year = left_year, right_year = right_year,
        num_pairs = nrow(pairs), num_matches = sum(pairs$match_id == "match"),
        match_vars = match_vars, year_suffix = year_suffix,
        training_date = Sys.time()
      )
    )
    saveRDS(results_to_save, model_file)
    cat("Model saved to", model_file, "\n")
  }

  # Return model object, importance scores, and training pairs
  return(list(
    model = m_rf,
    importance = ranger::importance(m_rf),
    training_pairs = pairs, # Useful for diagnostics
    comparison_vars = match_vars,
    year_suffix = year_suffix
  ))
}
```

### Define NGR Cleaning Function

```{r}
# Helper function to clean and standardize NGR values
# Attempts to extract valid NGR strings from potentially messy inputs.
clean_ngr <- function(x) {
  x <- case_when(
    toupper(x) == "UNABLE TO MATCH TO CONSENTS DATABASE" ~ NA_character_,
    toupper(x) == "NOT IN CONSENTS DATABASE" ~ NA_character_,
    TRUE ~ x
  )
  x <- ifelse(stringr::str_detect(x, "(?i)and"), stringr::str_extract(x, "(?i)(?<=and).*"), x)
  x <- stringr::str_replace(x, "(?i)Not.*", "")
  x <- stringr::str_extract(x, "^[^,&/\\(]+")
  x <- stringr::str_remove_all(x, "\\s+")
  return(trimws(x))
}
```

### Random Forest Matching Function

```{r, rf-matching-function}
# Function to apply a trained Random Forest model to find matches
perform_rf_matching <- function(
    df_left, df_right, # Dataframes with records to match
    rf_model, # Trained ranger model object
    match_threshold = 0.5, # Threshold for selecting matches based on predicted probability
    blocking_var = "water_company",
    match_vars = c(
      "site_name_ea", "site_name_wa_sc", "permit_reference_ea",
      "permit_reference_wa_sc", "activity_reference", "outlet_discharge_ngr"
    ),
    comparators_list = NULL,
    default_threshold = 0.85,
    calculate_distances = TRUE # Flag to enable NGR distance calculation
    ) {
  # --- Input Validation and Setup ---
  # Validate and extract site_id column name and year for left dataframe
  site_id_cols_left <- names(df_left)[startsWith(names(df_left), "site_id_")]
  if (length(site_id_cols_left) != 1) {
    stop(
      "df_left must have exactly one column starting with 'site_id_'"
    )
  }
  site_id_left <- site_id_cols_left[1]
  left_year <- sub("^site_id_", "", site_id_left)

  # Validate and extract site_id column name and year for right dataframe
  site_id_cols_right <- names(df_right)[startsWith(names(df_right), "site_id_")]
  if (length(site_id_cols_right) != 1) {
    stop(
      "df_right must have exactly one column starting with 'site_id_'"
    )
  }
  site_id_right <- site_id_cols_right[1]
  right_year <- sub("^site_id_", "", site_id_right)

  year_suffix <- paste0(left_year, "_", right_year)

  # --- Data Preparation ---
  df_left_clean <- df_left %>%
    mutate(
      across(
        all_of(match_vars),
        ~ if_else(toupper(.) %in% c("TBC", "N/A"), NA_character_, .)
      )
    ) %>%
    as.data.table()

  df_right_clean <- df_right %>%
    mutate(
      across(
        all_of(match_vars),
        ~ if_else(toupper(.) %in% c("TBC", "N/A"), NA_character_, .)
      )
    ) %>%
    as.data.table()

  # --- Pair Generation and Comparison ---
  # Create candidate pairs using blocking
  pairs <- pair_blocking(
    df_left_clean, df_right_clean,
    on = blocking_var, add_xy = TRUE
  )

  # If no pairs are generated, return empty results
  if (nrow(pairs) == 0) {
    cat("No candidate pairs found for", year_suffix, "after blocking.\n")
    return(list(
      matches = data.frame(),
      unmatched_left_ids = df_left[[site_id_left]],
      unmatched_right_ids = df_right[[site_id_right]],
      left_remaining = df_left,
      right_remaining = df_right
    ))
  }

  # Define default comparators if needed
  if (is.null(comparators_list)) {
    comparators_list <- list(
      site_name_ea = jaro_winkler_na(threshold = 0.89),
      site_name_wa_sc = jaro_winkler_na(threshold = 0.85),
      permit_reference_ea = jaro_winkler_na(threshold = 0.9),
      permit_reference_wa_sc = jaro_winkler_na(threshold = 0.9),
      activity_reference = jaro_winkler_na(threshold = 0.9),
      outlet_discharge_ngr = jaro_winkler_na(threshold = 0.97)
    )
  }

  # Compare pairs
  compare_pairs(
    pairs,
    on = match_vars,
    default_comparator = jaro_winkler_na(default_threshold),
    comparators = comparators_list, inplace = TRUE
  )

  # --- Prediction and Match Selection ---
  # Apply the RF model to predict match probabilities
  pred <- predict(rf_model, data = pairs)
  match_prob_col <- paste0("match_prob_", year_suffix)
  pairs[, (match_prob_col) := pred$predictions[, "match"]]

  # Select the best 1-to-1 matches above the probability threshold
  selected_var <- paste0("selected_ml_rf_", year_suffix)
  results <- select_n_to_m(
    pairs,
    variable = selected_var, score = match_prob_col,
    threshold = match_threshold, n = 1, m = 1, inplace = FALSE # Explicit 1:1
  )

  # Link selected pairs back to original data attributes
  results <- link(
    results,
    selection = selected_var, all_x = TRUE, all_y = TRUE,
    suffixes = c(paste0("_", left_year), paste0("_", right_year)),
    keep_from_pairs = c(match_prob_col)
  )

  # Extract only the rows representing matches
  matched_results <- results[!is.na(get(site_id_left)) & !is.na(get(site_id_right))]

  # If no matches selected, return early
  if (nrow(matched_results) == 0) {
    cat(
      "No matches found above threshold", match_threshold, "for", year_suffix, ".\n"
    )
    return(list(
      matches = data.frame(),
      unmatched_left_ids = df_left[[site_id_left]],
      unmatched_right_ids = df_right[[site_id_right]],
      left_remaining = df_left,
      right_remaining = df_right
    ))
  }

  # --- Optional: NGR Distance Calculation ---
  if (calculate_distances) {
    ngr_left_col <- paste0("outlet_discharge_ngr_", left_year)
    ngr_right_col <- paste0("outlet_discharge_ngr_", right_year)
    dist_col <- paste0("dist_ngr_", year_suffix) #

    # Check if required NGR columns exist in the matched results
    if (!all(c(ngr_left_col, ngr_right_col) %in% names(matched_results))) {
      cat("NGR columns not found; skipping distance calculation for", year_suffix, ".\n")
    } else {
      # Prepare data for distance calculation: clean, parse, extract coordinates
      coords_to_process <- matched_results %>%
        # 1. Select necessary columns and clean NGRs
        select(
          all_of(c(site_id_left, site_id_right, ngr_left_col, ngr_right_col))
        ) %>%
        mutate(
          ngr_left_clean = clean_ngr(.data[[ngr_left_col]]),
          ngr_right_clean = clean_ngr(.data[[ngr_right_col]])
        ) %>%
        # 2. Filter out rows where cleaned NGRs are already missing
        filter(!is.na(ngr_left_clean) & !is.na(ngr_right_clean)) %>%
        # 3. Parse NGRs with error handling
        mutate(
          coords_left_parsed = lapply(ngr_left_clean, function(ngr) {
            tryCatch(rnrfa::osg_parse(ngr, coord_system = "BNG"),
              error = function(e) {
                list(easting = NA_real_, northing = NA_real_)
              }
            )
          }),
          coords_right_parsed = lapply(ngr_right_clean, function(ngr) {
            tryCatch(rnrfa::osg_parse(ngr, coord_system = "BNG"),
              error = function(e) {
                list(easting = NA_real_, northing = NA_real_)
              }
            )
          })
        ) %>%
        # 4. Extract eastings and northings safely
        mutate(
          easting_left =
            sapply(
              coords_left_parsed,
              function(x) ifelse(is.null(x$easting), NA_real_, x$easting)
            ),
          northing_left = sapply(
            coords_left_parsed,
            function(x) ifelse(is.null(x$northing), NA_real_, x$northing)
          ),
          easting_right = sapply(
            coords_right_parsed,
            function(x) ifelse(is.null(x$easting), NA_real_, x$easting)
          ),
          northing_right = sapply(
            coords_right_parsed,
            function(x) ifelse(is.null(x$northing), NA_real_, x$northing)
          )
        ) %>%
        # 5. Keep only rows where both sets of coordinates are valid after parsing
        filter(
          !is.na(easting_left) & !is.na(northing_left) & !is.na(easting_right) &
            !is.na(northing_right)
        )

      # Check if any valid coordinate pairs remain after preparation
      if (nrow(coords_to_process) > 0) {
        # Create sf points (CRS 27700 for OSGB)
        points_left <- sf::st_as_sf(
          coords_to_process,
          coords = c("easting_left", "northing_left"), crs = 27700
        )
        points_right <- sf::st_as_sf(
          coords_to_process,
          coords = c("easting_right", "northing_right"), crs = 27700
        )

        # Calculate distances and create a tibble with IDs and distances
        distances <- tibble::tibble(
          !!site_id_left := coords_to_process[[site_id_left]],
          !!site_id_right := coords_to_process[[site_id_right]],
          !!dist_col := as.numeric(
            sf::st_distance(points_left, points_right, by_element = TRUE)
          )
        )

        # Join distances back to the main matched results table
        matched_results <- matched_results %>%
          left_join(distances, by = c(site_id_left, site_id_right))
      } else {
        cat("No valid coordinate pairs found for distance calculation for", year_suffix, "after cleaning/parsing.\n")
      }
    }
  }

  # --- Final Formatting and Return ---
  # Prepare the final results dataframe with consistent naming
  quality_col <- paste0("match_quality_rf_", year_suffix)
  level_col <- paste0("match_level_", year_suffix)

  final_results <- matched_results %>%
    rename(!!quality_col := all_of(match_prob_col)) %>%
    mutate(
      !!paste0("match_type_", year_suffix) := "one_to_one", # From select_n_to_m
      !!paste0("match_method_", year_suffix) := "rf",
      !!paste0("join_keys_", year_suffix) := "rf_probabilistic",
      !!level_col := (1 - !!sym(quality_col)) * 100
    ) %>%
    # Select relevant columns for output
    select(
      any_of(c(site_id_left, site_id_right)),
      starts_with("match_method_"), starts_with("match_type_"),
      starts_with("join_keys_"), starts_with("match_level_"),
      starts_with("match_quality_rf_"), starts_with("dist_ngr_"),
      any_of(paste0(blocking_var, "_", c(left_year, right_year))),
    ) %>%
    arrange(desc(!!sym(quality_col)))

  # Identify IDs that remain unmatched after this process
  matched_left_ids <- final_results[[site_id_left]]
  matched_right_ids <- final_results[[site_id_right]]
  unmatched_left_ids <- setdiff(df_left[[site_id_left]], matched_left_ids)
  unmatched_right_ids <- setdiff(df_right[[site_id_right]], matched_right_ids)

  # Get the actual data rows for remaining unmatched records
  unmatched_left <- df_left %>% filter(.data[[site_id_left]] %in% unmatched_left_ids)
  unmatched_right <- df_right %>% filter(.data[[site_id_right]] %in% unmatched_right_ids)

  # Return list containing matches and remaining unmatched data/IDs
  return(list(
    matches = final_results,
    unmatched_left_ids = unmatched_left_ids,
    unmatched_right_ids = unmatched_right_ids,
    left_remaining = unmatched_left,
    right_remaining = unmatched_right
  ))
}
```

### Define Function to Perform RF Matching

```{r}
# Function to prepare data for RF matching by filtering to unmatched IDs
prepare_rf_data <- function(df, unmatched_ids, fill_site_names = TRUE) {
  # Validate and extract site_id column name
  site_id_cols <- names(df)[startsWith(names(df), "site_id_")]
  if (length(site_id_cols) != 1) {
    stop("Input df must have exactly one column starting with 'site_id_'")
  }
  site_id_col <- site_id_cols[1]

  # Filter to keep only specified unmatched observations
  df_filtered <- filter(df, .data[[site_id_col]] %in% unmatched_ids)

  # Fill missing site names using the other site name column
  if (fill_site_names) {
    df_filtered <- df_filtered %>%
      mutate(
        site_name_ea = if_else(is.na(site_name_ea) & !is.na(site_name_wa_sc),
          site_name_wa_sc, site_name_ea
        ),
        site_name_wa_sc = if_else(is.na(site_name_wa_sc) & !is.na(site_name_ea),
          site_name_ea, site_name_wa_sc
        )
      )
  }

  return(df_filtered)
}
```

### Perform Random Forest Matching 

We train the model on 2023-2024 using unique_id as training data.
```{r}
# Check if the model already exists, otherwise train it
if (file.exists(here("output", "code_testing", "rf_model_2023_2024.rds"))) {
  rf_model_res <- readRDS(here("output", "code_testing", "rf_model_2023_2024.rds"))
  m_rf <- rf_model_res$m_rf
} else {
  # Get the unique_id matches
  windfall_lookup <- match_dataframes$`2023_2024` %>%
    filter(join_keys_2023_2024 == "water_company|unique_id_2023") %>%
    select(site_id_2024, site_id_2023)

  # Train the model
  gc(full = TRUE)
  rf_model_res <- train_rf_linkage_model(
    df_left = data_list$df2023,
    df_right = data_list$df2024,
    known_matches = windfall_lookup,
    left_id_col = "site_id_2023",
    right_id_col = "site_id_2024",
    model_file = here("output", "code_testing", "rf_model_2023_2024.rds")
  )

  # Extract the trained model
  m_rf <- rf_model_res$model

  # Display variable importance
  importance_df <- data.frame(
    variable = names(rf_model_res$importance),
    importance = rf_model_res$importance
  ) %>%
    arrange(desc(importance))
}
```

```{r, use-rf-matching-function-systematically}
# Simple RF matching using year_pairs
rf_match_results <- lapply(1:nrow(year_pairs), function(i) {
  # Get years from year_pairs
  left_year <- year_pairs$left_year[i]
  right_year <- year_pairs$right_year[i]
  pair_name <- paste(left_year, right_year, sep = "_")

  # Get unmatched IDs for left and right years
  site_id_left <- paste0("site_id_", left_year)
  site_id_right <- paste0("site_id_", right_year)
  data_left <- data_list[[paste0("df", left_year)]]
  data_right <- data_list[[paste0("df", right_year)]]

  um_id_left <- data_left[[site_id_left]] %>%
    setdiff(pull(
      filter(lookup_table, !is.na(!!sym(site_id_left))),
      !!sym(site_id_left)
    ))

  um_id_right <- data_right[[site_id_right]] %>%
    setdiff(pull(
      filter(lookup_table, !is.na(!!sym(site_id_right))),
      !!sym(site_id_right)
    ))

  # Apply RF matching
  rf_match_res <- perform_rf_matching(
    df_left = prepare_rf_data(data_left, um_id_left),
    df_right = prepare_rf_data(data_right, um_id_right),
    rf_model = m_rf,
    match_threshold = 0.05
  )
  rf_match_res <- rf_match_res$matches %>%
    select(
      contains("site_id"),
      contains("match_method"), contains("match_type"),
      contains("join_keys"), contains("match_level"),
      contains("match_quality"), contains("dist_ngr"),
      contains("water_company"), contains("year"),
      contains("site_name_ea"), contains("site_name_wa_sc"),
      contains("permit_reference_ea"), contains("permit_reference_wa_sc"),
      contains("activity_reference"), contains("outlet_discharge_ngr")
    ) %>%
    as_tibble()

  return(rf_match_res)
})

# Name the results with pair names
names(rf_match_results) <- apply(
  year_pairs, 1, function(x) paste(x[1], x[2], sep = "_")
)
```

### Create Lookup Table

We use graph theory to create a consolidated lookup table. In particular, we use the minimum spanning tree (MST) to create a consolidated lookup table. The MST is a tree that connects all the nodes with the minimum possible total edge weight. In this case, the edge weight is the number of join keys (proxy for match quality).

```{r}
### --- Combine Windfall and RF Matches ---
matches_dfs <- append(match_dataframes, rf_match_results)
rf_match_results[[1]]

## --- Build a year‑aware edge list ---
edges_df <- lapply(matches_dfs, function(df) {
  site_cols <- grep("^site_id_", names(df), value = TRUE)
  match_method_col <- grep("^match_method_", names(df), value = TRUE)
  match_type_col <- grep("^match_type_", names(df), value = TRUE)
  level_col <- grep("^match_level_", names(df), value = TRUE)
  join_keys_col <- grep("^join_keys_", names(df), value = TRUE)

  yr_l <- str_extract(site_cols[1], "\\d{4}$")
  yr_r <- str_extract(site_cols[2], "\\d{4}$")

  df %>%
    filter(!is.na(.data[[join_keys_col]])) %>%
    transmute(
      from = paste0(yr_l, "_", .data[[site_cols[1]]]),
      to = paste0(yr_r, "_", .data[[site_cols[2]]]),
      match_method = .data[[match_method_col]],
      match_type = .data[[match_type_col]],
      match_level = .data[[level_col]],
      join_keys = .data[[join_keys_col]]
    ) %>%
    filter(from != "", to != "")
}) %>%
  bind_rows() %>%
  distinct()

### --- Compute weights ---

# Compute number of join keys (proxy for match quality)
edges_df <- edges_df %>%
  mutate(n_keys = str_count(join_keys, "\\|") + 1)
max_keys <- max(edges_df$n_keys, na.rm = TRUE)

# Build weighting measure
# unique_id edges get max weight, otherwise weight is number of join keys
# tiebreak on match_level (1 is best), so subtract it
edges_df <- edges_df %>%
  mutate(
    raw_score = case_when(
      str_detect(join_keys, "unique_id") ~ max_keys + 2,
      str_detect(join_keys, "rf_probabilistic") ~ 1,
      TRUE ~ n_keys + 1
    ),
    weight = raw_score * 100 - match_level
  )

edges_df %>%
  slice_sample(n = 100, by = match_type)
filter(str_detect(join_keys, "rf_probabilistic"))

## --- Create graph and components ---
g <- graph_from_data_frame(edges_df, directed = FALSE)
g_mst <- mst(g, weights = -E(g)$weight)
comps_mst <- components(g_mst)


## --- Recover raw site_id and year from vertex names ---
membership_mst <- tibble(
  vertex    = names(comps_mst$membership),
  component = comps_mst$membership
) %>%
  mutate(
    year    = str_extract(vertex, "^\\d{4}"),
    site_id = str_remove(vertex, "^\\d{4}_")
  )

## --- Assemble final cross‑year lookup table ---
lookup_table <- membership_mst %>%
  group_by(component, year) %>%
  summarise(site_id = first(site_id), .groups = "drop") %>%
  pivot_wider(
    names_from   = year,
    values_from  = site_id,
    names_prefix = "site_id_",
    values_fill  = NA_character_
  ) %>%
  select(site_id_2021, site_id_2022, site_id_2023, site_id_2024)

## --- Edge metadata from the minimum‑spanning tree --------------------------
edge_metadata <- igraph::as_data_frame(g_mst, what = "edges") %>%
  mutate(
    component     = comps_mst$membership[from],
    year_from     = str_extract(from, "^\\d{4}"),
    site_id_from  = str_remove(from, "^\\d{4}_"),
    year_to       = str_extract(to, "^\\d{4}"),
    site_id_to    = str_remove(to, "^\\d{4}_")
  ) %>%
  select(
    component,
    year_from, site_id_from,
    year_to, site_id_to,
    match_method, match_type, match_level, join_keys, weight
  ) %>%
  as_tibble()
```

We then use the lookup table to analyse coverage.

```{r analyze_results}
# Create clean year names for analysis
year_names <- gsub("df", "", names(total_records_by_year))

match_coverage <- data.frame(
  year = year_names,
  total_records = unname(total_records_by_year),
  matched_records = matched_records_by_year[year_names],
  stringsAsFactors = FALSE
) %>%
  mutate(coverage_pct = round(matched_records / total_records * 100, 1))

match_coverage
```

We then use the lookup table to analyse coverage.

```{r analyze_results}
# Create clean year names for analysis
year_names <- gsub("df", "", names(total_records_by_year))

match_coverage <- data.frame(
  year = year_names,
  total_records = unname(total_records_by_year),
  matched_records = matched_records_by_year[year_names],
  stringsAsFactors = FALSE
) %>%
  mutate(coverage_pct = round(matched_records / total_records * 100, 1))

match_coverage
```



## Archive

### Reclin2 - EM Algorithm

```{r}
# -----------------------------
# Step 1. Initialise Data Frames and add row identifiers
# -----------------------------

# Blocking variable
blocking_var <- "water_company"

# Variables for fuzzy string matching
match_vars <- c(
  "site_name_ea",
  "site_name_wa_sc",
  "permit_reference_ea",
  "permit_reference_wa_sc",
  "activity_reference",
  "outlet_discharge_ngr"
)

# Initialise data frames
df2024_rl <- df2024_remaining3 %>%
  mutate(across(
    all_of(match_vars),
    ~ if_else(toupper(.) == toupper("TBC"), NA_character_, .)
  )) %>%
  as.data.table()
df2023_rl <- df2023_remaining3 %>%
  mutate(across(
    all_of(match_vars),
    ~ if_else(toupper(.) == toupper("TBC"), NA_character_, .)
  )) %>%
  as.data.table()


# -----------------------------
# Step 2. Create Candidate Pairs using Blocking on 'water_company'
# -----------------------------
# Use pair_blocking to restrict candidate pairs to those where water_company is
identical
pairs_24_23_um <- pair_blocking(
  df2024_rl, df2023_rl,
  on = blocking_var,
  add_xy = TRUE
)


# -----------------------------
# Step 3. Compare Candidate Pairs
# -----------------------------
# Define comparators:
comparators_list <- list(
  site_name_ea = cmp_jarowinkler(threshold = 0.89),
  site_name_wa_sc = cmp_jarowinkler(threshold = 0.85),
  permit_reference_ea = cmp_jarowinkler(threshold = 0.9),
  permit_reference_wa_sc = cmp_jarowinkler(threshold = 0.9),
  activity_reference = cmp_jarowinkler(threshold = 0.9),
  outlet_discharge_ngr = cmp_jarowinkler(threshold = 0.97)
)

# Compare on the selected variables
compare_pairs(
  pairs_24_23_um,
  on = match_vars,
  inplace = TRUE,
  comparators = comparators_list
)


# -----------------------------
# Step 4. Score the Pairs
# -----------------------------
# Use EM algorithm (Fellegi-Sunter) for probabilistic scoring
formula_str <- paste("~", paste(match_vars, collapse = " + "))
m_em <- problink_em(
  formula = as.formula(formula_str),
  data = pairs_24_23_um
)

# Calculate posterior probability P(Match | Comparison Vector) using EM model
predict(
  m_em,
  pairs = pairs_24_23_um,
  type = "mpost",
  add = TRUE,
  binary = TRUE,
  inplace = TRUE
)

# -----------------------------
# Step 5. Select Matches
# -----------------------------
matching_thr <- 0.2

# Use select_n_to_m for optimal one-to-one mapping
select_n_to_m(
  pairs_24_23_um,
  variable = "selected_match",
  score = "mpost",
  threshold = matching_thr,
  inplace = TRUE
)

num_selected <- sum(pairs_24_23_um$selected_match, na.rm = TRUE)
print(paste(
  "Selected", format(num_selected, big.mark = ","),
  "pairs based on threshold and 1:1 rule."
))


# -----------------------------
# Step 6. Link Data
# -----------------------------
linked_data_um <- link(
  pairs_24_23_um,
  selection = "selected_match",
  all_x = FALSE,
  all_y = FALSE,
  suffixes = c("_2024", "_2023"),
  keep_from_pairs = c("mpost")
)

linked_data_um <- linked_data_um %>%
  rename(match_quality = mpost) %>%
  mutate(
    match_type = "one_to_one",
    match_method = "reclin2",
    join_keys = "site_id_2024|site_id_2023"
  ) %>%
  select(
    site_id_2024, site_id_2023, match_method, match_type, match_quality,
    contains("site_name_ea"), contains("site_name_wa_sc"),
    contains("permit_reference"), contains("outlet_discharge")
  )

# -----------------------------
# Step 7. Extract incorrect matches
# -----------------------------

pairs_24_23

incorrect_matches <- c()
incorrect_matches_df <- linked_data %>%
  filter(site_id_2024 %in% x)

# -----------------------------
# Step 7. Calculate distance between NGR coordinates using sf package
# -----------------------------

# # Function to clean and standardize NGR values
# clean_ngr <- function(ngr) {
#   ngr %>%
#     # Handle problematic values
#     {
#       ifelse(. %in% c("Unable to match to Consents Database", "Not in
# Consents Database"),
#         NA_character_, .
#       )
#     } %>%
#     # Remove "Not..." text
#     str_replace("(?i)Not.*", "") %>%
#     # Extract first reference if multiple exist
#     str_extract("^[^,&/\\(]+") %>%
#     # Remove all whitespace
#     str_remove_all("\\s+")
# }
#
# # Clean NGRs and calculate distance
# linked_data <- linked_data %>%
#   # Clean both NGR columns using the function
#   mutate(across(
#     .cols = c(outlet_discharge_ngr_2024, outlet_discharge_ngr_2023),
#     .fns = clean_ngr
#   ))
#
# # Parse coordinates separately
# coords_2024 <- osg_parse(linked_data$outlet_discharge_ngr_2024)
# coords_2023 <- osg_parse(linked_data$outlet_discharge_ngr_2023)
#
# # Create a dataframe with both sets of coordinates
# coords_df <- data.frame(
#   id = 1:nrow(linked_data),
#   easting_2024 = coords_2024$easting,
#   northing_2024 = coords_2024$northing,
#   easting_2023 = coords_2023$easting,
#   northing_2023 = coords_2023$northing
# )
#
# # Convert to sf objects with British National Grid projection (EPSG:27700)
# points_2024 <- st_as_sf(coords_df,
#   coords = c("easting_2024", "northing_2024"),
#   crs = 27700
# )
# points_2023 <- st_as_sf(coords_df,
#   coords = c("easting_2023", "northing_2023"),
#   crs = 27700
# )
#
# # Calculate distances
# distances <- st_distance(points_2024, points_2023, by_element = TRUE)
#
# # Add distances to original dataframe
# linked_data$dist_ngr_24_23 <- as.numeric(distances)
#
# # Show results with distance information
# linked_data %>%
#   arrange(desc(dist_ngr_24_23))
```

#### GLM Simple

```{r}
# -----------------------------
# Configuration
# -----------------------------

# Blocking variable
blocking_var <- "water_company"

# Variables for fuzzy string matching
match_vars <- c(
  "site_name_ea",
  "site_name_wa_sc",
  "permit_reference_ea",
  "permit_reference_wa_sc",
  "activity_reference",
  "outlet_discharge_ngr"
)
# Known matches for supervised learning
match_id <- "match_id"
# all variables
all_vars <- c(match_vars, match_id)


# Initialise data tables
df2024_ml <- df2024 %>%
  mutate(across(
    all_of(match_vars),
    ~ if_else(toupper(.) == toupper("TBC"), NA_character_, .)
  )) %>%
  as.data.table()
df2023_ml <- df2023 %>%
  mutate(across(
    all_of(match_vars),
    ~ if_else(toupper(.) == toupper("TBC"), NA_character_, .)
  )) %>%
  as.data.table()

# Generate ML training data using windfall matches
windfall_lookup <- as.data.table(match_res_windfall_23_24)[
  , .(site_id_2024, site_id_2023, match_id = .I)
]
df2024_ml[windfall_lookup, on = .(site_id_2024), match_id := i.match_id]
df2023_ml[windfall_lookup, on = .(site_id_2023), match_id := i.match_id]


# -----------------------------
# Step 1. Create Candidate Pairs
# -----------------------------
# Use pair_blocking to restrict candidate pairs to those where water_company is
identical
pairs_24_23_ml <- pair_blocking(
  df2024_ml, df2023_ml,
  on = blocking_var,
  add_xy = TRUE
)


# -----------------------------
# Step 2. Compare Candidate Pairs
# -----------------------------
# Define comparators:
comparators_list <- list(
  site_name_ea = cmp_jarowinkler(threshold = 0.89),
  site_name_wa_sc = cmp_jarowinkler(threshold = 0.85),
  permit_reference_ea = cmp_jarowinkler(threshold = 0.9),
  permit_reference_wa_sc = cmp_jarowinkler(threshold = 0.9),
  activity_reference = cmp_jarowinkler(threshold = 0.9),
  outlet_discharge_ngr = cmp_jarowinkler(threshold = 0.97),
  match_id = cmp_identical()
)

# Compare on the selected variables
thr <- 0.85
compare_pairs(
  pairs_24_23_ml,
  on = all_vars,
  default_comparator = cmp_jarowinkler(thr),
  comparators = comparators_list,
  inplace = TRUE
)

# -----------------------------
# Step 3. Train Supervised Model
# -----------------------------
# Create formula for model
formula_ml <- paste(match_id, "~", paste(match_vars, collapse = " + "))

# Train logistic regression model
m <- speedglm(
  formula = as.formula(formula_ml),
  data = pairs_24_23_ml,
  family = binomial()
)

# -----------------------------
# Step 4. Apply Model to Find New Matches
# -----------------------------
# Predict match probabilities for all candidate pairs
pairs_24_23_ml[
  ,
  match_prob := predict(m, newdata = pairs_24_23_ml, type = "response")
]
pairs_24_23_ml[is.na(match_prob), match_prob := 0.0]

# Select matches using score and 1:1 constraint
results_simple <- select_n_to_m(
  pairs_24_23_ml,
  variable = "selected_ml",
  score = "match_prob",
  threshold = 0.5,
  inplace = FALSE
)

results_simple <- link(
  results_simple,
  selection = "selected_ml",
  all_x = TRUE,
  all_y = TRUE,
  suffixes = c("_24", "_23")
)

matched_data <- results_simple[!is.na(site_id_2024) & !is.na(site_id_2023)]
nrow(matched_data)
```

#### Add NA handling

```{r}
# -----------------------------
# Step 1. Create Candidate Pairs
# -----------------------------
# Use pair_blocking to restrict candidate pairs to those where water_company is
identical
pairs_24_23_ml <- pair_blocking(
  df2024_ml, df2023_ml,
  on = blocking_var,
  add_xy = TRUE
)

# -----------------------------
# Step 2. Compare Candidate Pairs
# -----------------------------
## NA cmp_jarowinkler
jaro_winkler_na <- function(threshold = 0.85, na_placeholder = "") {
  SCORE_BOTH_NA <- -1L
  SCORE_ONE_NA <- -2L

  base_comparator <- reclin2::cmp_jarowinkler(threshold = threshold)

  function(x, y) {
    is_na_x <- is.na(x) | x == na_placeholder
    is_na_y <- is.na(y) | y == na_placeholder

    scores <- ifelse(
      is_na_x & is_na_y,
      SCORE_BOTH_NA,
      ifelse(
        is_na_x | is_na_y,
        SCORE_ONE_NA,
        base_comparator(x, y)
      )
    )
    return(scores)
  }
}

# Define comparators:
comparators_list <- list(
  site_name_ea = jaro_winkler_na(threshold = 0.89),
  site_name_wa_sc = jaro_winkler_na(threshold = 0.85),
  permit_reference_ea = jaro_winkler_na(threshold = 0.9),
  permit_reference_wa_sc = jaro_winkler_na(threshold = 0.9),
  activity_reference = jaro_winkler_na(threshold = 0.9),
  outlet_discharge_ngr = jaro_winkler_na(threshold = 0.97),
  match_id = cmp_identical()
)

# Compare on the selected variables
thr <- 0.85
compare_pairs(
  pairs_24_23_ml,
  on = all_vars,
  default_comparator = jaro_winkler_na(thr),
  comparators = comparators_list,
  inplace = TRUE
)

# -----------------------------
# Step 3. Train Supervised Model
# -----------------------------
# Create formula for model
formula_ml <- paste(match_id, "~", paste(match_vars, collapse = " + "))

# Train logistic regression model
m <- speedglm(
  formula = as.formula(formula_ml),
  data = pairs_24_23_ml,
  family = binomial()
)

# -----------------------------
# Step 4. Apply Model to Find New Matches
# -----------------------------
# Predict match probabilities for all candidate pairs
pairs_24_23_ml[
  ,
  match_prob := predict(m, newdata = pairs_24_23_ml, type = "response")
]
pairs_24_23_ml[is.na(match_prob), match_prob := 0.0]

# Select matches using score and 1:1 constraint
results_na_handle <- select_n_to_m(
  pairs_24_23_ml,
  variable = "selected_ml",
  score = "match_prob",
  threshold = 0.5,
  inplace = FALSE
)

results_na_handle <- link(
  results_na_handle,
  selection = "selected_ml",
  all_x = TRUE,
  all_y = TRUE,
  suffixes = c("_24", "_23")
)

matched_data_na_handle <- results_na_handle[!is.na(site_id_2024) & !is.na
(site_id_2023)]
nrow(matched_data_na_handle)
```




```{r}
data("linkexample1", "linkexample2")
pairs <- pair_blocking(linkexample1, linkexample2, "postcode")
linkexample1
linkexample2

na_as_class <- function(x, y) {
  factor(
    ifelse(is.na(x) | is.na(y), 2L, (y == x) * 1L),
    levels = 0:2, labels = c("eq", "uneq", "mis")
  )
}

compare_pairs(
  pairs,
  on = c("lastname", "firstname", "address", "sex"),
  inplace = TRUE,
  comparators = list(
    lastname = cmp_jarowinkler(),
    firstname = cmp_jarowinkler(),
    address = cmp_jarowinkler(),
    sex = na_as_class
  )
)

linkexample2$known_id <- linkexample2$id
linkexample2$known_id[c(2, 5)] <- NA
setDT(linkexample2)

compare_vars(
  pairs,
  "y",
  on_x = "id",
  on_y = "known_id",
  y = linkexample2,
  inplace = TRUE
)


compare_vars(pairs, "y_true", on_x = "id", on_y = "id", inplace = TRUE)

m <- glm(y ~ lastname + firstname + address + sex,
  data = pairs, family =
    binomial()
)
pairs[, prob := predict(m, type = "response", newdata = pairs)]

pairs[, select := prob > 0.5]
table(pairs$select > 0.5, pairs$y_true)

# or alternatively can use select_n_to_m
select_n_to_m(pairs,
  variable = "select", score = "prob", threshold = 0.5,
  inplace = TRUE
)
table(pairs$select, pairs$y_true)

linked_data_set <- link(pairs, selection = "select", all_y = TRUE, all_x = TRUE)

linked_data_set %>%
  select(order(colnames(linked_data_set)))
linkexample1

results <- list(
  m_glm_na <- m,
  glm_na_pairs_24_23 <- pairs_24_23_ml,
  results_glm_na_24_23 <- results_na_handle,
  m_rf = m_rf
)
saveRDS(results, here("output", "code_testing", "results.RData"))
```
