## Introduction

This script performs matching between individual sewage spill event data and
summarised annual return data for the years defined in CONFIG. The goal is to enrich the individual spill events with consistent location and site information from the annual returns, which are considered more reliable for site identification. It uses a "windfall matching" approach, prioritising joins based on the largest sets of common identifying columns first, assuming longer keys imply higher quality matches. It specifically ensures matches are unique within the annual data for a given key.

## Configuration

```{r}
CONFIG <- list(
  years = 2021:2023,
  data_path_annual = here::here(
    "data", "processed", "annual_return_edm.parquet"
  ),
  data_path_individual = here::here(
    "data", "processed", "combined_edm_data.parquet"
  ),
  id_cols = c(
    "site_name_ea", "site_name_wa_sc",
    "permit_reference_ea", "permit_reference_wa_sc",
    "activity_reference", "asset_type", "unique_id",
    "site_id_2021", "site_id_2022", "site_id_2023",
    "site_id_2024"
  ),
  block_var = "blocking_var",
  threshold = 0.5,
  match_cols = c(
    "match_method", "match_type", "match_key", "key_length", "match_quality"
  )
)
```


## Setup and Data Load

Set up the environment and load the required packages.

```{r}
#' Initialize the R environment with required packages
#' @return NULL
initialise_environment <- function() {
  # Package management with renv
  if (!requireNamespace("renv", quietly = TRUE)) {
    install.packages("renv")
    renv::init()
  }

  # Define required packages
  required_packages <- c(
    "rmarkdown", "rio", "tidyverse", "purrr", "here", "logger", "glue",
    "fs", "conflicted", "reclin2", "data.table", "assertthat"
  )

  # Install and load packages
  invisible(sapply(required_packages, function(pkg) {
    if (!requireNamespace(pkg, quietly = TRUE)) {
      install.packages(pkg)
    }
    library(pkg, character.only = TRUE)
  }))
  conflict_prefer("flatten", "purrr")
  conflict_prefer("filter", "dplyr")
}
initialise_environment()
```

Load the data.

```{r}
load_data <- function() {
  logger::log_info("Loading EDM datasets: individual spill events and annual returns.")

  # Define file paths using configuration
  event_path <- fs::path(CONFIG$data_path_individual)
  annual_path <- fs::path(CONFIG$data_path_annual)

  # Check if both files exist before attempting to load
  files <- c(event_path, annual_path)
  missing_files <- files[!file.exists(files)]
  if (length(missing_files) > 0) {
    error_msg <- glue::glue(
      "Input files not found: {paste(missing_files, collapse = ', ')}"
    )
    logger::log_error(error_msg)
    stop(error_msg)
  }

  # Load the data and return
  tryCatch(
    {
      spill_event_df <- arrow::read_parquet(event_path) %>% 
        filter(year %in% CONFIG$years)
      annual_return_df <- arrow::read_parquet(annual_path) %>% 
        filter(year %in% CONFIG$years)
      logger::log_info("Data loaded successfully.")
    },
    error = function(e) {
      error_msg <- glue::glue("Failed to load data: {e$message}")
      logger::log_error(error_msg)
      stop(error_msg)
    }
  )

  return(list(
    spill_events = spill_event_df,
    annual_returns = annual_return_df
  ))
}

loaded_data <- load_data()
```

## Unique Windfall Matching

### Windfall Matching Functions

This is a function that generates all non-empty combinations of column names and orders them by length. The reason is that join key length is likely to be a proxy for join quality.
```{r}
#' Generate All Non-Empty Combinations of Shared Column Names
#' @param shared_cols Column names common to both datasets.
#' @return A list where each element is a character vector representing a
#'   potential key combination. Returns an empty list if input is empty.
generate_key_combinations <- function(shared_cols) {
  if (length(shared_cols) == 0) {
    return(list())
  }

  # Create combinations for each size from length(cols) down to 1
  seq_along(shared_cols) %>%
    rev() %>%
    map(~ combn(shared_cols, .x, simplify = FALSE)) %>%
    flatten()
}
```

Finds specific key values present in the event data and unique in the annual data for a given key combination. Uniqueness in the annual data is crucial as it represents the reference dataset; we want to map potentially multiple events (many) to one unique annual site record (one).

```{r}
#' Find Keys Present in Individual DF and Unique in Year DF
#' Identifies key values existing in event_df and appearing exactly once
#' in annual_df for a specific key combination.
#' @param event_df The individual spill event data frame.
#' @param annual_df The annual return data frame (summarised by site/year).
#' @param key A character vector representing the column names to use as the key.
#' @return A tibble containing the key columns for rows matching the criteria.
#'   Returns an empty tibble with the correct structure if no such keys are found.
find_matchable_keys <- function(event_df, annual_df, key) {
  if (!all(key %in% names(event_df)) || !all(key %in% names(annual_df))) {
    stop("Key columns must exist in both data frames: ", paste(key, collapse = ", "))
  }

  if (nrow(event_df) == 0 || nrow(annual_df) == 0 || length(key) == 0) {
    return(event_df %>% slice(0) %>% select(all_of(key)))
  }

  # Count occurrences of key values in both dataframes
  event_counts <- event_df %>%
    count(across(all_of(key)), name = "n_event", .drop = FALSE)
  annual_counts <- annual_df %>%
    count(across(all_of(key)), name = "n_annual", .drop = FALSE)

  # Identify keys that are unique in the annual (reference) data
  annual_unique_keys <- annual_counts %>%
    filter(n_annual == 1) %>%
    select(all_of(key))

  # Find the final set of keys to use for matching in this iteration.
  matchable_keys <- inner_join(
    event_counts %>% select(all_of(key)),
    annual_unique_keys,
    by = key,
    na_matches = "never"
  )

  return(matchable_keys)
}
```

Extracts subsets of event and annual data matching the identified unique keys and joins them. Adds metadata about which key combination produced the match.

```{r}
#' Extract Matching Subsets, Join, Add Metadata, and Coalesce Columns
#' Extracts rows corresponding to `matchable_keys`, joins them,
#' adds match metadata, then coalesces duplicated columns (prioritising annual data).
#' @param event_df The current individual spill event data subset.
#' @param annual_df The current annual return data subset.
#' @param matchable_keys A tibble of keys identified by `find_matchable_keys`.
#' @param key A character vector representing the column names used as the key.
#' @param event_suffix Suffix for overlapping non-key columns from event_df.
#' @param annual_suffix Suffix for overlapping non-key columns from annual_df.
#' @return A tibble containing the joined rows with added metadata and coalesced columns.
extract_join_tag <- function(
    event_df, annual_df,
    matchable_keys, key,
    event_suffix = "_event", annual_suffix = "_annual") {
  # Extract the matching rows
  event_sub <- dplyr::semi_join(event_df, matchable_keys, by = key, na_matches = "never")
  annual_sub <- dplyr::semi_join(annual_df, matchable_keys, by = key, na_matches = "never")

  # Join and tag
  matched_sub <- dplyr::inner_join(
    event_sub, annual_sub,
    by = key,
    na_matches = "never",
    suffix = c(event_suffix, annual_suffix)
  ) %>%
    dplyr::mutate(
      match_method = "windfall",
      match_quality = 1,
      match_type = "unique",
      match_key = paste(key, collapse = "|"),
      key_length = length(key),
      .before = 1
    )

  # Identify overlapping base names from suffixed columns
  overlap_bases <- names(matched_sub)[grepl(paste0(event_suffix, "$"), names(matched_sub))] %>%
    sub(paste0(event_suffix, "$"), "", .)

  # Coalesce each pair, preferring annual values
  for (base in overlap_bases) {
    event_col  <- paste0(base, event_suffix)
    annual_col <- paste0(base, annual_suffix)
    if (annual_col %in% names(matched_sub) && event_col %in% names(matched_sub)) {
      matched_sub[[base]] <- dplyr::coalesce(
        matched_sub[[annual_col]],
        matched_sub[[event_col]]
      )
    }
  }

  # Drop the original suffixed columns
  matched_sub <- matched_sub %>%
    dplyr::select(
      -dplyr::ends_with(event_suffix),
      -dplyr::ends_with(annual_suffix)
    )

  return(matched_sub)
}
```

Performs the main windfall matching process iteratively. Joins event and annual data based on shared columns, prioritising longer keys. Removes matched rows after each iteration and attempts matches with shorter keys. Returns three datasets: matched rows, unmatched event rows, and unmatched annual rows.
```{r}
#' Iteratively Join Data Frames Prioritising Larger, Unique-Right Keys
#' Performs a prioritised join between two data frames based on shared columns.
#' Iterates through key combinations (largest first), matching rows where
#' the key is unique in the annual data frame. Matched rows are removed for
#' subsequent iterations.
#' @param event_df The individual spill event data frame for the current group.
#' @param annual_df The annual return data frame for the current group.
#' @param event_suffix Suffix for overlapping non-key
#' @param annual_suffix Suffix for overlapping non-key
#' @return A list containing matched_data, events_unmatched, & annual_unmatched
run_windfall_match <- function(
    event_df,
    annual_df,
    event_suffix = "_event",
    annual_suffix = "_annual") {
  shared_cols <- intersect(names(event_df), names(annual_df))
  key_list <- generate_key_combinations(shared_cols)

  # Initialise state variables
  remaining_events <- event_df
  remaining_annual <- annual_df
  all_matched_data <- tibble()

  # Loop through potential keys, largest combinations first
  for (key in key_list) {
    # Stop if either dataset has no remaining rows
    if (nrow(remaining_events) == 0 || nrow(remaining_annual) == 0) {
      break
    }

    # Keys unique in the remaining annual data and present in remaining event data
    matchable_keys <- find_matchable_keys(
      remaining_events, remaining_annual, key
    )

    # If suitable keys are found for this iteration...
    if (nrow(matchable_keys) > 0) {
      # Extract, join, and tag the subset corresponding to these keys
      matched_sub <- extract_join_tag(
        remaining_events, remaining_annual,
        matchable_keys, key,
        event_suffix, annual_suffix
      )

      # Accumulate the matches
      all_matched_data <- bind_rows(all_matched_data, matched_sub)

      # Remove the matched rows from the pools for the next iteration
      remaining_events <- anti_join(
        remaining_events, matchable_keys,
        by = key, na_matches = "never"
      )
      remaining_annual <- anti_join(
        remaining_annual, matchable_keys,
        by = key, na_matches = "never"
      )
    }
  }

  # Return all components
  list(
    matched_data      = all_matched_data,
    events_unmatched  = remaining_events,
    annual_unmatched  = remaining_annual
  )
}
```

Adds zero-spill records from the unmatched annual data to the matched dataset. This is correct because annual records with zero spills cannot, by definition, exist in the individual spill event data, and thus would never be matched/removed during the windfall process, ensuring they are present in annual_unmatched.

```{r}
#' Add Unmatched Zero-Spill Annual Records and Separate Non-Zero Unmatched
#' @param matched_data A data frame or tibble containing the successfully matched
#' records from `run_windfall_match`.
#' @param unmatched_annual_data A data frame or tibble containing the annual
#' records that were not matched during `run_windfall_match`
#' (i.e., `$annual_unmatched`). Must contain `spill_hrs` and `spill_count` columns.
#' @return A list containing two tibbles:
#'   \item{matched_data_with_zeros}{The input `matched_data` with zero-spill rows
#'     from `unmatched_annual_data` appended.}
#'   \item{annual_unmatched_nonzero}{A subset of `unmatched_annual_data` containing
#'     only rows where `spill_hrs != 0` or `spill_count != 0`.}
add_zero_spill_stats <- function(matched_data, unmatched_annual_data) {
  # Filter the *unmatched* annual data for zero-spill records
  annual_data_zero <- unmatched_annual_data %>%
    filter(spill_hrs == 0 & spill_count == 0)

  # Filter the *unmatched* annual data for non-zero spill records
  annual_data_nonzero <- unmatched_annual_data %>%
    filter(spill_hrs != 0 | spill_count != 0)

  # Append the zero-spill records (if any) to the main matched dataset
  if (nrow(annual_data_zero) > 0) {
    matched_data_with_zeros <- bind_rows(matched_data, annual_data_zero)
  } else {
    matched_data_with_zeros <- matched_data
  }

  # Return the combined data and the separated non-zero unmatched annual records
  list(
    matched_data_with_zeros = matched_data_with_zeros,
    annual_unmatched_nonzero = annual_data_nonzero
  )
}
```

### Perform Windfall Matching

Orchestrates the matching process by looping through each combination of year and water company.

```{r}
spill_event_df <- loaded_data$spill_events
annual_return_df <- loaded_data$annual_returns

# Main merging function
merge_events_with_annual_returns <- function(spill_event_df, annual_return_df) {
  # Create combinations of years and water companies
  company_year_combinations <- expand_grid(
    water_company = unique(annual_return_df$water_company),
    year = CONFIG$years
  ) %>%
    arrange(year, water_company)

  logger::log_info("Starting matching process for company-year combinations.")

  # Iterate over each company-year subset
  match_results_list <- pmap(
    list(
      company_year_combinations$year,
      company_year_combinations$water_company
    ),
    ~ {
      # Assign arguments to named variables for clarity
      current_year <- ..1
      current_company <- ..2
      logger::log_debug(
        "Processing: Year {current_year}, Company {current_company}"
      )

      # Filter data for current company and year
      event_df_sub <- spill_event_df %>%
        filter(water_company == current_company, year == current_year) %>%
        select(where(~ any(!is.na(.))))
      annual_return_df_sub <- annual_return_df %>%
        filter(water_company == current_company, year == current_year) %>%
        select(where(~ any(!is.na(.))), any_of(c("spill_hrs", "spill_count")))

      # Perform the windfall matching on the subsets
      windfall_res <- run_windfall_match(
        event_df = event_df_sub,
        annual_df = annual_return_df_sub,
        event_suffix = "_event",
        annual_suffix = "_annual"
      )

      # Add unmatched zero-spill annual records and separate non-zero unmatched
      final_group_results <- add_zero_spill_stats(
        matched_data = windfall_res$matched_data,
        unmatched_annual_data = windfall_res$annual_unmatched
      )

      # Return results
      list(
        # Matched event data
        matched_combined = final_group_results$matched_data_with_zeros,
        # Event records that found no match in the annual data
        events_unmatched = windfall_res$events_unmatched,
        # Annual records that found no match AND had non-zero spills
        annual_unmatched_nonzero = final_group_results$annual_unmatched_nonzero
      )
    }
  )

  logger::log_info("Finished matching process.")

  # Combine all matched dataframes into a single dataframe
  return(list(
    matched_combined = rbindlist(
      map(match_results_list, ~ .x$matched_combined),
      fill = TRUE
    ),
    events_unmatched = rbindlist(
      map(match_results_list, ~ .x$events_unmatched),
      fill = TRUE
    ),
    annual_unmatched_nonzero = rbindlist(
      map(match_results_list, ~ .x$annual_unmatched_nonzero),
      fill = TRUE
    )
  ))
}

# Execute the merging process
final_results_list <- merge_events_with_annual_returns(
  spill_event_df, annual_return_df
)
```

### Many-to-Many Matching

```{r}
## Many-to-Many Matching by Company-Year
#' @param events_unmatched tibble of spill events remaining after unique windfall matching
#' @param annual_unmatched_nonzero tibble of annual records remaining after windfall
#' @return A list with three tibbles:
#'   - matches: retained event→annual pairs (one per event)
#'   - events_unmatched: events still without a match
#'   - annual_unmatched: annual records never selected
#' @param events_unmatched tibble of spill events remaining after unique windfall matching
#' @param annual_unmatched_nonzero tibble of annual records (spill_hrs>0 or spill_count>0) remaining after windfall
#' @param keep_joined_losses Logical; if TRUE, retains annual records that joined but lost the max selection.
#'                           If FALSE (default), only annual records never joined are kept in the remaining set.
#' @return A list with three tibbles:
#'   - matches: retained event→annual pairs (one per event)
#'   - events_unmatched: events still without a match
#'   - annual_unmatched: annual records never selected (subject to `keep_joined_losses`)
run_max_match <- function(
    events_unmatched,
    annual_unmatched_nonzero,
    keep_joined_losses = FALSE) {
  # prepare datasets and identify shared columns
  df_left <- events_unmatched %>% select(where(~ any(!is.na(.))))
  df_right <- annual_unmatched_nonzero %>% select(where(~ any(!is.na(.))))
  shared_cols <- intersect(names(df_left), names(df_right))

  # tag rows for later unmatched detection
  df_left <- df_left %>% tibble::rowid_to_column("event_row_id")
  df_right <- df_right %>% tibble::rowid_to_column("annual_row_id")

  # inner join on all shared columns (explicit many-to-many)
  joined_all <- inner_join(
    df_left, df_right,
    by = shared_cols,
    suffix = c("_event", "_annual"),
    na_matches = "never",
    relationship = "many-to-many"
  ) %>%
    mutate(
      match_method = "max",
      match_type   = "many-to-many",
      match_key    = paste(shared_cols, collapse = "|"),
      key_length   = length(shared_cols)
    )

  # compute tie indicator robustly: handle all-NA cases
  tie_info <- joined_all %>%
    group_by(event_row_id) %>%
    summarise(
      max_hrs = if (all(is.na(spill_hrs))) NA_real_ else max(spill_hrs, na.rm = TRUE),
      max_count = if (is.na(max_hrs)) {
        if (all(is.na(spill_count))) NA_real_ else max(spill_count, na.rm = TRUE)
      } else {
        max(spill_count[spill_hrs == max_hrs], na.rm = TRUE)
      },
      tie = sum(spill_hrs == max_hrs & spill_count == max_count, na.rm = TRUE) > 1,
      .groups = "drop"
    ) %>%
    select(event_row_id, tie)

  # select the single best record per event: highest spill_hrs, then highest spill_count
  best_matches <- joined_all %>%
    group_by(event_row_id) %>%
    arrange(desc(spill_hrs), desc(spill_count)) %>%
    slice(1) %>%
    ungroup() %>%
    left_join(tie_info, by = "event_row_id")

  # detect unmatched events
  events_remaining <- df_left %>%
    filter(!event_row_id %in% best_matches$event_row_id) %>%
    select(-event_row_id)

  # detect remaining annuals, conditional on keep_joined_losses
  if (keep_joined_losses) {
    # keep all non-selected
    annual_remaining <- df_right %>%
      filter(!annual_row_id %in% best_matches$annual_row_id)
  } else {
    # keep only those never joined at all
    annual_remaining <- df_right %>%
      filter(!annual_row_id %in% joined_all$annual_row_id)
  }
  annual_remaining <- annual_remaining %>% select(-annual_row_id)

  # drop row IDs from matches
  matches <- best_matches %>% select(-event_row_id, -annual_row_id)

  list(
    matches          = matches,
    events_unmatched = events_remaining,
    annual_unmatched = annual_remaining
  )
}

#' Many-to-Many Matching then Max(spill_hrs, spill_count) by Company-Year
#' @param events_unmatched tibble of spill events remaining
#' @param annual_unmatched_nonzero tibble of annual records remaining
#' @param keep_joined_losses Logical; passed to `run_max_match`
#' @return A list with three tibbles:
#'   - max_matches_all: retained event→annual pairs (one per event)
#'   - events_unmatched: events still without a match
#'   - annual_unmatched: annual records never selected
run_many_to_many_max_match <- function(
    events_unmatched,
    annual_unmatched_nonzero,
    keep_joined_losses = FALSE) {
  company_years <- expand_grid(
    water_company = unique(events_unmatched$water_company),
    year          = unique(events_unmatched$year)
  ) %>% arrange(year, water_company)

  results <- pmap(
    list(company_years$year, company_years$water_company),
    ~ {
      current_year <- ..1
      current_company <- ..2

      ev_sub <- events_unmatched %>%
        filter(water_company == current_company, year == current_year) %>%
        select(where(~ any(!is.na(.))))
      an_sub <- annual_unmatched_nonzero %>%
        filter(water_company == current_company, year == current_year) %>%
        select(where(~ any(!is.na(.))), any_of(c("spill_hrs", "spill_count")))

      if (nrow(ev_sub) == 0 || nrow(an_sub) == 0) {
        return(list(
          max_matches = ev_sub[0, ],
          events_unmatched = ev_sub,
          annual_unmatched = an_sub
        ))
      }

      mm <- run_max_match(
        events_unmatched         = ev_sub,
        annual_unmatched_nonzero = an_sub,
        keep_joined_losses       = keep_joined_losses
      )
      # bind all group-level results into master tibbles
      list(
        max_matches = mm$matches,
        events_unmatched = mm$events_unmatched,
        annual_unmatched = mm$annual_unmatched
      )
    }
  )

  list(
    max_matches_all  = rbindlist(map(results, "max_matches"), fill = TRUE),
    events_unmatched = rbindlist(map(results, "events_unmatched"), fill = TRUE),
    annual_unmatched = rbindlist(map(results, "annual_unmatched"), fill = TRUE)
  )
}

max_results <- run_many_to_many_max_match(
  events_unmatched           = final_results_list$events_unmatched,
  annual_unmatched_nonzero   = final_results_list$annual_unmatched_nonzero
)

final_results_list <- list(
  matched_combined = bind_rows(
    final_results_list$matched_combined,
    max_results$max_matches_all
  ),
  events_unmatched = max_results$events_unmatched,
  annual_unmatched_nonzero = max_results$annual_unmatched
)
```


## Unique Fuzzy Matching

```{r}
#' Prepare data for fuzzy matching by combining, grouping, and blocking.
#' @param events_df A data frame of individual spill events.
#' @param annual_df A data frame of annual spill returns.
#' @param vars Character vector of columns to include (e.g., identifiers and blocking variables).
#' @param id_cols Character vector of columns used to define unique records (defaults to `vars`).
#' @return A named list of four data.tables: `events`, `annual`, `events_full`, `annual_full`.
prepare_fuzzy_data <- function(events_df, annual_df, block_var, id_cols) {
  if (!all(c("water_company", "year") %in% names(events_df))) {
    stop("events_df must contain 'water_company' and 'year'")
  }
  if (!all(c("water_company", "year") %in% names(annual_df))) {
    stop("annual_df must contain 'water_company' and 'year'")
  }

  dfs <- list(events = events_df, annual = annual_df)
  prep <- lapply(dfs, function(df) {
    # assign group_id and blocking key
    full <- df %>%
      group_by(across(any_of(id_cols))) %>%
      mutate(group_id = cur_group_id()) %>%
      ungroup() %>%
      mutate(!!block_var := paste(water_company, year, sep = "_"), .before = 1)

    # minimal (deduped) version
    minimal <- full %>%
      select(any_of(id_cols), group_id, !!block_var) %>%
      distinct()

    list(
      full = as.data.table(full),
      minimal = as.data.table(minimal)
    )
  })

  # assemble into named list
  list(
    events        = prep$events$minimal,
    annual        = prep$annual$minimal,
    events_full   = prep$events$full,
    annual_full   = prep$annual$full
  )
}

#' Create candidate record pairs using blocking.
#' @param prepped A list returned by `prepare_fuzzy_data`.
#' @param block_var The blocking variable used to link x and y.
#' @return A data.table of candidate pairs.
create_candidate_pairs <- function(prepped, block_var) {
  logger::log_debug("Creating candidate pairs with block variable '{block_var}'")
  pairs <- pair_blocking(
    x      = prepped$events,
    y      = prepped$annual,
    on     = block_var,
    add_xy = TRUE
  )
  logger::log_info("Generated {nrow(pairs)} candidate pairs")
  pairs
}

#' Compare candidate pairs using fuzzy comparators.
#' @param pairs A data.table of candidate pairs.
#' @param fuzzy_vars Character vector of columns to compare.
#' @return The same data.table, updated in place with comparison columns.
compare_candidate_pairs <- function(pairs, fuzzy_vars) {
  logger::log_debug("Comparing candidate pairs on vars: {paste(fuzzy_vars, collapse = ', ')}")
  compare_pairs(
    pairs,
    on                  = fuzzy_vars,
    default_comparator  = reclin2::cmp_jarowinkler(threshold = 0.85),
    inplace             = TRUE
  )
  invisible(pairs)
}

#' Score candidate pairs using the EM algorithm for probabilistic linkage.
#' @param pairs A data.table of compared pairs.
#' @param fuzzy_vars Character vector used in EM formula.
#' @return The data.table with added posterior match probabilities (`mpost`).
score_pairs_em <- function(pairs, fuzzy_vars) {
  # Ensure there are pairs to score
  if (nrow(pairs) == 0) {
    logger::log_warn("No pairs to score with EM algorithm")
    return(pairs)
  }
  # Catch EM failures gracefully
  tryCatch(
    {
      fs_formula <- reformulate(fuzzy_vars)
      m_em <- problink_em(formula = fs_formula, data = pairs)
      predict(
        m_em,
        pairs   = pairs,
        type    = "mpost",
        add     = TRUE,
        binary  = TRUE,
        inplace = TRUE
      )
    },
    error = function(e) {
      logger::log_error("EM model failed: {e$message}")
      pairs[, mpost := 0]
      pairs
    }
  )
}

#' Select matching pairs based on posterior probabilities, n-to-m settings, and threshold.
#' @param pairs A data.table scored by `score_pairs_em`.
#' @param threshold Numeric cutoff for selecting matches (e.g., 0.2).
#' @param n Integer max matches per record in x (events).
#' @param m Integer max matches per record in y (annual).
#' @param include_ties Logical, whether to include ties at the threshold.
#' @return The data.table updated in place with a logical `selected_match` column.
select_matches <- function(
    pairs,
    threshold = CONFIG$threshold,
    n,
    m,
    include_ties = TRUE) {
  if (!is.numeric(threshold) || threshold <= 0 || threshold >= 1) {
    stop("'threshold' must be a numeric value between 0 and 1")
  }
  select_n_to_m(
    pairs,
    variable     = "selected_match",
    score        = "mpost",
    threshold    = threshold,
    n            = n,
    m            = m,
    include_ties = include_ties,
    inplace      = TRUE
  )
  n_sel <- sum(pairs$selected_match, na.rm = TRUE)
  logger::log_info(
    "Selected {n_sel} matches with threshold {threshold}, n={n}, m={m}, include_ties={include_ties}"
  )
  invisible(pairs)
}

#' Link the selected fuzzy matches, adding match metadata and suffixes.
#' @param pairs A data.table after `select_matches` with `selected_match` flags.
#' @return A tibble of linked records with match metadata columns.
link_selected_pairs <- function(pairs) {
  logger::log_debug("Linking selected pairs")
  linked <- link(
    pairs,
    selection       = "selected_match",
    suffixes        = c("_event", "_annual"),
    keep_from_pairs = "mpost",
    all_x           = FALSE,
    all_y           = FALSE
  ) %>%
    as_tibble() %>%
    rename(match_quality = mpost) %>%
    mutate(
      match_method = "fuzzy",
      match_type   = "unique",
      match_key    = "fuzzy",
      key_length   = NA_integer_,
      .before      = 1
    )
  logger::log_info("Linked {nrow(linked)} fuzzy match records")
  linked
}

#' Performs fuzzy linkage within that block and aggregates the results
#' @param final_res A list with elements `matched_combined`, `events_unmatched` and
#'   `annual_unmatched_nonzero`
#' @param threshold Cutoff (0–1) for posterior match probability
#' @param n Maximum matches per event record  
#' @param m Maximum matches per annual record
#' @param include_ties If TRUE, include any ties at the threshold
#' @param block_var Column name defining each block (e.g. "company_year")
#' @return A list with updated `matched_combined`, `events_unmatched` and
#'   `annual_unmatched_nonzero`.
run_fuzzy_matching <- function(
  final_res,
  threshold     = CONFIG$threshold,
  n,
  m,
  include_ties  = TRUE,
  block_var     = CONFIG$block_var
) {
  # validate input structure
  assert_that(is.list(final_res), msg = "final_res must be a list")
  required <- c("matched_combined", "events_unmatched", "annual_unmatched_nonzero")
  if (!all(required %in% names(final_res))) {
    stop("final_res missing: ", paste(setdiff(required, names(final_res)), collapse = ", "))
  }

  # prepare blocking + group IDs
  id_cols <- c("water_company", "year", CONFIG$id_cols)
  prepped  <- prepare_fuzzy_data(
    events_df = final_res$events_unmatched,
    annual_df = final_res$annual_unmatched_nonzero,
    block_var = block_var,
    id_cols   = id_cols
  )

  # perform fuzzy matching by block
  blocks       <- unique(prepped$events[[block_var]])
  fuzzy_merges <- purrr::map(blocks, function(b) {
    # subset to current block and drop all‐NA columns
    ev <- filter(prepped$events, .data[[block_var]] == b) %>% select(where(~ any(!is.na(.))))
    an <- filter(prepped$annual, .data[[block_var]] == b) %>% select(where(~ any(!is.na(.))))
    if (nrow(ev)==0 || nrow(an)==0) return(NULL)

    # identify comparators available in both subsets
    shared        <- intersect(names(ev), names(an))
    vars_block    <- setdiff(shared, c(block_var, "source","group_id","water_company","year"))
    if (length(vars_block)==0) return(NULL)

    # generate and score candidate pairs
    pairs <- create_candidate_pairs(list(events=ev, annual=an), block_var)
    if (nrow(pairs)==0) return(NULL)

    compare_candidate_pairs(pairs, vars_block)
    score_pairs_em(pairs, vars_block)
    select_matches(pairs, threshold, n, m, include_ties)

    # link and return minimal join keys
    link_selected_pairs(pairs) %>%
      select(all_of(CONFIG$match_cols), group_id_event, group_id_annual)
  }) %>% purrr::compact() %>% bind_rows()

  # reconstruct matched + unmatched sets
  matched_combined <- fuzzy_merges %>%
    left_join(prepped$annual_full,   by=c("group_id_annual"="group_id")) %>%
    left_join(prepped$events_full,
              by=c("group_id_event"="group_id"),
              suffix=c("","_dup")) %>%
    select(-ends_with("_dup")) %>%
    bind_rows(final_res$matched_combined, .)

  events_unmatched <- anti_join(
    prepped$events_full, fuzzy_merges,
    by=c("group_id"="group_id_event")
  )
  annual_unmatched <- anti_join(
    prepped$annual_full, fuzzy_merges,
    by=c("group_id"="group_id_annual")
  )

  list(
    matched_combined = matched_combined,
    events_unmatched = events_unmatched,
    annual_unmatched_nonzero = annual_unmatched
  )
}

res_fuzzy_unique <- run_fuzzy_matching(
  final_res = final_results_list,
  n = 1, m = 1
)

# matched_combined %>% 
#   filter(!is.na(group_id_event), !is.na(group_id_annual)) %>% 
#   group_by(group_id_event) %>% 
#   mutate(n=n_distinct(group_id_annual)) %>% 
#   ungroup() %>% 
#   select(order(names(.))) %>% 
#   relocate(contains("group"), .before = everything()) %>% 
#   select(where(~ any(!is.na(.)))) %>% 
#   arrange(match_quality) 
```

## Clean data

```{r}
fuzzy_results

finalise_merged_data <- function(fuzzy_results) {
  # Load lookup and annual returns
  lookup <- import(CONFIG$data_path_lookup)
  annual_returns <- import(CONFIG$data_path_annual)
  
  # Build lookup with per-year outlet discharge NGR
  years_lookup <- 2021:2024
  lookup <- purrr::reduce(
    yearsannual returns for the years of interestookup, .init = lookup,
    function(acc, yr) {
      year_id <- paste0("site_id_", yr)
      ngr_col <- paste0("outlet_discharge_ngr_", yr)
      coords <- annual_returns %>%
        filter(year == yr) %>%
        select({{year_id}}, outlet_discharge_ngr) %>%
        rename({{ngr_col}} := outlet_discharge_ngr)
      left_join(acc, coords, by = year_id, na_matches = "never")
    }
  )
  
  # Enrich matched_combined for each year, then combine
  enriched <- purrr::map(
    CONFIG$years,
    function(y) {
      id_col <- paste0("site_id_", y)
      other_ids <- setdiff(paste0("site_id_", years_lookup), id_col)
      fuzzy_results$matched_combined %>%
        filter(!is.na(.data[[id_col]])) %>%
        select(-any_of(other_ids)) %>%
        left_join(lookup, by = id_col)
    }
  ) %>% 
    rbindlist(., use.names = TRUE, fill = TRUE) %>% 
    rename(ngr_og = outlet_discharge_ngr) %>% 
    mutate(
      ngr = coalesce(
        outlet_discharge_ngr_2024,
        outlet_discharge_ngr_2023,
        outlet_discharge_ngr_2022,
        outlet_discharge_ngr_2021)) 
  
  fuzzy_results$matched_combined <- enriched
  
  # Trim all list elements to desired columns
  purrr::map(
    fuzzy_results,
    ~ dplyr::select(.x, any_of(CONFIG$keep_cols))
  ) %>% 
    return()
}

lookup %>% 
  filter(site_id_2021==1302)
```

