---
author: "Jacopo Olivieri"
date: 2025-07-18
editor: source
format: html
number-sections: true
number-depth: 4
execute: 
  echo: false
  warning: false
  message: false
  freeze: false
  fig-width: 9
  fig-asp: 0.618 
  fig-align: center
---

# Pipeline Overview {#sec-01-data-pipeline}

```{r setup, include=FALSE}
# Initialize packages with version control
if (!requireNamespace("renv", quietly = TRUE)) {
  install.packages("renv")
}

# Run manual renv commands if needed
# renv::activate() # Activate the project library
# renv::restore()  # Restore the environment if running for first time
# renv::snapshot()  # After adding/updating packages, snapshot the state

# Load required packages
required_packages <- c(
  "DiagrammeR"
)
install_if_missing <- function(packages) {
  new_packages <- packages[!sapply(packages, requireNamespace, quietly = TRUE)]
  if (length(new_packages) > 0) {
    install.packages(new_packages)
  }
  invisible(sapply(packages, library, character.only = TRUE))
}
install_if_missing(required_packages)
```

## Pipeline Organisation {#sec-01-01-organisation}

The current data cleaning pipeline consists of 20 R scripts that process sewage discharge data, house price data, and spatial relationships to create datasets for analysis. 

The pipeline is structured across 6 layers:

1. **Data Ingestion Layer (`01_data_ingestion/`)**: This layer contains scripts that retrieve or extract unprocessed data from external sources—such as downloading from APIs or unpacking zip archives. The scripts here do not clean or transform data; they only collect and save it locally.
2. **Data Cleaning Layer (`02_data_cleaning/`)**: This layer includes scripts that clean, reformat, and validate raw data files. These scripts ensure consistency across files by fixing column names, data types, missing values, and file formats. They produce uniform, structured outputs usable downstream.
3. **Data Enrichment Layer (`03_data_enrichment/`)**: This layer holds scripts that enhance cleaned data with additional structure—by generating lookup tables, calculating summaries, or tagging records with geographic or temporal metadata. These scripts prepare the data for matching and analysis by adding context.
4. **Feature Engineering Layer (`04_feature_engineering/`)**: This layer includes scripts that generate analysis-ready variables. This involves creating spatial matches, calculating distances, defining treatment indicators, and building other derived features required for regressions or causal analysis.
5. **Integration Layer (`05_data_integration/`)**: This layer contains scripts that merge datasets from different sources or time periods. These scripts align records across formats, join data on shared identifiers, and harmonise inconsistencies to produce a single dataset structure.
6. **Analysis Datasets Layer (`06_analysis_datasets/`)**: This layer includes scripts that build the final analysis datasets. These scripts define the unit of observation (e.g. house-level, site-level), assign exposure variables, and output clean panels or cross-sections used directly in empirical estimation.



## Flowchart {#sec-01-02-flowchart}

The flowchart below illustrates the data cleaning pipeline, showing how data flows through each layer and the dependencies between scripts. 

![](../book_figs/pipeline_flowchart.svg){.lightbox}

```{r}
require(DiagrammeR)
grViz(
  "
digraph DataPipeline {

  // --- Global Graph Settings ---
  graph [
    rankdir='TB',
    splines=ortho,
    nodesep=0.8,
    ranksep=1.5,
    fontname='Inter, -apple-system, sans-serif',
    fontsize=14,
    bgcolor='#fafaf9',
    label='Data Processing Pipeline',
    labelloc='t',
    fontcolor='#1e1b4b'
  ];

  // --- Default Node and Edge Styles ---
  node [
    fontname='Inter, -apple-system, sans-serif',
    fontsize=13,
    shape=box,
    style='filled,rounded'
  ];
  edge [
    color='#6b7280',
    penwidth=2
  ];

  // --- Subgraph Definitions (Layers) ---
  subgraph cluster_ING {
    label = '01 Ingestion Layer';
    style='filled,rounded'; fillcolor='#f3f4f6'; color='#6b7280'; fontcolor='#111827'; penwidth=2;
    node [style='filled,rounded', rx=6, ry=6, fillcolor='#e0e7ff', color='#6366f1', penwidth=2, fontcolor='#312e81'];
    S01 [label='edm_individ_data_standardisation_2021-2023.R\\nStandardises raw EDM data files from UK water companies'];
    S04 [label='fetch_edm_api_data_2024_onwards.R\\nDownloads EDM data from ArcGIS API endpoints for 2024+'];
  }

  subgraph cluster_CLN {
    label = '02 Cleaning & Standardisation Layer';
    style='filled,rounded'; fillcolor='#eff6ff'; color='#3b82f6'; fontcolor='#1e3a8a'; penwidth=2;
    node [style='filled,rounded', rx=6, ry=6, fillcolor='#e0e7ff', color='#6366f1', penwidth=2, fontcolor='#312e81'];
    S02 [label='convert_individ_raw_data_to_rdata_2021-2023.R\\nConverts raw EDM data files to standardised Parquet format'];
    S03 [label='combine_individ_edm_data_2021-2023.R\\nCombines individual water company Parquet files into single dataset'];
    S05 [label='process_edm_api_json_to_parquet_2024_onwards.R\\nProcesses raw API JSON data into standardised Parquet files'];
    S06 [label='combine_api_edm_data_2024_onwards.R\\nCombines individual water company API Parquet files'];
    S08 [label='combine_annual_return_data.R\\nCleans and combines annual sewage spill return data'];
    S11 [label='clean_consented_discharges_database.R\\nCleans Environment Agency\\'s consented discharges database'];
    S14 [label='clean_lr_house_price_data.R\\nCleans and combines HM Land Registry property sales data'];
  }
  
  subgraph cluster_INT {
    label = '05 Integration Layer';
    style='filled,rounded'; fillcolor='#fffbeb'; color='#f97316'; fontcolor='#7c2d12'; penwidth=2;
    node [style='filled,rounded', rx=6, ry=6, fillcolor='#e0e7ff', color='#6366f1', penwidth=2, fontcolor='#312e81'];
    S07 [label='combine_2021-2023_and_api_edm_data.R\\nHarmonises and combines 2021-2023 EDM data with API 2024+ data'];
    S10 [label='merge_individ_annual_location.R\\nMerges location data from annual datasets with individual spill data'];
  }
  
  subgraph cluster_ENR {
    label = '03 Enrichment & Aggregation Layer';
    style='filled,rounded'; fillcolor='#f0fdf4'; color='#22c55e'; fontcolor='#14532d'; penwidth=2;
    node [style='filled,rounded', rx=6, ry=6, fillcolor='#e0e7ff', color='#6366f1', penwidth=2, fontcolor='#312e81'];
    S09 [label='create_annual_return_lookup.R\\nBuilds cross-year lookup table linking same spill sites'];
    S12 [label='aggregate_spill_stats.R\\nAggregates individual sewage overflow spills into statistics'];
    S13 [label='create_unique_spill_sites.R\\nCreates unique spill sites dataset by cleaning location data'];
  }

  subgraph cluster_FEA {
    label = '04 Feature Engineering; Spatial Processing Layer';
    style='filled,rounded'; fillcolor='#fef2f2'; color='#ef4444'; fontcolor='#7f1d1d'; penwidth=2;
    node [style='filled,rounded', rx=6, ry=6, fillcolor='#e0e7ff', color='#6366f1', penwidth=2, fontcolor='#312e81'];
    S15 [label='10km_site_house_sale_match.R\\nPerforms spatial matching between house sales and spill sites'];
    S17 [label='compute_spill_stats.R\\nCalculates site-level spill statistics and treatment indicators'];
  }

  subgraph cluster_MAS {
    label = '06 Final Dataset Assembly Layer';
    style='filled,rounded'; fillcolor='#faf5ff'; color='#a855f7'; fontcolor='#581c87'; penwidth=2;
    node [style='filled,rounded', rx=6, ry=6, fillcolor='#e0e7ff', color='#6366f1', penwidth=2, fontcolor='#312e81'];
    S16 [label='cross_section_sales_db.R\\nCreates cross-sectional databases aggregating spill data (sales)'];
    S18 [label='site_panel_sales.R\\nCreates site-level panel data by aggregating house price statistics'];
    S19 [label='house_panel_within_radius.R\\nCreates house panel data for houses within specified radius thresholds'];
    S20 [label='sale_panel_exp.R\\nCreates comprehensive house panel data including all houses'];
    S21 [label='rental_panel_exp.R\\nCreates comprehensive rental panel data including all listings'];
    S22 [label='site_panel_rental.R\\nCreates site-level rental panel data by aggregating listing prices'];
    S23 [label='rental_panel_within_radius.R\\nCreates rental panel data for listings within radius thresholds'];
  }

  // --- External and Data Node Definitions ---
  node [shape=cylinder, style='filled,rounded', rx=8, ry=8];

  node [fillcolor='#d1fae5', color='#10b981', penwidth=2.5, fontcolor='#064e3b'];
  EXT1 [label=< <B>data/raw/edm_data/EDM*.zip</B><BR/>Raw EDM data archives from UK water companies >];
  EXT2 [label=< <B>scripts/config/api_config.R</B><BR/>API configuration for data fetching >];
  EXT3 [label=< <B>data/raw/edm_data/<BR/>YYYY_annual_return_edm.xlsx</B><BR/>Annual return data from water companies >];
  EXT4 [label=< <B>data/raw/ea_consents/consents_all.csv</B><BR/>Environment Agency consented discharges database >];
  EXT5 [label=< <B>data/raw/lr_house_price/pp-YYYY.csv</B><BR/>HM Land Registry property sales data >];

  node [fillcolor='#fef3c7', color='#f59e0b', penwidth=1.5, fontcolor='#78350f'];
  D01 [label='data/raw/edm_data/\\nYYYY_company_name_edm.*\\nStandardised EDM files from zip extraction'];
  D02 [label='data/processed/edm_data_2021_2023/*.parquet\\nIndividual company EDM data in Parquet format'];
  D03 [label='data/processed/combined_edm_data.parquet\\nCombined EDM data for 2021-2023'];
  D04 [label='data/raw/edm_data/raw_api_responses/*.json.gz\\nRaw API JSON responses from ArcGIS endpoints'];
  D05 [label='data/processed/edm_api_data/*.parquet\\nProcessed API data in Parquet format'];
  D06 [label='data/processed/edm_api_data/combined_api_data.parquet\\nCombined API data for 2024+'];
  D07 [label='data/processed/combined_edm_data.parquet\\nAll EDM data combined (2021-2024+)'];
  D08 [label='data/processed/annual_return_edm.parquet\\nProcessed annual return data'];
  D09 [label='data/processed/annual_return_lookup.parquet\\nAnnual return lookup table'];
  D10 [label='data/processed/matched_events_annual_data.parquet\\nMatched events with annual data'];
  D11 [label='data/processed/consent_discharges_db.csv\\nCleaned EA consented discharges database'];
  D12 [label='data/processed/spill_aggregated/agg_spill_*.parquet\\nAggregated spill statistics (monthly/quarterly/yearly)'];
  D13 [label='data/processed/unique_spill_sites.parquet\\nUnique spill sites dataset with location data'];
  D14 [label='data/processed/house_price.parquet\\nCleaned house price data with postcode coordinates'];
  D15 [label='data/processed/spill_house_lookup.parquet\\nSpatial lookup between spills and houses within 10km'];
  D16 [label='output/log/edm_api_download_log.csv\\nDownload log for API data fetching'];
  D17 [label='data/processed/agg_spill_stats/\\nComputed spill statistics with treatment indicators'];
  D18 [label='data/processed/zoopla/zoopla_rentals.parquet\\nCleaned Zoopla rental listings'];
  D19 [label='data/processed/zoopla/spill_rental_lookup.parquet\\nSpatial lookup between spills and rentals within 10km'];

  node [fillcolor='#fce7f3', color='#ec4899', penwidth=3, fontcolor='#831843'];
  F01 [label=< <B>data/processed/agg_*_cross_section/</B><BR/>Cross-sectional databases >];
  F02 [label=< <B>data/processed/dat_panel_site/sales/</B><BR/>Site-level panel data (sales) >];
  F03 [label=< <B>data/processed/within_radius_panel/sales/</B><BR/>House panel data within radius >];
  F04 [label=< <B>data/processed/general_panel/sales/</B><BR/>General sale panel data >];
  F05 [label=< <B>data/processed/general_panel/rentals/</B><BR/>General rental panel data >];
  F06 [label=< <B>data/processed/dat_panel_site/rentals/</B><BR/>Site-level panel data (rentals) >];
  F07 [label=< <B>data/processed/within_radius_panel/rentals/</B><BR/>Rental panel data within radius >];

  // --- Edge Definitions (Connections) ---
  EXT1 -> S01; EXT2 -> S04; EXT3 -> S08; EXT4 -> S11; EXT5 -> S14;
  S01 -> D01 -> S02 -> D02 -> S03 -> D03;
  S04 -> D04 -> S05 -> D05 -> S06 -> D06;
  {D03, D06} -> S07 -> D07;
  S08 -> D08 -> {S09, S10};
  S09 -> D09;
  {D07, D08, D09} -> S10 -> D10;
  S11 -> D11;
  D10 -> {S12, S13};
  S12 -> D12 -> S17 -> D17;
  S13 -> D13;
  S14 -> D14;
  {D13, D14} -> S15 -> D15;
  {D12, D14, D15} -> S16 -> F01;
  {D14, D15} -> S18 -> F02;
  {D14, D15} -> S19 -> F03;
  {D14, D15, D17} -> S20 -> F04;
  {D18, D19, D17} -> S21 -> F05;
  {D18, D19} -> S22 -> F06;
  {D18, D19} -> S23 -> F07;

  edge [style=dashed, color='#9ca3af', penwidth=1.5, constraint=false];
  S04 -> D16;
  S10 -> D11;
  S10 -> D09;
}
"
)
```

## Scripts Overview {#sec-01-03-script-overview}

### Raw Data Ingestion Layer {#sec-01-03-01-raw-data-ingestion}

**EDM Data Standardisation (2021-2023)**

- **script_name**: `edm_individ_data_standardisation_2021-2023.R`
- **purpose**: Standardises raw Event Duration Monitoring (EDM) data files from UK water companies for 2021-2023 by extracting, renaming, and organising files from zip archives.
- **inputs**: `["data/raw/edm_data/EDM*.zip"]`
- **outputs**: `["data/raw/edm_data/YYYY_company_name_edm.*"]`

**API Data Fetching (2024+)**

- **script_name**: `fetch_edm_api_data_2024_onwards.R`
- **purpose**: Downloads and processes EDM data from ArcGIS API endpoints for 2024 onwards using pagination and saves as compressed JSON files.
- **inputs**: `["scripts/config/api_config.R"]`
- **outputs**: 
  - `"data/raw/edm_data/raw_api_responses/company_name/*.json.gz"`
  - `"output/log/edm_api_download_log.csv"`

### Data Cleaning & Standardisation Layer {#sec-01-03-02-data-cleaning-standardisation}

**Raw Data Conversion**

- **script_name**: `convert_individ_raw_data_to_rdata_2021-2023.R`
- **purpose**: Converts and cleans individual raw EDM data files from CSV/Excel formats to standardised Parquet format for years 2021-2023.
- **inputs**: `["data/raw/edm_data/YYYY_company_name_edm.*"]`
- **outputs**: 
  - `"data/processed/edm_data_2021_2023/*.parquet"`
  - `"data/processed/edm_data_2021_2023/combined_edm_data_*.parquet"`

**Individual EDM Data Combination**

- **script_name**: `combine_individ_edm_data_2021-2023.R`
- **purpose**: Combines and cleans individual water company Parquet files from 2021-2023 into a single consolidated dataset with standardised datetime parsing.
- **inputs**: `["data/processed/edm_data_2021_2023/*.parquet"]`
- **outputs**: `["data/processed/combined_edm_data.parquet"]`

**API Data Processing**

- **script_name**: `process_edm_api_json_to_parquet_2024_onwards.R`
- **purpose**: Processes raw API JSON data into standardised Parquet files, extracts features data, and handles incremental updates for 2024 onwards.
- **inputs**: `["data/raw/edm_data/raw_api_responses/company_name/*.json.gz"]`
- **outputs**: `["data/processed/edm_api_data/*.parquet"]`

**API Data Combination**

- **script_name**: `combine_api_edm_data_2024_onwards.R`
- **purpose**: Combines and cleans individual water company API Parquet files from 2024 onwards into a single consolidated dataset.
- **inputs**: `["data/processed/edm_api_data/*.parquet"]`
- **outputs**: `["data/processed/edm_api_data/combined_api_data.parquet"]`

**Annual Return Data Processing**

- **script_name**: `combine_annual_return_data.R`
- **purpose**: Cleans and combines annual sewage spill return data from UK water companies for 2021-2024, standardising column names and formats.
- **inputs**: `["data/raw/edm_data/YYYY_annual_return_edm.xlsx"]`
- **outputs**: `["data/processed/annual_return_edm.parquet"]`

**Consented Discharges Database Cleaning**

- **script_name**: `clean_consented_discharges_database.R`
- **purpose**: Cleans the Environment Agency's consented discharges database, standardising water company names and column mappings.
- **inputs**: `["data/raw/ea_consents/consents_all.csv"]`
- **outputs**: 
  - `"data/processed/consent_discharges_db.RData"`
  - `"data/processed/consent_discharges_db.csv"`

**House Price Data Cleaning**

- **script_name**: `clean_lr_house_price_data.R`
- **purpose**: Cleans and combines HM Land Registry UK property sales data for 2021-2023, enriching with postcode coordinates using PostcodesioR API.
- **inputs**: `["data/raw/lr_house_price/pp-YYYY.csv"]`
- **outputs**: `["data/processed/house_price.parquet"]`

### Data Enrichment & Aggregation Layer {#sec-01-03-03-data-enrichment-aggregation}

**Annual Return Lookup Creation**

- **script_name**: `create_annual_return_lookup.R`
- **purpose**: Builds a cross-year lookup table linking the same spill sites across annual EDM returns (2021-2024) using deterministic and probabilistic matching.
- **inputs**: `["data/processed/annual_return_edm.parquet"]`
- **outputs**: 
  - `"data/processed/annual_return_lookup.parquet"`
  - `"data/processed/annual_return_lookup_edges.parquet"`
  - `"data/processed/annual_return_lookup.xlsx"`

**Spill Statistics Aggregation**

- **script_name**: `aggregate_spill_stats.R`
- **purpose**: Aggregates individual sewage overflow spills into monthly, quarterly, and yearly statistics using the 12/24 hour counting method.
- **inputs**: `["data/processed/matched_events_annual_data/matched_events_annual_data.parquet"]`
- **outputs**: 
  - `"data/processed/spill_aggregated/agg_spill_yr.parquet"`
  - `"data/processed/spill_aggregated/agg_spill_mo.parquet"`
  - `"data/processed/spill_aggregated/agg_spill_qtr.parquet"`

**Unique Spill Sites Creation**

- **script_name**: `create_unique_spill_sites.R`
- **purpose**: Creates unique spill sites dataset by cleaning location data and parsing British National Grid coordinates from merged EDM data.
- **inputs**: `["data/processed/matched_events_annual_data/matched_events_annual_data.parquet"]`
- **outputs**: 
  - `"data/processed/unique_spill_sites.parquet"`
  - `"data/processed/unique_spill_sites.xlsx"`

### Feature Engineering & Spatial Processing Layer {#sec-01-03-04-feature-engineering-spatial-processing}

**Spatial Matching**

- **script_name**: `10km_site_house_sale_match.R`
- **purpose**: Performs spatial matching between house sales and spill sites within 10km radius using spatial joins and distance calculations.
- **inputs**: 
  - `"data/processed/house_price.parquet"`
  - `"data/processed/unique_spill_sites.parquet"`
- **outputs**: `["data/processed/spill_house_lookup.parquet"]`

**Spill Statistics Computing**

- **script_name**: `compute_spill_stats.R`
- **purpose**: Calculates site-level spill statistics including cross-site thresholds and treatment indicators for monthly and quarterly periods.
- **inputs**: 
  - `"data/processed/spill_aggregated/agg_spill_mo.parquet"`
  - `"data/processed/spill_aggregated/agg_spill_qtr.parquet"`
- **outputs**: `["data/processed/agg_spill_stats/"]`

### Integration Layer {#sec-01-03-05-integration}

**Historical and API Data Integration**

- **script_name**: `combine_2021-2023_and_api_edm_data.R`
- **purpose**: Harmonises and combines the processed 2021-2023 EDM data with API-sourced 2024+ data into a single consolidated dataset.
- **inputs**: 
  - `"data/processed/combined_edm_data.parquet"`
  - `"data/processed/edm_api_data/combined_api_data.parquet"`
- **outputs**: `["data/processed/combined_edm_data.parquet"]`

**Individual and Annual Data Merging**

- **script_name**: `merge_individ_annual_location.R`
- **purpose**: Merges location data from annual sewage overflow datasets with individual spill data using windfall, many-to-many, and fuzzy matching methods.
- **inputs**: 
  - `"data/processed/combined_edm_data.parquet"`
  - `"data/processed/annual_return_edm.parquet"`
  - `"data/processed/annual_return_lookup.parquet"`
- **outputs**: 
  - `"data/processed/matched_events_annual_data/matched_events_annual_data.parquet"`
  - `"data/processed/matched_events_annual_data/events_unmatched.parquet"`
  - `"data/processed/matched_events_annual_data/annual_unmatched.parquet"`
  - `"data/processed/matched_events_annual_data/site_metadata.parquet"`

### Master Dataset Assembly Layer {#sec-01-03-06-master-dataset-assembly}

**Cross-Sectional Database Creation (Sales)**

- **script_name**: `cross_section_sales_db.R`
- **purpose**: Creates cross-sectional databases aggregating spill data: one for all years and one for 12 months prior to house sales, partitioned by radius thresholds.
- **inputs**: 
  - `"data/processed/house_price.parquet"`
  - `"data/processed/spill_house_lookup.parquet"`
  - `"data/processed/spill_aggregated/agg_spill_mo.parquet"`
- **outputs**: 
  - `"data/processed/cross_section/sales/all_years/"`
  - `"data/processed/cross_section/sales/prior_12mo/"`

**Cross-Sectional Database Creation (Rentals)**

- **script_name**: `cross_section_rental_db.R`
- **purpose**: Creates cross-sectional rental datasets: all years and 12 months prior to `rented_est`, partitioned by radius thresholds.
- **inputs**: 
  - `"data/processed/zoopla/zoopla_rentals.parquet"`
  - `"data/processed/zoopla/spill_rental_lookup.parquet"`
  - `"data/processed/spill_aggregated/agg_spill_mo.parquet"`
- **outputs**: 
  - `"data/processed/cross_section/rentals/all_years/"`
  - `"data/processed/cross_section/rentals/prior_12mo/"`

**Site-Level Panel Data (Sales)**

- **script_name**: `site_panel_sales.R`
- **purpose**: Creates site-level panel data by aggregating house price statistics (median, mean, weighted) for each spill site across multiple distance radii and time periods.
- **inputs**: 
  - `"data/processed/house_price.parquet"`
  - `"data/processed/spill_house_lookup.parquet"`
- **outputs**: `["data/processed/dat_panel_site/sales/"]`

**Site-Level Panel Data (Rentals)**

- **script_name**: `site_panel_rental.R`
- **purpose**: Builds site-level panel datasets of rental prices (median, mean, weighted) around each spill site for specified distance radii and periods.
- **inputs**:
  - `"data/processed/zoopla/zoopla_rentals.parquet"`
  - `"data/processed/zoopla/spill_rental_lookup.parquet"`
- **outputs**: `["data/processed/dat_panel_site/rentals/"]`

**House Panel Within Radius**

- **script_name**: `house_panel_within_radius.R`
- **purpose**: Creates house sale-level panel data containing only houses within specified radius thresholds of spill sites, with monthly and quarterly aggregation.
- **inputs**: 
  - `"data/processed/house_price.parquet"`
  - `"data/processed/spill_house_lookup.parquet"`
- **outputs**: `["data/processed/within_radius_panel/sales/"]`

**Rental Panel Within Radius**

- **script_name**: `rental_panel_within_radius.R`
- **purpose**: Builds rental listing-level panel data containing only listings within specified radii of spill sites, with monthly and quarterly aggregation.
- **inputs**:
  - `"data/processed/zoopla/zoopla_rentals.parquet"`
  - `"data/processed/zoopla/spill_rental_lookup.parquet"`
- **outputs**: `["data/processed/within_radius_panel/rentals/"]`

**General House Panel**

- **script_name**: `sale_panel_exp.R`
- **purpose**: Creates comprehensive house sale-level panel data including all houses (within and outside radius thresholds) with spill site relationship metadata for experimental analysis.
- **inputs**: 
  - `"data/processed/house_price.parquet"`
  - `"data/processed/spill_house_lookup.parquet"`
  - `"data/processed/agg_spill_stats/"`
- **outputs**: `["data/processed/general_panel/sales/"]`

**General Rental Panel**

- **script_name**: `rental_panel_exp.R`
- **purpose**: Creates comprehensive rental listing-level panel data including all listings (within and outside radius thresholds) with spill site relationship metadata for experimental analysis.
- **inputs**: 
  - `"data/processed/zoopla/zoopla_rentals.parquet"`
  - `"data/processed/zoopla/spill_rental_lookup.parquet"`
  - `"data/processed/agg_spill_stats/"`
- **outputs**: `["data/processed/general_panel/rentals/"]`
