---
author: "Jacopo Olivieri"
date: 2024-04-01
editor: source
format: html
number-sections: true
number-depth: 4
execute: 
  echo: false
  warning: false
  message: false
  freeze: auto
  fig-width: 9
  fig-asp: 0.618 
  fig-align: center
---

# Event Study {#sec-05-event-study}

```{r setup, include=FALSE}
# Initialize packages with version control
if (!requireNamespace("renv", quietly = TRUE)) {
  install.packages("renv")
}

# Run manual renv commands if needed
# renv::activate() # Activate the project library
# renv::restore()  # Restore the environment if running for first time
# renv::snapshot()  # After adding/updating packages, snapshot the state


# Load required packages
required_packages <- c(
  "rmarkdown", "rio", "tidyverse", "purrr", "here", "janitor", "viridis",
  "data.table", "DIDmultiplegtDYN", "arrow", "furrr"
)
install_if_missing <- function(packages) {
  new_packages <- packages[!sapply(packages, requireNamespace, quietly = TRUE)]
  if (length(new_packages) > 0) {
    install.packages(new_packages)
  }
  invisible(sapply(packages, library, character.only = TRUE))
}
install_if_missing(required_packages)


# Initialize logging
log_path <- here::here("output", "log", "house_data_exploration")
if (!dir.exists(dirname(log_path))) {
  dir.create(dirname(log_path), recursive = TRUE)
}
logger::log_appender(logger::appender_file(log_path))
logger::log_layout(logger::layout_glue_colors)

# Ggplot theme
theme_pref <- theme_minimal() +
  theme(
    text = element_text(size = 12),
    plot.title = element_text(
      face = "bold", size = 12,
      margin = ggplot2::margin(b = 10, unit = "pt")
    ),
    axis.title = element_text(face = "bold", size = 10),
    axis.text = element_text(angle = 45, hjust = 1, vjust = 1, size = 8),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_line(color = "gray95"),
    panel.grid.major.y = element_line(color = "gray95"),
    legend.position = "bottom",
    legend.title = element_text(face = "bold", size = 10),
    legend.text = element_text(size = 8),
    plot.margin = ggplot2::margin(t = 10, r = 10, b = 10, l = 10, unit = "pt")
  )
```


```{r}
#| eval: false
#| include: false

# ---------- Function to run event study ----------

# Build model name (helper function)
build_model_name <- function(outcome,
                             treatment_threshold,
                             time_agg,
                             normalized,
                             same_switchers,
                             treatment_type,
                             controls = NULL) {
  # Set binary (bin) or continuous
  base <- "model_"
  base <- ifelse(
    treatment_threshold == "cont", paste0(base, "cont"), paste0(base, "bin")
  )

  # Set spill statistic
  base <- ifelse(grepl("log_", outcome), paste0(base, "_logp"), base)
  base <- ifelse(grepl("_w$", outcome), paste0(base, "_w"), base)
  tt <- ifelse(grepl("spill_count", treatment_type), "sc", "sh")

  # Set model name
  base <- paste(base, tt, treatment_threshold, time_agg, sep = "_")

  # Set model parameters
  if (same_switchers) base <- paste0(base, "_sw")
  if (normalized) base <- paste0(base, "_norm")

  # Set controls
  if (!is.null(controls) && length(controls)) {
    ctrl_suffix <- paste(controls, collapse = "_")
    base <- paste(base, ctrl_suffix, sep = "_")
  }

  return(base)
}

# Build model description (helper function)
build_description <- function(outcome,
                              treatment_threshold,
                              time_agg,
                              treatment_type,
                              normalized,
                              same_switchers,
                              controls = NULL) {
  # Labels
  outcome_lbl <- dplyr::case_when(
    outcome == "price_median_w" ~ "Weighted Price Median",
    outcome == "log_price_median_w" ~ "Weighted Log Price Median",
    outcome == "price_median" ~ "Price Median",
    outcome == "log_price_median" ~ "Log Price Median",
    outcome == "price" ~ "Price",
    outcome == "log_price" ~ "Log Price",
    TRUE ~ outcome
  )

  threshold_lbl <- dplyr::case_when(
    treatment_threshold == "mean" ~ "Mean",
    treatment_threshold == "p50" ~ "P50",
    treatment_threshold == "p75" ~ "P75",
    treatment_threshold == "p90" ~ "P90",
    treatment_threshold == "max" ~ "Max",
    treatment_threshold == "cont" ~ "Continuous",
    TRUE ~ stringr::str_to_title(treatment_threshold)
  )

  time_lbl <- dplyr::case_when(
    time_agg == "mo" ~ "Monthly",
    time_agg == "qtr" ~ "Quarterly",
    time_agg == "yr" ~ "Yearly",
    TRUE ~ time_agg
  )
  time_lbl <- ifelse(threshold_lbl == "Continuous", "", time_lbl)

  treat_lbl <- dplyr::case_when(
    grepl("spill_count", treatment_type) & treatment_threshold != "cont"
    ~ "Spill Count",
    grepl("spill_hrs", treatment_type) & treatment_threshold != "cont"
    ~ "Spill Hours",
    grepl("spill_count", treatment_type) & treatment_threshold == "cont"
    ~ "Log Spill Count",
    grepl("spill_hrs", treatment_type) & treatment_threshold == "cont"
    ~ "Log Spill Hours",
    TRUE ~ NA_character_
  )

  norm_lbl <- ifelse(normalized, "Norm", "No Norm")
  sw_lbl <- ifelse(same_switchers, "Same Switchers", "All Switchers")

  ctrl_lbl <- if (is.null(controls) || length(controls) == 0) {
    ""
  } else {
    paste0("; Controls: ", paste(controls, collapse = ", "))
  }

  # Compose
  glue::glue(
    "{outcome_lbl} ~ {time_lbl} {threshold_lbl} {treat_lbl} ",
    "({norm_lbl}, {sw_lbl}{ctrl_lbl})"
  ) %>%
    as.character()
}

# ---- main function --------------------------------------------------------- #

run_event_study <- function(
    param_grid,
    data,
    rad,
    time_var = c("month_id", "qtr_id"),
    group_var = "site_id",
    cluster_var = "site_id",
    overwrite = FALSE,
    file_name = "did_results_site_qtr_{rad}.rds") {
  stopifnot(
    is.data.frame(param_grid),
    is.data.frame(data),
    is.logical(overwrite),
    length(rad) == 1
  )

  # ---- 0. results file ----------------------------------------------------- #
  res_path <- here::here(
    "book", "book_regs", glue::glue(file_name)
  )
  fs::dir_create(fs::path_dir(res_path))

  existing <- if (!overwrite && fs::file_exists(res_path)) readRDS(res_path) else list()

  # ---- 1. decide what we still need to run --------------------------------- #
  param_grid <- tibble::as_tibble(param_grid) %>%
    dplyr::mutate(
      model_name = purrr::pmap_chr(
        list(
          outcome,
          treatment_threshold,
          time_agg,
          normalized,
          same_switchers,
          treatment_type,
          controls
        ),
        build_model_name
      )
    )

  existing_names <- if (length(existing)) names(existing) else character(0)

  todo <- dplyr::anti_join(
    param_grid,
    tibble::tibble(model_name = existing_names),
    by = "model_name"
  )

  if (nrow(todo) == 0) {
    message("No new models to run for radius ", rad, ".")
    return(invisible(existing))
  }
  message("Estimating ", nrow(todo), " models for radius ", rad, "...")

  # ---- 2. run the models (parallel) --------------------------------------- #
  furrr::future_map(todo$model_name,
    function(mn) {
      # Get model iteration
      p <- dplyr::filter(todo, model_name == mn) %>%
        dplyr::slice(1)

      # Define treatment variable
      treatment_var <- paste0(
        "d_",
        p$treatment_threshold, "_",
        p$treatment_type, "_",
        p$time_agg
      )
      treatment_var <- ifelse(
        p$treatment_threshold == "cont",
        p$treatment_type,
        gsub("log_spill", "spill", treatment_var)
      )


      desc <- build_description(
        p$outcome,
        p$treatment_threshold,
        p$time_agg,
        p$treatment_type,
        p$normalized,
        p$same_switchers,
        unlist(p$controls)
      )

      message(" • ", mn, " …")

      res <- DIDmultiplegtDYN::did_multiplegt_dyn(
        df = data,
        outcome = p$outcome,
        group = group_var,
        time = time_var,
        treatment = treatment_var,
        effects = 6,
        placebo = 2,
        cluster = cluster_var,
        normalized = p$normalized,
        same_switchers = p$same_switchers,
        controls = unlist(p$controls),
        graph_off = TRUE
      )

      attr(res, "description") <- desc
      # return a named list so purrr::flatten will keep names
      rlist <- list(res)
      names(rlist) <- mn
      rlist
    },
    .options = furrr::furrr_options(seed = TRUE),
    .progress = TRUE
  ) %>%
    purrr::flatten() -> new_results

  # ---- 3. merge + save ----------------------------------------------------- #
  final <- c(existing, new_results)
  saveRDS(final, res_path)
  message("Results saved → ", res_path)

  invisible(final)
}
```


```{r}
#| eval: false
#| include: false

param_grid_bin <- expand.grid(
  outcome = c("log_price_median", "log_price_median_w"),
  treatment_threshold = c("mean", "p50", "p75", "p90"),
  time_agg = c("qtr", "yr"),
  treatment_type = c("spill_count", "spill_hrs"),
  normalized = c(TRUE),
  same_switchers = c(TRUE),
  stringsAsFactors = FALSE,
  controls = list(NULL)
)
param_grid_cont <- expand.grid(
  outcome = c("log_price_median", "log_price_median_w"),
  treatment_threshold = c("cont"),
  time_agg = c("qtr"),
  treatment_type = c("log_spill_count", "log_spill_hrs"),
  normalized = c(TRUE),
  same_switchers = c(TRUE),
  stringsAsFactors = FALSE,
  controls = list(NULL)
)
param_grid <- bind_rows(param_grid_bin, param_grid_cont)

# Radii to loop over
radii <- c(250, 500, 1000, 2000)

# Parallel processing
plan(multisession, workers = 3)

# Load data
## Data paths
path_house <- here::here("data", "processed", "panel_house")
path_site <- here::here("data", "processed", "dat_panel_site_level")
path_spill <- here::here("data", "processed", "agg_spill_stats")
path_house_controls <- here::here("data", "processed", "house_price.parquet")

# House panel data
house_qtr <- open_dataset(path_house) %>%
  filter(period_type == "quarterly") %>%
  select(-contains("month"))
# Aggregate site level panel data
site_qtr <- open_dataset(path_site) %>%
  filter(period_type == "quarterly") %>%
  select(-contains("month"))
# Spill statistics
spill_qtr <- open_dataset(path_spill) %>%
  filter(period_type == "quarterly") %>%
  collect() %>%
  select(-contains("month"), -contains("_mo"))
# House controls
house_controls <- open_dataset(path_house_controls) %>%
  collect() %>%
  select(
    -transaction_id,
    -price, -date_of_transfer, -postcode, -saon, -locality, -year,
    -easting, -northing, -longitude, -latitude
  )

for (r in radii) {
  message("Loading and preparing data for radius: ", r)

  # Site level panel data
  site_dat <- site_qtr %>%
    filter(radius == r) %>%
    collect()

  # Form panel data
  panel_site <- left_join(
    site_dat, spill_qtr,
    by = join_by(site_id, qtr_id, quarter, year, period_type)
  )

  message("Starting regressions for radius: ", r)
  run_event_study(
    param_grid = param_grid,
    data = panel_site,
    rad = r,
    time_var = "qtr_id",
    group_var = "site_id",
    cluster_var = "site_id",
    overwrite = TRUE,
    file_name = "did_results_site_qtr_{rad}.rds"
  )
}
```


```{r}
#| eval: false
#| include: false

# Create parameter grid
param_grid_bin <- expand.grid(
  outcome = c("log_price"),
  treatment_threshold = c("mean", "p50", "p75", "p90"),
  time_agg = c("qtr", "yr"),
  treatment_type = c("spill_count", "spill_hrs"),
  normalized = c(TRUE),
  same_switchers = c(TRUE),
  stringsAsFactors = FALSE,
  controls = list(NULL, c("property_type", "old_new", "duration"))
)
param_grid_cont <- expand.grid(
  outcome = c("log_price"),
  treatment_threshold = c("cont"),
  time_agg = c("qtr"),
  treatment_type = c("log_spill_count", "log_spill_hrs"),
  normalized = c(TRUE),
  same_switchers = c(TRUE),
  stringsAsFactors = FALSE,
  controls = list(NULL, c("property_type", "old_new", "duration"))
)
param_grid <- bind_rows(param_grid_bin, param_grid_cont)

# Radii to loop over
radii <- c(250, 500, 1000, 2000)

# Parallel processing
plan(multisession, workers = 3)

for (r in radii) {
  message("Loading and preparing data for radius: ", r)

  # Site level panel data
  house_dat <- house_qtr %>%
    filter(radius == r) %>%
    collect()

  # Form panel data
  panel_house <- left_join(
    house_dat, spill_qtr,
    by = join_by(site_id, qtr_id, quarter, year, period_type)
  ) %>%
    left_join(house_controls, by = join_by(house_id)) %>%
    mutate(
      property_type = factor(property_type, levels = c("D", "S", "T", "F", "O")),
      old_new = factor(old_new, levels = c("N", "Y")),
      duration = factor(duration, levels = c("F", "L"))
    )

  message("Starting regressions for radius: ", r)
  run_event_study(
    param_grid = param_grid,
    data = panel_house,
    rad = r,
    time_var = "qtr_id",
    group_var = "site_id",
    cluster_var = "site_id",
    overwrite = TRUE,
    file_name = "did_results_house_qtr_{rad}.rds"
  )
}
```


## Setting {#sec-05-01-setting}

```{r}
# Load results
load_results <- function(radii = c(250, 500, 1000, 2000),
                         freqs = c("qtr", "mo"),
                         dir_path = here("output", "regs"),
                         quiet = FALSE,
                         pattern = "*_did_results_site_{f}_{r}.rds") {
  safe_rds <- purrr::possibly(readRDS, otherwise = NULL)
  results <- list() # <- final nested list to be returned

  for (r in radii) {
    r_chr <- as.character(r)

    for (f in freqs) {
      pattern <- glue(pattern)
      file <- Sys.glob(file.path(dir_path, pattern))[1] # take first match

      # no file found → skip
      if (is.na(file) || is.null(file) || file == "") next

      obj <- safe_rds(file)
      if (is.null(obj)) next # corrupted file → skip

      # initialise slots if necessary
      if (is.null(results[[r_chr]])) results[[r_chr]] <- list()

      results[[r_chr]][[f]] <- obj # store
      if (!quiet) message("✓ loaded ", f, " ", r, ": ", basename(file))
    }
  }

  return(results)
}


# Make regression plot
plot_regression <- function(
    data,
    radius,
    model,
    freq = c("qtr", "mo"),
    use_desc = TRUE) {
  freq <- match.arg(freq)
  r <- as.character(radius)

  stopifnot(r %in% names(data))
  stopifnot(freq %in% names(data[[r]]))

  mod <- data[[r]][[freq]][[model]]
  if (is.null(mod)) {
    stop(
      "Model '", model, "' not found for radius ", r,
      " and freq '", freq, "'."
    )
  }

  if (is.null(mod$plot)) {
    stop("Model '", model, "' has no plot element.")
  }

  # ------------------------------------------------------------------------
  # Data wrangling
  df <- mod$plot$data %>%
    mutate(group = factor(
      ifelse(Time <= 0, "Pre", "Post"),
      levels = c("Pre", "Post")
    ))

  subtitle <- if (use_desc && !is.null(attr(mod, "description"))) {
    attr(mod, "description")
  } else {
    model
  }
  formula_caption <- paste0(
    "Regression specification: ", mod$args$outcome, " ~ ", mod$args$group,
    " + ", mod$args$time, " + ", mod$args$treatment
  )

  ggplot(df, aes(x = Time, y = Estimate, colour = group)) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
    geom_errorbar(aes(ymin = LB.CI, ymax = UB.CI), width = 0.2) +
    geom_point(aes(color = group), size = 1.2) +
    scale_color_manual(
      values = c(
        "Pre" = viridis(1, option = "magma"),
        "Post" = viridis(3, option = "magma")[2]
      ),
      breaks = c("Pre", "Post")
    ) +
    theme_minimal() +
    labs(
      x = "Time",
      y = "Estimate",
      subtitle = subtitle,
      caption = formula_caption
    ) +
    theme_pref +
    theme(plot.caption = element_text(hjust = 0))
}

results_qtr <- load_results(
  radii = c(250, 500, 1000, 2000),
  freqs = c("qtr", "mo"),
  dir_path = here("output", "regs"),
  quiet = TRUE
)
```

*This section is currently being revised as I read and process the recent DiD and event study literature. Some statements may be unclear or incorrect, which I will try to refine them as I go.*

We can conceptualise the setting as an event study where sewage spills constitute the treatment. To reduce compute time, I have aggregated the data to the X-meter radius around the spill site level by taking the median of house prices.

- **Treatment is non-absorbing:** spill sites can transition between treated and untreated states multiple times, as a location may experience large spill activity in one period and low in the next period (relative to other spill sites).
- **Treatment is staggered:** spills occur at different times across different locations
- **Treatment measurement:** spill severity is quantified by either incident count or duration in period $t$ (e.g., monthly), which is naturally continuous. However, we can simplify this into a binary treatment by classifying houses within radius X of a spill site as "treated" when the spill severity exceeds either the mean or a specified percentile threshold relative to other sites.
- **Fixed effects:** we can include both period and location-specific (spill site) fixed effects to estimate the effect of spills on house prices through within-spill site variation over time

Given the potential problems with the vanilla TWFE presented in the recent literature, I decide to use the Chaisemartin & d'Haultefoeuille (2024) estimator using the package `DIDmultiplegtDYN.` This estimator allows for a wide range of settings, including non-absorbing treatment, staggered treatment, continuous treatment, and many other settings that I still need to understand. 

## Basic Event Study Regressions {#sec-05-02-basic-event-study-regressions}

The following figures show the dynamic effect of sewage spills on house prices over time. Each graph plots changes in median house prices within X-metre radius buffers around spill sites, measured monthly. House prices are aggregated at the spill level using median values for each buffer distance. A buffer is considered "treated" in a given month when the number of spills exceeds either the average or a specified percentile of spill counts across all buffers, **calculated over either a monthly or yearly period**.

In the event study regressions, the effects are estimated for:

- **Same switchers only.** This ensures that event-study effects are estimated only using switchers for whom all the event-study effects can be estimated. This avoids the problem that if treatment effects are heterogeneous across spill sites where treatment switches, changes in the estimated effects across different time horizons might reflect changes in the composition of the sample rather than actual dynamic treatment effects.
- **Normalised.** This scales the estimates to represent effects per unit of treatment rather than total effects. For spill sites, this means showing the impact per unit of treatment intensity, making estimates comparable across time periods and sites.

Overall, all specifications show practically no effect of spills on house prices.

### Binary Treatment - Average Spill Count {#sec-05-02-01-binary-average}

::: {.panel-tabset group="threshold"}

#### 250m

::: {.panel-tabset group="radius-250m"}

##### Count Qt

```{r}
plot_regression(
  data = results_qtr, radius = 250, freq = "qtr",
  model = "model_bin_logp_sc_mean_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_regression(
  data = results_qtr, radius = 250, freq = "qtr",
  model = "model_bin_logp_sc_mean_yr_sw_norm"
)
```

##### Duration Qt
```{r}
plot_regression(
  data = results_qtr, radius = 250, freq = "qtr",
  model = "model_bin_logp_sh_mean_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_regression(
  data = results_qtr, radius = 250, freq = "qtr",
  model = "model_bin_logp_sh_mean_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-500m"}

##### Count Qt

```{r}
plot_regression(
  data = results_qtr, radius = 500, freq = "qtr",
  model = "model_bin_logp_sc_mean_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_regression(
  data = results_qtr, radius = 500, freq = "qtr",
  model = "model_bin_logp_sc_mean_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_regression(
  data = results_qtr, radius = 500, freq = "qtr",
  model = "model_bin_logp_sh_mean_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_regression(
  data = results_qtr, radius = 500, freq = "qtr",
  model = "model_bin_logp_sh_mean_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-1000m"}  

##### Count Qt

```{r}
plot_regression(
  data = results_qtr, radius = 1000, freq = "qtr",
  model = "model_bin_logp_sc_mean_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_regression(
  data = results_qtr, radius = 1000, freq = "qtr",
  model = "model_bin_logp_sc_mean_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_regression(
  data = results_qtr, radius = 1000, freq = "qtr",
  model = "model_bin_logp_sh_mean_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_regression(
  data = results_qtr, radius = 1000, freq = "qtr",
  model = "model_bin_logp_sh_mean_yr_sw_norm"
)
```

:::

#### 2000m

::: {.panel-tabset group="radius-2000m"}

##### Count Qt

```{r}
plot_regression(
  data = results_qtr, radius = 2000, freq = "qtr",
  model = "model_bin_logp_sc_mean_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_regression(
  data = results_qtr, radius = 2000, freq = "qtr",
  model = "model_bin_logp_sc_mean_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_regression(
  data = results_qtr, radius = 2000, freq = "qtr",
  model = "model_bin_logp_sh_mean_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_regression(
  data = results_qtr, radius = 2000, freq = "qtr",
  model = "model_bin_logp_sh_mean_yr_sw_norm"
)
```

:::

:::

### Binary Treatment - Median Spill Count {#sec-05-02-02-binary-median}

::: {.panel-tabset group="threshold"}

#### 250m

::: {.panel-tabset group="radius-250m"}

##### Count Qt

```{r}
plot_regression(
  data = results_qtr, radius = 250, freq = "qtr",
  model = "model_bin_logp_sc_p50_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_regression(
  data = results_qtr, radius = 250, freq = "qtr",
  model = "model_bin_logp_sc_p50_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_regression(
  data = results_qtr, radius = 250, freq = "qtr",
  model = "model_bin_logp_sh_p50_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_regression(
  data = results_qtr, radius = 250, freq = "qtr",
  model = "model_bin_logp_sh_p50_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-500m"}

##### Count Qt

```{r}
plot_regression(
  data = results_qtr, radius = 500, freq = "qtr",
  model = "model_bin_logp_sc_p50_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_regression(
  data = results_qtr, radius = 500, freq = "qtr",
  model = "model_bin_logp_sc_p50_yr_sw_norm"
)
```

##### Duration Qt

```{r}  
plot_regression(
  data = results_qtr, radius = 500, freq = "qtr",
  model = "model_bin_logp_sh_p50_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_regression(
  data = results_qtr, radius = 500, freq = "qtr",
  model = "model_bin_logp_sh_p50_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-1000m"}

##### Count Qt

```{r}
plot_regression(
  data = results_qtr, radius = 1000, freq = "qtr",
  model = "model_bin_logp_sc_p50_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_regression(
  data = results_qtr, radius = 1000, freq = "qtr",
  model = "model_bin_logp_sc_p50_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_regression(
  data = results_qtr, radius = 1000, freq = "qtr",
  model = "model_bin_logp_sh_p50_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_regression(
  data = results_qtr, radius = 1000, freq = "qtr",
  model = "model_bin_logp_sh_p50_yr_sw_norm"
)
```

:::

#### 2000m

::: {.panel-tabset group="radius-2000m"}

##### Count Qt

```{r}
plot_regression(
  data = results_qtr, radius = 2000, freq = "qtr",
  model = "model_bin_logp_sc_p50_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_regression(
  data = results_qtr, radius = 2000, freq = "qtr",
  model = "model_bin_logp_sc_p50_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_regression(
  data = results_qtr, radius = 2000, freq = "qtr",
  model = "model_bin_logp_sh_p50_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_regression(
  data = results_qtr, radius = 2000, freq = "qtr",
  model = "model_bin_logp_sh_p50_yr_sw_norm"
)
```

:::

:::

### Binary Treatment - 75th Percentile Spill Count {#sec-05-02-03-binary-p75}

::: {.panel-tabset group="threshold"}  

#### 250m

::: {.panel-tabset group="radius-250m"}

##### Count Qt

```{r}
plot_regression(
  data = results_qtr, radius = 250, freq = "qtr",
  model = "model_bin_logp_sc_p75_qtr_sw_norm"
)
```

##### Count Yr

```{r}  
plot_regression(
  data = results_qtr, radius = 250, freq = "qtr",
  model = "model_bin_logp_sc_p75_yr_sw_norm"
)
```

##### Duration Qt

```{r}  
plot_regression(
  data = results_qtr, radius = 250, freq = "qtr",
  model = "model_bin_logp_sh_p75_qtr_sw_norm"
)
```

##### Duration Yr

```{r}  
plot_regression(
  data = results_qtr, radius = 250, freq = "qtr",
  model = "model_bin_logp_sh_p75_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-500m"}

##### Count Qt

```{r}
plot_regression(
  data = results_qtr, radius = 500, freq = "qtr",
  model = "model_bin_logp_sc_p75_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_regression(
  data = results_qtr, radius = 500, freq = "qtr",
  model = "model_bin_logp_sc_p75_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_regression(
  data = results_qtr, radius = 500, freq = "qtr",
  model = "model_bin_logp_sh_p75_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_regression(
  data = results_qtr, radius = 500, freq = "qtr",
  model = "model_bin_logp_sh_p75_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-1000m"}

##### Count Qt

```{r}
plot_regression(
  data = results_qtr, radius = 1000, freq = "qtr",
  model = "model_bin_logp_sc_p75_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_regression(
  data = results_qtr, radius = 1000, freq = "qtr",
  model = "model_bin_logp_sc_p75_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_regression(
  data = results_qtr, radius = 1000, freq = "qtr",
  model = "model_bin_logp_sh_p75_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_regression(
  data = results_qtr, radius = 1000, freq = "qtr",
  model = "model_bin_logp_sh_p75_yr_sw_norm"
)
```

:::

#### 2000m

::: {.panel-tabset group="radius-2000m"}

##### Count Qt

```{r}
plot_regression(
  data = results_qtr, radius = 2000, freq = "qtr",
  model = "model_bin_logp_sc_p75_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_regression(
  data = results_qtr, radius = 2000, freq = "qtr",
  model = "model_bin_logp_sc_p75_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_regression(
  data = results_qtr, radius = 2000, freq = "qtr",
  model = "model_bin_logp_sh_p75_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_regression(
  data = results_qtr, radius = 2000, freq = "qtr",
  model = "model_bin_logp_sh_p75_yr_sw_norm"
)
```

:::

:::

### Binary Treatment - 90th Percentile Spill Count {#sec-05-02-04-binary-p90}

::: {.panel-tabset group="threshold"}    

#### 250m

::: {.panel-tabset group="radius-250m"}

##### Count Qt

```{r}
plot_regression(
  data = results_qtr, radius = 250, freq = "qtr",
  model = "model_bin_logp_sc_p90_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_regression(
  data = results_qtr, radius = 250, freq = "qtr",
  model = "model_bin_logp_sc_p90_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_regression(
  data = results_qtr, radius = 250, freq = "qtr",
  model = "model_bin_logp_sh_p90_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_regression(
  data = results_qtr, radius = 250, freq = "qtr",
  model = "model_bin_logp_sh_p90_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-500m"}

##### Count Qt

```{r}
plot_regression(
  data = results_qtr, radius = 500, freq = "qtr",
  model = "model_bin_logp_sc_p90_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_regression(
  data = results_qtr, radius = 500, freq = "qtr",
  model = "model_bin_logp_sc_p90_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_regression(
  data = results_qtr, radius = 500, freq = "qtr",
  model = "model_bin_logp_sh_p90_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_regression(
  data = results_qtr, radius = 500, freq = "qtr",
  model = "model_bin_logp_sh_p90_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-1000m"}

##### Count Qt

```{r}
plot_regression(
  data = results_qtr, radius = 1000, freq = "qtr",
  model = "model_bin_logp_sc_p90_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_regression(
  data = results_qtr, radius = 1000, freq = "qtr",
  model = "model_bin_logp_sc_p90_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_regression(
  data = results_qtr, radius = 1000, freq = "qtr",
  model = "model_bin_logp_sh_p90_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_regression(
  data = results_qtr, radius = 1000, freq = "qtr",
  model = "model_bin_logp_sh_p90_yr_sw_norm"
)
```

:::

#### 2000m

::: {.panel-tabset group="radius-2000m"}

##### Count Qt

```{r}
plot_regression(
  data = results_qtr, radius = 2000, freq = "qtr",
  model = "model_bin_logp_sc_p90_qtr_sw_norm"
)
```

##### Count Yr

```{r}
plot_regression(
  data = results_qtr, radius = 2000, freq = "qtr",
  model = "model_bin_logp_sc_p90_yr_sw_norm"
)
```

##### Duration Qt

```{r}
plot_regression(
  data = results_qtr, radius = 2000, freq = "qtr",
  model = "model_bin_logp_sh_p90_qtr_sw_norm"
)
```

##### Duration Yr

```{r}
plot_regression(
  data = results_qtr, radius = 2000, freq = "qtr",
  model = "model_bin_logp_sh_p90_yr_sw_norm"
)
```

:::

:::

### Continuous Treatment - Average Spill Count {#sec-05-02-04-continuous-treatment}

::: {.panel-tabset group="continuous"}

#### 250m

::: {.panel-tabset group="radius-250m-cont"}

##### Count

```{r}
plot_regression(
  data = results_qtr, radius = 250, freq = "qtr",
  model = "model_cont_logp_sc_cont_qtr_sw_norm"
)
```

##### Duration

```{r}
plot_regression(
  data = results_qtr, radius = 250, freq = "qtr",
  model = "model_cont_logp_sh_cont_qtr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-500m-cont"}

##### Count

```{r}
plot_regression(
  data = results_qtr, radius = 500, freq = "qtr",
  model = "model_cont_logp_sc_cont_qtr_sw_norm"
)
```

##### Duration

```{r}
plot_regression(
  data = results_qtr, radius = 500, freq = "qtr",
  model = "model_cont_logp_sh_cont_qtr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-1000m-cont"}

##### Count

```{r}
plot_regression(
  data = results_qtr, radius = 1000, freq = "qtr",
  model = "model_cont_logp_sc_cont_qtr_sw_norm"
)
```

##### Duration

```{r}
plot_regression(
  data = results_qtr, radius = 1000, freq = "qtr",
  model = "model_cont_logp_sh_cont_qtr_sw_norm"
)
```

:::

#### 2000m

::: {.panel-tabset group="radius-2000m-cont"}

##### Count

```{r}
plot_regression(
  data = results_qtr, radius = 2000, freq = "qtr",
  model = "model_cont_logp_sc_cont_qtr_sw_norm"
)
```

##### Duration

```{r}
plot_regression(
  data = results_qtr, radius = 2000, freq = "qtr",
  model = "model_cont_logp_sh_cont_qtr_sw_norm"
)
```

:::

:::

## Notes and Things to Try

- Temporal lags: Correlation between lagged spills (1–6 months prior) and prices
- Event studies using distance weighted aggregations
- Using quarterly data to reduce seasonality
- Using P90

```{r}
#| eval: false
dat_panel_site <- open_dataset(
  here::here("data", "processed", "dat_panel_site_qtr")
) %>%
  filter(radius == 250) %>%
  collect()

dat_panel_site %>%
  filter(site_id == 2)
```
