---
author: "Jacopo Olivieri"
date: 2024-04-01
editor: source
format: html
number-sections: true
number-depth: 4
execute: 
  echo: true
  warning: false
  message: false
  freeze: auto
  fig-width: 9
  fig-asp: 0.618 
  fig-align: center
---

# Event Study Walkthrough {#sec-event-study-walkthrough}

This document walks through estimating an event study using both the `DIDmultiplegtDYN` and `fixest` packages for a single specification.

**Specification:**
- Outcome: `log_price_median`
- Treatment: Binary, `treated_spill_count_mean_mo` (monthly spill count > mean)
- Radius: `250m`
- Unit: `site_id`
- Time: `month_id`

## Setup and Data Loading

```{r setup_walkthrough}
#| message: true

# Load required packages
required_packages <- c(
  "tidyverse", "here", "arrow", "dbplyr",
  "DIDmultiplegtDYN", "fixest", "ggplot2"
)
install_if_missing <- function(packages) {
  new_packages <- packages[!sapply(packages, requireNamespace, quietly = TRUE)]
  if (length(new_packages) > 0) {
    install.packages(new_packages)
  }
  invisible(sapply(packages, library, character.only = TRUE))
}
install_if_missing(required_packages)

# Ggplot theme (simplified)
theme_pref <- theme_minimal(base_size = 11) +
  theme(
    plot.title = element_text(face = "bold"),
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
    legend.position = "bottom"
  )
```

```{r data_load_and_sample}
#| message: true

# Specify radius and load data
radius_to_load <- 500
message(paste("Loading data for radius:", radius_to_load))

dat_panel_site_250_full <- tryCatch(
  {
    open_dataset(
      here::here("data", "processed", "dat_panel_site_mo")
    ) %>%
      filter(radius == radius_to_load) %>%
      collect()
  },
  error = function(e) {
    message("Error loading data: ", e$message)
    return(NULL)
  }
)

if (is.null(dat_panel_site_250_full)) {
  stop("Data loading failed. Cannot proceed.")
} else {
  message("Full data loaded successfully.")

  # Sample site_ids
  set.seed(123) # for reproducibility
  n_sample <- 10000
  unique_sites <- unique(dat_panel_site_250_full$site_id)
  n_unique_sites <- length(unique_sites)

  if (n_unique_sites > n_sample) {
    message(paste("Sampling", n_sample, "site_ids from", n_unique_sites, "unique sites."))
    sampled_site_ids <- sample(unique_sites, n_sample)
    dat_panel_site_250 <- dat_panel_site_250_full %>%
      filter(site_id %in% sampled_site_ids)
    message(paste("Using a sample of", n_sample, "sites."))
  } else {
    message(paste("Using all", n_unique_sites, "available sites (less than or equal to target sample size of", n_sample, ")."))
    dat_panel_site_250 <- dat_panel_site_250_full
  }

  # Clear the full dataset if no longer needed, to save memory
  # rm(dat_panel_site_250_full)
  # gc()

  # Optional: Glimpse the sampled data
  # glimpse(dat_panel_site_250)
}
```

## DIDmultiplegtDYN Analysis

```{r did_multiplegt_dyn_walkthrough}
#| message: true

message("Running DIDmultiplegtDYN...")

# Define parameters
did_outcome <- "log_price_median"
did_treatment <- "treated_spill_hrs_p90_mo"

did_multi_results <- tryCatch(
  {
    did_multiplegt_dyn(
      df = dat_panel_site_250,
      outcome = did_outcome,
      group = "site_id",
      time = "month_id",
      treatment = did_treatment,
      effects = 8, # Same as your original setup
      placebo = 0, # Same as your original setup
      cluster = "site_id",
      normalized = TRUE, # As per your original setup
      same_switchers = TRUE, # As per your original setup
      less_conservative_se = TRUE,
      graph_off = FALSE # Keep the plot object
    )
  },
  error = function(e) {
    message("Error running did_multiplegt_dyn: ", e$message)
    return(NULL)
  }
)

# Check and display plot
if (!is.null(did_multi_results) && !is.null(did_multi_results$plot)) {
  message("DIDmultiplegtDYN estimation complete. Displaying plot.")

  # Customize and print the plot
  did_multi_plot <- did_multi_results$plot +
    labs(
      title = "DIDmultiplegtDYN Event Study",
      subtitle = paste("Outcome:", did_outcome, " | Treatment:", did_treatment, " | Radius:", radius_to_load, "m"),
      caption = "Normalized=TRUE, Same Switchers=TRUE"
    ) +
    theme_pref

  print(did_multi_plot)
} else {
  message("DIDmultiplegtDYN estimation failed or produced no plot.")
}

```

## Fixest (Sun & Abraham) Analysis

This section uses `fixest::sunab` to estimate the same event study.

```{r fixest_walkthrough}
#| message: true

message("Running fixest::sunab...")

# 1. Prepare data: Create cohort_id
fixest_treatment_var <- "treated_spill_hrs_p90_mo"

dat_panel_fixest <- dat_panel_site_250 %>%
  # Ensure treatment is 0/1, handle potential NAs if they mean untreated
  mutate({{ fixest_treatment_var }} := ifelse(is.na(.data[[fixest_treatment_var]]), 0, .data[[fixest_treatment_var]])) %>%
  # Remove observations with NA outcome *before* calculating cohort
  filter(!is.na(log_price_median)) %>%
  group_by(site_id) %>%
  # Calculate first period of treatment
  mutate(cohort_id = min(month_id[.data[[fixest_treatment_var]] == 1], na.rm = TRUE)) %>%
  ungroup() %>%
  # Set cohort_id to NA for never-treated (Inf becomes NA)
  mutate(cohort_id = ifelse(is.infinite(cohort_id), NA, cohort_id))

# Check if any units are treated
if (all(is.na(dat_panel_fixest$cohort_id))) {
  message("Warning: No site_id ever meets the treatment criteria for '", fixest_treatment_var, "'. Cannot run fixest::sunab.")
  fixest_results <- NULL
} else {
  message("Cohort ID created. Proceeding with fixest estimation.")

  # 2. Estimate model
  fixest_outcome <- "log_price_median"
  formula_fixest <- as.formula(paste0("`", fixest_outcome, "` ~ sunab(cohort_id, month_id) | site_id + month_id"))

  fixest_results <- tryCatch(
    {
      feols(
        fml = formula_fixest,
        data = dat_panel_fixest,
        cluster = ~site_id
        # We can add , notes = FALSE to suppress default fixest notes if desired
      )
    },
    error = function(e) {
      message("Error running feols: ", e$message)
      return(NULL)
    }
  )
}

# 3. Plot results
if (!is.null(fixest_results)) {
  message("Fixest estimation complete. Displaying plot.")

  # Get model description elements
  outcome_label <- "Log Price Median"
  treat_label <- "Spill Count > Mean (Monthly)"

  fixest_plot <- tryCatch(
    {
      gg_fixest <- iplot(fixest_results,
        # Use labs() for titles/captions to work better with theme_pref
        # main = paste("Fixest S&A Event Study | Radius:", radius_to_load, "m"),
        xlab = "Months Relative to First Treatment",
        ylab = "Estimate",
        # sub = paste("Outcome:", outcome_label, " | Treatment:", treat_label), # Use labs subtitle
        ggplot = TRUE # Render as ggplot object
      )

      # Add titles, theme, and horizontal line manually
      gg_fixest +
        theme_pref +
        geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
        labs(
          title = paste("Fixest S&A Event Study | Radius:", radius_to_load, "m"),
          subtitle = paste("Outcome:", outcome_label, " | Treatment:", treat_label),
          caption = paste("Model:", deparse(formula_fixest), "\nCluster SEs: site_id")
        ) +
        theme(plot.caption = element_text(hjust = 0))
    },
    error = function(e) {
      message(paste("Error generating iplot:", e$message))
      return(NULL)
    }
  )

  if (!is.null(fixest_plot)) {
    print(fixest_plot)
  }
} else {
  message("Fixest estimation failed or was skipped.")
}

```

