---
author: "Jacopo Olivieri"
date: 2024-04-01
editor: source
format: html
number-sections: true
number-depth: 4
execute: 
  echo: false
  warning: false
  message: false
  freeze: auto
  fig-width: 9
  fig-asp: 0.618 
  fig-align: center
---

# Event Study {#sec-06-event-study}

```{r setup, include=FALSE}
# Initialize packages with version control
if (!requireNamespace("renv", quietly = TRUE)) {
  install.packages("renv")
}

# Run manual renv commands if needed
# renv::activate() # Activate the project library
# renv::restore()  # Restore the environment if running for first time
# renv::snapshot()  # After adding/updating packages, snapshot the state

# Load required packages
required_packages <- c(
  "rmarkdown",
  "rio",
  "tidyverse",
  "purrr",
  "here",
  "janitor",
  "viridis",
  "data.table",
  "DIDmultiplegtDYN",
  "arrow",
  "furrr",
  "glue"
)
install_if_missing <- function(packages) {
  new_packages <- packages[!sapply(packages, requireNamespace, quietly = TRUE)]
  if (length(new_packages) > 0) {
    install.packages(new_packages)
  }
  invisible(sapply(packages, library, character.only = TRUE))
}
install_if_missing(required_packages)


# Initialize logging
log_path <- here::here("output", "log", "house_data_exploration")
if (!dir.exists(dirname(log_path))) {
  dir.create(dirname(log_path), recursive = TRUE)
}
logger::log_appender(logger::appender_file(log_path))
logger::log_layout(logger::layout_glue_colors)

# Ggplot theme
theme_pref <- theme_minimal() +
  theme(
    text = element_text(size = 12),
    plot.title = element_text(
      face = "bold",
      size = 12,
      margin = ggplot2::margin(b = 10, unit = "pt")
    ),
    axis.title = element_text(face = "bold", size = 10),
    axis.text = element_text(angle = 45, hjust = 1, vjust = 1, size = 8),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_line(color = "gray95"),
    panel.grid.major.y = element_line(color = "gray95"),
    legend.position = "bottom",
    legend.title = element_text(face = "bold", size = 10),
    legend.text = element_text(size = 8),
    plot.margin = ggplot2::margin(t = 10, r = 10, b = 10, l = 10, unit = "pt")
  )
```


## Setting {#sec-06-01-setting}

*This section is currently being revised as I read and process the recent DiD and event study literature. Some statements may be unclear or incorrect, which I will try to refine them as I go.*

We can conceptualise the empirical setting as an event study, where *treatment* occurs when a location experiences a sewage spill above a defined threshold, and house prices serve as the outcome variable.

- **Absorbing vs. non-absorbing treatment:** Treatment status can be defined in two ways. In a non-absorbing framework, locations may alternate between treated and control states, depending on spill severity in each period. For example, a location may experience a large spill in one quarter and no spill in the next quarter. Alternatively, in an absorbing framework, a location is considered treated from the first period it exceeds the threshold and remains treated thereafter.
- **Treatment is staggered:** Spill events, and therefore treatment, occur at different times across different locations.
- **Treatment measurement:** Spill severity is measured by either the number of incidents or by total duration in a given period $t$ (e.g., monthly or quarterly). While these measures are continuous, we can construct a binary treatment indicator by classifying a house as treated if it lies within radius X of a spill site whose severity exceeds a predetermined threshold.
- **Fixed effects:** To (partially) address confounding, we include both time and location fixed effects. This ensures that identification relies on within-location variation over time, controlling for any time-invariant differences across locations and common shocks across periods.

Given the potential problems with the vanilla TWFE presented in the recent literature, I decide to use the Chaisemartin & d'Haultefoeuille (2024) estimator using the package `DIDmultiplegtDYN.` This estimator allows for a wide range of settings, including non-absorbing treatment, staggered treatment, continuous treatment, and many other settings that I still need to understand. 

## House Sales: Site-Level Event Study Regressions Within Spill Buffers {#sec-06-02-basic-event-study-regressions}

The following figures present the dynamic effects of sewage spills on house prices within an X-metre radius around spill sites. For each spill site and quarter, I aggregate spill statistics and average house prices within the corresponding X-metre buffer.^[This aggregation is primarily for computational efficiency given the size of the dataset; the analysis could alternatively be conducted at the individual house level.] The estimated regression coefficients capture the within-buffer change in average house prices over time, relative to untreated periods, conditional on the buffer experiencing a high-severity spill in a given quarter. That is, they reflect how **prices evolve in a given spill site's buffer following the occurrence of a high-severity spill within that buffer**.

The regressions below are estimated using the Chaisemartin & d'Haultefoeuille (2024) estimator using the package `DIDmultiplegtDYN.` This estimator allows for a wide range of settings, including non-absorbing treatment, staggered treatment, continuous treatment, and many other settings that I still need to understand. In the event study regressions, the effects are estimated for:

- **Same switchers only.** This ensures that event-study effects are estimated only using switchers for whom all the event-study effects can be estimated. This avoids the problem that if treatment effects are heterogeneous across spill sites where treatment switches, changes in the estimated effects across different time horizons might reflect changes in the composition of the sample rather than actual dynamic treatment effects.
- **Normalised.** This scales the estimates to represent effects per unit of treatment rather than total effects. For spill sites, this means showing the impact per unit of treatment intensity, making estimates comparable across time periods and sites.

```{r func-run-event-study-chaisemartin}
#| eval: false
#| include: false

# ---------- Function to run event study ----------

# Build model name (helper function)
build_model_name <- function(
  outcome,
  treatment_threshold,
  time_agg,
  normalized,
  same_switchers,
  treatment_type,
  controls = NULL
) {
  # Set binary (bin) or continuous
  base <- "model_"
  base <- ifelse(
    treatment_threshold == "cont",
    paste0(base, "cont"),
    paste0(base, "bin")
  )

  # Set spill statistic
  base <- ifelse(grepl("log_", outcome), paste0(base, "_logp"), base)
  base <- ifelse(grepl("_w$", outcome), paste0(base, "_w"), base)
  tt <- ifelse(grepl("spill_count", treatment_type), "sc", "sh")

  # Set model name
  base <- paste(base, tt, treatment_threshold, time_agg, sep = "_")

  # Set model parameters
  if (same_switchers) {
    base <- paste0(base, "_sw")
  }
  if (normalized) {
    base <- paste0(base, "_norm")
  }

  # Set controls
  if (!is.null(controls) && length(controls)) {
    ctrl_suffix <- paste(controls, collapse = "_")
    base <- paste(base, ctrl_suffix, sep = "_")
  }

  return(base)
}

# Build model description (helper function)
build_description <- function(
  outcome,
  treatment_threshold,
  time_agg,
  treatment_type,
  normalized,
  same_switchers,
  controls = NULL
) {
  # Labels
  outcome_lbl <- dplyr::case_when(
    outcome == "price_median_w" ~ "Weighted Price Median",
    outcome == "log_price_median_w" ~ "Weighted Log Price Median",
    outcome == "price_median" ~ "Price Median",
    outcome == "log_price_median" ~ "Log Price Median",
    outcome == "price" ~ "Price",
    outcome == "log_price" ~ "Log Price",
    TRUE ~ outcome
  )

  threshold_lbl <- dplyr::case_when(
    treatment_threshold == "mean" ~ "Mean",
    treatment_threshold == "p50" ~ "P50",
    treatment_threshold == "p75" ~ "P75",
    treatment_threshold == "p90" ~ "P90",
    treatment_threshold == "max" ~ "Max",
    treatment_threshold == "cont" ~ "Continuous",
    TRUE ~ stringr::str_to_title(treatment_threshold)
  )

  time_lbl <- dplyr::case_when(
    time_agg == "mo" ~ "Monthly",
    time_agg == "qtr" ~ "Quarterly",
    time_agg == "yr" ~ "Yearly",
    TRUE ~ time_agg
  )
  time_lbl <- ifelse(threshold_lbl == "Continuous", "", time_lbl)

  treat_lbl <- dplyr::case_when(
    grepl("spill_count", treatment_type) & treatment_threshold != "cont" ~
      "Spill Count",
    grepl("spill_hrs", treatment_type) & treatment_threshold != "cont" ~
      "Spill Hours",
    grepl("spill_count", treatment_type) & treatment_threshold == "cont" ~
      "Log Spill Count",
    grepl("spill_hrs", treatment_type) & treatment_threshold == "cont" ~
      "Log Spill Hours",
    TRUE ~ NA_character_
  )

  norm_lbl <- ifelse(normalized, "Norm", "No Norm")
  sw_lbl <- ifelse(same_switchers, "Same Switchers", "All Switchers")

  ctrl_lbl <- if (is.null(controls) || length(controls) == 0) {
    ""
  } else {
    paste0("; Controls: ", paste(controls, collapse = ", "))
  }

  # Compose
  glue::glue(
    "{outcome_lbl} ~ {time_lbl} {threshold_lbl} {treat_lbl} ",
    "({norm_lbl}, {sw_lbl}{ctrl_lbl})"
  ) %>%
    as.character()
}

# ---- main function --------------------------------------------------------- #

run_event_study <- function(
  param_grid,
  data,
  rad,
  time_var = c("month_id", "qtr_id"),
  group_var = "site_id",
  cluster_var = "site_id",
  overwrite = FALSE,
  file_name = "sales_did_results_site_qtr_{rad}.rds"
) {
  stopifnot(
    is.data.frame(param_grid),
    is.data.frame(data),
    is.logical(overwrite),
    length(rad) == 1
  )

  # ---- 0. results file ----------------------------------------------------- #
  res_path <- here::here(
    "book",
    "book_regs",
    glue::glue(file_name)
  )
  fs::dir_create(fs::path_dir(res_path))

  existing <- if (!overwrite && fs::file_exists(res_path)) {
    readRDS(res_path)
  } else {
    list()
  }

  # ---- 1. decide what we still need to run --------------------------------- #
  param_grid <- tibble::as_tibble(param_grid) %>%
    dplyr::mutate(
      model_name = purrr::pmap_chr(
        list(
          outcome,
          treatment_threshold,
          time_agg,
          normalized,
          same_switchers,
          treatment_type,
          controls
        ),
        build_model_name
      )
    )

  existing_names <- if (length(existing)) names(existing) else character(0)

  todo <- dplyr::anti_join(
    param_grid,
    tibble::tibble(model_name = existing_names),
    by = "model_name"
  )

  if (nrow(todo) == 0) {
    message("No new models to run for radius ", rad, ".")
    return(invisible(existing))
  }
  message("Estimating ", nrow(todo), " models for radius ", rad, "...")

  # ---- 2. run the models (parallel) --------------------------------------- #
  furrr::future_map(
    todo$model_name,
    function(mn) {
      # Get model iteration
      p <- dplyr::filter(todo, model_name == mn) %>%
        dplyr::slice(1)

      # Define treatment variable
      treatment_var <- paste0(
        "d_",
        p$treatment_threshold,
        "_",
        p$treatment_type,
        "_",
        p$time_agg
      )
      treatment_var <- ifelse(
        p$treatment_threshold == "cont",
        p$treatment_type,
        gsub("log_spill", "spill", treatment_var)
      )

      desc <- build_description(
        p$outcome,
        p$treatment_threshold,
        p$time_agg,
        p$treatment_type,
        p$normalized,
        p$same_switchers,
        unlist(p$controls)
      )

      message(" • ", mn, " …")

      res <- DIDmultiplegtDYN::did_multiplegt_dyn(
        df = data,
        outcome = p$outcome,
        group = group_var,
        time = time_var,
        treatment = treatment_var,
        effects = 6,
        placebo = 2,
        cluster = cluster_var,
        normalized = p$normalized,
        same_switchers = p$same_switchers,
        controls = unlist(p$controls),
        graph_off = TRUE
      )

      attr(res, "description") <- desc
      # return a named list so purrr::flatten will keep names
      rlist <- list(res)
      names(rlist) <- mn
      rlist
    },
    .options = furrr::furrr_options(seed = TRUE),
    .progress = TRUE
  ) %>%
    purrr::flatten() -> new_results

  # ---- 3. merge + save ----------------------------------------------------- #
  final <- c(existing, new_results)
  saveRDS(final, res_path)
  message("Results saved → ", res_path)

  invisible(final)
}
```


```{r exec-run-event-study-house-site-level}
#| eval: false
#| include: false

param_grid_bin <- expand.grid(
  outcome = c("log_price_median", "log_price_median_w"),
  treatment_threshold = c("mean", "p50", "p75", "p90"),
  time_agg = c("qtr", "yr"),
  treatment_type = c("spill_count", "spill_hrs"),
  normalized = c(TRUE),
  same_switchers = c(TRUE),
  stringsAsFactors = FALSE,
  controls = list(NULL)
)
param_grid_cont <- expand.grid(
  outcome = c("log_price_median", "log_price_median_w"),
  treatment_threshold = c("cont"),
  time_agg = c("qtr"),
  treatment_type = c("log_spill_count", "log_spill_hrs"),
  normalized = c(TRUE),
  same_switchers = c(TRUE),
  stringsAsFactors = FALSE,
  controls = list(NULL)
)
param_grid <- bind_rows(param_grid_bin, param_grid_cont)

# Radii to loop over
radii <- c(250, 500, 1000, 2000)

# Parallel processing
plan(multisession, workers = 3)

# Load data
## Data paths
path_house <- here::here("data", "processed", "within_radius_panel", "sales")
path_site <- here::here("data", "processed", "dat_panel_site", "sales")
path_spill <- here::here("data", "processed", "agg_spill_stats", "agg_spill_stats_qtr.parquet")
path_house_controls <- here::here("data", "processed", "house_price.parquet")

# House panel data
house_qtr <- open_dataset(path_house) %>%
  filter(period_type == "quarterly") %>%
  select(-contains("month"))
# Aggregate site level panel data
site_qtr <- open_dataset(path_site) %>%
  filter(period_type == "quarterly") %>%
  select(-contains("month"))
# Spill statistics
spill_qtr <- import(path_spill, trust = TRUE) %>%
  select(-contains("month"), -contains("_mo"))
# House controls
house_controls <- open_dataset(path_house_controls) %>%
  collect() %>%
  select(
    -transaction_id,
    -price,
    -date_of_transfer,
    -postcode,
    -saon,
    -locality,
    -easting,
    -northing,
    -longitude,
    -latitude
  )

for (r in radii) {
  message("Loading and preparing data for radius: ", r)

  # Site level panel data
  site_dat <- site_qtr %>%
    filter(radius == r) %>%
    collect()

  # Form panel data
  panel_site <- left_join(
    site_dat,
    spill_qtr,
    by = join_by(site_id, qtr_id)
  )

  message("Starting regressions for radius: ", r)
  run_event_study(
    param_grid = param_grid,
    data = panel_site,
    rad = r,
    time_var = "qtr_id",
    group_var = "site_id",
    cluster_var = "site_id",
    overwrite = TRUE,
    file_name = "sales_did_results_site_qtr_{rad}.rds"
  )
}
```


```{r exec-run-event-study-house-house-level}
#| eval: false
#| include: false

# Create parameter grid
param_grid_bin <- expand.grid(
  outcome = c("log_price"),
  treatment_threshold = c("mean", "p50", "p75", "p90"),
  time_agg = c("qtr", "yr"),
  treatment_type = c("spill_count", "spill_hrs"),
  normalized = c(TRUE),
  same_switchers = c(TRUE),
  stringsAsFactors = FALSE,
  controls = list(NULL, c("property_type", "old_new", "duration"))
)
param_grid_cont <- expand.grid(
  outcome = c("log_price"),
  treatment_threshold = c("cont"),
  time_agg = c("qtr"),
  treatment_type = c("log_spill_count", "log_spill_hrs"),
  normalized = c(TRUE),
  same_switchers = c(TRUE),
  stringsAsFactors = FALSE,
  controls = list(NULL, c("property_type", "old_new", "duration"))
)
param_grid <- bind_rows(param_grid_bin, param_grid_cont)

# Radii to loop over
radii <- c(250, 500, 1000)

# Parallel processing
plan(multisession, workers = 3)

for (r in radii) {
  message("Loading and preparing data for radius: ", r)

  # Site level panel data
  house_dat <- house_qtr %>%
    filter(radius == r) %>%
    collect()

  # Form panel data
  panel_house <- left_join(
    house_dat,
    spill_qtr,
    by = join_by(site_id, qtr_id)
  ) %>%
    left_join(house_controls, by = join_by(house_id)) %>%
    mutate(
      property_type = factor(
        property_type,
        levels = c("D", "S", "T", "F", "O")
      ),
      old_new = factor(old_new, levels = c("N", "Y")),
      duration = factor(duration, levels = c("F", "L"))
    )

  message("Starting regressions for radius: ", r)
  run_event_study(
    param_grid = param_grid,
    data = panel_house,
    rad = r,
    time_var = "qtr_id",
    group_var = "site_id",
    cluster_var = "site_id",
    overwrite = TRUE,
    file_name = "sales_did_results_house_qtr_{rad}.rds"
  )
}
```

```{r func-load-plot-chaisemartin}
# Load results
load_results <- function(
  radii = c(250, 500, 1000, 2000),
  freqs = c("qtr", "mo"),
  dir_path = here("output", "regs"),
  quiet = FALSE,
  pattern = "sales_did_results_site_{f}_{r}.rds"
) {
  safe_rds <- purrr::possibly(readRDS, otherwise = NULL)
  results <- list() # <- final nested list to be returned

  for (r in radii) {
    r_chr <- as.character(r)

    for (f in freqs) {
      pattern_eval <- glue::glue(pattern, .envir = rlang::env(f = f, r = r))
      file <- Sys.glob(file.path(dir_path, pattern_eval))[1]

      # no file found → skip
      if (is.na(file) || is.null(file) || file == "") {
        next
      }

      obj <- safe_rds(file)
      if (is.null(obj)) {
        next
      } # corrupted file → skip

      # initialise slots if necessary
      if (is.null(results[[r_chr]])) {
        results[[r_chr]] <- list()
      }

      results[[r_chr]][[f]] <- obj # store
      if (!quiet) message("✓ loaded ", f, " ", r, ": ", basename(file))
    }
  }

  return(results)
}


# Make regression plot
plot_reg_chaisemartin <- function(
  data,
  radius,
  model,
  freq = c("qtr", "mo"),
  use_desc = TRUE
) {
  freq <- match.arg(freq)
  r <- as.character(radius)

  stopifnot(r %in% names(data))
  stopifnot(freq %in% names(data[[r]]))

  mod <- data[[r]][[freq]][[model]]
  if (is.null(mod)) {
    stop(
      "Model '",
      model,
      "' not found for radius ",
      r,
      " and freq '",
      freq,
      "'."
    )
  }

  if (is.null(mod$plot)) {
    stop("Model '", model, "' has no plot element.")
  }

  # ------------------------------------------------------------------------
  # Data wrangling
  df <- mod$plot$data %>%
    mutate(
      group = factor(
        ifelse(Time <= 0, "Pre", "Post"),
        levels = c("Pre", "Post")
      )
    )

  subtitle <- if (use_desc && !is.null(attr(mod, "description"))) {
    attr(mod, "description")
  } else {
    model
  }
  formula_caption <- paste0(
    "Regression specification: ",
    mod$args$outcome,
    " ~ ",
    mod$args$group,
    " + ",
    mod$args$time,
    " + ",
    mod$args$treatment
  )

  ggplot(df, aes(x = Time, y = Estimate, colour = group)) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
    geom_errorbar(aes(ymin = LB.CI, ymax = UB.CI), width = 0.2) +
    geom_point(aes(color = group), size = 1.2) +
    scale_color_manual(
      values = c(
        "Pre" = viridis(1, option = "magma"),
        "Post" = viridis(3, option = "magma")[2]
      ),
      breaks = c("Pre", "Post")
    ) +
    theme_minimal() +
    labs(
      x = "Time",
      y = "Estimate",
      subtitle = subtitle,
      caption = formula_caption
    ) +
    theme_pref +
    theme(plot.caption = element_text(hjust = 0))
}

results_qtr <- load_results(
  radii = c(250, 500, 1000, 2000),
  freqs = c("qtr", "mo"),
  dir_path = here("output", "regs"),
  quiet = TRUE,
  pattern = "sales_did_results_site_{f}_{r}.rds"
)

results_house_qtr <- load_results(
  radii = c(250, 500, 1000, 2000),
  freqs = c("qtr"),
  dir_path = here("output", "regs"),
  quiet = TRUE,
  pattern = "sales_did_results_house_{f}_{r}.rds"
)
```

### Binary Treatment - Average Spill Count {#sec-06-02-01-binary-average}

::: {.panel-tabset group="threshold-site"}

#### 250m

::: {.panel-tabset group="radius-site-250m"}

##### Count Qt

```{r plot-house-site-250m-count-qt-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-house-site-250m-count-yr-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_yr_sw_norm"
)
```

##### Duration Qt
```{r plot-house-site-250m-duration-qt-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-house-site-250m-duration-yr-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-site-500m"}

##### Count Qt

```{r plot-house-site-500m-count-qt-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-house-site-500m-count-yr-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-house-site-500m-duration-qt-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-house-site-500m-duration-yr-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-site-1000m"}  

##### Count Qt

```{r plot-house-site-1000m-count-qt-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-house-site-1000m-count-yr-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-house-site-1000m-duration-qt-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-house-site-1000m-duration-yr-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_yr_sw_norm"
)
```

:::

#### 2000m

::: {.panel-tabset group="radius-site-2000m"}

##### Count Qt

```{r plot-house-site-2000m-count-qt-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 2000,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-house-site-2000m-count-yr-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 2000,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-house-site-2000m-duration-qt-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 2000,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-house-site-2000m-duration-yr-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 2000,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_yr_sw_norm"
)
```

:::

:::

### Binary Treatment - Median Spill Count {#sec-06-02-02-binary-median}

::: {.panel-tabset group="threshold-site"}

#### 250m

::: {.panel-tabset group="radius-site-250m"}

##### Count Qt

```{r plot-house-site-250m-count-qt-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-house-site-250m-count-yr-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-house-site-250m-duration-qt-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-house-site-250m-duration-yr-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-site-500m"}

##### Count Qt

```{r plot-house-site-500m-count-qt-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-house-site-500m-count-yr-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-house-site-500m-duration-qt-p50}  
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-house-site-500m-duration-yr-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-site-1000m"}

##### Count Qt

```{r plot-house-site-1000m-count-qt-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-house-site-1000m-count-yr-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-house-site-1000m-duration-qt-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-house-site-1000m-duration-yr-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_yr_sw_norm"
)
```

:::

#### 2000m

::: {.panel-tabset group="radius-site-2000m"}

##### Count Qt

```{r plot-house-site-2000m-count-qt-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 2000,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-house-site-2000m-count-yr-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 2000,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-house-site-2000m-duration-qt-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 2000,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-house-site-2000m-duration-yr-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 2000,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_yr_sw_norm"
)
```

:::

:::

### Binary Treatment - 75th Percentile Spill Count {#sec-06-02-03-binary-p75}

::: {.panel-tabset group="threshold-site"}  

#### 250m

::: {.panel-tabset group="radius-site-250m"}

##### Count Qt

```{r plot-house-site-250m-count-qt-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-house-site-250m-count-yr-p75}  
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-house-site-250m-duration-qt-p75}  
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-house-site-250m-duration-yr-p75}  
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-site-500m"}

##### Count Qt

```{r plot-house-site-500m-count-qt-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-house-site-500m-count-yr-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-house-site-500m-duration-qt-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-house-site-500m-duration-yr-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-site-1000m"}

##### Count Qt

```{r plot-house-site-1000m-count-qt-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-house-site-1000m-count-yr-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-house-site-1000m-duration-qt-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-house-site-1000m-duration-yr-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_yr_sw_norm"
)
```

:::

#### 2000m

::: {.panel-tabset group="radius-site-2000m"}

##### Count Qt

```{r plot-house-site-2000m-count-qt-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 2000,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-house-site-2000m-count-yr-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 2000,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-house-site-2000m-duration-qt-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 2000,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-house-site-2000m-duration-yr-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 2000,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_yr_sw_norm"
)
```

:::

:::

### Binary Treatment - 90th Percentile Spill Count {#sec-06-02-04-binary-p90}

::: {.panel-tabset group="threshold-site"}    

#### 250m

::: {.panel-tabset group="radius-site-250m"}

##### Count Qt

```{r plot-house-site-250m-count-qt-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-house-site-250m-count-yr-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-house-site-250m-duration-qt-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-house-site-250m-duration-yr-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-site-500m"}

##### Count Qt

```{r plot-house-site-500m-count-qt-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-house-site-500m-count-yr-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-house-site-500m-duration-qt-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-house-site-500m-duration-yr-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-site-1000m"}

##### Count Qt

```{r plot-house-site-1000m-count-qt-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-house-site-1000m-count-yr-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-house-site-1000m-duration-qt-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-house-site-1000m-duration-yr-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_yr_sw_norm"
)
```

:::

#### 2000m

::: {.panel-tabset group="radius-site-2000m"}

##### Count Qt

```{r plot-house-site-2000m-count-qt-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 2000,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-house-site-2000m-count-yr-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 2000,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-house-site-2000m-duration-qt-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 2000,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-house-site-2000m-duration-yr-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 2000,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_yr_sw_norm"
)
```

:::

:::
### Continuous Treatment - Average Spill Count {#sec-06-02-05-continuous-treatment}

::: {.panel-tabset group="continuous-site"}

#### 250m

::: {.panel-tabset group="radius-site-250m-cont"}

##### Count

```{r plot-house-site-250m-count-cont}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_cont_logp_sc_cont_qtr_sw_norm"
)
```

##### Duration

```{r plot-house-site-250m-duration-cont}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_cont_logp_sh_cont_qtr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-site-500m-cont"}

##### Count

```{r plot-house-site-500m-count-cont}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_cont_logp_sc_cont_qtr_sw_norm"
)
```

##### Duration

```{r plot-house-site-500m-duration-cont}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_cont_logp_sh_cont_qtr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-site-1000m-cont"}

##### Count

```{r plot-house-site-1000m-count-cont}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_cont_logp_sc_cont_qtr_sw_norm"
)
```

##### Duration

```{r plot-house-site-1000m-duration-cont}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_cont_logp_sh_cont_qtr_sw_norm"
)
```

:::

#### 2000m

::: {.panel-tabset group="radius-site-2000m-cont"}

##### Count

```{r plot-house-site-2000m-count-cont}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 2000,
  freq = "qtr",
  model = "model_cont_logp_sc_cont_qtr_sw_norm"
)
```

##### Duration

```{r plot-house-site-2000m-duration-cont}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 2000,
  freq = "qtr",
  model = "model_cont_logp_sh_cont_qtr_sw_norm"
)
```

:::

:::

## House Sales: House-Level Event Study Regressions Within Admin Boundaries {#sec-06-03-house-level-event-study}

The advantages of using house-level data relative to site-level data in the event study regressions are:

- **House-level controls:** Working at the house-level allows us to include property attributes (e.g. newly built, property type etc.) as controls. This ensures that any post-spill changes in the composition of sales do not confound price effects.
- **No double-counting from overlapping buffers:** Each property appears only once, even if it falls within 500 m of multiple outfalls. This avoids mechanical correlation among treated observations, which could inflate standard errors.
- **Larger control group:** Properties outside of the X-metre buffer remain in the sample. We can therefore use different location fixed effects (e.g., LSOA, MSOA, Admin Ward, Admin County, County, Region, Country, NHS HA) to account for any pre-existing differences in house prices across the study area.

The figures below show the dynamic effects of sewage spills on house prices across different administrative boundaries. Using geocoded transaction data, I calculate the total volume of sewage spills within an Xm radius of each property for every calendar quarter. A property is classified as treated in a given quarter if the spill volume exceeds a specified threshold. This approach allows treatment timing to vary across properties, depending on the occurrence and intensity of nearby spills.

The regressions estimate changes in house prices over time within the same location, comparing treated and untreated periods. Regressions are estimated both without controls (NC) and with controls (C): 

- **Old/New:** A binary variable indicating whether the property was a newly built property that had not been previosly sold.
- **Property Type:** A categorical variable indicating the type of property (detached, semi-detached, terraced, flats/maisonettes, other)
- **Duration:** A binary variable indicating the tenure of the property (freehold, leasehold)

 Regressions are estimated using the event-study estimator developed by Sun and Abraham (2021).

```{r load-data-house-sunab}
#| eval: false
# Load Data

# Define file paths
path_house <- here::here("data", "processed", "general_panel", "sales")
path_spill <- here::here("data", "processed", "agg_spill_stats", "agg_spill_stats_qtr.parquet")
path_house_controls <- here::here("data", "processed", "house_price.parquet")

# Load house panel data
house_panel <- arrow::open_dataset(path_house)

# Load quarterly spill stats, filter to quarterly data
spill_qtr <- import(path_spill, trust = TRUE) %>%
  select(-contains("month"), -contains("_mo")) %>%
  as.data.table()

# Load house controls, removing redundant columns
house_controls <- open_dataset(path_house_controls) %>%
  collect() %>%
  select(
    -transaction_id,
    -date_of_transfer,
    -postcode,
    -saon,
    -locality,
    -easting,
    -northing,
    -longitude,
    -latitude
  ) %>%
  as.data.table()
```


```{r create-event-data-house-sunab}
#| eval: false
# Create Event Data

# Create event data for each radius
radii <- c(250L, 500L)
event_data_list <- purrr::map(
  radii,
  function(rad) {
    # 1. Load data for radius and add spill statistics
    panel_dt_ext <- house_panel %>%
      filter(radius == rad) %>%
      filter(!is.na(site_id)) %>% 
      collect() %>%
      as.data.table()

    # 2. Calculate spill summaries
    # For houses within radius, merge with spill data
    house_qtr_in_sum <- merge(
      panel_dt_ext[within_radius == TRUE],
      spill_qtr[, .(site_id, qtr_id, spill_count, spill_hrs)],
      by = c("site_id", "qtr_id")
    )[,
      .(
        qtr_id_transfer = first(qtr_id_transfer),
        spill_count = sum(spill_count, na.rm = TRUE),
        spill_hrs = sum(spill_hrs, na.rm = TRUE),
        min_dist_m = min(distance_m, na.rm = TRUE),
        avg_dist_m = mean(distance_m, na.rm = TRUE),
        n_spill_sites = uniqueN(site_id),
        within_radius = TRUE,
        radius = rad
      ),
      by = .(house_id, qtr_id)
    ]

    # For houses outside radius, create zero-spill records
    house_qtr_out_sum <- panel_dt_ext[
      within_radius == FALSE,
      .(
        qtr_id_transfer = first(qtr_id_transfer),
        spill_count = 0,
        spill_hrs = 0,
        min_dist_m = NA,
        avg_dist_m = NA,
        n_spill_sites = 0,
        within_radius = FALSE,
        radius = rad
      ),
      by = .(house_id, qtr_id)
    ]

    # Combine and sort data
    house_qtr_sum <- rbind(house_qtr_in_sum, house_qtr_out_sum)
    setorder(house_qtr_sum, house_id, qtr_id)

    ## 3. Create treatment indicators

    # Extract threshold column names
    thr_col_names <- grep("^thr_.*_all$", names(spill_qtr), value = TRUE)
    # Create threshold lookup
    thr <- unique(spill_qtr[, c("qtr_id", thr_col_names), with = FALSE])
    setorder(thr, qtr_id)

    # Join houses with thresholds
    treat_cand <- merge(
      house_qtr_in_sum,
      thr,
      by = "qtr_id",
      all.x = TRUE
    )

    # Separate threshold columns by type
    count_thr <- grep("_spill_count_", thr_col_names, value = TRUE)
    hrs_thr <- grep("_spill_hrs_", thr_col_names, value = TRUE)

    # Create count threshold indicators
    treat_cand[,
      paste0("d_", count_thr) := lapply(.SD, \(x) as.integer(spill_count > x)),
      .SDcols = count_thr
    ]

    # Create hours threshold indicators
    treat_cand[,
      paste0("d_", hrs_thr) := lapply(.SD, \(x) as.integer(spill_hrs > x)),
      .SDcols = hrs_thr
    ]

    # 4. First-treated indicators

    # Get all treatment columns
    treat_cols <- grep("^d_", names(treat_cand), value = TRUE)

    # Find first treatment quarter for each house-threshold combination
    treat_long <- melt(
      treat_cand,
      id.vars = c("house_id", "qtr_id"),
      measure.vars = treat_cols,
      variable.name = "threshold",
      value.name = "treated",
      variable.factor = FALSE
    )[
      treated == 1L, # Keep only treated observations
      .(first_qtr = min(qtr_id)), # Find earliest treatment quarter
      by = .(house_id, threshold)
    ]

    # Convert to wide format
    treat_wide <- dcast(
      treat_long,
      house_id ~ threshold,
      value.var = "first_qtr",
      fill = NA_integer_ # NA for never treated houses
    )

    # Rename threshold columns
    setnames(
      treat_wide,
      old = grep("^d_thr_", names(treat_wide), value = TRUE),
      new = sub(
        "^d_thr_",
        "first_t_",
        grep("^d_thr_", names(treat_wide), value = TRUE)
      )
    )

    # 5. Finalise data

    # Join treatment data with house data
    event_data <- treat_wide[
      house_qtr_sum[qtr_id_transfer == qtr_id],
      on = "house_id",
      nomatch = NA
    ][
      # Join with house controls
      house_controls,
      on = "house_id",
      nomatch = NA
    ][,
      .(
        # IDs, time, and price
        house_id,
        qtr_id,
        qtr_id_transfer,
        price,
        log_price = log(price), # Add log price
        # Spill data
        spill_count,
        spill_hrs,
        # Treatment quarters
        first_t_mean_spill_count_all,
        first_t_mean_spill_hrs_all,
        first_t_p50_spill_count_all,
        first_t_p50_spill_hrs_all,
        first_t_p75_spill_count_all,
        first_t_p75_spill_hrs_all,
        first_t_p90_spill_count_all,
        first_t_p90_spill_hrs_all,
        first_t_max_spill_count_all,
        first_t_max_spill_hrs_all,
        # Spatial data
        min_dist_m,
        avg_dist_m,
        n_spill_sites,
        within_radius,
        radius,
        # Add categorical columns
        property_type,
        old_new,
        duration,
        town_city,
        district,
        county,
        quality,
        country,
        nhs_ha,
        region,
        lsoa,
        msoa,
        admin_county,
        admin_ward
      )
    ]

    # Convert categorical columns to factors using purrr::map
    categorical_cols <- c(
      "property_type",
      "old_new",
      "duration",
      "town_city",
      "district",
      "county",
      "quality",
      "country",
      "nhs_ha",
      "region",
      "lsoa",
      "msoa",
      "admin_county",
      "admin_ward"
    )

    event_data[,
      (categorical_cols) := purrr::map(.SD, as.factor),
      .SDcols = categorical_cols
    ]

    # Set quarter treated to above max quarter for never treated houses
    event_data[,
      names(.SD) := purrr::map(.SD, ~ ifelse(is.na(.), 999999L, .)),
      .SDcols = patterns("^first_t_")
    ]

    # Clean up local variables
    rm(
      house_qtr_in_sum,
      house_qtr_out_sum,
      treat_cand,
      treat_long,
      treat_wide,
      house_qtr_sum,
      panel_dt_ext
    )
    gc()

    return(event_data)
  }
) %>%
  purrr::set_names(paste0("rad_", radii))
```


```{r func-run-event-study-sunab}
#| eval: false
# Define Functions to Run Event Study Regressions

# Helper: build model name
build_model_name <- function(
  outcome,
  treatment_threshold,
  treatment_type,
  thr_time_agg,
  time_agg,
  time_fe,
  space_fe,
  cluster_var,
  controls = NULL
) {
  # Set binary (bin) or continuous
  base <- ifelse(
    treatment_threshold == "cont",
    "cont",
    "bin"
  )

  # Set outcome
  base <- ifelse(grepl("log_price", outcome), paste0(base, "_logp"), base)
  base <- ifelse(outcome == "price", paste0(base, "_p"), base)

  # Set treatment
  tt <- ifelse(treatment_type == "spill_count", "sc", "sh")
  base <- paste(base, tt, treatment_threshold, sep = "_")

  # Set time aggregation
  base <- paste0(base, "_", thr_time_agg)

  # Set FE unit
  base <- paste0(base, "_fe_", time_fe, "-", space_fe)

  # Set controls
  if (!is.null(controls) && length(controls)) {
    ctrl_suffix <- paste(controls, collapse = "_")
    base <- paste(base, ctrl_suffix, sep = "_")
  }

  # Clean up
  janitor::make_clean_names(base)
}

# Helper: Build Model Description
build_description <- function(
  outcome,
  treatment_threshold,
  treatment_type,
  time_agg,
  thr_time_agg,
  time_fe,
  space_fe,
  cluster_var,
  controls = NULL
) {
  # Outcome
  outcome_lbl <- dplyr::case_when(
    grepl("log_price", outcome) ~ "Log Price",
    grepl("price", outcome) ~ "Price",
    TRUE ~ outcome
  )

  # Threshold
  threshold_lbl <- dplyr::case_when(
    treatment_threshold == "mean" ~ "Mean",
    treatment_threshold == "p50" ~ "P50",
    treatment_threshold == "p75" ~ "P75",
    treatment_threshold == "p90" ~ "P90",
    treatment_threshold == "max" ~ "Max",
    treatment_threshold == "cont" ~ "Continuous",
    TRUE ~ stringr::str_to_title(treatment_threshold)
  )

  # Time aggregation
  time_lbl <- dplyr::case_when(
    grepl("mo", time_agg) ~ "Monthly",
    grepl("qtr", time_agg) ~ "Quarterly",
    grepl("yr", time_agg) ~ "Yearly",
    TRUE ~ time_agg
  )
  time_lbl <- ifelse(threshold_lbl == "Continuous", "", time_lbl)

  # Treatment
  treat_lbl <- dplyr::case_when(
    grepl("spill_count", treatment_type) & treatment_threshold != "cont" ~
      "Spill Count",
    grepl("spill_hrs", treatment_type) & treatment_threshold != "cont" ~
      "Spill Hours",
    grepl("spill_count", treatment_type) & treatment_threshold == "cont" ~
      "Log Spill Count",
    grepl("spill_hrs", treatment_type) & treatment_threshold == "cont" ~
      "Log Spill Hours",
    TRUE ~ NA_character_
  )

  # Fixed effects
  time_fe_lbl <- dplyr::case_when(
    time_fe == "mo" ~ "Monthly FE",
    time_fe == "qtr" ~ "Quarterly FE",
    time_fe == "yr" ~ "Yearly FE",
    TRUE ~ "No time FE"
  )
  space_fe_lbl <- dplyr::case_when(
    space_fe == "lsoa" ~ "LSOA FE",
    space_fe == "msoa" ~ "MSOA FE",
    space_fe == "admin_ward" ~ "Admin Ward FE",
    space_fe == "admin_county" ~ "Admin County FE",
    space_fe == "county" ~ "County FE",
    space_fe == "region" ~ "Region FE",
    space_fe == "country" ~ "Country FE",
    space_fe == "nhs_ha" ~ "NHS HA FE",
    TRUE ~ "No location FE"
  )

  # Controls
  ctrl_lbl <- if (is.null(controls) || length(controls) == 0) {
    "No controls"
  } else {
    paste(controls, collapse = ", ")
  }

  # Compose
  glue::glue(
    "Outcome: {outcome_lbl}; Treatment: {treat_lbl}; Aggregation: {time_lbl};
    FE: {time_fe_lbl} + {space_fe_lbl}; Controls: {ctrl_lbl}"
  ) %>%
    as.character()
}

# Main function ------------------------------------------------------
run_event_study_sunab <- function(
  param_grid,
  data,
  rad,
  overwrite = FALSE,
  file_name = "sales_sunab_results_{rad}.rds"
) {
  # Data validation
  stopifnot(
    is.data.frame(param_grid),
    is.data.frame(data),
    length(rad) == 1
  )

  # ---- 0. results directory/file setup ----------------------------------- #
  # Create directory for individual model files
  res_dir <- here::here(
    "book",
    "book_regs",
    glue::glue("sales_sunab_models_rad_{rad}")
  )
  fs::dir_create(res_dir)

  # Create/read index file to track which models are complete
  index_path <- file.path(res_dir, "model_index.rds")
  if (!overwrite && fs::file_exists(index_path)) {
    model_index <- readRDS(index_path)
  } else {
    model_index <- tibble::tibble(
      model_name = character(),
      completed = logical(),
      file_path = character()
    )
  }
  existing_names <- model_index$model_name

  # ---- 1. identify the models still to run ------------------------------- #
  param_grid <- tibble::as_tibble(param_grid) %>%
    dplyr::mutate(
      model_name = purrr::pmap_chr(
        list(
          outcome,
          treatment_threshold,
          treatment_type,
          thr_time_agg,
          time_agg,
          time_fe,
          space_fe,
          cluster_var,
          controls
        ),
        build_model_name
      )
    )

  todo <- dplyr::anti_join(
    param_grid,
    tibble::tibble(model_name = existing_names),
    by = "model_name"
  )

  if (nrow(todo) == 0) {
    cli::cli_alert_info("No new models to run for radius {rad}.")
    return(invisible(model_index))
  }
  cli::cli_alert_info("Estimating {nrow(todo)} models for radius {rad} …")

  # ---- 2. run the models one by one, saving each individually ------------- #
  for (i in 1:nrow(todo)) {
    mn <- todo$model_name[i]
    cli::cli_alert(" • {i}/{nrow(todo)}: {mn}")

    # Get model iteration
    p <- todo[i, ]

    # Define treatment variable
    treatment_var <- paste0(
      "first_t_",
      p$treatment_threshold,
      "_",
      p$treatment_type,
      "_",
      p$thr_time_agg
    )

    # Build formula -------------------------------------------------
    rhs_terms <- c(
      paste0("sunab(", treatment_var, ", ", p$time_agg, ")"),
      unlist(p$controls)
    ) %>%
      purrr::compact()

    fml <- as.formula(
      paste0(
        p$outcome,
        " ~ ",
        paste(rhs_terms, collapse = " + "),
        " | ",
        p$space_fe,
        " + ",
        p$time_fe
      )
    )
    cl_fml <- as.formula(paste0(" ~ ", p$cluster_var, " + ", p$time_fe))

    # Build description
    desc <- build_description(
      p$outcome,
      p$treatment_threshold,
      p$treatment_type,
      p$time_agg,
      p$thr_time_agg,
      p$time_fe,
      p$space_fe,
      p$cluster_var,
      unlist(p$controls)
    )

    # Run the model
    res <- tryCatch(
      {
        fixest::feols(
          fml = fml,
          data = data,
          vcov = cl_fml
        )
      },
      error = function(e) {
        cli::cli_alert_danger("Error fitting model {mn}: {e$message}")
        return(NULL)
      }
    )

    # Skip if model failed
    if (is.null(res)) {
      next
    }

    # Only save the plotting data
    res <- ggfixest::iplot_data(
      res,
      .ci_level = 0.95
    )

    # Build specification for ggplot
    controls <- if (is.null(p$controls) || length(p$controls) == 0) {
      ""
    } else {
      paste0(
        "+ ",
        paste(unlist(p$controls), collapse = " + ")
      )
    }

    spec <- glue::glue(
      "{p$outcome} ~ {p$time_fe} + {p$space_fe} + {treatment_var} {controls}"
    )

    attr(res, "description") <- desc
    attr(res, "spec") <- spec

    # Save to individual file
    model_file <- file.path(res_dir, paste0(mn, ".rds"))
    saveRDS(res, model_file)

    # Update index
    model_index <- model_index %>%
      dplyr::add_row(
        model_name = mn,
        completed = TRUE,
        file_path = model_file
      )
    saveRDS(model_index, index_path)

    # Clean up memory
    rm(res, fml, cl_fml, desc, spec, treatment_var, rhs_terms, controls)
    gc(verbose = FALSE)
  }

  cli::cli_alert_success("All models saved in → {res_dir}")
  invisible(model_index)
}
```


```{r exec-run-event-study-house-sunab}
#| eval: false
# Run Event Study Regressions

param_grid <- expand.grid(
  outcome = c("log_price"),
  treatment_threshold = c("mean", "p50", "p75", "p90"),
  treatment_type = c("spill_count", "spill_hrs"),
  thr_time_agg = "all",
  time_agg = "qtr_id",
  time_fe = "qtr_id",
  space_fe = "lsoa",
  cluster_var = "lsoa",
  controls = I(list(
    NULL,
    c("old_new"),
    c("property_type"),
    c("duration"),
    c("old_new", "property_type", "duration")
  ))
)

event_data_list_sample <- purrr::map(1:length(event_data_list), function(i) {
  event_data_list[[i]] %>%
    slice_sample(prop = 0.05)
}) %>%
  purrr::set_names(paste0("rad_", radii))

purrr::imap(
  event_data_list_sample,
  ~ {
    rad_value <- as.numeric(gsub("rad_", "", .y))
    run_event_study_sunab(
      param_grid = param_grid[1:2, ],
      data = .x,
      rad = rad_value,
      overwrite = TRUE,
      file_name = glue::glue("sales_sunab_results_{rad_value}.rds")
    )
  }
)
```


```{r func-load-plot-sunab-house}
# Define Function to Load Results
load_results_sunab <- function(
  radii = c(250, 500, 1000),
  freqs = c("qtr", "mo"),
  dir_path = here::here("output", "regs"),
  quiet = FALSE,
  pattern = "sales_sunab_models_rad_{r}"
) {
  results <- list()

  for (r in radii) {
    r_chr <- as.character(r)

    # Initialize radius slot if needed
    if (is.null(results[[r_chr]])) {
      results[[r_chr]] <- list()
    }

    for (f in freqs) {
      # Create path to model index file
      model_dir_pattern <- glue::glue(
        pattern,
        .envir = rlang::env(r = r, f = f)
      )
      model_dir <- file.path(dir_path, model_dir_pattern)
      index_path <- file.path(model_dir, "model_index.rds")

      # Skip if no index file exists
      if (!file.exists(index_path)) {
        if (!quiet) {
          cli::cli_alert_warning(
            "No model index found for radius {r}, freq {f}"
          )
        }
        next
      }

      # Read model index
      model_index <- readRDS(index_path)

      # Initialize frequency slot
      results[[r_chr]][[f]] <- list()

      # Load each model into the structure
      model_count <- 0
      for (mn in model_index$model_name) {
        model_path <- file.path(model_dir, paste0(mn, ".rds"))
        if (file.exists(model_path)) {
          results[[r_chr]][[f]][[mn]] <- readRDS(model_path)
          model_count <- model_count + 1
        }
      }

      if (!quiet) {
        cli::cli_alert_success(
          "Loaded {model_count} models for radius {r}, freq {f}"
        )
      }
    }
  }

  return(results)
}


# Define Function to Plot Sunab Regressions
plot_reg_sunab <- function(
  data,
  radius,
  model,
  freq = c("qtr", "mo"),
  use_desc = TRUE
) {
  freq <- match.arg(freq)
  r <- as.character(radius)

  stopifnot(r %in% names(data))
  stopifnot(freq %in% names(data[[r]]))

  mod <- data[[r]][[freq]][[model]]
  if (is.null(mod)) {
    stop(
      "Model '",
      model,
      "' not found for radius ",
      r,
      " and freq '",
      freq,
      "'."
    )
  }

  # ------------------------------------------------------------------------
  # Data Wrangling
  subtitle <- if (use_desc && !is.null(attr(mod, "description"))) {
    attr(mod, "description")
  } else {
    model
  }
  spec <- if (use_desc && !is.null(attr(mod, "spec"))) {
    attr(mod, "spec")
  } else {
    ""
  }

  # Plot
  mod %>%
    mutate(
      estimate_names = estimate_names + 1,
      group = factor(
        ifelse(estimate_names <= 0, "Pre", "Post"),
        levels = c("Pre", "Post")
      )
    ) %>%
    filter(
      estimate_names <= 8,
      estimate_names >= -4,
      ci_level == .95
    ) %>%
    ggplot(aes(x = estimate_names, y = estimate, color = group)) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    geom_errorbar(aes(ymin = ci_low, ymax = ci_high), width = 0.2) +
    geom_point(size = 1.2) +
    # geom_line(aes(group = 1), linewidth = 0.25) +
    scale_color_manual(
      values = c(
        "Pre" = viridis(1, option = "magma"),
        "Post" = viridis(3, option = "magma")[2]
      ),
      breaks = c("Pre", "Post")
    ) +
    theme_minimal() +
    labs(
      x = "Time",
      y = "Estimate",
      title = "",
      subtitle = subtitle,
      caption = spec
    ) +
    theme_pref +
    theme(plot.caption = element_text(hjust = 0))
}

results_sunab <- load_results_sunab(
  radii = c(250, 500, 1000),
  freqs = c("qtr"),
  quiet = FALSE,
  pattern = "sales_sunab_models_rad_{r}"
)
```

### Binary Treatment - Average Spill Count {#sec-06-03-01-binary-average}

::: {.panel-tabset group="threshold-house"}

#### 250m

::: {.panel-tabset group="radius-house-250m"}

##### Count (NC)

```{r plot-house-sunab-250m-count-nc}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_mean_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-house-sunab-250m-count-c}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_mean_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

##### Duration (NC)

```{r plot-house-sunab-250m-duration-nc}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_mean_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-house-sunab-250m-duration-c}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_mean_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-house-500m"}

##### Count (NC)

```{r plot-house-sunab-500m-count-nc}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_mean_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-house-sunab-500m-count-c}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_mean_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

##### Duration (NC)

```{r plot-house-sunab-500m-duration-nc}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_mean_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-house-sunab-500m-duration-c}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_mean_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-house-1000m"}

##### Count (NC)

```{r plot-house-sunab-1000m-count-nc}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_mean_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-house-sunab-1000m-count-c}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_mean_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

##### Duration (NC)

```{r plot-house-sunab-1000m-duration-nc}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_mean_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-house-sunab-1000m-duration-c}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_mean_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

:::

:::

### Binary Treatment - Median Spill Count {#sec-06-03-02-binary-median}

::: {.panel-tabset group="threshold-house"}

#### 250m

::: {.panel-tabset group="radius-house-250m"}

##### Count (NC)

```{r plot-house-sunab-250m-count-nc-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_p50_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-house-sunab-250m-count-c-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_p50_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

##### Duration (NC)

```{r plot-house-sunab-250m-duration-nc-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_p50_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-house-sunab-250m-duration-c-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_p50_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-house-500m"}

##### Count (NC)

```{r plot-house-sunab-500m-count-nc-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_p50_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-house-sunab-500m-count-c-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_p50_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

##### Duration (NC)

```{r plot-house-sunab-500m-duration-nc-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_p50_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-house-sunab-500m-duration-c-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_p50_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-house-1000m"}

##### Count (NC)

```{r plot-house-sunab-1000m-count-nc-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_p50_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-house-sunab-1000m-count-c-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_p50_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

##### Duration (NC)

```{r plot-house-sunab-1000m-duration-nc-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_p50_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-house-sunab-1000m-duration-c-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_p50_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

:::

:::

### Binary Treatment - 75th Percentile Spill Count {#sec-06-03-03-binary-p75}

::: {.panel-tabset group="threshold-house"}

#### 250m

::: {.panel-tabset group="radius-house-250m"}

##### Count (NC)

```{r plot-house-sunab-250m-count-nc-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_p75_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-house-sunab-250m-count-c-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_p75_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

##### Duration (NC)

```{r plot-house-sunab-250m-duration-nc-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_p75_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-house-sunab-250m-duration-c-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_p75_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-house-500m"}

##### Count (NC)

```{r plot-house-sunab-500m-count-nc-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_p75_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-house-sunab-500m-count-c-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_p75_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

##### Duration (NC)

```{r plot-house-sunab-500m-duration-nc-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_p75_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-house-sunab-500m-duration-c-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_p75_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-house-1000m"}

##### Count (NC)

```{r plot-house-sunab-1000m-count-nc-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_p75_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-house-sunab-1000m-count-c-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_p75_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

##### Duration (NC)

```{r plot-house-sunab-1000m-duration-nc-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_p75_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-house-sunab-1000m-duration-c-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_p75_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

:::

:::

### Binary Treatment - 90th Percentile Spill Count {#sec-06-03-04-binary-p90}

::: {.panel-tabset group="threshold-house"}

#### 250m

::: {.panel-tabset group="radius-house-250m"}

##### Count (NC)

```{r plot-house-sunab-250m-count-nc-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_p90_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-house-sunab-250m-count-c-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_p90_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

##### Duration (NC)

```{r plot-house-sunab-250m-duration-nc-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_p90_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-house-sunab-250m-duration-c-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_p90_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-house-500m"}

##### Count (NC)

```{r plot-house-sunab-500m-count-nc-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_p90_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-house-sunab-500m-count-c-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_p90_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

##### Duration (NC)

```{r plot-house-sunab-500m-duration-nc-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_p90_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-house-sunab-500m-duration-c-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_p90_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-house-1000m"}

##### Count (NC)

```{r plot-house-sunab-1000m-count-nc-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_p90_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-house-sunab-1000m-count-c-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_p90_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

##### Duration (NC)

```{r plot-house-sunab-1000m-duration-nc-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_p90_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-house-sunab-1000m-duration-c-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_p90_all_fe_qtr_id_lsoa_old_new_property_type_duration"
)
```

:::

:::




## House Rent: Site-Level Event Study Regressions Within Spill Buffers {#sec-06-04-basic-event-study-regressions}

```{r func-run-event-study-chaisemartin-rental-helper}
#| eval: false
#| include: false

# ---------- Function to run event study ----------

# Build model name (helper function)
build_model_name <- function(
  outcome,
  treatment_threshold,
  time_agg,
  normalized,
  same_switchers,
  treatment_type,
  controls = NULL
) {
  # Set binary (bin) or continuous
  base <- "model_"
  base <- ifelse(
    treatment_threshold == "cont",
    paste0(base, "cont"),
    paste0(base, "bin")
  )

  # Set spill statistic
  base <- ifelse(grepl("log_", outcome), paste0(base, "_logp"), base)
  base <- ifelse(grepl("_w$", outcome), paste0(base, "_w"), base)
  tt <- ifelse(grepl("spill_count", treatment_type), "sc", "sh")

  # Set model name
  base <- paste(base, tt, treatment_threshold, time_agg, sep = "_")

  # Set model parameters
  if (same_switchers) {
    base <- paste0(base, "_sw")
  }
  if (normalized) {
    base <- paste0(base, "_norm")
  }

  # Set controls
  if (!is.null(controls) && length(controls)) {
    ctrl_suffix <- paste(controls, collapse = "_")
    base <- paste(base, ctrl_suffix, sep = "_")
  }

  return(base)
}

# Build model description (helper function)
build_description <- function(
  outcome,
  treatment_threshold,
  time_agg,
  treatment_type,
  normalized,
  same_switchers,
  controls = NULL
) {
  # Labels
  outcome_lbl <- dplyr::case_when(
    outcome == "rent_median_w" ~ "Weighted Rent Median",
    outcome == "log_rent_median_w" ~ "Weighted Log Rent Median",
    outcome == "rent_median" ~ "Rent Median",
    outcome == "log_rent_median" ~ "Log Rent Median",
    outcome == "price_listing" ~ "Listing Price",
    outcome == "log_price_listing" ~ "Log Listing Price",
    TRUE ~ outcome
  )

  threshold_lbl <- dplyr::case_when(
    treatment_threshold == "mean" ~ "Mean",
    treatment_threshold == "p50" ~ "P50",
    treatment_threshold == "p75" ~ "P75",
    treatment_threshold == "p90" ~ "P90",
    treatment_threshold == "max" ~ "Max",
    treatment_threshold == "cont" ~ "Continuous",
    TRUE ~ stringr::str_to_title(treatment_threshold)
  )

  time_lbl <- dplyr::case_when(
    time_agg == "mo" ~ "Monthly",
    time_agg == "qtr" ~ "Quarterly",
    time_agg == "yr" ~ "Yearly",
    TRUE ~ time_agg
  )
  time_lbl <- ifelse(threshold_lbl == "Continuous", "", time_lbl)

  treat_lbl <- dplyr::case_when(
    grepl("spill_count", treatment_type) & treatment_threshold != "cont" ~
      "Spill Count",
    grepl("spill_hrs", treatment_type) & treatment_threshold != "cont" ~
      "Spill Hours",
    grepl("spill_count", treatment_type) & treatment_threshold == "cont" ~
      "Log Spill Count",
    grepl("spill_hrs", treatment_type) & treatment_threshold == "cont" ~
      "Log Spill Hours",
    TRUE ~ NA_character_
  )

  norm_lbl <- ifelse(normalized, "Norm", "No Norm")
  sw_lbl <- ifelse(same_switchers, "Same Switchers", "All Switchers")

  ctrl_lbl <- if (is.null(controls) || length(controls) == 0) {
    ""
  } else {
    paste0("; Controls: ", paste(controls, collapse = ", "))
  }

  # Compose
  glue::glue(
    "{outcome_lbl} ~ {time_lbl} {threshold_lbl} {treat_lbl} ",
    "({norm_lbl}, {sw_lbl}{ctrl_lbl})"
  ) %>%
    as.character()
}

# ---- main function --------------------------------------------------------- #

run_event_study <- function(
  param_grid,
  data,
  rad,
  time_var = c("month_id", "qtr_id"),
  group_var = "site_id",
  cluster_var = "site_id",
  overwrite = FALSE,
  file_name = "rentals_did_results_site_qtr_{rad}.rds"
) {
  stopifnot(
    is.data.frame(param_grid),
    is.data.frame(data),
    is.logical(overwrite),
    length(rad) == 1
  )

  # ---- 0. results file ----------------------------------------------------- #
  res_path <- here::here(
    "book",
    "book_regs",
    glue::glue(file_name)
  )
  fs::dir_create(fs::path_dir(res_path))

  existing <- if (!overwrite && fs::file_exists(res_path)) {
    readRDS(res_path)
  } else {
    list()
  }

  # ---- 1. decide what we still need to run --------------------------------- #
  param_grid <- tibble::as_tibble(param_grid) %>%
    dplyr::mutate(
      model_name = purrr::pmap_chr(
        list(
          outcome,
          treatment_threshold,
          time_agg,
          normalized,
          same_switchers,
          treatment_type,
          controls
        ),
        build_model_name
      )
    )

  existing_names <- if (length(existing)) names(existing) else character(0)

  todo <- dplyr::anti_join(
    param_grid,
    tibble::tibble(model_name = existing_names),
    by = "model_name"
  )

  if (nrow(todo) == 0) {
    message("No new models to run for radius ", rad, ".")
    return(invisible(existing))
  }
  message("Estimating ", nrow(todo), " models for radius ", rad, "...")

  # ---- 2. run the models (parallel) --------------------------------------- #
  furrr::future_map(
    todo$model_name,
    function(mn) {
      # Get model iteration
      p <- dplyr::filter(todo, model_name == mn) %>%
        dplyr::slice(1)

      # Define treatment variable
      treatment_var <- paste0(
        "d_",
        p$treatment_threshold,
        "_",
        p$treatment_type,
        "_",
        p$time_agg
      )
      treatment_var <- ifelse(
        p$treatment_threshold == "cont",
        p$treatment_type,
        gsub("log_spill", "spill", treatment_var)
      )

      desc <- build_description(
        p$outcome,
        p$treatment_threshold,
        p$time_agg,
        p$treatment_type,
        p$normalized,
        p$same_switchers,
        unlist(p$controls)
      )

      message(" • ", mn, " …")

      res <- DIDmultiplegtDYN::did_multiplegt_dyn(
        df = data,
        outcome = p$outcome,
        group = group_var,
        time = time_var,
        treatment = treatment_var,
        effects = 6,
        placebo = 2,
        cluster = cluster_var,
        normalized = p$normalized,
        same_switchers = p$same_switchers,
        controls = unlist(p$controls),
        graph_off = TRUE
      )

      attr(res, "description") <- desc
      # return a named list so purrr::flatten will keep names
      rlist <- list(res)
      names(rlist) <- mn
      rlist
    },
    .options = furrr::furrr_options(seed = TRUE),
    .progress = TRUE
  ) %>%
    purrr::flatten() -> new_results

  # ---- 3. merge + save ----------------------------------------------------- #
  final <- c(existing, new_results)
  saveRDS(final, res_path)
  message("Results saved → ", res_path)

  invisible(final)
}
```


```{r exec-run-event-study-rental-site-level}
#| eval: false
#| include: false

param_grid_bin <- expand.grid(
  outcome = c("log_rent_median", "log_rent_median_w"),
  treatment_threshold = c("mean", "p50", "p75", "p90"),
  time_agg = c("qtr", "yr"),
  treatment_type = c("spill_count", "spill_hrs"),
  normalized = c(TRUE),
  same_switchers = c(TRUE),
  stringsAsFactors = FALSE,
  controls = list(NULL)
)
param_grid_cont <- expand.grid(
  outcome = c("log_rent_median", "log_rent_median_w"),
  treatment_threshold = c("cont"),
  time_agg = c("qtr"),
  treatment_type = c("log_spill_count", "log_spill_hrs"),
  normalized = c(TRUE),
  same_switchers = c(TRUE),
  stringsAsFactors = FALSE,
  controls = list(NULL)
)
param_grid <- bind_rows(param_grid_bin, param_grid_cont)

# Radii to loop over
radii <- c(250, 500, 1000)

# Parallel processing
plan(multisession, workers = 3)

# Load data
## Data paths
path_rental <- here::here("data", "processed", "within_radius_panel", "rentals")
path_site <- here::here("data", "processed", "dat_panel_site", "rentals")
path_spill <- here::here("data", "processed", "agg_spill_stats", "agg_spill_stats_qtr.parquet")
path_rental_controls <- here::here(
  "data",
  "processed",
  "zoopla",
  "zoopla_rentals.parquet"
)

# Rental panel data
rental_qtr <- open_dataset(path_rental) %>%
  filter(period_type == "quarterly") %>%
  select(-contains("month"))
# Aggregate site level panel data
site_qtr <- open_dataset(path_site) %>%
  filter(period_type == "quarterly") %>%
  select(-contains("month"))
# Spill statistics
spill_qtr <- import(path_spill, trust = TRUE) %>%
  select(-contains("month"), -contains("_mo"))
# Rental controls snapshot (not used directly here)
rental_controls <- open_dataset(path_rental_controls) %>%
  collect() %>%
  select(
    rental_id,
    listing_price,
    property_type,
    quality,
    country,
    nhs_ha,
    region,
    lsoa,
    msoa,
    admin_county,
    admin_ward
  )

for (r in radii) {
  message("Loading and preparing data for radius: ", r)

  # Site level panel data
  site_dat <- site_qtr %>%
    filter(radius == r) %>%
    collect()

  # Form panel data
  panel_site <- left_join(
    site_dat,
    spill_qtr,
    by = join_by(site_id, qtr_id)
  )

  message("Starting regressions for radius: ", r)
  run_event_study(
    param_grid = param_grid,
    data = panel_site,
    rad = r,
    time_var = "qtr_id",
    group_var = "site_id",
    cluster_var = "site_id",
    overwrite = TRUE,
    file_name = "rentals_did_results_site_qtr_{rad}.rds"
  )
}
```


```{r exec-run-event-study-rental-rental-level}
#| eval: false
#| include: false

# Create parameter grid
param_grid_bin <- expand.grid(
  outcome = c("log_price_listing"),
  treatment_threshold = c("mean", "p50", "p75", "p90"),
  time_agg = c("qtr", "yr"),
  treatment_type = c("spill_count", "spill_hrs"),
  normalized = c(TRUE),
  same_switchers = c(TRUE),
  stringsAsFactors = FALSE,
  controls = list(NULL, c("property_type"))
)
param_grid_cont <- expand.grid(
  outcome = c("log_price_listing"),
  treatment_threshold = c("cont"),
  time_agg = c("qtr"),
  treatment_type = c("log_spill_count", "log_spill_hrs"),
  normalized = c(TRUE),
  same_switchers = c(TRUE),
  stringsAsFactors = FALSE,
  controls = list(NULL, c("property_type"))
)
param_grid <- bind_rows(param_grid_bin, param_grid_cont)

# Radii to loop over
radii <- c(250, 500, 1000)

# Parallel processing
plan(multisession, workers = 3)

for (r in radii) {
  message("Loading and preparing data for radius: ", r)

  # Site level panel data
  rental_dat <- rental_qtr %>%
    filter(radius == r) %>%
    collect() %>%
    rename(
      price_listing = price,
      log_price_listing = log_price
    )

  # Form panel data
  panel_rental <- left_join(
    rental_dat,
    spill_qtr,
    by = join_by(site_id, qtr_id)
  ) %>%
    left_join(rental_controls, by = join_by(rental_id)) %>%
    mutate(
      property_type = factor(property_type)
    )

  message("Starting regressions for radius: ", r)
  run_event_study(
    param_grid = param_grid,
    data = panel_rental,
    rad = r,
    time_var = "qtr_id",
    group_var = "site_id",
    cluster_var = "site_id",
    overwrite = TRUE,
    file_name = "rentals_did_results_house_qtr_{rad}.rds"
  )
}
```

```{r func-load-plot-chaisemartin-rental}
# Load results
load_results <- function(
  radii = c(250, 500, 1000),
  freqs = c("qtr", "mo"),
  dir_path = here("output", "regs"),
  quiet = FALSE,
  pattern = "rentals_did_results_site_{f}_{r}.rds"
) {
  safe_rds <- purrr::possibly(readRDS, otherwise = NULL)
  results <- list() # <- final nested list to be returned

  for (r in radii) {
    r_chr <- as.character(r)

    for (f in freqs) {
      pattern_eval <- glue::glue(pattern, .envir = rlang::env(f = f, r = r))
      file <- Sys.glob(file.path(dir_path, pattern_eval))[1]

      # no file found → skip
      if (is.na(file) || is.null(file) || file == "") {
        next
      }

      obj <- safe_rds(file)
      if (is.null(obj)) {
        next
      } # corrupted file → skip

      # initialise slots if necessary
      if (is.null(results[[r_chr]])) {
        results[[r_chr]] <- list()
      }

      results[[r_chr]][[f]] <- obj # store
      if (!quiet) message("✓ loaded ", f, " ", r, ": ", basename(file))
    }
  }

  return(results)
}


results_qtr <- load_results(
  radii = c(250, 500, 1000),
  freqs = c("qtr", "mo"),
  dir_path = here("output", "regs"),
  quiet = TRUE,
  pattern = "rentals_did_results_site_{f}_{r}.rds"
)

results_rental_qtr <- load_results(
  radii = c(250, 500, 1000),
  freqs = c("qtr"),
  dir_path = here("output", "regs"),
  quiet = TRUE,
  pattern = "rentals_did_results_house_{f}_{r}.rds"
)
```

### Binary Treatment - Average Spill Count {#sec-06-04-01-binary-average}

::: {.panel-tabset group="threshold-site"}

#### 250m

::: {.panel-tabset group="radius-site-250m"}

##### Count Qt

```{r plot-rental-site-250m-count-qt-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-rental-site-250m-count-yr-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_yr_sw_norm"
)
```

##### Duration Qt
```{r plot-rental-site-250m-duration-qt-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-rental-site-250m-duration-yr-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-site-500m"}

##### Count Qt

```{r plot-rental-site-500m-count-qt-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-rental-site-500m-count-yr-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-rental-site-500m-duration-qt-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-rental-site-500m-duration-yr-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-site-1000m"}  

##### Count Qt

```{r plot-rental-site-1000m-count-qt-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-rental-site-1000m-count-yr-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_mean_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-rental-site-1000m-duration-qt-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-rental-site-1000m-duration-yr-mean}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_mean_yr_sw_norm"
)
```

:::

:::

### Binary Treatment - Median Spill Count {#sec-06-04-02-binary-median}

::: {.panel-tabset group="threshold-site"}

#### 250m

::: {.panel-tabset group="radius-site-250m"}

##### Count Qt

```{r plot-rental-site-250m-count-qt-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-rental-site-250m-count-yr-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-rental-site-250m-duration-qt-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-rental-site-250m-duration-yr-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-site-500m"}

##### Count Qt

```{r plot-rental-site-500m-count-qt-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-rental-site-500m-count-yr-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-rental-site-500m-duration-qt-p50}  
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-rental-site-500m-duration-yr-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-site-1000m"}

##### Count Qt

```{r plot-rental-site-1000m-count-qt-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-rental-site-1000m-count-yr-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_p50_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-rental-site-1000m-duration-qt-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-rental-site-1000m-duration-yr-p50}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_p50_yr_sw_norm"
)
```

:::

:::

### Binary Treatment - 75th Percentile Spill Count {#sec-06-04-03-binary-p75}

::: {.panel-tabset group="threshold-site"}  

#### 250m

::: {.panel-tabset group="radius-site-250m"}

##### Count Qt

```{r plot-rental-site-250m-count-qt-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-rental-site-250m-count-yr-p75}  
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-rental-site-250m-duration-qt-p75}  
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-rental-site-250m-duration-yr-p75}  
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-site-500m"}

##### Count Qt

```{r plot-rental-site-500m-count-qt-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-rental-site-500m-count-yr-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-rental-site-500m-duration-qt-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-rental-site-500m-duration-yr-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-site-1000m"}

##### Count Qt

```{r plot-rental-site-1000m-count-qt-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-rental-site-1000m-count-yr-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_p75_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-rental-site-1000m-duration-qt-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-rental-site-1000m-duration-yr-p75}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_p75_yr_sw_norm"
)
```

:::

:::

### Binary Treatment - 90th Percentile Spill Count {#sec-06-04-04-binary-p90}

::: {.panel-tabset group="threshold-site"}    

#### 250m

::: {.panel-tabset group="radius-site-250m"}

##### Count Qt

```{r plot-rental-site-250m-count-qt-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-rental-site-250m-count-yr-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-rental-site-250m-duration-qt-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-rental-site-250m-duration-yr-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-site-500m"}

##### Count Qt

```{r plot-rental-site-500m-count-qt-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-rental-site-500m-count-yr-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-rental-site-500m-duration-qt-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-rental-site-500m-duration-yr-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-site-1000m"}

##### Count Qt

```{r plot-rental-site-1000m-count-qt-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_qtr_sw_norm"
)
```

##### Count Yr

```{r plot-rental-site-1000m-count-yr-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sc_p90_yr_sw_norm"
)
```

##### Duration Qt

```{r plot-rental-site-1000m-duration-qt-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_qtr_sw_norm"
)
```

##### Duration Yr

```{r plot-rental-site-1000m-duration-yr-p90}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_bin_logp_sh_p90_yr_sw_norm"
)
```

:::

:::

### Continuous Treatment - Average Spill Count {#sec-06-04-05-continuous-treatment}

::: {.panel-tabset group="continuous-site"}

#### 250m

::: {.panel-tabset group="radius-site-250m-cont"}

##### Count

```{r plot-rental-site-250m-count-cont}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_cont_logp_sc_cont_qtr_sw_norm"
)
```

##### Duration

```{r plot-rental-site-250m-duration-cont}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 250,
  freq = "qtr",
  model = "model_cont_logp_sh_cont_qtr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-site-500m-cont"}

##### Count

```{r plot-rental-site-500m-count-cont}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_cont_logp_sc_cont_qtr_sw_norm"
)
```

##### Duration

```{r plot-rental-site-500m-duration-cont}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 500,
  freq = "qtr",
  model = "model_cont_logp_sh_cont_qtr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-site-1000m-cont"}

##### Count

```{r plot-rental-site-1000m-count-cont}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_cont_logp_sc_cont_qtr_sw_norm"
)
```

##### Duration

```{r plot-rental-site-1000m-duration-cont}
plot_reg_chaisemartin(
  data = results_qtr,
  radius = 1000,
  freq = "qtr",
  model = "model_cont_logp_sh_cont_qtr_sw_norm"
)
```

:::

:::


## House Rent: House-Level Event Study Regressions Within Admin Boundaries {#sec-06-05-house-level-event-study}

```{r load-data-rental-sunab}
#| eval: false
# Load Data

# Define file paths
path_rental_panel <- here::here("data", "processed", "general_panel", "rentals")
path_spill <- here::here("data", "processed", "agg_spill_stats", "agg_spill_stats_qtr.parquet")
path_rental_controls <- here::here(
  "data",
  "processed",
  "zoopla",
  "zoopla_rentals.parquet"
)

# Load rental panel data
rental_panel <- arrow::open_dataset(path_rental_panel)

# Load quarterly spill stats, filter to quarterly data
spill_qtr <- import(path_spill, trust = TRUE) %>%
  select(-contains("month"), -contains("_mo")) %>%
  as.data.table()

# Load rental controls, removing redundant columns
rental_controls <- open_dataset(path_rental_controls) %>%
  collect() %>%
  transmute(
    rental_id,
    price_listing = listing_price,
    log_price_listing = log(listing_price),
    property_type,
    bedrooms,
    bathrooms,
    receptions,
    quality,
    country,
    nhs_ha,
    region,
    lsoa,
    msoa,
    admin_county,
    admin_ward
  ) %>%
  as.data.table()
```


```{r create-event-data-rental-sunab}
#| eval: false
# Create Event Data

# Create event data for each radius
radii <- c(1000L)
event_data_list <- purrr::map(
  radii,
  function(rad) {
    # 1. Load data for radius and add spill statistics
    panel_dt_ext <- house_panel %>%
      filter(radius == rad) %>%
      filter(!is.na(site_id)) %>% 
      collect() %>%
      as.data.table()

    # 2. Calculate spill summaries
    # For rentals within radius, merge with spill data
    rental_qtr_in_sum <- merge(
      panel_dt_ext[within_radius == TRUE],
      spill_qtr[, .(site_id, qtr_id, spill_count, spill_hrs)],
      by = c("site_id", "qtr_id")
    )[,
      .(
        qtr_id_transfer = first(qtr_id_transfer),
        spill_count = sum(spill_count, na.rm = TRUE),
        spill_hrs = sum(spill_hrs, na.rm = TRUE),
        min_dist_m = min(distance_m, na.rm = TRUE),
        avg_dist_m = mean(distance_m, na.rm = TRUE),
        n_spill_sites = uniqueN(site_id),
        within_radius = TRUE,
        radius = rad
      ),
      by = .(rental_id, qtr_id)
    ]

    # For rentals outside radius, create zero-spill records
    rental_qtr_out_sum <- panel_dt_ext[
      within_radius == FALSE,
      .(
        qtr_id_transfer = first(qtr_id_transfer),
        spill_count = 0,
        spill_hrs = 0,
        min_dist_m = NA,
        avg_dist_m = NA,
        n_spill_sites = 0,
        within_radius = FALSE,
        radius = rad
      ),
      by = .(rental_id, qtr_id)
    ]

    # Combine and sort data
    rental_qtr_sum <- rbind(rental_qtr_in_sum, rental_qtr_out_sum)
    setorder(rental_qtr_sum, rental_id, qtr_id)

    ## 3. Create treatment indicators

    # Extract threshold column names
    thr_col_names <- grep("^thr_.*_all$", names(spill_qtr), value = TRUE)
    # Create threshold lookup
    thr <- unique(spill_qtr[, c("qtr_id", thr_col_names), with = FALSE])
    setorder(thr, qtr_id)

    # Join rentals with thresholds
    treat_cand <- merge(
      rental_qtr_in_sum,
      thr,
      by = "qtr_id",
      all.x = TRUE
    )

    # Separate threshold columns by type
    count_thr <- grep("_spill_count_", thr_col_names, value = TRUE)
    hrs_thr <- grep("_spill_hrs_", thr_col_names, value = TRUE)

    # Create count threshold indicators
    treat_cand[,
      paste0("d_", count_thr) := lapply(.SD, \(x) as.integer(spill_count > x)),
      .SDcols = count_thr
    ]

    # Create hours threshold indicators
    treat_cand[,
      paste0("d_", hrs_thr) := lapply(.SD, \(x) as.integer(spill_hrs > x)),
      .SDcols = hrs_thr
    ]

    # 4. First-treated indicators

    # Get all treatment columns
    treat_cols <- grep("^d_", names(treat_cand), value = TRUE)

    # Find first treatment quarter for each rental-threshold combination
    treat_long <- melt(
      treat_cand,
      id.vars = c("rental_id", "qtr_id"),
      measure.vars = treat_cols,
      variable.name = "threshold",
      value.name = "treated",
      variable.factor = FALSE
    )[
      treated == 1L, # Keep only treated observations
      .(first_qtr = min(qtr_id)), # Find earliest treatment quarter
      by = .(rental_id, threshold)
    ]

    # Convert to wide format
    treat_wide <- dcast(
      treat_long,
      rental_id ~ threshold,
      value.var = "first_qtr",
      fill = NA_integer_ # NA for never treated rentals
    )

    # Rename threshold columns
    setnames(
      treat_wide,
      old = grep("^d_thr_", names(treat_wide), value = TRUE),
      new = sub(
        "^d_thr_",
        "first_t_",
        grep("^d_thr_", names(treat_wide), value = TRUE)
      )
    )

    # 5. Finalise data

    # Join treatment data with rental data
    event_data <- treat_wide[
      rental_qtr_sum[qtr_id_transfer == qtr_id],
      on = "rental_id",
      nomatch = NA
    ][
      # Join with rental controls
      rental_controls,
      on = "rental_id",
      nomatch = NA
    ][,
      .(
        # IDs, time, and price
        rental_id,
        qtr_id,
        qtr_id_transfer,
        price_listing,
        log_price_listing,
        # Spill data
        spill_count,
        spill_hrs,
        # Treatment quarters
        first_t_mean_spill_count_all,
        first_t_mean_spill_hrs_all,
        first_t_p50_spill_count_all,
        first_t_p50_spill_hrs_all,
        first_t_p75_spill_count_all,
        first_t_p75_spill_hrs_all,
        first_t_p90_spill_count_all,
        first_t_p90_spill_hrs_all,
        first_t_max_spill_count_all,
        first_t_max_spill_hrs_all,
        # Spatial data
        min_dist_m,
        avg_dist_m,
        n_spill_sites,
        within_radius,
        radius,
        # Property characteristics
        property_type,
        bedrooms,
        bathrooms,
        receptions,
        quality,
        country,
        nhs_ha,
        region,
        lsoa,
        msoa,
        admin_county,
        admin_ward
      )
    ]

    # Convert categorical columns to factors using purrr::map
    categorical_cols <- c(
      "property_type",
      "quality",
      "country",
      "nhs_ha",
      "region",
      "lsoa",
      "msoa",
      "admin_county",
      "admin_ward"
    )

    event_data[,
      (categorical_cols) := purrr::map(.SD, as.factor),
      .SDcols = categorical_cols
    ]

    # Set quarter treated to above max quarter for never treated rentals
    event_data[,
      names(.SD) := purrr::map(.SD, ~ ifelse(is.na(.), 999999L, .)),
      .SDcols = patterns("^first_t_")
    ]

    # Clean up local variables
    rm(
      rental_qtr_in_sum,
      rental_qtr_out_sum,
      treat_cand,
      treat_long,
      treat_wide,
      rental_qtr_sum,
      panel_dt_ext
    )
    gc()

    return(event_data)
  }
) %>%
  purrr::set_names(paste0("rad_", radii))
```


```{r func-run-event-study-sunab-rental-helper}
#| eval: false
# Define Functions to Run Event Study Regressions

# Helper: build model name
build_model_name <- function(
  outcome,
  treatment_threshold,
  treatment_type,
  thr_time_agg,
  time_agg,
  time_fe,
  space_fe,
  cluster_var,
  controls = NULL
) {
  # Set binary (bin) or continuous
  base <- ifelse(
    treatment_threshold == "cont",
    "cont",
    "bin"
  )

  # Set outcome
  base <- ifelse(grepl("log_price", outcome), paste0(base, "_logp"), base)
  base <- ifelse(
    outcome %in% c("price", "price_listing"),
    paste0(base, "_p"),
    base
  )

  # Set treatment
  tt <- ifelse(treatment_type == "spill_count", "sc", "sh")
  base <- paste(base, tt, treatment_threshold, sep = "_")

  # Set time aggregation
  base <- paste0(base, "_", thr_time_agg)

  # Set FE unit
  base <- paste0(base, "_fe_", time_fe, "-", space_fe)

  # Set controls
  if (!is.null(controls) && length(controls)) {
    ctrl_suffix <- paste(controls, collapse = "_")
    base <- paste(base, ctrl_suffix, sep = "_")
  }

  # Clean up
  janitor::make_clean_names(base)
}

# Helper: Build Model Description
build_description <- function(
  outcome,
  treatment_threshold,
  treatment_type,
  time_agg,
  thr_time_agg,
  time_fe,
  space_fe,
  cluster_var,
  controls = NULL
) {
  # Outcome
  outcome_lbl <- dplyr::case_when(
    grepl("log_price_listing", outcome) ~ "Log Listing Price",
    grepl("price_listing", outcome) ~ "Listing Price",
    grepl("log_price", outcome) ~ "Log Price",
    grepl("price", outcome) ~ "Price",
    TRUE ~ outcome
  )

  # Threshold
  threshold_lbl <- dplyr::case_when(
    treatment_threshold == "mean" ~ "Mean",
    treatment_threshold == "p50" ~ "P50",
    treatment_threshold == "p75" ~ "P75",
    treatment_threshold == "p90" ~ "P90",
    treatment_threshold == "max" ~ "Max",
    treatment_threshold == "cont" ~ "Continuous",
    TRUE ~ stringr::str_to_title(treatment_threshold)
  )

  # Time aggregation
  time_lbl <- dplyr::case_when(
    grepl("mo", time_agg) ~ "Monthly",
    grepl("qtr", time_agg) ~ "Quarterly",
    grepl("yr", time_agg) ~ "Yearly",
    TRUE ~ time_agg
  )
  time_lbl <- ifelse(threshold_lbl == "Continuous", "", time_lbl)

  # Treatment
  treat_lbl <- dplyr::case_when(
    grepl("spill_count", treatment_type) & treatment_threshold != "cont" ~
      "Spill Count",
    grepl("spill_hrs", treatment_type) & treatment_threshold != "cont" ~
      "Spill Hours",
    grepl("spill_count", treatment_type) & treatment_threshold == "cont" ~
      "Log Spill Count",
    grepl("spill_hrs", treatment_type) & treatment_threshold == "cont" ~
      "Log Spill Hours",
    TRUE ~ NA_character_
  )

  # Fixed effects
  time_fe_lbl <- dplyr::case_when(
    time_fe == "mo" ~ "Monthly FE",
    time_fe == "qtr" ~ "Quarterly FE",
    time_fe == "yr" ~ "Yearly FE",
    TRUE ~ "No time FE"
  )
  space_fe_lbl <- dplyr::case_when(
    space_fe == "lsoa" ~ "LSOA FE",
    space_fe == "msoa" ~ "MSOA FE",
    space_fe == "admin_ward" ~ "Admin Ward FE",
    space_fe == "admin_county" ~ "Admin County FE",
    space_fe == "county" ~ "County FE",
    space_fe == "region" ~ "Region FE",
    space_fe == "country" ~ "Country FE",
    space_fe == "nhs_ha" ~ "NHS HA FE",
    TRUE ~ "No location FE"
  )

  # Controls
  ctrl_lbl <- if (is.null(controls) || length(controls) == 0) {
    "No controls"
  } else {
    paste(controls, collapse = ", ")
  }

  # Compose
  glue::glue(
    "Outcome: {outcome_lbl}; Treatment: {treat_lbl}; Aggregation: {time_lbl};
    FE: {time_fe_lbl} + {space_fe_lbl}; Controls: {ctrl_lbl}"
  ) %>%
    as.character()
}

# Main function ------------------------------------------------------
run_event_study_sunab <- function(
  param_grid,
  data,
  rad,
  overwrite = FALSE,
  file_name = "rentals_sunab_results_{rad}.rds"
) {
  # Data validation
  stopifnot(
    is.data.frame(param_grid),
    is.data.frame(data),
    length(rad) == 1
  )

  # ---- 0. results directory/file setup ----------------------------------- #
  # Create directory for individual model files
  res_dir <- here::here(
    "book",
    "book_regs",
    glue::glue("rentals_sunab_models_rad_{rad}")
  )
  fs::dir_create(res_dir)

  # Create/read index file to track which models are complete
  index_path <- file.path(res_dir, "model_index.rds")
  if (!overwrite && fs::file_exists(index_path)) {
    model_index <- readRDS(index_path)
  } else {
    model_index <- tibble::tibble(
      model_name = character(),
      completed = logical(),
      file_path = character()
    )
  }
  existing_names <- model_index$model_name

  # ---- 1. identify the models still to run ------------------------------- #
  param_grid <- tibble::as_tibble(param_grid) %>%
    dplyr::mutate(
      model_name = purrr::pmap_chr(
        list(
          outcome,
          treatment_threshold,
          treatment_type,
          thr_time_agg,
          time_agg,
          time_fe,
          space_fe,
          cluster_var,
          controls
        ),
        build_model_name
      )
    )

  todo <- dplyr::anti_join(
    param_grid,
    tibble::tibble(model_name = existing_names),
    by = "model_name"
  )

  if (nrow(todo) == 0) {
    cli::cli_alert_info("No new models to run for radius {rad}.")
    return(invisible(model_index))
  }
  cli::cli_alert_info("Estimating {nrow(todo)} models for radius {rad} …")

  # ---- 2. run the models one by one, saving each individually ------------- #
  for (i in 1:nrow(todo)) {
    mn <- todo$model_name[i]
    cli::cli_alert(" • {i}/{nrow(todo)}: {mn}")

    # Get model iteration
    p <- todo[i, ]

    # Define treatment variable
    treatment_var <- paste0(
      "first_t_",
      p$treatment_threshold,
      "_",
      p$treatment_type,
      "_",
      p$thr_time_agg
    )

    # Build formula -------------------------------------------------
    rhs_terms <- c(
      paste0("sunab(", treatment_var, ", ", p$time_agg, ")"),
      unlist(p$controls)
    ) %>%
      purrr::compact()

    fml <- as.formula(
      paste0(
        p$outcome,
        " ~ ",
        paste(rhs_terms, collapse = " + "),
        " | ",
        p$space_fe,
        " + ",
        p$time_fe
      )
    )
    cl_fml <- as.formula(paste0(" ~ ", p$cluster_var, " + ", p$time_fe))

    # Build description
    desc <- build_description(
      p$outcome,
      p$treatment_threshold,
      p$treatment_type,
      p$time_agg,
      p$thr_time_agg,
      p$time_fe,
      p$space_fe,
      p$cluster_var,
      unlist(p$controls)
    )

    # Run the model
    res <- tryCatch(
      {
        fixest::feols(
          fml = fml,
          data = data,
          vcov = cl_fml
        )
      },
      error = function(e) {
        cli::cli_alert_danger("Error fitting model {mn}: {e$message}")
        return(NULL)
      }
    )

    # Skip if model failed
    if (is.null(res)) {
      next
    }

    # Only save the plotting data
    res <- ggfixest::iplot_data(
      res,
      .ci_level = 0.95
    )

    # Build specification for ggplot
    controls <- if (is.null(p$controls) || length(p$controls) == 0) {
      ""
    } else {
      paste0(
        "+ ",
        paste(unlist(p$controls), collapse = " + ")
      )
    }

    spec <- glue::glue(
      "{p$outcome} ~ {p$time_fe} + {p$space_fe} + {treatment_var} {controls}"
    )

    attr(res, "description") <- desc
    attr(res, "spec") <- spec

    # Save to individual file
    model_file <- file.path(res_dir, paste0(mn, ".rds"))
    saveRDS(res, model_file)

    # Update index
    model_index <- model_index %>%
      dplyr::add_row(
        model_name = mn,
        completed = TRUE,
        file_path = model_file
      )
    saveRDS(model_index, index_path)

    # Clean up memory
    rm(res, fml, cl_fml, desc, spec, treatment_var, rhs_terms, controls)
    gc(verbose = FALSE)
  }

  cli::cli_alert_success("All models saved in → {res_dir}")
  invisible(model_index)
}
```


```{r exec-run-event-study-rental-sunab}
#| eval: false
# Run Event Study Regressions

param_grid <- expand.grid(
  outcome = c("log_price_listing"),
  treatment_threshold = c("mean", "p50", "p75", "p90"),
  treatment_type = c("spill_count", "spill_hrs"),
  thr_time_agg = "all",
  time_agg = "qtr_id",
  time_fe = "qtr_id",
  space_fe = "lsoa",
  cluster_var = "lsoa",
  controls = I(list(
    NULL,
    c("property_type")
  ))
)

event_data_list_sample <- purrr::map(1:length(event_data_list), function(i) {
  event_data_list[[i]] %>%
    slice_sample(prop = 0.10)
}) %>%
  purrr::set_names(paste0("rad_", radii))

purrr::imap(
  event_data_list,
  ~ {
    rad_value <- as.numeric(gsub("rad_", "", .y))
    run_event_study_sunab(
      param_grid = param_grid,
      data = .x,
      rad = rad_value,
      overwrite = TRUE,
      file_name = glue::glue("rentals_sunab_results_{rad_value}.rds")
    )
  }
)
```


```{r func-load-plot-sunab-rental}
# Define Function to Load Results
load_results_sunab <- function(
  radii = c(250, 500, 1000),
  freqs = c("qtr", "mo"),
  dir_path = here::here("output", "regs"),
  quiet = FALSE,
  pattern = "rentals_sunab_models_rad_{r}"
) {
  results <- list()

  for (r in radii) {
    r_chr <- as.character(r)

    # Initialize radius slot if needed
    if (is.null(results[[r_chr]])) {
      results[[r_chr]] <- list()
    }

    for (f in freqs) {
      # Create path to model index file
      model_dir_pattern <- glue::glue(
        pattern,
        .envir = rlang::env(r = r, f = f)
      )
      model_dir <- file.path(dir_path, model_dir_pattern)
      index_path <- file.path(model_dir, "model_index.rds")

      # Skip if no index file exists
      if (!file.exists(index_path)) {
        if (!quiet) {
          cli::cli_alert_warning(
            "No model index found for radius {r}, freq {f}"
          )
        }
        next
      }

      # Read model index
      model_index <- readRDS(index_path)

      # Initialize frequency slot
      results[[r_chr]][[f]] <- list()

      # Load each model into the structure
      model_count <- 0
      for (mn in model_index$model_name) {
        model_path <- file.path(model_dir, paste0(mn, ".rds"))
        if (file.exists(model_path)) {
          results[[r_chr]][[f]][[mn]] <- readRDS(model_path)
          model_count <- model_count + 1
        }
      }

      if (!quiet) {
        cli::cli_alert_success(
          "Loaded {model_count} models for radius {r}, freq {f}"
        )
      }
    }
  }

  return(results)
}


results_sunab <- load_results_sunab(
  radii = c(250, 500, 1000),
  freqs = c("qtr"),
  quiet = FALSE,
  pattern = "rentals_sunab_models_rad_{r}"
)
```

### Binary Treatment - Average Spill Count {#sec-06-05-01-binary-average}

::: {.panel-tabset group="threshold-rental"}

#### 250m

::: {.panel-tabset group="radius-rental-250m"}

##### Count (NC)

```{r plot-rental-sunab-250m-count-nc}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_mean_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-rental-sunab-250m-count-c}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_mean_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r plot-rental-sunab-250m-duration-nc}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_mean_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-rental-sunab-250m-duration-c}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_mean_all_fe_qtr_id_lsoa_property_type"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-rental-500m"}

##### Count (NC)

```{r plot-rental-sunab-500m-count-nc}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_mean_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-rental-sunab-500m-count-c}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_mean_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r plot-rental-sunab-500m-duration-nc}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_mean_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-rental-sunab-500m-duration-c}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_mean_all_fe_qtr_id_lsoa_property_type"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-rental-1000m"}

##### Count (NC)

```{r plot-rental-sunab-1000m-count-nc}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_mean_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-rental-sunab-1000m-count-c}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_mean_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r plot-rental-sunab-1000m-duration-nc}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_mean_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-rental-sunab-1000m-duration-c}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_mean_all_fe_qtr_id_lsoa_property_type"
)
```

:::

:::

### Binary Treatment - Median Spill Count {#sec-06-05-02-binary-median}

::: {.panel-tabset group="threshold-rental"}

#### 250m

::: {.panel-tabset group="radius-rental-250m"}

##### Count (NC)

```{r plot-rental-sunab-250m-count-nc-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_p50_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-rental-sunab-250m-count-c-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_p50_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r plot-rental-sunab-250m-duration-nc-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_p50_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-rental-sunab-250m-duration-c-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_p50_all_fe_qtr_id_lsoa_property_type"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-rental-500m"}

##### Count (NC)

```{r plot-rental-sunab-500m-count-nc-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_p50_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-rental-sunab-500m-count-c-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_p50_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r plot-rental-sunab-500m-duration-nc-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_p50_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-rental-sunab-500m-duration-c-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_p50_all_fe_qtr_id_lsoa_property_type"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-rental-1000m"}

##### Count (NC)

```{r plot-rental-sunab-1000m-count-nc-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_p50_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-rental-sunab-1000m-count-c-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_p50_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r plot-rental-sunab-1000m-duration-nc-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_p50_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-rental-sunab-1000m-duration-c-p50}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_p50_all_fe_qtr_id_lsoa_property_type"
)
```

:::

:::

### Binary Treatment - 75th Percentile Spill Count {#sec-06-05-03-binary-p75}

::: {.panel-tabset group="threshold-rental"}

#### 250m

::: {.panel-tabset group="radius-rental-250m"}

##### Count (NC)

```{r plot-rental-sunab-250m-count-nc-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_p75_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-rental-sunab-250m-count-c-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_p75_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r plot-rental-sunab-250m-duration-nc-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_p75_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-rental-sunab-250m-duration-c-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_p75_all_fe_qtr_id_lsoa_property_type"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-rental-500m"}

##### Count (NC)

```{r plot-rental-sunab-500m-count-nc-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_p75_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-rental-sunab-500m-count-c-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_p75_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r plot-rental-sunab-500m-duration-nc-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_p75_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-rental-sunab-500m-duration-c-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_p75_all_fe_qtr_id_lsoa_property_type"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-rental-1000m"}

##### Count (NC)

```{r plot-rental-sunab-1000m-count-nc-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_p75_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-rental-sunab-1000m-count-c-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_p75_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r plot-rental-sunab-1000m-duration-nc-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_p75_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-rental-sunab-1000m-duration-c-p75}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_p75_all_fe_qtr_id_lsoa_property_type"
)
```

:::

:::

### Binary Treatment - 90th Percentile Spill Count {#sec-06-05-04-binary-p90}

::: {.panel-tabset group="threshold-rental"}

#### 250m

::: {.panel-tabset group="radius-rental-250m"}

##### Count (NC)

```{r plot-rental-sunab-250m-count-nc-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_p90_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-rental-sunab-250m-count-c-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sc_p90_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r plot-rental-sunab-250m-duration-nc-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_p90_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-rental-sunab-250m-duration-c-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 250,
  model = "bin_logp_sh_p90_all_fe_qtr_id_lsoa_property_type"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-rental-500m"}

##### Count (NC)

```{r plot-rental-sunab-500m-count-nc-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_p90_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-rental-sunab-500m-count-c-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sc_p90_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r plot-rental-sunab-500m-duration-nc-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_p90_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-rental-sunab-500m-duration-c-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 500,
  model = "bin_logp_sh_p90_all_fe_qtr_id_lsoa_property_type"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-rental-1000m"}

##### Count (NC)

```{r plot-rental-sunab-1000m-count-nc-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_p90_all_fe_qtr_id_lsoa"
)
```

##### Count (C)

```{r plot-rental-sunab-1000m-count-c-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sc_p90_all_fe_qtr_id_lsoa_property_type"
)
```

##### Duration (NC)

```{r plot-rental-sunab-1000m-duration-nc-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_p90_all_fe_qtr_id_lsoa"
)
```

##### Duration (C)

```{r plot-rental-sunab-1000m-duration-c-p90}
plot_reg_sunab(
  data = results_sunab,
  radius = 1000,
  model = "bin_logp_sh_p90_all_fe_qtr_id_lsoa_property_type"
)
```

:::

:::