---
author: "Jacopo Olivieri"
date: 2024-04-01
editor: source
format: html
number-sections: true
number-depth: 4
execute: 
  echo: false
  warning: false
  message: false
  freeze: auto
  fig-width: 9
  fig-asp: 0.618 
  fig-align: center
---

# Event Study {#sec-05-event-study}

```{r setup, include=FALSE}
# Initialize packages with version control
if (!requireNamespace("renv", quietly = TRUE)) {
  install.packages("renv")
}

# Run manual renv commands if needed
# renv::activate() # Activate the project library
# renv::restore()  # Restore the environment if running for first time
# renv::snapshot()  # After adding/updating packages, snapshot the state


# Load required packages
required_packages <- c(
  "rmarkdown", "rio", "tidyverse", "purrr", "here",
  "janitor", "sf", "sp", "rnaturalearth",
  "rnaturalearthdata", "rnrfa", "DescTools",
  "modelsummary", "tmap", "leaflet",
  "htmltools", "servr", "viridis", "data.table",
  "reactable", "htmlwidgets", "reactablefmtr", "dbplyr",
  "DIDmultiplegtDYN", "arrow"
)
install_if_missing <- function(packages) {
  new_packages <- packages[!sapply(packages, requireNamespace, quietly = TRUE)]
  if (length(new_packages) > 0) {
    install.packages(new_packages)
  }
  invisible(sapply(packages, library, character.only = TRUE))
}
install_if_missing(required_packages)


# Initialize logging
log_path <- here::here("output", "log", "house_data_exploration")
if (!dir.exists(dirname(log_path))) {
  dir.create(dirname(log_path), recursive = TRUE)
}
logger::log_appender(logger::appender_file(log_path))
logger::log_layout(logger::layout_glue_colors)

# Ggplot theme
theme_pref <- theme_minimal() +
  theme(
    text = element_text(size = 12),
    plot.title = element_text(
      face = "bold", size = 12,
      margin = ggplot2::margin(b = 10, unit = "pt")
    ),
    axis.title = element_text(face = "bold", size = 10),
    axis.text = element_text(angle = 45, hjust = 1, vjust = 1, size = 8),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_line(color = "gray95"),
    panel.grid.major.y = element_line(color = "gray95"),
    legend.position = "bottom",
    legend.title = element_text(face = "bold", size = 10),
    legend.text = element_text(size = 8),
    plot.margin = ggplot2::margin(t = 10, r = 10, b = 10, l = 10, unit = "pt")
  )
```


```{r}
#| eval: false
#| include: false

# Set up parallel plan (adjust workers based on RAM and cores)
num_workers <- 2
plan(multisession, workers = num_workers)

# message(paste("Setting up parallel execution using 'multicore' with", num_workers, "workers..."))
message(paste("Setting up parallel execution using 'multisession' with", num_workers, "workers..."))

# The rest of the script uses this plan via future_lapply

# Binary
# Function to run event study models with flexible parameters
run_bin_event_study <- function(param_grid, rad = 2000, overwrite = FALSE) {
  # Path for results files
  results_path <- here("book", "book_regs", paste0("binary_did_results_", rad, ".rds"))
  partial_path <- here("book", "book_regs", paste0("binary_did_results_partial_", rad, ".rds"))

  # Create directory if it doesn't exist
  results_dir <- dirname(results_path)
  if (!dir.exists(results_dir)) {
    dir.create(results_dir, recursive = TRUE)
    message("Created directory: ", results_dir)
  }

  # Load existing results if not overwriting and file exists
  existing_results <- list()
  if (!overwrite && file.exists(results_path)) {
    existing_results <- readRDS(results_path)
    message("Loaded existing results from: ", results_path)
  } else if (!overwrite) {
    message("No existing results file found or overwrite=TRUE. Starting fresh for radius ", rad)
  } else {
    message("overwrite=TRUE. Starting fresh for radius ", rad)
  }

  # Load the dataset for the current radius
  message(paste("Loading data for radius:", rad))
  dat_panel_site <- tryCatch(
    {
      open_dataset(
        here::here("data", "processed", "dat_panel_site_mo")
      ) %>%
        filter(radius == rad) %>%
        collect()
    },
    error = function(e) {
      message("Error loading data for radius ", rad, ": ", e$message)
      return(NULL) # Return NULL if data loading fails
    }
  )

  if (is.null(dat_panel_site)) {
    message("Skipping radius ", rad, " due to data loading error.")
    return(existing_results) # Return existing (potentially empty) results
  }
  message(paste("Data loaded successfully for radius:", rad, " - Rows:", nrow(dat_panel_site)))

  # --- Helper function to run a single model ---
  run_single_bin_model <- function(params, data_for_radius) {
    # Extract parameters from the list 'params'
    outcome <- params$outcome
    treatment_threshold <- params$treatment_threshold
    time_agg <- params$time_agg
    normalized <- params$normalized
    same_switchers <- params$same_switchers
    treatment_type <- params$treatment_type

    # Construct the treatment variable name dynamically
    treatment_var <- paste0("treated_", treatment_type, "_", treatment_threshold, "_", time_agg)

    # Build model name
    outcome_suffix <- ifelse(outcome == "log_price_median_w", "_logpw", "_logp")
    treat_type_suffix <- ifelse(treatment_type == "spill_count", "_sc", "_sh")
    threshold_suffix <- paste0("_", treatment_threshold)
    time_agg_suffix <- paste0("_", time_agg)
    sw_suffix <- if (same_switchers) "_sw" else ""
    norm_suffix <- if (normalized) "_norm" else ""
    model_name <- paste0(
      "model_bin", # Base name
      outcome_suffix, # _logp or _logpw
      treat_type_suffix, # _sc or _sh
      threshold_suffix, # _mean, _p50, etc.
      time_agg_suffix, # _mo or _yr
      sw_suffix, # _sw (if TRUE)
      norm_suffix # _norm (if TRUE)
    )

    # Build model description
    outcome_label <- case_when(
      outcome == "price_median_w" ~ "Weighted Price Median",
      outcome == "log_price_median_w" ~ "Weighted Log Price Median",
      outcome == "price_median" ~ "Price Median",
      outcome == "log_price_median" ~ "Log Price Median",
      TRUE ~ outcome
    )
    threshold_label <- case_when(
      treatment_threshold == "mean" ~ "Mean",
      treatment_threshold == "p50" ~ "P50",
      treatment_threshold == "p75" ~ "P75",
      treatment_threshold == "p90" ~ "P90",
      treatment_threshold == "max" ~ "Max",
      TRUE ~ paste0(toupper(substr(treatment_threshold, 1, 1)), substr(treatment_threshold, 2, nchar(treatment_threshold)))
    )
    time_agg_label <- ifelse(time_agg == "mo", "Monthly", "Yearly")
    treat_type_label <- ifelse(treatment_type == "spill_count", "Spill Count", "Spill Hrs")
    norm_label <- ifelse(normalized, "Norm", "No Norm")
    switchers_label <- ifelse(same_switchers, "Same Switchers", "All Switchers")
    model_description <- sprintf(
      "%s ~ %s %s %s (%s, %s)",
      outcome_label, time_agg_label, threshold_label, treat_type_label,
      norm_label, switchers_label
    )

    cat(sprintf("Running model: %s (%s)\n", model_name, model_description))

    # Run the actual DID model
    model_result <- try(did_multiplegt_dyn(
      df = data_for_radius,
      outcome = outcome,
      group = "site_id",
      time = "month_id",
      treatment = treatment_var,
      effects = 12,
      placebo = 3,
      cluster = "site_id",
      normalized = normalized,
      trends_lin = FALSE,
      same_switchers = same_switchers,
      less_conservative_se = TRUE,
      graph_off = TRUE # Typically turn off graph in parallel runs
    ), silent = FALSE) # Set silent=FALSE to see errors from did_multiplegt_dyn

    # Return a named list for this model
    result <- list()
    result[[model_name]] <- model_result
    attr(result[[model_name]], "description") <- model_description
    return(result)
  }
  # --- End Helper function ---

  # Filter param_grid: Keep only models not present in existing_results if overwrite=FALSE
  models_to_run_indices <- 1:nrow(param_grid)
  if (!overwrite && length(existing_results) > 0) {
    existing_model_names <- names(existing_results)
    models_to_run_indices <- which(!apply(param_grid, 1, function(row) {
      # Reconstruct model name to check existence (ensure this logic matches exactly)
      outcome <- row[["outcome"]]
      treatment_threshold <- row[["treatment_threshold"]]
      time_agg <- row[["time_agg"]]
      normalized <- as.logical(row[["normalized"]]) # Ensure logical
      same_switchers <- as.logical(row[["same_switchers"]]) # Ensure logical
      treatment_type <- row[["treatment_type"]]

      model_name <- "model_bin"
      if (grepl("log_", outcome)) model_name <- paste0(model_name, "_log")
      if (grepl("_w$", outcome)) model_name <- paste0(model_name, "_w")
      treat_type_short <- ifelse(treatment_type == "spill_count", "sc", "sh")
      model_name <- paste0(model_name, "_", treat_type_short)
      model_name <- paste0(model_name, "_", treatment_threshold)
      model_name <- paste0(model_name, "_", time_agg)
      if (same_switchers) model_name <- paste0(model_name, "_sw")
      if (normalized) model_name <- paste0(model_name, "_norm")
      return(model_name %in% existing_model_names)
    }))

    if (length(models_to_run_indices) < nrow(param_grid)) {
      message(sprintf(
        "Skipping %d models already present in results for radius %d.",
        nrow(param_grid) - length(models_to_run_indices), rad
      ))
    }
  }

  # Convert param_grid rows to a list of lists for lapply
  params_list <- split(param_grid[models_to_run_indices, , drop = FALSE], seq_len(length(models_to_run_indices)))

  total_models_to_run <- length(params_list)
  if (total_models_to_run == 0) {
    message("No new models to run for radius ", rad)
    return(existing_results)
  }

  cat(sprintf("Starting parallel model estimation for radius %d - total models to run: %d\n", rad, total_models_to_run))

  # Run models in parallel using future_lapply
  # Pass necessary objects explicitly if needed using future.globals
  # future_lapply automatically tries to find globals, but being explicit can help
  # Especially ensure 'dat_panel_site' and 'did_multiplegt_dyn' are available
  new_results_list <- future_lapply(params_list, run_single_bin_model,
    data_for_radius = dat_panel_site,
    future.seed = TRUE, # for reproducibility if needed
    future.globals = list(
      did_multiplegt_dyn = DIDmultiplegtDYN::did_multiplegt_dyn,
      case_when = dplyr::case_when
      # Add other necessary functions/objects if errors occur
    ),
    future.packages = c("dplyr", "DIDmultiplegtDYN") # Explicitly load packages on workers
  )

  # Combine the list of lists into a single named list
  new_results <- do.call(c, new_results_list)

  # Combine new results with existing ones
  # If overwrite=TRUE, existing_results is empty, so this just becomes new_results
  # If overwrite=FALSE, this adds new results to the loaded ones
  final_results <- c(existing_results, new_results)

  # Save the final results for this radius
  tryCatch(
    {
      saveRDS(final_results, file = results_path)
      message("Results saved successfully for radius ", rad, " to: ", results_path)
      # Optionally remove partial file if main save succeeds
      if (file.exists(partial_path)) file.remove(partial_path)
    },
    error = function(e) {
      message("Error saving final results for radius ", rad, ": ", e$message)
      # Attempt to save partial results if final save fails
      tryCatch(
        {
          saveRDS(final_results, file = partial_path)
          message("Partial results saved for radius ", rad, " to: ", partial_path)
        },
        error = function(e_partial) {
          message("CRITICAL ERROR: Failed to save even partial results for radius ", rad, ": ", e_partial$message)
        }
      )
    }
  )

  cat("Finished model estimation for radius ", rad, "\n")

  # Return results invisibly
  invisible(final_results)
}

binary_param_grid <- expand.grid(
  outcome = c("log_price_median", "log_price_median_w"),
  treatment_threshold = c("mean", "p50", "p75", "p90", "max"),
  time_agg = c("mo", "yr"),
  treatment_type = c("spill_count", "spill_hrs"),
  normalized = c(TRUE),
  same_switchers = c(TRUE),
  stringsAsFactors = FALSE
)

# Define radii
radii <- c(500, 250)

# NEW sequential radii loop
bin_results_status <- list()
for (r in radii) {
  message(paste("\n--- Starting processing for radius:", r, "---\n"))
  success <- tryCatch(
    {
      # Call the function for the current radius.
      # Set overwrite = FALSE to append/skip existing models by default
      # Set overwrite = TRUE if you want to rerun everything for this radius
      run_bin_event_study(binary_param_grid, rad = r, overwrite = FALSE)
      TRUE # Indicate success
    },
    error = function(e) {
      message(paste("Error processing binary models for radius:", r, "-", e$message))
      FALSE # Indicate failure
    }
  )
  bin_results_status[[as.character(r)]] <- success # Store status by radius
  # Optional: Add a small delay or GC call between radii if memory is an issue
  gc()
  Sys.sleep(1) # Small pause
}

message("Finished all binary event studies.")
# Check if any radius failed
if (any(!unlist(bin_results_status))) {
  failed_radii <- names(bin_results_status)[!unlist(bin_results_status)]
  warning("Binary event studies failed for radii: ", paste(failed_radii, collapse = ", "), ". Check logs.")
} else {
  message("All binary event studies completed successfully for all radii.")
}

# Clean up memory before continuous runs
gc()


##########################################


# Continuous treatment
# Function to run event study models with flexible parameters
run_continuous_event_study <- function(param_grid, rad = 2000, overwrite = FALSE) {
  # Path for results files
  results_path <- here("book", "book_regs", paste0("cont_did_results_", rad, ".rds"))
  partial_path <- here("book", "book_regs", paste0("cont_did_results_partial_", rad, ".rds"))

  # Create directory if it doesn't exist
  results_dir <- dirname(results_path)
  if (!dir.exists(results_dir)) {
    dir.create(results_dir, recursive = TRUE)
    message("Created directory: ", results_dir)
  }

  # Load existing results if not overwriting and file exists
  existing_results <- list()
  if (!overwrite && file.exists(results_path)) {
    existing_results <- readRDS(results_path)
    message("Loaded existing continuous results from: ", results_path)
  } else if (!overwrite) {
    message("No existing continuous results file found or overwrite=TRUE. Starting fresh for radius ", rad)
  } else {
    message("overwrite=TRUE. Starting fresh for continuous models for radius ", rad)
  }

  # Load the dataset for the current radius
  message(paste("Loading data for continuous models, radius:", rad))
  dat_panel_site <- tryCatch(
    {
      open_dataset(
        here::here("data", "processed", "dat_panel_site_mo")
      ) %>%
        filter(radius == rad) %>%
        collect()
    },
    error = function(e) {
      message("Error loading data for continuous models, radius ", rad, ": ", e$message)
      return(NULL) # Return NULL if data loading fails
    }
  )

  if (is.null(dat_panel_site)) {
    message("Skipping continuous models for radius ", rad, " due to data loading error.")
    return(existing_results) # Return existing (potentially empty) results
  }
  message(paste("Data loaded successfully for continuous models, radius:", rad, " - Rows:", nrow(dat_panel_site)))

  # --- Helper function to run a single continuous model ---
  run_single_cont_model <- function(params, data_for_radius) {
    # Extract parameters
    outcome <- params$outcome
    treatment_var <- params$treatment # Note: param name is 'treatment' in continuous_param_grid
    normalized <- params$normalized
    same_switchers <- params$same_switchers

    # Build model name
    outcome_suffix <- ifelse(outcome == "log_price_median_w", "_logpw", "_logp")
    treat_suffix <- case_when(
      treatment_var == "spill_count" ~ "_sc",
      treatment_var == "log_spill_count" ~ "_logsc",
      treatment_var == "spill_hrs" ~ "_sh",
      treatment_var == "log_spill_hrs" ~ "_logsh",
      TRUE ~ paste0("_", gsub("[^[:alnum:]]", "", treatment_var))
    )
    sw_suffix <- if (same_switchers) "_sw" else ""
    norm_suffix <- if (normalized) "_norm" else ""
    model_name <- paste0(
      "model_cont", # Base name for continuous
      outcome_suffix, # _logp or _logpw
      treat_suffix, # _sc, _logsc, _sh, _logsh
      sw_suffix, # _sw (if TRUE)
      norm_suffix # _norm (if TRUE)
    )

    # Build model description
    outcome_label <- case_when(
      outcome == "price_median_w" ~ "Weighted Price Median",
      outcome == "log_price_median_w" ~ "Weighted Log Price Median",
      outcome == "price_median" ~ "Price Median",
      outcome == "log_price_median" ~ "Log Price Median",
      TRUE ~ outcome
    )
    treatment_label <- case_when(
      treatment_var == "spill_count" ~ "Spill Count",
      treatment_var == "log_spill_count" ~ "Log Spill Count",
      treatment_var == "spill_hrs" ~ "Spill Hours",
      treatment_var == "log_spill_hrs" ~ "Log Spill Hours",
      TRUE ~ treatment_var
    )
    norm_label <- ifelse(normalized, "Norm", "No Norm")
    switchers_label <- ifelse(same_switchers, "Same Switchers", "All Switchers")
    model_description <- sprintf(
      "%s ~ %s (Continuous; %s, %s)",
      outcome_label, treatment_label, norm_label, switchers_label
    )

    cat(sprintf("Running model: %s (%s)\n", model_name, model_description))

    # Run the actual DID model for continuous treatment
    model_result <- try(did_multiplegt_dyn(
      df = data_for_radius,
      outcome = outcome,
      group = "site_id",
      time = "month_id",
      treatment = treatment_var,
      effects = 9,
      placebo = 2,
      cluster = "site_id",
      normalized = normalized,
      trends_lin = FALSE,
      same_switchers = same_switchers,
      less_conservative_se = TRUE,
      graph_off = TRUE, # Turn off graph in parallel runs
      effects_equal = TRUE # Specific to continuous setup
    ), silent = FALSE) # Keep silent = FALSE to see errors

    # Return a named list for this model
    result <- list()
    result[[model_name]] <- model_result
    attr(result[[model_name]], "description") <- model_description
    return(result)
  }
  # --- End Helper function ---

  # Filter param_grid: Keep only models not present in existing_results if overwrite=FALSE
  models_to_run_indices <- 1:nrow(param_grid)
  if (!overwrite && length(existing_results) > 0) {
    existing_model_names <- names(existing_results)
    models_to_run_indices <- which(!apply(param_grid, 1, function(row) {
      # Reconstruct model name to check existence
      outcome <- row[["outcome"]]
      treatment_var <- row[["treatment"]]
      normalized <- as.logical(row[["normalized"]])
      same_switchers <- as.logical(row[["same_switchers"]])

      model_name <- "model_cont"
      if (grepl("log_", outcome)) model_name <- paste0(model_name, "_log")
      if (grepl("_w$", outcome)) model_name <- paste0(model_name, "_w")
      treat_short_name <- gsub("spill_count", "sc", treatment_var)
      treat_short_name <- gsub("spill_hrs", "sh", treat_short_name)
      treat_short_name <- gsub("log_", "log", treat_short_name)
      model_name <- paste0(model_name, "_", treat_short_name)
      if (same_switchers) model_name <- paste0(model_name, "_sw")
      if (normalized) model_name <- paste0(model_name, "_norm")
      return(model_name %in% existing_model_names)
    }))

    if (length(models_to_run_indices) < nrow(param_grid)) {
      message(sprintf(
        "Skipping %d continuous models already present in results for radius %d.",
        nrow(param_grid) - length(models_to_run_indices), rad
      ))
    }
  }

  # Convert param_grid rows to a list of lists for lapply
  params_list <- split(param_grid[models_to_run_indices, , drop = FALSE], seq_len(length(models_to_run_indices)))

  total_models_to_run <- length(params_list)
  if (total_models_to_run == 0) {
    message("No new continuous models to run for radius ", rad)
    return(existing_results)
  }

  cat(sprintf("Starting parallel continuous model estimation for radius %d - total models to run: %d\n", rad, total_models_to_run))

  # Run models in parallel using future_lapply
  new_results_list <- future_lapply(params_list, run_single_cont_model,
    data_for_radius = dat_panel_site,
    future.seed = TRUE,
    future.globals = list(
      did_multiplegt_dyn = DIDmultiplegtDYN::did_multiplegt_dyn,
      case_when = dplyr::case_when
    ),
    future.packages = c("dplyr", "DIDmultiplegtDYN")
  )

  # Combine the list of lists into a single named list
  new_results <- do.call(c, new_results_list)

  # Combine new results with existing ones
  final_results <- c(existing_results, new_results)

  # Save the final results for this radius
  tryCatch(
    {
      saveRDS(final_results, file = results_path)
      message("Continuous results saved successfully for radius ", rad, " to: ", results_path)
      if (file.exists(partial_path)) file.remove(partial_path)
    },
    error = function(e) {
      message("Error saving final continuous results for radius ", rad, ": ", e$message)
      # Attempt to save partial results if final save fails
      tryCatch(
        {
          saveRDS(final_results, file = partial_path)
          message("Partial continuous results saved for radius ", rad, " to: ", partial_path)
        },
        error = function(e_partial) {
          message("CRITICAL ERROR: Failed to save even partial continuous results for radius ", rad, ": ", e_partial$message)
        }
      )
    }
  )

  cat("Finished continuous model estimation for radius ", rad, "\n")

  # Return results invisibly
  invisible(final_results)
}

continuous_param_grid <- expand.grid(
  outcome = c("log_price_median", "log_price_median_w"),
  treatment = c("spill_count", "log_spill_count", "spill_hrs", "log_spill_hrs"),
  normalized = c(TRUE),
  same_switchers = c(TRUE),
  stringsAsFactors = FALSE
)

# NEW sequential radii loop
cont_results_status <- list()
for (r in radii) {
  message(paste("\n--- Starting continuous processing for radius:", r, "---\n"))
  success <- tryCatch(
    {
      # Call the function for the current radius.
      # Set overwrite = FALSE to append/skip existing models by default
      run_continuous_event_study(continuous_param_grid, rad = r, overwrite = FALSE)
      TRUE # Indicate success
    },
    error = function(e) {
      message(paste("Error processing continuous models for radius:", r, "-", e$message))
      FALSE # Indicate failure
    }
  )
  cont_results_status[[as.character(r)]] <- success # Store status by radius
  # Optional: Add GC call and sleep between radii
  gc()
  Sys.sleep(1)
}

message("Finished all continuous event studies.")
# Check if any radius failed
if (any(!unlist(cont_results_status))) {
  failed_radii <- names(cont_results_status)[!unlist(cont_results_status)]
  warning("Continuous event studies failed for radii: ", paste(failed_radii, collapse = ", "), ". Check logs.")
} else {
  message("All continuous event studies completed successfully for all radii.")
}

# Reset to sequential plan after parallel execution (good practice)
plan(sequential)
```



```{r}
all_results <- list()
rads <- c(250, 500, 1000, 2000)

for (rad in rads) {
  rad_str <- as.character(rad)

  # Handle binary results
  path_binary <- here("output", "regs", 
                      paste0("binary_did_results_", rad, "_qt", ".rds"))
  if (file.exists(path_binary)) {
    all_results$binary[[rad_str]] <- readRDS(path_binary)
  } else {
    print(paste("Binary file does not exist:", path_binary))
    # We don't return or skip - continue processing other files
  }

  # Handle continuous results
  path_cont <- here("output", "regs", 
                    paste0("cont_did_results_", rad, "_qt", ".rds"))
  if (file.exists(path_cont)) {
    all_results$continuous[[rad_str]] <- readRDS(path_cont)
  } else {
    print(paste("Continuous file does not exist:", path_cont))
    # We don't return or skip - continue processing other files
  }
}


get_regression_plot <- function(results,
                                treatment_type = c("binary", "continuous"),
                                radius = NULL,
                                model = NULL,
                                use_description = TRUE,
                                arrange_plots = TRUE,
                                ncol = 2) {
  # Parameter validation
  treatment_type <- match.arg(treatment_type)

  # Handle radius validation
  valid_radii <- c("250", "500", "1000", "2000", "5000", "10000")
  if (is.null(radius)) {
    radius <- valid_radii[1]
    message(paste("No radius specified. Using default radius:", radius))
  } else {
    radius <- as.character(radius)
    # Check if all specified radiuses are valid
    invalid_radii <- radius[!radius %in% valid_radii]
    if (length(invalid_radii) > 0) {
      stop(paste(
        "Invalid radiuses:", paste(invalid_radii, collapse = ", "),
        "\nValid options are:", paste(valid_radii, collapse = ", ")
      ))
    }
  }

  # Create a list to store plots
  plot_list <- list()

  # Loop through each radius
  for (r in radius) {
    # Check if treatment and radius exist
    if (!treatment_type %in% names(results)) {
      message(paste("Treatment type", treatment_type, "not found in results. Skipping."))
      next
    }

    if (!r %in% names(results[[treatment_type]])) {
      message(paste("Radius", r, "not found for treatment type", treatment_type, ". Skipping."))
      next
    }

    # Get models for the specified treatment type and radius
    available_models <- names(results[[treatment_type]][[r]])

    if (length(available_models) == 0) {
      message(paste("No models found for treatment type", treatment_type, "and radius", r, ". Skipping."))
      next
    }

    # Handle model selection by number or name
    selected_model <- NULL

    if (is.numeric(model)) {
      if (model <= 0 || model > length(available_models)) {
        message(paste("Model index must be between 1 and", length(available_models), "for radius", r, ". Skipping."))
        next
      }
      selected_model <- available_models[model]
    } else if (is.character(model)) {
      if (!model %in% available_models) {
        message(paste("Model", model, "not found for radius", r, ". Skipping."))
        next
      }
      selected_model <- model
    } else if (is.null(model)) {
      # If no model specified, use the first one
      selected_model <- available_models[1]
      message(paste("No model specified. Using first model for radius", r, ":", selected_model))
    } else {
      message("Model must be specified as a character string or numeric index. Skipping radius", r)
      next
    }

    # Get the model object
    model_obj <- results[[treatment_type]][[r]][[selected_model]]

    # Check if the model has a plot
    if (is.null(model_obj$plot)) {
      message(paste("No plot found for model", selected_model, "and radius", r, ". Skipping."))
      next
    }

    # Get subtitle from model description or name
    subtitle <- selected_model
    if (use_description && !is.null(attr(model_obj, "description"))) {
      subtitle <- attr(model_obj, "description")
    }

    # Create plot with subtitle and radius info
    plot_title <- paste("Radius:", r, "m")
    plot_obj <- model_obj$plot +
      ggplot2::labs(
        subtitle = subtitle,
        title = plot_title
      )

    # Add to the list of plots
    plot_list[[r]] <- plot_obj
  }

  # If no plots were created, return NULL
  if (length(plot_list) == 0) {
    message("No plots were created.")
    return(NULL)
  }

  # If there's only one plot, return it directly
  if (length(plot_list) == 1) {
    return(plot_list[[1]])
  }

  # If there are multiple plots and arrange_plots is TRUE, arrange them in a grid
  if (arrange_plots) {
    # Check if required packages are available
    if (!requireNamespace("gridExtra", quietly = TRUE)) {
      message("Package 'gridExtra' is required to arrange multiple plots. Installing...")
      install.packages("gridExtra")
      library(gridExtra)
    }

    # Arrange plots in a grid
    return(gridExtra::grid.arrange(grobs = plot_list, ncol = ncol))
  } else {
    # Return the list of plots
    return(plot_list)
  }
}

# Plot for a single radius
# plot <- get_regression_plot(
#   all_results,
#   treatment_type = "continuous", # binary
#   radius = 2000, # c(2000, 5000)
#   model = "model_cont_mean_log_logtreat_sw_norm" # 16
# )

create_regression_plot <- function(data = all_results,
                                   treatment_type, radius, model) {
  # Get the base plot using the existing function
  plot <- get_regression_plot(
    data,
    treatment_type = treatment_type,
    radius = radius,
    model = model
  )

  # Retrieve the specific model object AGAIN to access arguments
  # (get_regression_plot already did this, but didn't return args)
  model_obj <- data[[treatment_type]][[as.character(radius)]][[model]]

  # Construct the formula caption if arguments are available
  formula_caption <- NULL # Default to NULL
  if (!is.null(model_obj) && !inherits(model_obj, "try-error") && !is.null(model_obj$args) &&
    all(c("outcome", "group", "time", "treatment") %in% names(model_obj$args))) {
    args <- model_obj$args
    # Ensure args components are not NULL before pasting
    if (!is.null(args$outcome) && !is.null(args$group) && !is.null(args$time) && !is.null(args$treatment)) {
      formula_caption <- paste0(
        "Regression specification: ",
        args$outcome, " ~ ", args$group, " + ", args$time, " + ", args$treatment
      )
    } else {
      formula_caption <- paste("Regression specification: Partial details unavailable for:", model)
    }
  } else {
    # Fallback if args aren't available or model_obj is an error
    formula_caption <- paste("Regression specification: Details unavailable for:", model)
  }

  # Add group column based on Time and convert to factor with explicit order
  plot$data$group <- factor(ifelse(plot$data$Time <= 0, "Pre", "Post"),
    levels = c("Pre", "Post")
  )

  # Create the new plot
  new_plot <- ggplot(plot$data, aes(x = Time, y = Estimate)) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
    geom_errorbar(aes(ymin = LB.CI, ymax = UB.CI, color = group), width = 0.2) +
    geom_point(aes(color = group), size = 1) +
    scale_color_manual(
      values = c(
        "Pre" = viridis(1, option = "magma"),
        "Post" = viridis(3, option = "magma")[2]
      ),
      breaks = c("Pre", "Post")
    ) +
    theme_minimal() +
    labs(x = "Time", y = "Estimate", subtitle = plot$labels$subtitle, caption = formula_caption) +
    theme_pref +
    theme(plot.caption = element_text(hjust = 0)) # Left-align caption

  # Generate filename
  filename <- gsub("^model_", "", model)
  filename <- paste0(filename, "_", radius, ".png")
  filepath <- here("agents", "book", "book_figs", filename)

  # ggsave(filename = filepath, plot = new_plot, width = 8, height = 0.618 * 6, dpi = 600)

  # Return invisible to indicate function completed
  # invisible(NULL)
  return(new_plot)
}
```

## Setting {#sec-05-01-setting}

*This section is currently being revised as I read and process the recent DiD and event study literature. Some statements may be unclear or incorrect, which I will try to refine them as I go.*

We can conceptualise the setting as an event study where sewage spills constitute the treatment. To reduce compute time, I have aggregated the data to the X-meter radius around the spill site level by taking the median of house prices.

- **Treatment is non-absorbing:** spill sites can transition between treated and untreated states multiple times, as a location may experience large spill activity in one period and low in the next period (relative to other spill sites).
- **Treatment is staggered:** spills occur at different times across different locations
- **Treatment measurement:** spill severity is quantified by either incident count or duration in period $t$ (e.g., monthly), which is naturally continuous. However, we can simplify this into a binary treatment by classifying houses within radius X of a spill site as "treated" when the spill severity exceeds either the mean or a specified percentile threshold relative to other sites.
- **Fixed effects:** we can include both period and location-specific (spill site) fixed effects to estimate the effect of spills on house prices through within-spill site variation over time

Given the potential problems with the vanilla TWFE presented in the recent literature, I decide to use the Chaisemartin & d'Haultefoeuille (2024) estimator using the package `DIDmultiplegtDYN.` This estimator allows for a wide range of settings, including non-absorbing treatment, staggered treatment, continuous treatment, and many other settings that I still need to understand. 

## Basic Event Study Regressions {#sec-05-02-basic-event-study-regressions}

The following figures show the dynamic effect of sewage spills on house prices over time. Each graph plots changes in median house prices within X-metre radius buffers around spill sites, measured monthly. House prices are aggregated at the spill level using median values for each buffer distance. A buffer is considered "treated" in a given month when the number of spills exceeds either the average or a specified percentile of spill counts across all buffers, **calculated over either a monthly or yearly period**.

In the event study regressions, the effects are estimated for:

- **Same switchers only.** This ensures that event-study effects are estimated only using switchers for whom all the event-study effects can be estimated. This avoids the problem that if treatment effects are heterogeneous across spill sites where treatment switches, changes in the estimated effects across different time horizons might reflect changes in the composition of the sample rather than actual dynamic treatment effects.
- **Normalised.** This scales the estimates to represent effects per unit of treatment rather than total effects. For spill sites, this means showing the impact per unit of treatment intensity, making estimates comparable across time periods and sites.

Overall, all specifications show practically no effect of spills on house prices.

### Binary Treatment - Average Spill Count {#sec-05-02-01-binary-average}

::: {.panel-tabset group="threshold"}

#### 250m

::: {.panel-tabset group="radius-250m"}

##### Count Qt

```{r}
# model_binary_log_mean_sw_norm; radius 250
create_regression_plot(
  treatment_type = "binary", radius = 250,
  model = "model_bin_log_sc_mean_qt_sw_norm"
)
```

##### Count Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 250,
  model = "model_bin_log_sc_mean_yr_sw_norm"
)
```

##### Duration Qt
```{r}
create_regression_plot(
  treatment_type = "binary", radius = 250,
  model = "model_bin_log_sh_mean_qt_sw_norm"
)
```

##### Duration Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 250,
  model = "model_bin_log_sh_mean_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-500m"}

##### Count Mo

```{r}
# model_binary_log_mean_sw_norm; radius 500
create_regression_plot(
  treatment_type = "binary", radius = 500,
  model = "model_bin_log_sc_mean_qt_sw_norm"
)
```

##### Count Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 500,
  model = "model_bin_log_sc_mean_yr_sw_norm"
)
```

##### Duration Mo

```{r}

create_regression_plot(
  treatment_type = "binary", radius = 500,
  model = "model_bin_log_sh_mean_qt_sw_norm"
)
```

##### Duration Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 500,
  model = "model_bin_log_sh_mean_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-1000m"}  

##### Count Mo

```{r}
# model_binary_log_mean_sw_norm; radius 1000
create_regression_plot(
  treatment_type = "binary", radius = 1000,
  model = "model_bin_log_sc_mean_qt_sw_norm"
)
```

##### Count Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 1000,
  model = "model_bin_log_sc_mean_yr_sw_norm"
)
```

##### Duration Mo

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 1000,
  model = "model_bin_log_sh_mean_qt_sw_norm"
)
```

##### Duration Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 1000,
  model = "model_bin_log_sh_mean_yr_sw_norm"
)
```

:::

#### 2000m

::: {.panel-tabset group="radius-2000m"}

##### Count Mo

```{r}
# model_binary_log_mean_sw_norm; radius 2000
create_regression_plot(
  treatment_type = "binary", radius = 2000,
  model = "model_bin_log_sc_mean_qt_sw_norm"
)
```

##### Count Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 2000,
  model = "model_bin_log_sc_mean_yr_sw_norm"
)
```

##### Duration Mo

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 2000,
  model = "model_bin_log_sh_mean_qt_sw_norm"
)
```

##### Duration Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 2000,
  model = "model_bin_log_sh_mean_yr_sw_norm"
)
```

:::

:::

### Binary Treatment - Median Spill Count {#sec-05-02-02-binary-median}

::: {.panel-tabset group="threshold"}

#### 250m

::: {.panel-tabset group="radius-250m"}

##### Count Mo

```{r}
# model_binary_log_p50_sw_norm; radius 250
create_regression_plot(
  treatment_type = "binary", radius = 250,
  model = "model_bin_log_sc_p50_qt_sw_norm"
)
```

##### Count Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 250,
  model = "model_bin_log_sc_p50_yr_sw_norm"
)
```

##### Duration Mo

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 250,
  model = "model_bin_log_sh_p50_qt_sw_norm"
)
```

##### Duration Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 250,
  model = "model_bin_log_sh_p50_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-500m"}

##### Count Mo

```{r}
# model_binary_log_p50_sw_norm; radius 500
create_regression_plot(
  treatment_type = "binary", radius = 500,
  model = "model_bin_log_sc_p50_qt_sw_norm"
)
```

##### Count Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 500,
  model = "model_bin_log_sc_p50_yr_sw_norm"
)
```

##### Duration Mo

```{r}  
create_regression_plot(
  treatment_type = "binary", radius = 500,
  model = "model_bin_log_sh_p50_qt_sw_norm"
)
```

##### Duration Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 500,
  model = "model_bin_log_sh_p50_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-1000m"}

##### Count Mo

```{r}
# model_binary_log_p50_sw_norm; radius 1000
create_regression_plot(
  treatment_type = "binary", radius = 1000,
  model = "model_bin_log_sc_p50_qt_sw_norm"
)
```

##### Count Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 1000,
  model = "model_bin_log_sc_p50_yr_sw_norm"
)
```

##### Duration Mo

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 1000,
  model = "model_bin_log_sh_p50_qt_sw_norm"
)
```

##### Duration Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 1000,
  model = "model_bin_log_sh_p50_yr_sw_norm"
)
```

:::

#### 2000m

::: {.panel-tabset group="radius-2000m"}

##### Count Mo

```{r}
# model_binary_log_p50_sw_norm; radius 2000
create_regression_plot(
  treatment_type = "binary", radius = 2000,
  model = "model_bin_log_sc_p50_qt_sw_norm"
)
```

##### Count Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 2000,
  model = "model_bin_log_sc_p50_yr_sw_norm"
)
```

##### Duration Mo

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 2000,
  model = "model_bin_log_sh_p50_qt_sw_norm"
)
```

##### Duration Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 2000,
  model = "model_bin_log_sh_p50_yr_sw_norm"
)
```

:::

:::

### Binary Treatment - 75th Percentile Spill Count {#sec-05-02-03-binary-p75}

::: {.panel-tabset group="threshold"}  

#### 250m

::: {.panel-tabset group="radius-250m"}

##### Count Mo

```{r}
# model_binary_log_p75_sw_norm; radius 250
create_regression_plot(
  treatment_type = "binary", radius = 250,
  model = "model_bin_log_sc_p75_qt_sw_norm"
)
```

##### Count Yr

```{r}  
create_regression_plot(
  treatment_type = "binary", radius = 250,
  model = "model_bin_log_sc_p75_yr_sw_norm"
)
```

##### Duration Mo

```{r}  
create_regression_plot(
  treatment_type = "binary", radius = 250,
  model = "model_bin_log_sh_p75_qt_sw_norm"
)
```

##### Duration Yr

```{r}  
create_regression_plot(
  treatment_type = "binary", radius = 250,
  model = "model_bin_log_sh_p75_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-500m"}

##### Count Mo

```{r}
# model_binary_log_p75_sw_norm; radius 500
create_regression_plot(
  treatment_type = "binary", radius = 500,
  model = "model_bin_log_sc_p75_qt_sw_norm"
)
```

##### Count Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 500,
  model = "model_bin_log_sc_p75_yr_sw_norm"
)
```

##### Duration Mo

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 500,
  model = "model_bin_log_sh_p75_qt_sw_norm"
)
```

##### Duration Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 500,
  model = "model_bin_log_sh_p75_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-1000m"}

##### Count Mo

```{r}
# model_binary_log_p75_sw_norm; radius 1000
create_regression_plot(
  treatment_type = "binary", radius = 1000,
  model = "model_bin_log_sc_p75_qt_sw_norm"
)
```

##### Count Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 1000,
  model = "model_bin_log_sc_p75_yr_sw_norm"
)
```

##### Duration Mo

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 1000,
  model = "model_bin_log_sh_p75_qt_sw_norm"
)
```

##### Duration Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 1000,
  model = "model_bin_log_sh_p75_yr_sw_norm"
)
```

:::

#### 2000m

::: {.panel-tabset group="radius-2000m"}

##### Count Mo

```{r}
# model_binary_log_p75_sw_norm; radius 2000
create_regression_plot(
  treatment_type = "binary", radius = 2000,
  model = "model_bin_log_sc_p75_qt_sw_norm"
)
```

##### Count Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 2000,
  model = "model_bin_log_sc_p75_yr_sw_norm"
)
```

##### Duration Mo

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 2000,
  model = "model_bin_log_sh_p75_qt_sw_norm"
)
```

##### Duration Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 2000,
  model = "model_bin_log_sh_p75_yr_sw_norm"
)
```

:::

:::

### Binary Treatment - 90th Percentile Spill Count {#sec-05-02-04-binary-p90}

::: {.panel-tabset group="threshold"}    

#### 250m

::: {.panel-tabset group="radius-250m"}

##### Count Mo

```{r}
# model_binary_log_p90_sw_norm; radius 250
create_regression_plot(
  treatment_type = "binary", radius = 250,
  model = "model_bin_log_sc_p90_qt_sw_norm"
)
```

##### Count Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 250,
  model = "model_bin_log_sc_p90_yr_sw_norm"
)
```

##### Duration Mo

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 250,
  model = "model_bin_log_sh_p90_qt_sw_norm"
)
```

##### Duration Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 250,
  model = "model_bin_log_sh_p90_yr_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-500m"}

##### Count Mo

```{r}
# model_binary_log_p90_sw_norm; radius 500
create_regression_plot(
  treatment_type = "binary", radius = 500,
  model = "model_bin_log_sc_p90_qt_sw_norm"
)
```

##### Count Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 500,
  model = "model_bin_log_sc_p90_yr_sw_norm"
)
```

##### Duration Mo

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 500,
  model = "model_bin_log_sh_p90_qt_sw_norm"
)
```

##### Duration Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 500,
  model = "model_bin_log_sh_p90_yr_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-1000m"}

##### Count Mo

```{r}
# model_binary_log_p90_sw_norm; radius 1000
create_regression_plot(
  treatment_type = "binary", radius = 1000,
  model = "model_bin_log_sc_p90_qt_sw_norm"
)
```

##### Count Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 1000,
  model = "model_bin_log_sc_p90_yr_sw_norm"
)
```

##### Duration Mo

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 1000,
  model = "model_bin_log_sh_p90_qt_sw_norm"
)
```

##### Duration Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 1000,
  model = "model_bin_log_sh_p90_yr_sw_norm"
)
```

:::

#### 2000m

::: {.panel-tabset group="radius-2000m"}

##### Count Mo

```{r}
# model_binary_log_p90_sw_norm; radius 1000
create_regression_plot(
  treatment_type = "binary", radius = 2000,
  model = "model_bin_log_sc_p90_qt_sw_norm"
)
```

##### Count Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 2000,
  model = "model_bin_log_sc_p90_yr_sw_norm"
)
```

##### Duration Mo

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 2000,
  model = "model_bin_log_sh_p90_qt_sw_norm"
)
```

##### Duration Yr

```{r}
create_regression_plot(
  treatment_type = "binary", radius = 2000,
  model = "model_bin_log_sh_p90_yr_sw_norm"
)
```

:::

:::

### Continuous Treatment - Average Spill Count {#sec-05-02-04-continuous-treatment}

::: {.panel-tabset group="continuous"}

#### 250m

::: {.panel-tabset group="radius-250m"}

##### Count

```{r}
# model_cont_log_mean_sw_norm; radius 250
create_regression_plot(
  treatment_type = "continuous", radius = 250,
  model = "model_cont_log_logsc_sw_norm"
)
```

##### Duration

```{r}
create_regression_plot(
  treatment_type = "continuous", radius = 250,
  model = "model_cont_log_logsh_sw_norm"
)
```

:::

#### 500m

::: {.panel-tabset group="radius-500m"}

##### Count

```{r}
# model_cont_log_mean_sw_norm; radius 500
create_regression_plot(
  treatment_type = "continuous", radius = 500,
  model = "model_cont_log_logsc_sw_norm"
)
```

##### Duration

```{r}
create_regression_plot(
  treatment_type = "continuous", radius = 500,
  model = "model_cont_log_logsh_sw_norm"
)
```

:::

#### 1000m

::: {.panel-tabset group="radius-1000m"}

##### Count

```{r}
# model_cont_log_mean_sw_norm; radius 1000
create_regression_plot(
  treatment_type = "continuous", radius = 1000,
  model = "model_cont_log_logsc_sw_norm"
)
```

##### Duration

```{r}
create_regression_plot(
  treatment_type = "continuous", radius = 1000,
  model = "model_cont_log_logsh_sw_norm"
)
```

:::

#### 2000m

::: {.panel-tabset group="radius-2000m"}

##### Count

```{r}
# model_cont_log_mean_sw_norm; radius 2000
create_regression_plot(
  treatment_type = "continuous", radius = 2000,
  model = "model_cont_log_logsc_sw_norm"
)
```

##### Duration

```{r}
create_regression_plot(
  treatment_type = "continuous", radius = 2000,
  model = "model_cont_log_logsh_sw_norm"
)
```

:::

:::

## Notes and Things to Try

- Temporal lags: Correlation between lagged spills (1–6 months prior) and prices
- Event studies using distance weighted aggregations
- Using quarterly data to reduce seasonality
- Using P90

```{r}
#| eval: false
dat_panel_site <- open_dataset(
  here::here("data", "processed", "dat_panel_site_mo")
) %>%
  filter(radius == 250) %>%
  collect()

dat_panel_site %>%
  filter(site_id == 2)
```
