---
author: "Jacopo Olivieri"
date: 2025-06-01
editor: source
format: html
number-sections: true
number-depth: 4
execute: 
  echo: false
  warning: false
  message: false
  freeze: auto
  fig-width: 9
  fig-asp: 0.618 
  fig-align: center
---

# Hedonics Regressions {#sec-07-hedonics-regs}

```{r setup, include=FALSE}
# Initialize packages with version control
if (!requireNamespace("renv", quietly = TRUE)) {
  install.packages("renv")
}

# Load required packages
required_packages <- c(
  "rmarkdown",
  "rio",
  "tidyverse",
  "purrr",
  "here",
  "janitor",
  "viridis",
  "data.table",
  "arrow",
  "fixest",
  "modelsummary",
  "logger",
  "nanoparquet"
)
install_if_missing <- function(packages) {
  new_packages <- packages[!sapply(packages, requireNamespace, quietly = TRUE)]
  if (length(new_packages) > 0) {
    install.packages(new_packages)
  }
  invisible(sapply(packages, library, character.only = TRUE))
}
install_if_missing(required_packages)


# Initialize logging
log_path <- here::here("output", "log", "house_data_exploration")
if (!dir.exists(dirname(log_path))) {
  dir.create(dirname(log_path), recursive = TRUE)
}
logger::log_appender(logger::appender_file(log_path))
logger::log_layout(logger::layout_glue_colors)

# Ggplot theme
theme_pref <- theme_minimal() +
  theme(
    text = element_text(size = 12),
    plot.title = element_text(
      face = "bold",
      size = 12,
      margin = ggplot2::margin(b = 10, unit = "pt")
    ),
    axis.title = element_text(face = "bold", size = 10),
    axis.text = element_text(angle = 45, hjust = 1, vjust = 1, size = 8),
    panel.grid.minor = element_blank(),
    panel.grid.major.x = element_line(color = "gray95"),
    panel.grid.major.y = element_line(color = "gray95"),
    legend.position = "bottom",
    legend.title = element_text(face = "bold", size = 10),
    legend.text = element_text(size = 8),
    plot.margin = ggplot2::margin(t = 10, r = 10, b = 10, l = 10, unit = "pt")
  )
```

```{r}
#| eval: false
# Load Data

# Define file paths
path_house <- here::here("data", "processed", "general_house_panel_qtr")
path_spill <- here::here("data", "processed", "agg_spill_stats", "agg_spill_stats_qtr.parquet")
path_house_controls <- here::here("data", "processed", "house_price.parquet")

# Load house panel data
house_panel <- arrow::open_dataset(path_house)

# Load quarterly spill stats, filter to quarterly data
spill_qtr <- import(path_spill, trust = TRUE) %>%
  select(-contains("month"), -contains("_mo")) %>%
  as.data.table()

# Load house controls, removing redundant columns
house_controls <- open_dataset(path_house_controls) %>%
  collect() %>%
  select(
    -transaction_id,
    -date_of_transfer,
    -postcode,
    -saon,
    -locality,
    -easting,
    -northing,
    -longitude,
    -latitude
  ) %>%
  as.data.table()
```

```{r}
#| eval: false

# Create hedonic regression data for each radius
radii <- c(1000L)
event_data_list <- purrr::map(
  radii,
  function(rad) {
    # 1. Load data for radius and add spill statistics
    panel_dt_ext <- house_panel %>%
      filter(radius == rad) %>%
      collect() %>%
      as.data.table()

    # 2. Calculate spill summaries
    # For houses within radius, merge with spill data
    house_qtr_in_sum <- merge(
      panel_dt_ext[within_radius == TRUE],
      spill_qtr[, .(site_id, qtr_id, spill_count, spill_hrs)],
      by = c("site_id", "qtr_id")
    )[,
      .(
        qtr_id_transfer = first(qtr_id_transfer),
        spill_count = sum(spill_count, na.rm = TRUE),
        spill_hrs = sum(spill_hrs, na.rm = TRUE),
        min_dist_m = min(distance_m, na.rm = TRUE),
        avg_dist_m = mean(distance_m, na.rm = TRUE),
        n_spill_sites = uniqueN(site_id),
        within_radius = TRUE,
        radius = rad
      ),
      by = .(house_id, qtr_id)
    ]
    gc(full = TRUE)

    # Add lags and rolling sum
    house_qtr_in_sum[,
      `:=`(
        spill_count_l1 = shift(spill_count, n = 1, type = "lag"),
        spill_hrs_l1 = shift(spill_hrs, n = 1, type = "lag"),
        spill_count_c4 = frollsum(spill_count, n = 4),
        spill_hrs_c4 = frollsum(spill_hrs, n = 4)
      ),
      by = house_id
    ]

    # For houses outside radius, create zero-spill records
    house_qtr_out_sum <- panel_dt_ext[
      within_radius == FALSE,
      .(
        qtr_id_transfer = first(qtr_id_transfer),
        spill_count = 0,
        spill_count_l1 = 0,
        spill_count_c4 = 0,
        spill_hrs = 0,
        spill_hrs_l1 = 0,
        spill_hrs_c4 = 0,
        min_dist_m = NA,
        avg_dist_m = NA,
        n_spill_sites = 0,
        within_radius = FALSE,
        radius = rad
      ),
      by = .(house_id, qtr_id)
    ]
    gc(full = TRUE)

    # Combine and sort data
    house_qtr_sum <- rbind(house_qtr_in_sum, house_qtr_out_sum)
    setorder(house_qtr_sum, house_id, qtr_id)

    # Filter to transaction quarters only
    house_qtr_sum <- house_qtr_sum[qtr_id == qtr_id_transfer]

    # 3. Finalise data

    # Join with house controls
    hedonic_data <- house_qtr_sum[
      house_controls,
      on = "house_id",
      nomatch = NA
    ][,
      .(
        # IDs, time, and price
        house_id,
        qtr_id,
        qtr_id_transfer,
        price,
        log_price = log(price), # Add log price
        # Spill data
        spill_count,
        spill_hrs,
        log_spill_count = log1p(spill_count),
        log_spill_hrs = log1p(spill_hrs),
        log_spill_count_l1 = log1p(spill_count_l1),
        log_spill_hrs_l1 = log1p(spill_hrs_l1),
        log_spill_count_c4 = log1p(spill_count_c4),
        log_spill_hrs_c4 = log1p(spill_hrs_c4),
        # Spatial data
        min_dist_m,
        avg_dist_m,
        n_spill_sites,
        within_radius,
        radius,
        inv_min_distance = 1 / min_dist_m,
        inv_avg_distance = 1 / avg_dist_m,
        # Add categorical columns
        property_type,
        old_new,
        duration,
        town_city,
        district,
        county,
        quality,
        country,
        nhs_ha,
        region,
        lsoa,
        msoa,
        admin_county,
        admin_ward
      )
    ]

    # Convert categorical columns to factors using purrr::map
    categorical_cols <- c(
      "property_type",
      "old_new",
      "duration",
      "town_city",
      "district",
      "county",
      "quality",
      "country",
      "nhs_ha",
      "region",
      "lsoa",
      "msoa",
      "admin_county",
      "admin_ward"
    )

    hedonic_data[,
      (categorical_cols) := purrr::map(.SD, as.factor),
      .SDcols = categorical_cols
    ]

    # Clean up local variables
    rm(
      house_qtr_in_sum,
      house_qtr_out_sum,
      house_qtr_sum,
      panel_dt_ext
    )
    gc(full = TRUE)

    return(hedonic_data)
  }
) %>%
  purrr::set_names(paste0("rad_", radii))


# arrow::write_parquet(
#   x = event_data_list$rad_1000,
#   sink = here("data", "processed", "dat_complete_hedonic",
#               "dat_complete_1000.parquet")
# )
```


```{r}
# Load data
radii <- c(250, 500, 1000)
dat_list <- setNames(
  map(
    radii,
    ~ import(
      here(
        "data",
        "processed",
        "dat_complete_hedonic",
        paste0("dat_complete_", .x, ".parquet")
      )
    )
  ),
  paste0("dat_", radii)
)
```


```{r}
# Run regressions
run_hedonic_regs <- function(df) {
  cluster_var <- "lsoa" # Define the clustering variable

  # Define the spill variables to test
  spill_vars <- c(
    "log_spill_count_l1",
    "log_spill_hrs_l1",
    "log_spill_count_c4",
    "log_spill_hrs_c4"
  )

  # Create models for each spill variable
  results <- map(spill_vars, function(spill_var) {
    # Block 1: no FE, just spill variable (and its interaction)
    m1 <- feols(
      as.formula(paste("log_price ~", spill_var)),
      data = df,
      cluster = cluster_var
    )
    m1i <- feols(
      as.formula(paste("log_price ~", spill_var, "* inv_min_distance")),
      data = df,
      cluster = cluster_var
    )

    # Block 2: with unit FE (qtr_id + lsoa), no additional controls
    m2 <- feols(
      as.formula(paste("log_price ~", spill_var, "| qtr_id + lsoa")),
      data = df,
      cluster = cluster_var
    )
    m2i <- feols(
      as.formula(paste(
        "log_price ~",
        spill_var,
        "* inv_min_distance | qtr_id + lsoa"
      )),
      data = df,
      cluster = cluster_var
    )

    # Block 3: with FE + extra covariates (property_type, old_new, duration)
    m3 <- feols(
      as.formula(
        paste(
          "log_price ~",
          spill_var,
          "+ property_type + old_new + duration | qtr_id + lsoa"
        )
      ),
      data = df,
      cluster = cluster_var
    )
    m3i <- feols(
      as.formula(
        paste(
          "log_price ~",
          spill_var,
          "* inv_min_distance + property_type + old_new + duration | qtr_id + lsoa"
        )
      ),
      data = df,
      cluster = cluster_var
    )

    # Pack the six model objects into a structured list
    list(
      "Vanilla" = list(
        "(I)" = m1,
        "(II)" = m1i
      ),
      "Simple FE" = list(
        "(I)" = m2,
        "(II)" = m2i
      ),
      "Controls FE" = list(
        "(I)" = m3,
        "(II)" = m3i
      )
    )
  })

  # Name the results by spill variable
  names(results) <- spill_vars
  return(results)
}

# Now map over dat_list:
models_by_rad <- map(dat_list, run_hedonic_regs)
names(models_by_rad) <- c("250", "500", "1000")
```

## House-Level Hedonic Regressions {#sec-07-01-hedonics-regs-house}

### Setting {#sec-07-01-01-setting}

We employ hedonic regression analysis to quantify the monetary impact of sewage spills on residential property values. This approach statistically isolates the effect of varying sewage spill volumes within a defined proximity to homes, while controlling for other property and locational characteristics. The hedonic methodology enables us to estimate the implicit price adjustment—either premium or discount—that buyers apply when sewage spills are present.

The results below examine hedonic regressions across three spatial radii (250m, 500m, and 1000m) around each property. For each transaction, I calculate the total volume of sewage spills within the specified radius for every calendar quarter. Properties located beyond the radius boundary are assigned a spill statistic of zero. I also calculate the inverse of the minimum distance to the nearest sewage spill site, which serves as a spatial control variable, allowing us to account for the proximity effect of sewage spills on property values.

The spill exposure variables are constructed using two temporal aggregation methods:

1. **Lagged statistic**: Total sewage spill volume in the quarter immediately preceding the property transaction
2. **Rolling statistic**: Cumulative sewage spill volume over the four quarters preceding the property transaction

Regressions are estimated both without controls (NC) and with controls (C): 

- **Old/New:** A binary variable indicating whether the property was a newly built property that had not been previosly sold.
- **Property Type:** A categorical variable indicating the type of property (detached, semi-detached, terraced, flats/maisonettes, other)
- **Duration:** A binary variable indicating the tenure of the property (freehold, leasehold)

```{css, echo = FALSE}
/* Custom CSS for modelsummary tables */
.table, th, td {
  font-size: 0.9em;  /* Base font size */
}

/* Headers */
.table th {
  font-size: 0.95em !important;     /* Header font size */
  white-space: normal !important;  /* Allow header text wrapping */
  padding: 0.25em 0.5em !important;  /* Compact padding */
}

/* Cells */
.table td {
  white-space: nowrap !important;  /* Prevent cell text wrapping */
  padding: 0.25em 0.5em !important;  /* Compact padding */
}
```

```{r}
coef_map_list <- c(
  "log_spill_count" = "Log Spill Count",
  "log_spill_count_l1" = "L1 Log Spill Count",
  "log_spill_hrs_l1" = "L1 Log Spill Hours",
  "log_spill_count_c4" = "C4 Log Spill Count",
  "log_spill_hrs_c4" = "C4 Log Spill Hours",
  "inv_min_distance" = "Inverse Min Distance",
  "log_spill_count:inv_min_distance" = "Log Spill Count × Inverse Min Distance",
  "log_spill_count_l1:inv_min_distance" = "L1 Log Spill Count × Inverse Min Distance",
  "log_spill_hrs_l1:inv_min_distance" = "L1 Log Spill Hours × Inverse Min Distance",
  "log_spill_count_c4:inv_min_distance" = "C4 Log Spill Count × Inverse Min Distance",
  "log_spill_hrs_c4:inv_min_distance" = "C4 Log Spill Hours × Inverse Min Distance",
  "property_typeF" = "Property Type: Flat",
  "property_typeO" = "Property Type: Other",
  "property_typeS" = "Property Type: Semi-detached",
  "property_typeT" = "Property Type: Terraced",
  "old_newY" = "Old/New: Yes",
  "durationL" = "Duration: Leasehold"
)
```

### Lagged Spill Statistic {#sec-07-01-02-lagged-spill-statistic}

::: {.panel-tabset group = "house-hedonic-regs"}

#### 250m

::: {.panel-tabset group = "radius-house-250m"}

##### Count

```{r}
modelsummary(
  models_by_rad$`250`$log_spill_count_l1,
  estimate = "{estimate}{stars}",
  coef_map = coef_map_list,
  statistic = "std.error",
  fmt = 3,
  gof_omit = "IC|AIC|BIC|RMSE|R2 Within|R2 Within Adj.",
  shape = "cbind",
  notes = list(
    "Regression specifications:",
    "Vanilla (I): log_price ~ log_spill_count_l1",
    "Vanilla (II): log_price ~ log_spill_count_l1 * inv_min_distance",
    "Simple FE (I): log_price ~ log_spill_count_l1 | qtr_id + lsoa",
    "Simple FE (II): log_price ~ log_spill_count_l1 * inv_min_distance | qtr_id + lsoa",
    "Controls FE (I): log_price ~ log_spill_count_l1 + property_type + old_new + duration | qtr_id + lsoa",
    "Controls FE (II): log_price ~ log_spill_count_l1 * inv_min_distance + property_type + old_new + duration | qtr_id + lsoa",
    "",
    "Sample: Spill exposure aggregated across all sites within 250m radius for each house-quarter, with zero exposure assigned to houses outside radius.",
    "L1 = lagged 1 quarter.",
    "inv_min_distance = 1 / minimum distance to nearest spill site (meters)"
  )
)
```

##### Hours

```{r}
modelsummary(
  models_by_rad$`250`$log_spill_hrs_l1,
  estimate = "{estimate}{stars}",
  coef_map = coef_map_list,
  statistic = "std.error",
  fmt = 3,
  gof_omit = "IC|AIC|BIC|RMSE|R2 Within|R2 Within Adj.",
  shape = "cbind",
  notes = list(
    "Regression specifications:",
    "Vanilla (I): log_price ~ log_spill_hrs_l1",
    "Vanilla (II): log_price ~ log_spill_hrs_l1 * inv_min_distance",
    "Simple FE (I): log_price ~ log_spill_hrs_l1 | qtr_id + lsoa",
    "Simple FE (II): log_price ~ log_spill_hrs_l1 * inv_min_distance | qtr_id + lsoa",
    "Controls FE (I): log_price ~ log_spill_hrs_l1 + property_type + old_new + duration | qtr_id + lsoa",
    "Controls FE (II): log_price ~ log_spill_hrs_l1 * inv_min_distance + property_type + old_new + duration | qtr_id + lsoa",
    "",
    "Sample: Spill exposure aggregated across all sites within 250m radius for each house-quarter, with zero exposure assigned to houses outside radius.",
    "L1 = lagged 1 quarter.",
    "inv_min_distance = 1 / minimum distance to nearest spill site (meters)"
  )
)
```

:::

#### 500m

::: {.panel-tabset group = "radius-house-500m"}

##### Count

```{r}
modelsummary(
  models_by_rad$`500`$log_spill_count_l1,
  estimate = "{estimate}{stars}",
  coef_map = coef_map_list,
  statistic = "std.error",
  fmt = 3,
  gof_omit = "IC|AIC|BIC|RMSE|R2 Within|R2 Within Adj.",
  shape = "cbind",
  notes = list(
    "Regression specifications:",
    "Vanilla (I): log_price ~ log_spill_count_l1",
    "Vanilla (II): log_price ~ log_spill_count_l1 * inv_min_distance",
    "Simple FE (I): log_price ~ log_spill_count_l1 | qtr_id + lsoa",
    "Simple FE (II): log_price ~ log_spill_count_l1 * inv_min_distance | qtr_id + lsoa",
    "Controls FE (I): log_price ~ log_spill_count_l1 + property_type + old_new + duration | qtr_id + lsoa",
    "Controls FE (II): log_price ~ log_spill_count_l1 * inv_min_distance + property_type + old_new + duration | qtr_id + lsoa",
    "",
    "Sample: Spill exposure aggregated across all sites within 500m radius for each house-quarter, with zero exposure assigned to houses outside radius.",
    "L1 = lagged 1 quarter.",
    "inv_min_distance = 1 / minimum distance to nearest spill site (meters)"
  )
)
```

##### Hours

```{r}
modelsummary(
  models_by_rad$`500`$log_spill_hrs_l1,
  estimate = "{estimate}{stars}",
  coef_map = coef_map_list,
  statistic = "std.error",
  fmt = 3,
  gof_omit = "IC|AIC|BIC|RMSE|R2 Within|R2 Within Adj.",
  shape = "cbind",
  notes = list(
    "Regression specifications:",
    "Vanilla (I): log_price ~ log_spill_hrs_l1",
    "Vanilla (II): log_price ~ log_spill_hrs_l1 * inv_min_distance",
    "Simple FE (I): log_price ~ log_spill_hrs_l1 | qtr_id + lsoa",
    "Simple FE (II): log_price ~ log_spill_hrs_l1 * inv_min_distance | qtr_id + lsoa",
    "Controls FE (I): log_price ~ log_spill_hrs_l1 + property_type + old_new + duration | qtr_id + lsoa",
    "Controls FE (II): log_price ~ log_spill_hrs_l1 * inv_min_distance + property_type + old_new + duration | qtr_id + lsoa",
    "",
    "Sample: Spill exposure aggregated across all sites within 500m radius for each house-quarter, with zero exposure assigned to houses outside radius.",
    "L1 = lagged 1 quarter.",
    "inv_min_distance = 1 / minimum distance to nearest spill site (meters)"
  )
)
```

:::

#### 1000m

::: {.panel-tabset group = "radius-house-1000m"}

##### Count

```{r}
modelsummary(
  models_by_rad$`1000`$log_spill_count_l1,
  estimate = "{estimate}{stars}",
  coef_map = coef_map_list,
  statistic = "std.error",
  fmt = 3,
  gof_omit = "IC|AIC|BIC|RMSE|R2 Within|R2 Within Adj.",
  shape = "cbind",
  notes = list(
    "Regression specifications:",
    "Vanilla (I): log_price ~ log_spill_count_l1",
    "Vanilla (II): log_price ~ log_spill_count_l1 * inv_min_distance",
    "Simple FE (I): log_price ~ log_spill_count_l1 | qtr_id + lsoa",
    "Simple FE (II): log_price ~ log_spill_count_l1 * inv_min_distance | qtr_id + lsoa",
    "Controls FE (I): log_price ~ log_spill_count_l1 + property_type + old_new + duration | qtr_id + lsoa",
    "Controls FE (II): log_price ~ log_spill_count_l1 * inv_min_distance + property_type + old_new + duration | qtr_id + lsoa",
    "",
    "Sample: Spill exposure aggregated across all sites within 1000m radius for each house-quarter, with zero exposure assigned to houses outside radius.",
    "L1 = lagged 1 quarter.",
    "inv_min_distance = 1 / minimum distance to nearest spill site (meters)"
  )
)
```

##### Hours

```{r}
modelsummary(
  models_by_rad$`1000`$log_spill_hrs_l1,
  estimate = "{estimate}{stars}",
  coef_map = coef_map_list,
  statistic = "std.error",
  fmt = 3,
  gof_omit = "IC|AIC|BIC|RMSE|R2 Within|R2 Within Adj.",
  shape = "cbind",
  notes = list(
    "Regression specifications:",
    "Vanilla (I): log_price ~ log_spill_hrs_l1",
    "Vanilla (II): log_price ~ log_spill_hrs_l1 * inv_min_distance",
    "Simple FE (I): log_price ~ log_spill_hrs_l1 | qtr_id + lsoa",
    "Simple FE (II): log_price ~ log_spill_hrs_l1 * inv_min_distance | qtr_id + lsoa",
    "Controls FE (I): log_price ~ log_spill_hrs_l1 + property_type + old_new + duration | qtr_id + lsoa",
    "Controls FE (II): log_price ~ log_spill_hrs_l1 * inv_min_distance + property_type + old_new + duration | qtr_id + lsoa",
    "",
    "Sample: Spill exposure aggregated across all sites within 1000m radius for each house-quarter, with zero exposure assigned to houses outside radius.",
    "L1 = lagged 1 quarter.",
    "inv_min_distance = 1 / minimum distance to nearest spill site (meters)"
  )
)
```

:::

:::

### Rolling Year Spill Statistic {#sec-07-01-03-rolling-year-spill-statistic}

::: {.panel-tabset group = "house-hedonic-regs"}

#### 250m

::: {.panel-tabset group = "radius-house-250m"}

##### Count

```{r}
modelsummary(
  models_by_rad$`250`$log_spill_count_c4,
  estimate = "{estimate}{stars}",
  coef_map = coef_map_list,
  statistic = "std.error",
  fmt = 3,
  gof_omit = "IC|AIC|BIC|RMSE|R2 Within|R2 Within Adj.",
  shape = "cbind",
  notes = list(
    "Regression specifications:",
    "Vanilla (I): log_price ~ log_spill_count_c4",
    "Vanilla (II): log_price ~ log_spill_count_c4 * inv_min_distance",
    "Simple FE (I): log_price ~ log_spill_count_c4 | qtr_id + lsoa",
    "Simple FE (II): log_price ~ log_spill_count_c4 * inv_min_distance | qtr_id + lsoa",
    "Controls FE (I): log_price ~ log_spill_count_c4 + property_type + old_new + duration | qtr_id + lsoa",
    "Controls FE (II): log_price ~ log_spill_count_c4 * inv_min_distance + property_type + old_new + duration | qtr_id + lsoa",
    "",
    "Sample: Spill exposure aggregated across all sites within 250m radius for each house-quarter, with zero exposure assigned to houses outside radius.",
    "C4 = cumulative 4 quarters.",
    "inv_min_distance = 1 / minimum distance to nearest spill site (meters)"
  )
)
```

##### Hours

```{r}
modelsummary(
  models_by_rad$`250`$log_spill_hrs_c4,
  estimate = "{estimate}{stars}",
  coef_map = coef_map_list,
  statistic = "std.error",
  fmt = 3,
  gof_omit = "IC|AIC|BIC|RMSE|R2 Within|R2 Within Adj.",
  shape = "cbind",
  notes = list(
    "Regression specifications:",
    "Vanilla (I): log_price ~ log_spill_hrs_c4",
    "Vanilla (II): log_price ~ log_spill_hrs_c4 * inv_min_distance",
    "Simple FE (I): log_price ~ log_spill_hrs_c4 | qtr_id + lsoa",
    "Simple FE (II): log_price ~ log_spill_hrs_c4 * inv_min_distance | qtr_id + lsoa",
    "Controls FE (I): log_price ~ log_spill_hrs_c4 + property_type + old_new + duration | qtr_id + lsoa",
    "Controls FE (II): log_price ~ log_spill_hrs_c4 * inv_min_distance + property_type + old_new + duration | qtr_id + lsoa",
    "",
    "Sample: Spill exposure aggregated across all sites within 250m radius for each house-quarter, with zero exposure assigned to houses outside radius.",
    "C4 = cumulative 4 quarters.",
    "inv_min_distance = 1 / minimum distance to nearest spill site (meters)"
  )
)
```

:::

#### 500m

::: {.panel-tabset group = "radius-house-500m"}

##### Count

```{r}
modelsummary(
  models_by_rad$`500`$log_spill_count_c4,
  estimate = "{estimate}{stars}",
  coef_map = coef_map_list,
  statistic = "std.error",
  fmt = 3,
  gof_omit = "IC|AIC|BIC|RMSE|R2 Within|R2 Within Adj.",
  shape = "cbind",
  notes = list(
    "Regression specifications:",
    "Vanilla (I): log_price ~ log_spill_count_c4",
    "Vanilla (II): log_price ~ log_spill_count_c4 * inv_min_distance",
    "Simple FE (I): log_price ~ log_spill_count_c4 | qtr_id + lsoa",
    "Simple FE (II): log_price ~ log_spill_count_c4 * inv_min_distance | qtr_id + lsoa",
    "Controls FE (I): log_price ~ log_spill_count_c4 + property_type + old_new + duration | qtr_id + lsoa",
    "Controls FE (II): log_price ~ log_spill_count_c4 * inv_min_distance + property_type + old_new + duration | qtr_id + lsoa",
    "",
    "Sample: Spill exposure aggregated across all sites within 500m radius for each house-quarter, with zero exposure assigned to houses outside radius.",
    "C4 = cumulative 4 quarters.",
    "inv_min_distance = 1 / minimum distance to nearest spill site (meters)"
  )
)
```

##### Hours

```{r}
modelsummary(
  models_by_rad$`500`$log_spill_hrs_c4,
  estimate = "{estimate}{stars}",
  coef_map = coef_map_list,
  statistic = "std.error",
  fmt = 3,
  gof_omit = "IC|AIC|BIC|RMSE|R2 Within|R2 Within Adj.",
  shape = "cbind",
  notes = list(
    "Regression specifications:",
    "Vanilla (I): log_price ~ log_spill_hrs_c4",
    "Vanilla (II): log_price ~ log_spill_hrs_c4 * inv_min_distance",
    "Simple FE (I): log_price ~ log_spill_hrs_c4 | qtr_id + lsoa",
    "Simple FE (II): log_price ~ log_spill_hrs_c4 * inv_min_distance | qtr_id + lsoa",
    "Controls FE (I): log_price ~ log_spill_hrs_c4 + property_type + old_new + duration | qtr_id + lsoa",
    "Controls FE (II): log_price ~ log_spill_hrs_c4 * inv_min_distance + property_type + old_new + duration | qtr_id + lsoa",
    "",
    "Sample: Spill exposure aggregated across all sites within 500m radius for each house-quarter, with zero exposure assigned to houses outside radius.",
    "C4 = cumulative 4 quarters.",
    "inv_min_distance = 1 / minimum distance to nearest spill site (meters)"
  )
)
```

:::

#### 1000m

::: {.panel-tabset group = "radius-house-1000m"}

##### Count

```{r}
modelsummary(
  models_by_rad$`1000`$log_spill_count_c4,
  estimate = "{estimate}{stars}",
  coef_map = coef_map_list,
  statistic = "std.error",
  fmt = 3,
  gof_omit = "IC|AIC|BIC|RMSE|R2 Within|R2 Within Adj.",
  shape = "cbind",
  notes = list(
    "Regression specifications:",
    "Vanilla (I): log_price ~ log_spill_count_c4",
    "Vanilla (II): log_price ~ log_spill_count_c4 * inv_min_distance",
    "Simple FE (I): log_price ~ log_spill_count_c4 | qtr_id + lsoa",
    "Simple FE (II): log_price ~ log_spill_count_c4 * inv_min_distance | qtr_id + lsoa",
    "Controls FE (I): log_price ~ log_spill_count_c4 + property_type + old_new + duration | qtr_id + lsoa",
    "Controls FE (II): log_price ~ log_spill_count_c4 * inv_min_distance + property_type + old_new + duration | qtr_id + lsoa",
    "",
    "Sample: Spill exposure aggregated across all sites within 1000m radius for each house-quarter, with zero exposure assigned to houses outside radius.",
    "C4 = cumulative 4 quarters.",
    "inv_min_distance = 1 / minimum distance to nearest spill site (meters)"
  )
)
```

##### Hours

```{r}
modelsummary(
  models_by_rad$`1000`$log_spill_hrs_c4,
  estimate = "{estimate}{stars}",
  coef_map = coef_map_list,
  statistic = "std.error",
  fmt = 3,
  gof_omit = "IC|AIC|BIC|RMSE|R2 Within|R2 Within Adj.",
  shape = "cbind",
  notes = list(
    "Regression specifications:",
    "Vanilla (I): log_price ~ log_spill_hrs_c4",
    "Vanilla (II): log_price ~ log_spill_hrs_c4 * inv_min_distance",
    "Simple FE (I): log_price ~ log_spill_hrs_c4 | qtr_id + lsoa",
    "Simple FE (II): log_price ~ log_spill_hrs_c4 * inv_min_distance | qtr_id + lsoa",
    "Controls FE (I): log_price ~ log_spill_hrs_c4 + property_type + old_new + duration | qtr_id + lsoa",
    "Controls FE (II): log_price ~ log_spill_hrs_c4 * inv_min_distance + property_type + old_new + duration | qtr_id + lsoa",
    "",
    "Sample: Spill exposure aggregated across all sites within 1000m radius for each house-quarter, with zero exposure assigned to houses outside radius.",
    "C4 = cumulative 4 quarters.",
    "inv_min_distance = 1 / minimum distance to nearest spill site (meters)"
  )
)
```

:::

:::

