---
author: "Jacopo Olivieri"
date: 2026-06-11
editor: source
format: html
number-sections: true
number-depth: 4
execute:
  echo: false
  warning: false
  message: false
  freeze: false
---

# Scaled Effects for Identification Strategies {#sec-scaled-effects}

This chapter rescales the preferred spill-count specifications in the identification-strategy comparison table. Effects are reported for a 1-SD increase in the relevant exposure variable and for a move from the 25th to the 75th percentile of that same variable in the estimation sample.

```{r setup}
rv_library_candidates <- file.path(
  unique(c(normalizePath(".", mustWork = FALSE), normalizePath("..", mustWork = FALSE))),
  "rv", "library", "4.6", "arm64"
)
rv_library_candidates <- rv_library_candidates[dir.exists(rv_library_candidates)]
if (length(rv_library_candidates) > 0) {
  .libPaths(c(rv_library_candidates[[1]], .libPaths()))
}

project_root_candidates <- unique(c(
  normalizePath(".", mustWork = FALSE),
  normalizePath("..", mustWork = FALSE)
))
project_root_candidates <- project_root_candidates[
  file.exists(file.path(project_root_candidates, "rproject.toml"))
]
if (length(project_root_candidates) == 0) {
  stop("Could not find repository root containing rproject.toml.", call. = FALSE)
}
PROJECT_ROOT <- project_root_candidates[[1]]
root_path <- function(...) file.path(PROJECT_ROOT, ...)

required_packages <- c(
  "arrow",
  "data.table",
  "dplyr",
  "fixest",
  "forcats",
  "knitr",
  "purrr",
  "readr",
  "readxl",
  "stringr",
  "tibble",
  "tidyr"
)

missing_packages <- required_packages[
  !vapply(required_packages, requireNamespace, logical(1), quietly = TRUE)
]
if (length(missing_packages) > 0) {
  stop(
    "Missing required package(s): ",
    paste(missing_packages, collapse = ", "),
    call. = FALSE
  )
}

invisible(lapply(required_packages, library, character.only = TRUE))

options(scipen = 999)

RAD <- 250L
YEAR_START <- 2021L
YEAR_END <- 2023L
SPILL_WINDOW <- 4L
WARMUP_QUARTERS <- SPILL_WINDOW
DEPRECIATION_RATE <- 0.01
RIVER_DIST_CAP <- 1000L
```

```{r helpers}
resolve_upstream_file <- function(file_name) {
  repo_path <- root_path(
    "upstream_downstream", "output", "18-03", "river_filter", file_name
  )

  data_root <- normalizePath(root_path("data"), mustWork = TRUE)
  storage_path <- file.path(
    dirname(data_root),
    "upstream_downstream", "output", "18-03", "river_filter", file_name
  )

  candidates <- c(repo_path, storage_path)
  existing <- candidates[file.exists(candidates)]

  if (length(existing) == 0) {
    stop(
      "Missing upstream/downstream signed-pair input: ", file_name, "\n",
      "Checked:\n  - ", paste(candidates, collapse = "\n  - "), "\n",
      "Restore or regenerate the signed-pair files before rendering this chapter.",
      call. = FALSE
    )
  }

  existing[[1]]
}

drop_fixest_removed_obs <- function(data, model) {
  removed <- unlist(model$obs_selection, use.names = FALSE)
  removed <- suppressWarnings(as.integer(removed))
  removed <- removed[!is.na(removed)]
  removed <- abs(removed[removed < 0])

  if (length(removed) == 0) {
    return(data)
  }

  data[-removed, , drop = FALSE]
}

skewness <- function(x) {
  x <- x[is.finite(x)]
  x_sd <- stats::sd(x)

  if (length(x) < 3 || is.na(x_sd) || x_sd == 0) {
    return(NA_real_)
  }

  mean(((x - mean(x)) / x_sd)^3)
}

summarise_exposure <- function(x) {
  x <- x[is.finite(x)]
  qs <- stats::quantile(
    x,
    probs = c(0.25, 0.50, 0.75, 0.95, 0.99),
    na.rm = TRUE,
    names = FALSE
  )

  tibble::tibble(
    n = length(x),
    mean = mean(x),
    sd = stats::sd(x),
    skew = skewness(x),
    p25 = qs[[1]],
    p50 = qs[[2]],
    p75 = qs[[3]],
    p95 = qs[[4]],
    p99 = qs[[5]]
  )
}

scaled_percent_effect <- function(beta, scale) {
  100 * (exp(beta * scale) - 1)
}

format_number <- function(x, digits = 3) {
  ifelse(
    is.na(x),
    "",
    formatC(x, format = "f", digits = digits, big.mark = ",")
  )
}

format_percent <- function(x) {
  ifelse(
    is.na(x),
    "",
    ifelse(abs(x) < 0.05, "0.0%", paste0(format_number(x, 1), "%"))
  )
}

format_contrast <- function(scale, unit_type) {
  dplyr::case_when(
    unit_type == "daily_count" ~ paste0(
      format_number(scale, 3),
      " spills/day, about ",
      format_number(scale * 365.25, 0),
      " spills/year"
    ),
    unit_type == "annual_delta" ~ paste0(
      format_number(scale, 2),
      " annual spills"
    ),
    unit_type == "four_quarter_delta" ~ paste0(
      format_number(scale, 2),
      " spills over the four-quarter window"
    ),
    TRUE ~ format_number(scale, 2)
  )
}

format_range_contrast <- function(p25, p75, unit_type) {
  delta <- p75 - p25

  dplyr::case_when(
    unit_type == "daily_count" ~ paste0(
      format_number(p25, 3),
      " to ",
      format_number(p75, 3),
      " spills/day, a change of about ",
      format_number(delta * 365.25, 0),
      " spills/year"
    ),
    unit_type == "annual_delta" ~ paste0(
      format_number(p25, 2),
      " to ",
      format_number(p75, 2),
      " annual spills"
    ),
    unit_type == "four_quarter_delta" ~ paste0(
      format_number(p25, 2),
      " to ",
      format_number(p75, 2),
      " spills over the four-quarter window"
    ),
    TRUE ~ paste0(format_number(p25, 2), " to ", format_number(p75, 2))
  )
}

scale_phrase <- function(contrast) {
  ifelse(
    contrast == "sd",
    "a 1-SD increase",
    "a P25-to-P75 increase"
  )
}

direction_word <- function(effect, beta) {
  sign_value <- ifelse(is.na(effect) || abs(effect) < 0.05, beta, effect)
  ifelse(sign_value < 0, "lower", "higher")
}

format_abs_percent <- function(effect) {
  format_percent(abs(effect))
}

format_abs_points <- function(effect) {
  format_number(abs(effect), 1)
}

make_interpretation <- function(template_id, contrast, effect, beta) {
  scale <- scale_phrase(contrast)
  scale_no_article <- sub("^a ", "", scale)
  direction <- direction_word(effect, beta)
  percent <- format_abs_percent(effect)
  points <- format_abs_points(effect)

  dplyr::case_when(
    template_id == "sales_hedonic" ~ paste0(
      "Among sold properties in the same LSOA and with the same observed ",
      "characteristics, ", scale,
      " in average daily spill exposure across storm overflows within 250m ",
      "between January 2021 and the sale date is associated with a ",
      percent, " ", direction, " transaction price."
    ),
    template_id == "sales_long" ~ paste0(
      "Among 250 m x 250 m grid cells with house-sale transactions in both ",
      "2021 and 2023, ", scale,
      " between 2021 and 2023 in the average annual number of sewage spills ",
      "within 250 m of a cell's sold properties is associated with mean ",
      "sale-price growth over the same period that is ",
      points, " percentage points ", direction, "."
    ),
    template_id == "sales_repeat" ~ paste0(
      "A ", scale_no_article,
      " between consecutive sales in the total number of spills recorded ",
      "across storm overflows within 250 m during the four quarters preceding ",
      "each sale is associated with depreciation-adjusted price growth between ",
      "those sales that is ", percent, " ", direction, "."
    ),
    template_id == "sales_upstream" ~ paste0(
      "Among sold properties in the same MSOA, with the same observed ",
      "characteristics and river distance to the nearest storm overflow, ",
      scale, " in average daily spill exposure at that site, averaged from ",
      "January 2021 to the sale date, is associated with a ",
      percent, " ", direction,
      " sale price when the site lies upstream rather than downstream of the ",
      "property."
    ),
    template_id == "sales_publicity" ~ paste0(
      "Among sold properties in the same LSOA and month, with the same ",
      "observed characteristics, ", scale,
      " in average daily spill exposure across storm overflows within 250m ",
      "between January 2021 and the sale date is associated with a ",
      "transaction price ", percent, " ", direction,
      " after the August 2022 peak in sewage media coverage than before."
    ),
    template_id == "rentals_hedonic" ~ paste0(
      "Among rental properties in the same LSOA and with the same observed ",
      "characteristics, ", scale,
      " in average daily spill exposure across storm overflows within 250m ",
      "between January 2021 and the letting date is associated with a ",
      percent, " ", direction, " weekly asking rent."
    ),
    template_id == "rentals_long" ~ paste0(
      "Among 250 m x 250 m grid cells with rental listings in both 2021 and ",
      "2023, ", scale,
      " between 2021 and 2023 in the average annual number of sewage spills ",
      "within 250 m of a cell's listed rental properties is associated with ",
      "growth in mean weekly asking rent over the same period that is ",
      points, " percentage points ", direction, "."
    ),
    template_id == "rentals_repeat" ~ paste0(
      "A ", scale_no_article,
      " between consecutive rental listings in the total number of spills ",
      "recorded across storm overflows within 250 m during the four quarters ",
      "preceding each listing is associated with depreciation-adjusted growth ",
      "in weekly asking rent between those listings that is ",
      points, " percentage points ", direction, "."
    ),
    template_id == "rentals_upstream" ~ paste0(
      "Among rental properties in the same MSOA, with the same observed ",
      "characteristics and river distance to the nearest storm overflow, ",
      scale, " in average daily spill exposure at that site, averaged from ",
      "January 2021 to the letting date, is associated with a ",
      percent, " ", direction,
      " weekly asking rent when the site lies upstream rather than downstream ",
      "of the property."
    ),
    template_id == "rentals_publicity" ~ paste0(
      "Among rental properties in the same LSOA and month, with the same ",
      "observed characteristics, ", scale,
      " in average daily spill exposure across storm overflows within 250m ",
      "between January 2021 and the letting date is associated with a weekly ",
      "asking rent ", percent, " ", direction,
      " after the August 2022 peak in sewage media coverage than before."
    ),
    TRUE ~ ""
  )
}

extract_result <- function(
  strategy,
  market,
  model,
  data,
  coefficient,
  exposure,
  exposure_label,
  unit_type,
  interpretation_id
) {
  retained_data <- drop_fixest_removed_obs(data, model)
  exposure_values <- retained_data[[exposure]]
  exposure_stats <- summarise_exposure(exposure_values)
  beta <- unname(stats::coef(model)[[coefficient]])

  sd_scale <- exposure_stats$sd
  iqr_scale <- exposure_stats$p75 - exposure_stats$p25

  sd_effect <- scaled_percent_effect(beta, sd_scale)
  iqr_effect <- scaled_percent_effect(beta, iqr_scale)

  scaled <- tibble::tibble(
    market = market,
    strategy = strategy,
    raw_coefficient = beta,
    effect_1sd = sd_effect,
    interpretation_1sd = make_interpretation(
      interpretation_id, "sd", sd_effect, beta
    ),
    effect_p25_p75 = iqr_effect,
    interpretation_p25_p75 = make_interpretation(
      interpretation_id, "iqr", iqr_effect, beta
    )
  )

  exposure_summary <- exposure_stats |>
    dplyr::mutate(
      market = market,
      strategy = strategy,
      main_variable = exposure_label,
      .before = 1
    )

  list(scaled = scaled, exposure = exposure_summary)
}

render_table <- function(data, caption) {
  knitr::kable(
    data,
    format = "html",
    caption = caption,
    escape = TRUE,
    align = "ll"
  )
}
```

```{r data-loading}
sales_controls <- arrow::read_parquet(
  root_path("data", "processed", "house_price.parquet")
) |>
  dplyr::select(
    house_id, transaction_id, price, month_id, qtr_id,
    latitude, longitude, lsoa, msoa, property_type, old_new, duration
  ) |>
  dplyr::mutate(
    property_type = forcats::as_factor(property_type),
    old_new = forcats::as_factor(old_new),
    duration = forcats::as_factor(duration)
  )

rental_controls <- arrow::read_parquet(
  root_path("data", "processed", "zoopla", "zoopla_rentals.parquet")
) |>
  dplyr::select(
    rental_id, listing_price, month_id, qtr_id,
    latitude, longitude, lsoa, msoa, property_type, bedrooms, bathrooms
  ) |>
  dplyr::mutate(
    property_type = forcats::as_factor(property_type)
  )

cross_section_sales <- arrow::open_dataset(
  root_path("data", "processed", "cross_section", "sales", "prior_to_sale")
) |>
  dplyr::filter(radius == RAD, n_spill_sites > 0) |>
  dplyr::collect()

cross_section_rentals <- arrow::open_dataset(
  root_path("data", "processed", "cross_section", "rentals", "prior_to_rental")
) |>
  dplyr::filter(radius == RAD, n_spill_sites > 0) |>
  dplyr::collect()

house_site_sales <- arrow::open_dataset(
  root_path("data", "processed", "cross_section", "sales", "prior_to_sale_house_site")
) |>
  dplyr::filter(radius == RAD) |>
  dplyr::collect()

rental_site_rentals <- arrow::open_dataset(
  root_path("data", "processed", "cross_section", "rentals", "prior_to_rental_rental_site")
) |>
  dplyr::filter(radius == RAD) |>
  dplyr::collect()
```

```{r sample-builders}
build_sales_prior_sample <- function() {
  cross_section_sales |>
    dplyr::select(-dplyr::any_of("price")) |>
    dplyr::inner_join(sales_controls, by = "house_id") |>
    dplyr::mutate(log_price = log(price)) |>
    dplyr::filter(
      !is.na(spill_count_daily_avg),
      !is.na(spill_hrs_daily_avg),
      !is.na(lsoa),
      !is.na(property_type),
      !is.na(old_new),
      !is.na(duration),
      is.finite(log_price)
    ) |>
    dplyr::mutate(
      lsoa = forcats::fct_drop(forcats::as_factor(lsoa)),
      msoa = forcats::fct_drop(forcats::as_factor(msoa)),
      property_type = forcats::fct_drop(property_type),
      old_new = forcats::fct_drop(old_new),
      duration = forcats::fct_drop(duration)
    )
}

build_rental_prior_sample <- function() {
  cross_section_rentals |>
    dplyr::select(-dplyr::any_of("listing_price")) |>
    dplyr::inner_join(rental_controls, by = "rental_id") |>
    dplyr::mutate(log_price = log(listing_price)) |>
    dplyr::filter(
      !is.na(spill_count_daily_avg),
      !is.na(spill_hrs_daily_avg),
      !is.na(lsoa),
      !is.na(property_type),
      !is.na(bedrooms),
      !is.na(bathrooms),
      is.finite(log_price)
    ) |>
    dplyr::mutate(
      lsoa = forcats::fct_drop(forcats::as_factor(lsoa)),
      msoa = forcats::fct_drop(forcats::as_factor(msoa)),
      property_type = forcats::fct_drop(property_type)
    )
}

build_long_difference <- function(data) {
  start <- data |>
    dplyr::filter(year == YEAR_START) |>
    dplyr::select(
      grid_cell_id,
      mean_log_price_start = mean_log_price,
      mean_spill_count_start = mean_spill_count
    )

  end <- data |>
    dplyr::filter(year == YEAR_END) |>
    dplyr::select(
      grid_cell_id,
      mean_log_price_end = mean_log_price,
      mean_spill_count_end = mean_spill_count
    )

  start |>
    dplyr::inner_join(end, by = "grid_cell_id") |>
    dplyr::mutate(
      delta_log_price = mean_log_price_end - mean_log_price_start,
      delta_spill_count = mean_spill_count_end - mean_spill_count_start
    ) |>
    dplyr::filter(
      !is.na(delta_log_price),
      !is.na(delta_spill_count)
    )
}

build_repeat_pairs <- function(market) {
  agg_spill <- arrow::read_parquet(
    root_path("data", "processed", "agg_spill_stats", "agg_spill_qtr.parquet")
  ) |>
    dplyr::select(site_id, qtr_id, spill_count_qt)

  agg_spill_dt <- data.table::as.data.table(agg_spill)
  data.table::setorder(agg_spill_dt, site_id, qtr_id)

  agg_spill_dt[
    ,
    spill_count_roll_raw := data.table::frollsum(
      spill_count_qt,
      n = SPILL_WINDOW,
      align = "right"
    ),
    by = site_id
  ]
  agg_spill_dt[
    ,
    spill_count_roll := data.table::shift(
      spill_count_roll_raw,
      n = 1,
      type = "lag"
    ),
    by = site_id
  ]

  agg_spill <- tibble::as_tibble(
    agg_spill_dt[, .(site_id, qtr_id, spill_count_roll)]
  )

  if (market == "sales") {
    repeat_ids <- arrow::read_parquet(
      root_path("data", "processed", "repeated_transactions", "repeated_sales.parquet")
    )

    transactions <- sales_controls |>
      dplyr::select(house_id, transaction_id, price, qtr_id, latitude, longitude)

    lookup <- arrow::read_parquet(
      root_path("data", "processed", "spill_house_lookup.parquet")
    ) |>
      dplyr::filter(distance_m <= RAD) |>
      dplyr::select(house_id, site_id, distance_m)

    panel <- repeat_ids |>
      dplyr::inner_join(transactions, by = "house_id") |>
      dplyr::group_by(repeat_id) |>
      dplyr::filter(dplyr::n() > 1) |>
      dplyr::ungroup() |>
      dplyr::semi_join(lookup, by = "house_id") |>
      dplyr::inner_join(lookup, by = "house_id", relationship = "many-to-many") |>
      dplyr::inner_join(agg_spill, by = c("site_id", "qtr_id")) |>
      dplyr::group_by(house_id, transaction_id, repeat_id, qtr_id, price, latitude, longitude) |>
      dplyr::summarise(
        spill_count_roll = sum(spill_count_roll, na.rm = TRUE),
        .groups = "drop"
      ) |>
      dplyr::filter(qtr_id > WARMUP_QUARTERS)

    panel |>
      dplyr::arrange(repeat_id, qtr_id) |>
      dplyr::group_by(repeat_id) |>
      dplyr::mutate(
        lag_price = dplyr::lag(price),
        lag_qtr_id = dplyr::lag(qtr_id),
        lag_spill_count_roll = dplyr::lag(spill_count_roll)
      ) |>
      dplyr::filter(!is.na(lag_price)) |>
      dplyr::ungroup() |>
      dplyr::mutate(
        years_between = (qtr_id - lag_qtr_id) / 4,
        log_price_ratio = log(price) - log(lag_price),
        r = log_price_ratio + DEPRECIATION_RATE * years_between,
        delta_spill_count = spill_count_roll - lag_spill_count_roll
      ) |>
      dplyr::filter(
        !is.na(r),
        !is.na(delta_spill_count),
        !is.na(latitude),
        !is.na(longitude),
        !is.na(qtr_id),
        !is.na(lag_qtr_id)
      )
  } else {
    repeat_ids <- arrow::read_parquet(
      root_path("data", "processed", "repeated_transactions", "repeated_rentals.parquet")
    )

    transactions <- rental_controls |>
      dplyr::select(rental_id, listing_price, qtr_id, latitude, longitude)

    lookup <- arrow::read_parquet(
      root_path("data", "processed", "zoopla", "spill_rental_lookup.parquet")
    ) |>
      dplyr::filter(distance_m <= RAD) |>
      dplyr::select(rental_id, site_id, distance_m)

    panel <- repeat_ids |>
      dplyr::inner_join(transactions, by = "rental_id") |>
      dplyr::group_by(repeat_id) |>
      dplyr::filter(dplyr::n() > 1) |>
      dplyr::ungroup() |>
      dplyr::semi_join(lookup, by = "rental_id") |>
      dplyr::inner_join(lookup, by = "rental_id", relationship = "many-to-many") |>
      dplyr::inner_join(agg_spill, by = c("site_id", "qtr_id")) |>
      dplyr::group_by(rental_id, repeat_id, qtr_id, listing_price, latitude, longitude) |>
      dplyr::summarise(
        spill_count_roll = sum(spill_count_roll, na.rm = TRUE),
        .groups = "drop"
      ) |>
      dplyr::filter(qtr_id > WARMUP_QUARTERS)

    panel |>
      dplyr::arrange(repeat_id, qtr_id) |>
      dplyr::group_by(repeat_id) |>
      dplyr::mutate(
        lag_price = dplyr::lag(listing_price),
        lag_qtr_id = dplyr::lag(qtr_id),
        lag_spill_count_roll = dplyr::lag(spill_count_roll)
      ) |>
      dplyr::filter(!is.na(lag_price)) |>
      dplyr::ungroup() |>
      dplyr::mutate(
        years_between = (qtr_id - lag_qtr_id) / 4,
        log_price_ratio = log(listing_price) - log(lag_price),
        r = log_price_ratio + DEPRECIATION_RATE * years_between,
        delta_spill_count = spill_count_roll - lag_spill_count_roll
      ) |>
      dplyr::filter(
        !is.na(r),
        !is.na(delta_spill_count),
        !is.na(latitude),
        !is.na(longitude),
        !is.na(qtr_id),
        !is.na(lag_qtr_id)
      )
  }
}

build_bmn_formula <- function(data) {
  data <- data |>
    dplyr::mutate(
      qtr_id_num = as.integer(qtr_id),
      lag_qtr_id_num = as.integer(lag_qtr_id)
    )

  all_qtrs <- sort(unique(c(data$qtr_id_num, data$lag_qtr_id_num)))

  for (q in all_qtrs[-1]) {
    col_name <- paste0("time_", q)
    data[[col_name]] <- dplyr::case_when(
      data$qtr_id_num == q ~ 1L,
      data$lag_qtr_id_num == q ~ -1L,
      TRUE ~ 0L
    )
  }

  time_formula <- paste0("time_", all_qtrs[-1], collapse = " + ")

  list(
    data = data,
    formula = stats::as.formula(paste("r ~ delta_spill_count +", time_formula))
  )
}

build_upstream_samples <- function() {
  ud_sales_raw <- readr::read_csv(
    resolve_upstream_file("spill_house_signed.csv"),
    show_col_types = FALSE
  )
  ud_rentals_raw <- readr::read_csv(
    resolve_upstream_file("spill_rental_signed.csv"),
    show_col_types = FALSE
  )

  ud_sales <- ud_sales_raw |>
    dplyr::mutate(
      direction = ifelse(direction == -1, 1, 0),
      dist_river_m = abs(signed_dist_m)
    ) |>
    dplyr::filter(
      spill_lateral_m <= RAD,
      house_lateral_m <= RAD,
      dist_river_m <= RIVER_DIST_CAP,
      spill_house_euclid_m <= RAD
    ) |>
    dplyr::distinct()

  ud_rentals <- ud_rentals_raw |>
    dplyr::mutate(
      direction = ifelse(direction == -1, 1, 0),
      dist_river_m = abs(signed_dist_m)
    ) |>
    dplyr::filter(
      spill_lateral_m <= RAD,
      rental_lateral_m <= RAD,
      dist_river_m <= RIVER_DIST_CAP,
      spill_rental_euclid_m <= RAD
    ) |>
    dplyr::distinct()

  sales <- house_site_sales |>
    dplyr::select(-dplyr::any_of("price")) |>
    dplyr::inner_join(sales_controls, by = "house_id") |>
    dplyr::inner_join(ud_sales, by = c("house_id", "site_id")) |>
    dplyr::mutate(log_price = log(price)) |>
    dplyr::filter(
      !is.na(spill_count_daily_avg),
      !is.na(spill_hrs_daily_avg),
      !is.na(lsoa),
      !is.na(msoa),
      !is.na(property_type),
      !is.na(old_new),
      !is.na(duration),
      !is.na(direction),
      is.finite(log_price)
    ) |>
    dplyr::mutate(
      lsoa = forcats::fct_drop(forcats::as_factor(lsoa)),
      msoa = forcats::fct_drop(forcats::as_factor(msoa)),
      property_type = forcats::fct_drop(property_type),
      old_new = forcats::fct_drop(old_new),
      duration = forcats::fct_drop(duration)
    ) |>
    dplyr::arrange(house_id, distance_m) |>
    dplyr::group_by(house_id) |>
    dplyr::slice_head(n = 1) |>
    dplyr::ungroup()

  rentals <- rental_site_rentals |>
    dplyr::select(-dplyr::any_of("listing_price")) |>
    dplyr::inner_join(rental_controls, by = "rental_id") |>
    dplyr::inner_join(ud_rentals, by = c("rental_id", "site_id")) |>
    dplyr::mutate(log_price = log(listing_price)) |>
    dplyr::filter(
      !is.na(spill_count_daily_avg),
      !is.na(spill_hrs_daily_avg),
      !is.na(lsoa),
      !is.na(msoa),
      !is.na(property_type),
      !is.na(bedrooms),
      !is.na(bathrooms),
      !is.na(direction),
      is.finite(log_price)
    ) |>
    dplyr::mutate(
      lsoa = forcats::fct_drop(forcats::as_factor(lsoa)),
      msoa = forcats::fct_drop(forcats::as_factor(msoa)),
      property_type = forcats::fct_drop(property_type)
    ) |>
    dplyr::arrange(rental_id, distance_m) |>
    dplyr::group_by(rental_id) |>
    dplyr::slice_head(n = 1) |>
    dplyr::ungroup()

  list(sales = sales, rentals = rentals)
}

build_news_samples <- function() {
  google_trends <- readxl::read_excel(
    root_path("data", "raw", "google_trends", "google_trends_uk.xlsx"),
    sheet = "united_kingdom"
  ) |>
    dplyr::filter(Year >= 2021, Year <= 2023)

  peak_row <- google_trends |>
    dplyr::slice_max(`'Sewage Spill' Google Searches`, n = 1, with_ties = FALSE)

  peak_year <- peak_row$Year[[1]]
  peak_month <- as.integer(substr(peak_row$Date[[1]], 6, 7))
  peak_month_id <- (peak_year - 2021) * 12 + peak_month

  sales <- build_sales_prior_sample() |>
    dplyr::filter(!is.na(month_id), !is.na(latitude), !is.na(longitude)) |>
    dplyr::mutate(post = as.integer(month_id >= peak_month_id)) |>
    dplyr::filter(!is.na(post))

  rentals <- build_rental_prior_sample() |>
    dplyr::filter(!is.na(month_id), !is.na(latitude), !is.na(longitude)) |>
    dplyr::mutate(post = as.integer(month_id >= peak_month_id)) |>
    dplyr::filter(!is.na(post))

  list(sales = sales, rentals = rentals)
}
```

```{r estimate-models}
sales_prior <- build_sales_prior_sample()
rentals_prior <- build_rental_prior_sample()

hedonic_sales_model <- fixest::feols(
  log_price ~ spill_count_daily_avg + property_type + old_new + duration | lsoa,
  data = sales_prior,
  vcov = "hetero"
)

hedonic_rentals_model <- fixest::feols(
  log_price ~ spill_count_daily_avg + property_type + bedrooms + bathrooms | lsoa,
  data = rentals_prior,
  vcov = "hetero"
)

long_sales <- arrow::read_parquet(
  root_path("data", "processed", "long_difference", "long_diff_grid_house_sales.parquet")
) |>
  build_long_difference()

long_rentals <- arrow::read_parquet(
  root_path("data", "processed", "long_difference", "long_diff_grid_rentals.parquet")
) |>
  build_long_difference()

long_sales_model <- fixest::feols(
  delta_log_price ~ delta_spill_count,
  data = long_sales,
  vcov = "hetero"
)

long_rentals_model <- fixest::feols(
  delta_log_price ~ delta_spill_count,
  data = long_rentals,
  vcov = "hetero"
)

repeat_sales <- build_bmn_formula(build_repeat_pairs("sales"))
repeat_rentals <- build_bmn_formula(build_repeat_pairs("rentals"))

repeat_sales_model <- fixest::feols(
  repeat_sales$formula,
  data = repeat_sales$data,
  vcov = "hetero"
)

repeat_rentals_model <- fixest::feols(
  repeat_rentals$formula,
  data = repeat_rentals$data,
  vcov = "hetero"
)

upstream_samples <- build_upstream_samples()

upstream_sales_model <- fixest::feols(
  log_price ~ spill_count_daily_avg * direction + dist_river_m +
    property_type + old_new + duration | msoa,
  data = upstream_samples$sales,
  vcov = "hetero"
)

upstream_rentals_model <- fixest::feols(
  log_price ~ spill_count_daily_avg * direction + dist_river_m +
    property_type + bedrooms + bathrooms | msoa,
  data = upstream_samples$rentals,
  vcov = "hetero"
)

news_samples <- build_news_samples()

news_sales_model <- fixest::feols(
  log_price ~ spill_count_daily_avg + spill_count_daily_avg:post +
    property_type + old_new + duration | lsoa + month_id,
  data = news_samples$sales,
  vcov = "hetero"
)

news_rentals_model <- fixest::feols(
  log_price ~ spill_count_daily_avg + spill_count_daily_avg:post +
    property_type + bedrooms + bathrooms | lsoa + month_id,
  data = news_samples$rentals,
  vcov = "hetero"
)
```

```{r assemble-results}
results <- list(
  extract_result(
    strategy = "Hedonic cross-sections",
    market = "House Sales",
    model = hedonic_sales_model,
    data = sales_prior,
    coefficient = "spill_count_daily_avg",
    exposure = "spill_count_daily_avg",
    exposure_label = "Daily spill count",
    unit_type = "daily_count",
    interpretation_id = "sales_hedonic"
  ),
  extract_result(
    strategy = "Grid-cell long difference, 2023-2021",
    market = "House Sales",
    model = long_sales_model,
    data = long_sales,
    coefficient = "delta_spill_count",
    exposure = "delta_spill_count",
    exposure_label = "Change in annual spill count",
    unit_type = "annual_delta",
    interpretation_id = "sales_long"
  ),
  extract_result(
    strategy = "Repeat sales (Palmquist)",
    market = "House Sales",
    model = repeat_sales_model,
    data = repeat_sales$data,
    coefficient = "delta_spill_count",
    exposure = "delta_spill_count",
    exposure_label = "Change in four-quarter spill count",
    unit_type = "four_quarter_delta",
    interpretation_id = "sales_repeat"
  ),
  extract_result(
    strategy = "Upstream/downstream nearest site",
    market = "House Sales",
    model = upstream_sales_model,
    data = upstream_samples$sales,
    coefficient = "spill_count_daily_avg:direction",
    exposure = "spill_count_daily_avg",
    exposure_label = "Nearest-site daily spill count",
    unit_type = "daily_count",
    interpretation_id = "sales_upstream"
  ),
  extract_result(
    strategy = "Publicity DiD intensive margin",
    market = "House Sales",
    model = news_sales_model,
    data = news_samples$sales,
    coefficient = "spill_count_daily_avg:post",
    exposure = "spill_count_daily_avg",
    exposure_label = "Daily spill count",
    unit_type = "daily_count",
    interpretation_id = "sales_publicity"
  ),
  extract_result(
    strategy = "Hedonic cross-sections",
    market = "House Rentals",
    model = hedonic_rentals_model,
    data = rentals_prior,
    coefficient = "spill_count_daily_avg",
    exposure = "spill_count_daily_avg",
    exposure_label = "Daily spill count",
    unit_type = "daily_count",
    interpretation_id = "rentals_hedonic"
  ),
  extract_result(
    strategy = "Grid-cell long difference, 2023-2021",
    market = "House Rentals",
    model = long_rentals_model,
    data = long_rentals,
    coefficient = "delta_spill_count",
    exposure = "delta_spill_count",
    exposure_label = "Change in annual spill count",
    unit_type = "annual_delta",
    interpretation_id = "rentals_long"
  ),
  extract_result(
    strategy = "Repeat rentals (Palmquist)",
    market = "House Rentals",
    model = repeat_rentals_model,
    data = repeat_rentals$data,
    coefficient = "delta_spill_count",
    exposure = "delta_spill_count",
    exposure_label = "Change in four-quarter spill count",
    unit_type = "four_quarter_delta",
    interpretation_id = "rentals_repeat"
  ),
  extract_result(
    strategy = "Upstream/downstream nearest site",
    market = "House Rentals",
    model = upstream_rentals_model,
    data = upstream_samples$rentals,
    coefficient = "spill_count_daily_avg:direction",
    exposure = "spill_count_daily_avg",
    exposure_label = "Nearest-site daily spill count",
    unit_type = "daily_count",
    interpretation_id = "rentals_upstream"
  ),
  extract_result(
    strategy = "Publicity DiD intensive margin",
    market = "House Rentals",
    model = news_rentals_model,
    data = news_samples$rentals,
    coefficient = "spill_count_daily_avg:post",
    exposure = "spill_count_daily_avg",
    exposure_label = "Daily spill count",
    unit_type = "daily_count",
    interpretation_id = "rentals_publicity"
  )
)

scaled_effects <- purrr::map_dfr(results, "scaled") |>
  dplyr::mutate(
    market = factor(market, levels = c("House Sales", "House Rentals")),
    strategy = factor(
      strategy,
      levels = c(
        "Hedonic cross-sections",
        "Grid-cell long difference, 2023-2021",
        "Repeat sales (Palmquist)",
        "Repeat rentals (Palmquist)",
        "Upstream/downstream nearest site",
        "Publicity DiD intensive margin"
      )
    )
  ) |>
  dplyr::arrange(market, strategy)

exposure_summary <- purrr::map_dfr(results, "exposure") |>
  dplyr::mutate(
    market = factor(market, levels = c("House Sales", "House Rentals")),
    strategy = factor(
      strategy,
      levels = c(
        "Hedonic cross-sections",
        "Grid-cell long difference, 2023-2021",
        "Repeat sales (Palmquist)",
        "Repeat rentals (Palmquist)",
        "Upstream/downstream nearest site",
        "Publicity DiD intensive margin"
      )
    )
  ) |>
  dplyr::arrange(market, strategy)

scaled_effects_display <- scaled_effects |>
  dplyr::transmute(
    Market = as.character(market),
    Strategy = as.character(strategy),
    `Effect of 1 SD` = format_percent(effect_1sd),
    `1 SD interpretation` = interpretation_1sd,
    `Effect of P25 to P75` = format_percent(effect_p25_p75),
    `P25-P75 interpretation` = interpretation_p25_p75
  )

exposure_summary_display <- exposure_summary |>
  dplyr::transmute(
    Market = as.character(market),
    Strategy = as.character(strategy),
    `Main variable` = main_variable,
    N = format_number(n, 0),
    Mean = format_number(mean, 3),
    SD = format_number(sd, 3),
    Skew = format_number(skew, 2),
    P25 = format_number(p25, 3),
    P50 = format_number(p50, 3),
    P75 = format_number(p75, 3),
    P95 = format_number(p95, 3),
    P99 = format_number(p99, 3)
  )
```

```{r scaled-effects-table}
render_table(
  scaled_effects_display,
  "Scaled effects for preferred identification-strategy specifications."
)
```

For rows where the 25th and 75th percentiles coincide, the interquartile contrast is mechanically zero. This is especially relevant for the grid-cell long-difference specifications, where most cells experience no change in nearby annual spill counts between 2021 and 2023.

```{r exposure-summary-table}
render_table(
  exposure_summary_display,
  "Distribution of the main spill-count exposure in each preferred estimation sample."
)
```
