---
author: "Jacopo Olivieri"
date: 2024-01-02
editor: source
format: html
number-sections: true
number-depth: 4
execute: 
  echo: false
  warning: false
  message: false
  freeze: auto
  fig-width: 9
  fig-asp: 0.618 
  fig-align: center
---

# Sewage Spill Data Exploration {#sec-03-spill-exploration}

```{r setup, include=FALSE}
# Initialize packages with version control
if (!requireNamespace("renv", quietly = TRUE)) {
  install.packages("renv")
}

# Run manual renv commands if needed
# renv::activate() # Activate the project library
# renv::restore()  # Restore the environment if running for first time
# renv::snapshot()  # After adding/updating packages, snapshot the state


# Load required packages
required_packages <- c("rmarkdown", "rio", "tidyverse", "purrr", "here",
                       "janitor", "sf", "sp", "rnaturalearth", 
                       "rnaturalearthdata", "rnrfa", "DescTools",
                       "gridExtra", "modelsummary", "rgeoboundaries",
                       "tmap", "leaflet", "htmltools", "servr",
                       "viridis")
install_if_missing <- function(packages) {
  new_packages <- packages[!sapply(packages, requireNamespace, quietly = TRUE)]
  if (length(new_packages) > 0) {
    install.packages(new_packages)
  }
  invisible(sapply(packages, library, character.only = TRUE))
}
install_if_missing(required_packages)


# Initialize logging
log_path <- here::here("output", "log", "spill_data_exploration.log")
if (!dir.exists(dirname(log_path))) {
  dir.create(dirname(log_path), recursive = TRUE)
}
logger::log_appender(logger::appender_file(log_path))
logger::log_layout(logger::layout_glue_colors)

# Ggplot theme
theme_pref <- theme_minimal() +
    theme(
      text = element_text(size = 12),
      plot.title = element_text(face = "bold", size = 12, 
                                margin = ggplot2::margin(b = 10, unit = "pt")),
      axis.title = element_text(face = "bold", size = 10),
      axis.text = element_text(angle = 45, hjust = 1, vjust = 1, size = 8),
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_line(color = "gray95"),
      panel.grid.major.y = element_line(color = "gray95"),
      legend.position = "bottom",
      legend.title = element_text(face = "bold", size = 10),
      legend.text = element_text(size = 8),
      plot.margin = ggplot2::margin(t = 10, r = 10, b = 10, l = 10, unit = "pt")
    ) 
```

```{css, echo = FALSE}
/* Custom CSS for modelsummary tables */
.table, th, td {
  font-size: 0.9em;  /* Base font size (matches reactable's cell style) */
}

/* Headers */
.table th {
  font-size: 0.95em !important;     /* Header font size */
  white-space: normal !important;  /* Allow header text wrapping */
  padding: 0.25em 0.5em !important;  /* Compact padding */
}

/* Cells */
.table td {
  white-space: nowrap !important;  /* Prevent cell text wrapping */
  padding: 0.25em 0.5em !important;  /* Compact padding */
}
```

```{r, load_data}
# Aggregated spill data
dat <- import(here("data", "processed", 
                   "individual_edm_location.RDATA"), trust = TRUE)

dat_yr <- dat$yearly
dat_mo <- dat$monthly

# Spill sites
spill_sites <- import(here("data", "processed", "unique_spill_sites.rds"),
  trust = TRUE
)
```

## Geographic Distribution in 2023 {#sec-03-01-geo-distribution}

Sewage spill sites are spread relatively uniformly around England. Spills appear to be more frequent near the coast, particularly in the South and South West, which is expected as these regions have a higher concentration of water channels. Beyond this, there doesn't seem to be any other visual pattern.

```{r, plot-spill-stats}

dat_yr_clean <- left_join(
  dat_yr, spill_sites, 
  by = join_by(water_company, outlet_discharge_ngr, site_id))

# Create spill map functions
plot_spill_map <- function(data, value_col, legend_title) {
  ggplot() +
    # Maximize plot area by adjusting margins and expanding plot limits
    theme_minimal() +
    theme(
      panel.grid = element_blank(),
      plot.margin = unit(c(.1,.1,.1,.1), "cm"),
      legend.title = element_text(size = 14, hjust = 0),  
      legend.position = "bottom"
    ) +
    # Base map
    geom_sf(data = uk_map, fill = "grey90", colour = "white") +
    # Data points
    geom_sf(
      data = data, 
      aes(colour = .data[[value_col]],
          size = .data[[value_col]]), 
      alpha = 0.7,
      size = 1
    ) +
    scale_colour_viridis_c(
      option = "magma",
      direction = -1,
      guide = guide_colourbar(
        barwidth = 15,  
        barheight = 1.5 
      )) +
    coord_sf(
      xlim = c(-8, 2), 
      ylim = c(50, 59),
      expand = FALSE
    ) +
    labs(
      colour = str_wrap(legend_title, width = 20)  # Wrap title text
    )
}

plot_spill_map_tmap <- function(data, value_col, legend_title) {
  data <- data %>% 
    select(water_company, # site_name_ea, site_name_wa_sc, 
           all_of(value_col))
  
  tm_shape(uk_map) +
    tm_polygons(
      fill = "grey90",
      col = "white"
    ) +
    tm_shape(data) +
    tm_dots(
      size = 0.4,
      fill = value_col,
      fill_alpha = 0.7,
      fill.scale = tm_scale(
        values = "-magma",
        interval = "continuous"
      ),
      fill.legend = tm_legend(
        title = legend_title,
        position = c("left", "bottom")
      )
    ) +
    tm_layout(
      legend.text.size = 0.8,
      legend.title.size = 1
    ) +
    tm_view(
      set_view = c(-2, 53, 5.5)  
    )
}

# UK Map
uk_map <- ne_countries(scale = "medium", returnclass = "sf") %>%
  filter(sovereignt %in% c("United Kingdom"))

# Function to process yearly data
process_yearly_data <- function(data, year) {
  data %>%
    filter(year == !!year) %>%
    mutate(
      across(
        contains("spill"),
        ~ Winsorize(.x, 
                    val = quantile(.x, probs = c(0.01, 0.99), na.rm = TRUE))
      ),
      across(contains("spill"), ~ log(1 + .), .names = "log_{.col}")
    ) %>%
    st_as_sf(coords = c("easting", "northing"), crs = 27700) %>%
    st_transform(crs = 4326)
}

# Create plots for multiple years
create_yearly_plots <- function(sf_data, year) {
  list(
    hrs = plot_spill_map(
      sf_data,
      "log_spill_hrs_yr",
      glue::glue("Log\nAnnual Spill\nDuration")
    ),
    hrs_tmap = plot_spill_map_tmap(
      sf_data,
      "log_spill_hrs_yr",
      glue::glue("Log\nAnnual Spill\nDuration")
    ),
    count = plot_spill_map(
      sf_data,
      "log_spill_count_yr",
      glue::glue("Log\nAnnual Spill\nCount")
    ),
    count_tmap = plot_spill_map_tmap(
      sf_data,
      "log_spill_count_yr",
      glue::glue("Log\nAnnual Spill\nCount")
    )
  )
}

# Process data and create plots for all years
years <- c(2021, 2022, 2023)
plots <- years %>%
  set_names(paste0("dat_sf", str_sub(., 3, 4))) %>%
  map(~process_yearly_data(dat_yr_clean, .)) %>%
  imap(~create_yearly_plots(.x, .y))
```

```{r}
#| eval: false

# Function to save tmap plots
save_tmap_plots <- function(plot_list, base_name) {
  tmap_mode("view")
  
  # Save hours plot
  tmap_save(
    plot_list$hrs_tmap,
    filename = file.path("book_figs", paste0(base_name, "_hours.html")),
    width = 800,
    height = 600
  )
  
  # Save count plot
  tmap_save(
    plot_list$count_tmap,
    filename = file.path("book_figs", paste0(base_name, "_count.html")),
    width = 800,
    height = 600
  )
}

# Save all plots for each year
walk2(
  plots,
  names(plots),
  ~save_tmap_plots(.x, .y)
)
```

### Spill Count

```{=html}
<iframe src="book_figs/dat_sf23_count.html" width="800" height="600" frameborder="0"></iframe>
```

```{r, geo-spill-plots-count-23}
#| fig-width: 16
#| fig-asp: 0.618 
#| eval: false

#plots$dat_sf23$count_tmap
plots$dat_sf23$count
```

### Spill Duration

```{=html}
<iframe src="book_figs/dat_sf23_hours.html" width="800" height="600" frameborder="0"></iframe>
```

```{r, geo-spill-plots-hrs-23}
#| fig-width: 16
#| fig-asp: 0.618 
#| eval: false

# plots$dat_sf23$hrs_tmap
plots$dat_sf23$hrs
```

## Frequency and Duration of Sewage Spills {#sec-03-02-frequency-duration}

Both the summary tables and the histograms show that the frequency and duration are very positively skewed. A priori, this could be due various factors (also considering that left side is bound at zero):

1.  **Malfunctioning of EDM sensors**: Malfunctioning EDM sensors may detect 'blank' sewage overflows, creating outliers in the right tail.
2.  **Extreme weather events**: Sewage overflows are (theoretically) caused by rainfall. Episodic heavy rain could create temporal clusters of long-duration events, stretching the right tail.
3.  **Aging or Inconsistent Infrastructure**: Older sewer systems or uneven maintenance across regions could lead to chronic sewage spills, stretching the right tail

### Summary Tables {#sec-03-02-01-summary-tables}

```{r, }
dat_yr_clean_list <- map(
  2023:2021, 
  function(yr) {
    # Get required variables
    dat_yr_clean %>%
      filter(year == yr) %>% 
      select(
      water_company,
      contains("spill"),
      -ends_with("ea"),
      -contains("log")
    ) %>% 
      mutate(
        `Sites with Spill Count > 0` = if_else(spill_count_yr > 0, 1, 0),
        `Sites with Spill Duration >= 15m` = if_else(spill_hrs_yr >= 0.25, 1, 0)
        ) %>% 
      rename(
        `Spill Count` = spill_count_yr,
        `Spill Duration (hrs)` = spill_hrs_yr,
        `Water Company` = water_company
      ) 
})
```

::: panel-tabset
#### 2023

```{r}
datasummary_skim(dat_yr_clean_list[[1]], fmt = 2)
```

#### 2022

```{r}
datasummary_skim(dat_yr_clean_list[[2]], fmt = 2)
```

#### 2021

```{r}
datasummary_skim(dat_yr_clean_list[[1]], fmt = 2)
```
:::

### Histogram in 2023 {#sec-03-02-02-histogram}

```{r}
plot_hist <- function(data=dat_yr_clean, yr, x_var, x_label, bins, title) {
  filter(data, year == yr) %>% 
  ggplot(., aes(x = {{x_var}})) +
    geom_histogram(
      bins = bins, 
      fill = viridis(1, option = "magma"), alpha = 0.7, col = "black") +
    labs(
      title = title,
      x = x_label,
      y = "Count"
    ) +
    theme_pref
}

plot_hist_norm <- function(data = dat_yr_clean, yr, x_var, x_label, bins, title) {
  data <- filter(data, year == yr) %>% 
    mutate({{ x_var }} := log(1 + {{ x_var }}))
  
  mu <- mean(data %>% pull({{ x_var }}), na.rm = TRUE)
  sigma <- sd(data %>% pull({{ x_var }}), na.rm = TRUE)
  
  ggplot(data, aes(x = {{ x_var }})) +
    geom_histogram(
      aes(y = ..density..),
      bins = bins, 
      fill = viridis(1, option = "magma"), alpha = 0.7, col = "black"
    ) +
    stat_function(
      fun = dnorm,
      args = list(mean = mu, sd = sigma),
      color = viridis(3, option = "magma")[2],
      alpha = 0.7,
      linewidth = 0.8
    ) + 
    labs(
      title = title,
      x = x_label,
      y = "Density"
    ) +
    theme_pref
}

```

::: panel-tabset
#### Spill Duration

```{r}
plot_hist(yr = 2023, 
          x_var = spill_hrs_yr, x_label = "Spill Hours",
          bins =50,
          title = "Duration of Sewage Spills of all Water Companies in 2023")
```

#### Spill Count

```{r}
plot_hist(yr = 2023, 
          x_var = spill_count_yr, x_label = "Spill Count",
          bins =60,
          title = "Count of Sewage Spills of all Water Companies")
```

#### Log Spill Duration

```{r}
plot_hist_norm(
  yr = 2023,
  x_var = spill_hrs_yr, 
  x_label = "Spill Hours",
  bins = 50,
  title = "(1+Log) Duration of Sewage Spills of all Water Companies in 2023
  with Normal Curve"
)
```

#### Log Spill Count

```{r}
plot_hist_norm(
  yr = 2023,
  x_var = spill_count_yr, 
  x_label = "Spill Count",
  bins = 50,
  title = "(1+Log) (1+Log) Count of Sewage Spills of all Water Companies
  with Normal Curve"
)
```
:::

## Temporal Sewage Spill Distribution {#sec-03-03-temporal}

Sewage Spills are seasonal, peaking between October and February, which aligns with the wettest months of the year. Given this seasonality, the analysis will need to use time fixed effects.

```{r, clean-data-mo}
dat_mo_clean <- dat_mo %>%
  filter(spill_hrs_mo >=0) %>% 
  mutate(
    month = factor(month, levels = 1:12, labels = month.abb),
    year = factor(year)
  ) %>% 
  group_by(year) %>%  
  mutate(
    across(
      contains("spill"),
      ~ Winsorize(.x, val = quantile(.x, probs = c(0.01, 0.99), na.rm = TRUE)))
  ) %>%
  group_by(year, month) %>% 
  summarize(
    spill_hrs_mo = sum(spill_hrs_mo), 
    spill_count_mo = sum(spill_count_mo),
    unique_spill_sites = n_distinct(outlet_discharge_ngr),
    .groups = "drop") %>% 
  mutate(
    across(starts_with("spill"), ~ log(1 + .), .names = "log_{.col}"),
    across(starts_with("spill"), ~ ./unique_spill_sites, .names = "{.col}_site")
    )
```

### Total Spill Duration and Count {#sec-03-03-01-total}

::: panel-tabset
#### Spill Duration

```{r, temporal-hrs-plot}
plot_monthly_bars <- function(data, y_var, title, y_label) {
  ggplot(data, aes(x = month, y = {{y_var}}, fill = year)) +
    geom_bar(
      stat = "identity", 
      position = position_dodge(width = 0.9),
      width = 0.8,
      alpha = 0.9
    ) +
    scale_fill_viridis_d(option = "magma") +
    labs(
      title = title,
      y = y_label,
      x = NULL,
      fill = "Year"
    ) +
    theme_pref +
    scale_y_continuous(expand = expansion(mult = c(0, 0.1)))
}

# For your original spill hours plot
fig23_temporal_hrs <- plot_monthly_bars(
  dat_mo_clean, spill_hrs_mo, 
  "Monthly Spill Duration by Year",
  "Spill Duration per Month (hrs)")

fig23_temporal_hrs
```

#### Spill Count

```{r, temporal-count-plot}
fig23_temporal_count <- plot_monthly_bars(
  dat_mo_clean, spill_count_mo,
  "Monthly Spill Count by Year",
  "Spill Count per Month")

fig23_temporal_count
```
:::

### Per Unique Spill Site {#sec-03-03-02-unique}

::: panel-tabset
#### Spill Duration

```{r, temporal-hrs-plot-standardised}
plot_monthly_bars(
  dat_mo_clean, spill_hrs_mo_site, 
  "Monthly Spill Duration by Year per Unique Active Spill Site",
  "Spill Duration per Month (hrs)")
```

#### Spill Count

```{r, temporal-count-plot-standardised}
plot_monthly_bars(
  dat_mo_clean, spill_count_mo_site,
  "Monthly Spill Count by Year",
  "Spill Count per Month")
```
:::

## Sewage Spill Distribution by Water Company {#sec-03-04-company}

The violin plots and bar charts below show the sewage spill count and duration, normalised by the number of sewage sites, for each water company. Certain water companies---particularly South West Water---experience sewage spills more frequently than others.

### Violin Plots

```{r}
# Generate a plot for each year
plots_list_violin <- map(2023:2021, function(yr) {
  
  # Filter data by year
  data_year <- dat_yr_clean %>% 
    filter(year == yr)
  
  # Reshape data to long format for both spill_count_yr and spill_hrs_yr
  data_long <- data_year %>% 
    pivot_longer(
      cols = c(spill_count_yr, spill_hrs_yr),
      names_to = "spill_metric",
      values_to = "value"
    ) %>%
    mutate(spill_metric = recode(spill_metric,
                                 spill_count_yr = "Spill Count",
                                 spill_hrs_yr = "Spill Duration"))
  
  # Create the violin plot with overlaid boxplots and facets by spill_metric
  ggplot(data_long, aes(x = water_company, y = value, fill = water_company)) +
    geom_violin(trim = FALSE, alpha = 0.7) +
    geom_boxplot(width = 0.1, fill = "white", outlier.shape = NA) +
    scale_fill_viridis_d(option = "magma") + 
    facet_wrap(~ spill_metric, scales = "free_y") +
    labs(
      title = paste("Distribution of Sewage Spill Statistics by Water Company in", yr),
      x = "Water Company",
      y = "Value"
    ) +
    theme_pref +
    theme(legend.position = "none")
})
```

::: panel-tabset
#### 2023

```{r}
plots_list_violin[[1]]
```

#### 2022

```{r}
plots_list_violin[[2]]
```

#### 2021

```{r}
plots_list_violin[[3]]
```
:::

### Bar Charts {#sec-03-04-02-bar}

```{r}
plots_list_bar <- map(2023:2021, function(yr) {
  
  # Filter data for the specified year
  data_year <- dat_yr_clean %>% 
    filter(year == yr)
  
  # Reshape data to long format and calculate average values by water company and metric
  data_summary <- data_year %>% 
    pivot_longer(
      cols = c(spill_count_yr, spill_hrs_yr),
      names_to = "spill_metric",
      values_to = "value"
    ) %>% 
    group_by(water_company, spill_metric) %>% 
    summarise(avg_value = mean(value, na.rm = TRUE), .groups = "drop") %>%
    mutate(spill_metric = recode(spill_metric,
                                 spill_count_yr = "Spill Count",
                                 spill_hrs_yr = "Spill Duration"))
  
  # Create the bar chart with uniform fill colour from viridis magma, alpha 0.7 and black borders
  ggplot(data_summary, aes(x = water_company, y = avg_value)) +
    geom_bar(stat = "identity", 
             fill = viridis::viridis(1, option = "magma"), 
             alpha = 0.7, 
             colour = "black",
             position = "dodge") +
    facet_wrap(~ spill_metric, scales = "free_y") +
    labs(
      title = paste("Average Sewage Spill Statistics by Water Company in", yr),
      x = "Water Company",
      y = "Average Value"
    ) +
    theme_pref
})
```

::: panel-tabset
#### 2023

```{r}
plots_list_bar[[1]]
```

#### 2022

```{r}
plots_list_bar[[2]]
```

#### 2021

```{r}
plots_list_bar[[3]]
```
:::


## Temporal Coverage {#sec-03-05-coverage}

Water companies installed EDM sensors at sewage spill sites gradually, resulting in incomplete coverage for some sites between 2021 and 2023. A total of 23,585 observations have full coverage.

```{r}
# Create a new variable to indicate complete panel observations
dat_panel <- dat_yr_clean %>%
  mutate(panel_complete = if_else(
    available_year_2021 == 1 & available_year_2022 == 1 & available_year_2023 == 1,
    "Complete", "Incomplete"
  ))

# Summarise counts and percentages
panel_summary <- dat_panel %>%
  group_by(panel_complete) %>%
  summarise(n = dplyr::n()) %>%
  mutate(percentage = round(n / sum(n) * 100, 1))

# Display the summary table
knitr::kable(panel_summary, 
             caption = "Observations by Panel Completeness (2021-2023)",
             col.names = c("Panel Status", "Count", "Percentage (%)"))
```

